### 2018-11-09 density.tex
first commit

\documentclass{article} % For LaTeX2e
\usepackage{amsmath}
\usepackage[noend]{algorithmic}
\usepackage{algorithm}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{amsfonts}

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{observation}[theorem]{Observation}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{fact}[theorem]{Fact}

\newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}

\newcommand{\ip}[1]{\left \langle #1 \right \rangle}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\D}{\text{Density}}
\newcommand{\eps}{\epsilon}
%\usepackage{ntheorem}
%\usepackage{amsthm}

%\newtheorem*{definition*}{Definition}
\newtheorem{definition}{Definition}
\newtheorem{claim}{Claim}

\title{Sketching for Density Estimation}
\date{\nonumber}

\author{
Zohar Karnin\\Amazon\\zkarnin@amazon.com
\and
Edo Liberty\\Amazon\\libertye@amazon.com
}

\begin{document}

\maketitle

\begin{abstract}
abs\end{abstract}

\section{Problem Definition}
Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density of a point $y$ is defined as 
$$ \D(y) = \sum_{x \in X} K(y,x) $$
Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent example is 
$$ K(x,y) = \exp(-\lambda \|x-y\|_2^2) $$
where $\lambda$ is a scaling parameter. What we discuss in what follows applies for any kernel, an depends on a bound on $K(x,x)$. For simplicity we assume that $K(x,x) \leq 1$ for all datapoints. Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.

Our objective is obtaining a core-set $z_1,\ldots, z_\ell \in \R^d$, $\ell \ll n$ along with weights $w_1,\ldots, w_\ell$ such that for any point $y \in \R^d$
$$ \left| \sum_{i=1}^\ell w_i \cdot K(z_i, y) - \D(y) \right| < \eps n $$
We are interested in achieving this in the streaming setting, while bounding the amount of memory used

\section{Compactor}
We use the compactor approach. We collect $k$ data points $x_1,\ldots, x_k$ and output $m \approx k/2$ points $\tilde{x}_1,\ldots, \tilde{x}_m$ such that 
$$ \left| \sum_{i =1}^k K(x_i,y) - 2\sum_{i=1}^m K(\tilde{x}_i, y) \right| = o(k)$$
This can be used to transform a stream of $n$ to $n/2$, then the $n/2$ stream to $n/4$, until we have a stream we can keep in memory. We move to define the compactor. First, consider the error induced by a single compaction
$$ \text{Err}(y) = \sum_{i =1}^k K(x_i,y) - 2\sum_{i=1}^m K(\tilde{x}_i, y) $$
If the $\tilde{x}_i$'s are chosen as a subset of the $x_i$'s the error can be re-written as
$$ \text{Err}(y) = \sum_{i=1}^k s_i K(x_i,y)  $$
where $s_i \in \{-1, 1\}$ according to whether $x_i$ is in the set of $\tilde{x}$'s. It follows that our objective is the following function
$$ \min_{s \in \{-1,1\}^k} \max_y \sum_{i=1}^k s_i K(x_i,y) $$

We now exploit a property of kernel functions to reformulate the problem. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
$$ K(x,y) = \ip{\phi(x), \phi(y)} $$
Using this function $\phi$ our objective function becomes
$$\sum_{i=1}^k s_i K(x_i,y) = \sum_{i=1}^k s_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^k s_i \phi(x_i), \phi(y)} \leq $$
$$ \|\phi(y)\| \cdot \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| $$
This upper bound allows to optimize a much easier minimization function.

We continue to solve the following problem: Given $k$ vectors $z_1,\ldots,z_k$ in an inner product space, compute signs minimizing 
$$\| \sum_i s_i z_i \| $$
We first notice that for i.i.d uniform signs, it holds that
$$\E[\| \sum_i s_i z_i \|^2] = \E[\sum_{i,j} s_i s_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
leading to a randomized approach. We use the method of expectation minimization to achieve this bound deterministically. Specifically, we set $s_i$ sequentially for $i$ while minimizing the expectation. We prove by induction on $i$ that for the fixed $s_j$'s up to and not including $i$,
$$\E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
For $i=1$ this is trivial. For $i>1$ let $m=\sum_{j=1}^{i-1} s_j z_j$.
$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \E[\| m + \sum_{j=i}^k s_j z_j \|^2] = \|m\|^2 + \sum_{j=i}^k \|z_j\|^2$$
It follows that by fixing $s_i$ deterministically,
$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2  $$
so in order to make sure that 
$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] $$
we need
$$ 2\ip{m,s_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2 \geq 0 $$
We thus set 
$$ s_i = -\text{sign} \ip{m,z_i}$$

Let us now translate this to an algorithm w.r.t the $d$ dimensional points $x_1,\ldots, x_k$. The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
$$ s_i = -\text{sign} \left( \ip{\sum_{j<i} s_j \phi(x_j), \phi(x_i)} \right) = -\text{sign} \left( \sum_{j<i} s_j K(x_j, x_i) \right) $$
This guarantees that for any $y \in \R^d$,
$$ \sum_i s_i K(x_i, y) \leq \sqrt{ \sum_i \|\phi(x_i)\|^2 } = \sqrt{k} $$

For the coreset, this means that we can choose the $\tilde{x}$'s as either the $x$ vectors with positive $s_i$'s or negative $s_i$'s.

\end{document}

### 2018-11-09 density.tex
draft

@@
 
+\subsection{Another approach}
+Considering the view with $\phi$ let us restate the objective. For a point $y$ we wish to estimate
+$$ \D(y) = \sum_i K(x_i,y) = \ip{\sum_i  \phi(x_i), \phi(y)} $$
+simultaneously for all $y$. We can try to do this with any re-weighting of the $x_i$'s
+$$ \sum_i K(x_i,y) \approx \sum_i w_i K(x_i,y) =  \ip{\sum_i w_i \phi(x_i), \phi(y)} $$
+while aiming for the $w$ vector to be sparse. Letting $z_i=\phi(x_i)$, $Z$ be the matrix whose columns are $z_i$ and $v=\sum_i z_i$ we have a sparse regression problem with a single data point
+$$ \min_w \| Zw -  v\|^2 \ \ \text{s.t.} \|w\|_0 \leq k/2$$
+We proved that there exist a solution achieving $\sqrt{k}$.
+Could we prove that better solutions exist?
+In one extreme, all $z_i$ are orthogonal (corresponding to vectors that are very far away).
+Here you cannot achieve more than
+
 \end{document}

### 2018-11-10 density.tex
some edit

--- 2018-11-09 density.tex
@@
 \newcommand{\E}{\mathbb{E}}
-\newcommand{\D}{\text{Density}}
+\newcommand{\D}{\rho}
 \newcommand{\eps}{\epsilon}
@@
 \section{Problem Definition}
-Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density of a point $y$ is defined as 
-$$ \D(y) = \sum_{x \in X} K(y,x) $$
-Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent example is 
-$$ K(x,y) = \exp(-\lambda \|x-y\|_2^2) $$
-where $\lambda$ is a scaling parameter.
+Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $\rho: \R^d \rightarrow \R$ of a point $y$ is defined as 
+$$ \rho(y) = \sum_{i=1}^{n} K(x_i,y) $$
+Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
+$$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = \frac{1}{1+\|x-y\|_2^2/\sigma^2)}$$
+where $\sigma$ is a scaling parameter.
 What we discuss in what follows applies for any kernel, an depends on a bound on $K(x,x)$.
@@
 $$ \left| \sum_{i=1}^\ell w_i \cdot K(z_i, y) - \D(y) \right| < \eps n $$
-We are interested in achieving this in the streaming setting, while bounding the amount of memory used
+We are interested in achieving this in the streaming setting, while bounding the amount of memory used throughout the run of the algorithm.
 
@@
 $$\| \sum_i s_i z_i \| $$
-We first notice that for i.i.d uniform signs, it holds that
+We first notice that for i.i.d.\ uniform signs, it holds that
 $$\E[\| \sum_i s_i z_i \|^2] = \E[\sum_{i,j} s_i s_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
-leading to a randomized approach.
-We use the method of expectation minimization to achieve this bound deterministically.
-Specifically, we set $s_i$ sequentially for $i$ while minimizing the expectation.
-We prove by induction on $i$ that for the fixed $s_j$'s up to and not including $i$,
-$$\E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
-For $i=1$ this is trivial. For $i>1$ let $m=\sum_{j=1}^{i-1} s_j z_j$.
-$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \E[\| m + \sum_{j=i}^k s_j z_j \|^2] = \|m\|^2 + \sum_{j=i}^k \|z_j\|^2$$
-It follows that by fixing $s_i$ deterministically,
-$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2  $$
-so in order to make sure that 
-$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] $$
-we need
-$$ 2\ip{m,s_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2 \geq 0 $$
-We thus set 
-$$ s_i = -\text{sign} \ip{m,z_i}$$
+leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i s_i z_i \| \le 2\sum_i \|z_i\|$.
 
-Let us now translate this to an algorithm w.r.t the $d$ dimensional points $x_1,\ldots, x_k$. The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
-$$ s_i = -\text{sign} \left( \ip{\sum_{j<i} s_j \phi(x_j), \phi(x_i)} \right) = -\text{sign} \left( \sum_{j<i} s_j K(x_j, x_i) \right) $$
+We can also use the method of expectation minimization to achieve this bound deterministically.
+Specifically, we will guaranty that $\| \sum_{j=1}^i s_j z_j \| \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
+This is trivially true for $i=1$. 
+For another value $i$ set $s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle z_j, z_i \rangle)$ 
+and  assume by induction that $\| \sum_{j=1}^{i-1} s_j z_j\|^2 \le \sum_{j=1}^{i-1} \|z_j\|^2$.
+
+\begin{eqnarray*}
+\| \sum_{j=1}^{i}s_j z_j\|^2 &=& \|\sum_{j=1}^{i-1}s_j z_j\|^2 + \|z_i\|^2 + \langle \sum_{j=1}^{i-1}s_j z_j, s_i z_i\rangle \\
+&\le& \sum_{j=1}^{i-1} \|z_j\|^2 + \|z_i\|^2 + s_i \sum_{j=1}^{i-1}s_j \langle  z_j,  z_i\rangle \mbox{\;\;\; by the induction assumption}\\ 
+&=& \sum_{j=1}^{i} \|z_j\|^2 - |\sum_{j=1}^{i-1}s_j \langle  z_j,  z_i\rangle| \le \sum_{j=1}^{i} \|z_j\|^2
+\end{eqnarray*}
+
+Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
+The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
+$$ s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j  K(x_j, x_i)) $$
 This guarantees that for any $y \in \R^d$,
 $$ \sum_i s_i K(x_i, y) \leq \sqrt{ \sum_i \|\phi(x_i)\|^2 } = \sqrt{k} $$
+
+Before we extend this to a complete algorithm, it is worth getting an intuition for the meaning of this result.
 
@@
 \end{document}
+
+Let us choose the value  and assume by induction that
+
+%Specifically, we set $s_i$ sequentially for $i$ while minimizing the expectation. 
+%We prove by induction on $i$ that for the fixed $s_j$'s up to and not including $i$,
+%$$\E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
+%For $i=1$ this is trivial. For $i>1$ let $v=\sum_{j=1}^{i-1} s_j z_j$.
+%$$ \E_{s_i,\ldots,s_k}[\| \sum_{j=1}^k s_j z_j \|^2] = \E[\| v + \sum_{j=i}^k s_j z_j \|^2] = \|v\|^2 + \sum_{j=i}^k \|z_j\|^2$$
+%It follows that by fixing $s_i$ deterministically,
+%$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \|v\|^2 + \|z_i\|^2 - \|v + s_i z_i\|^2  $$
+%so in order to make sure that 
+%$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] $$
+%we need
+%$$ 2\ip{m,s_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2 \geq 0 $$
+%We thus set 
+%$$ s_i = -\text{sign} \ip{m,z_i}$$

### 2018-11-11 density.tex
general formulation

@@
 
+\section{General note about sketching and flat signed function}
+In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
+The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
+If $z \subset x$ this is a subset selection problem. 
+For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
+However, it is often far from being the best possible in terms of its space-accuracy tradeoff.
+
+Here are some examples:
+\begin{itemize}
+\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else.
+\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else.
+\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
+\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see above)
+\item in machine learning $f(x, q) = \operatorname{loss}(x,q)$ where $q$ is the parameters of the model and $x$ is a training example and its label.
+\end{itemize}
+For all of the above, we can find flat error functions $E(q) = \sum_{i=1}^{k} s_i f(x_i,q)$ such that $\sup_q E(q)$ is small. 
+We argue that this gives a general mechanism for sketching in a diverse set of scenarios. 
 \end{document}

### 2018-11-11 density.tex
row subset selection

@@
 We can also use the method of expectation minimization to achieve this bound deterministically.
-Specifically, we will guaranty that $\| \sum_{j=1}^i s_j z_j \| \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
+Specifically, we will guaranty that $\| \sum_{j=1}^i s_j z_j \|^2 \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
 This is trivially true for $i=1$. 
@@
 \item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else.
-\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
+\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
 \item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see above)
@@
 We argue that this gives a general mechanism for sketching in a diverse set of scenarios.
-\end{document}
 
 Let us choose the value  and assume by induction that
+\section{Row subset selection}
+Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
+for simplicity, assume $x_i$ are all unit length. Moreover, assume each vector $Z$ must be one of the rows in $X$ up to some constant factor.
+This is called the row subset selection problem. 
+Since you are trying to minimize the quadratic form, you get that $f(x, q) = \langle x,q \rangle ^2$ and 
+$$E(y) = \sum_i s_i \langle x_i,q \rangle ^2 = q^T (\sum_i s_i x_i x_i^T ) q \le \|\sum_i s_i x_i x_i^T\|$$
+It is clear that we can get $\|\sum_i s_i x_i x_i^T\| \le \sqrt{k \log(d)}$. Could it would see that maybe $O(1)$ is also possible?
+When summing rank one projections matrices $x_i x_i^T$ you can think of two extreme cases. 
+If $x_i$ are orthogonal to each other than $\|\sum_i s_i x_i x_i^T\| = 1$ independently of $s_i$.
+If $x_i$ are all equal than a random assignment would get  $\E[\|\sum_i s_i x_i x_i^T\|] = E[|\sum_i s_i|] = \Omega(\sqrt{k})$.
+But, in that case it's also easy to find a sequence of $s_i$ which gives $\|\sum_i s_i x_i x_i^T\| = O(1)$. Is that always possible?
+If so, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
+
+\end{document}
 

### 2018-11-11 density.tex
some edits

@@
 $$E(y) = \sum_i s_i \langle x_i,q \rangle ^2 = q^T (\sum_i s_i x_i x_i^T ) q \le \|\sum_i s_i x_i x_i^T\|$$
-It is clear that we can get $\|\sum_i s_i x_i x_i^T\| \le \sqrt{k \log(d)}$. Could it would see that maybe $O(1)$ is also possible?
 When summing rank one projections matrices $x_i x_i^T$ you can think of two extreme cases. 
@@
 But, in that case it's also easy to find a sequence of $s_i$ which gives $\|\sum_i s_i x_i x_i^T\| = O(1)$. Is that always possible?
-If so, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
+\zk{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
+If this is correct, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
 

### 2018-11-12 density.tex
Jeff did it...
column subset selection experiments

@@
 \begin{abstract}
-abs\end{abstract}
+abc
+\end{abstract}
 
-\section{Problem Definition}
+\section{introduction}
+def
+
+\section{General framework for sketching}
+In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
+The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
+If $z \subset x$ this is a subset selection problem. 
+For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
+However, it is often far from being the best possible in terms of its space-accuracy tradeoff.
+
+Here are some examples:
+\begin{itemize}
+\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else.
+\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else.
+\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
+\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see above)
+\item in machine learning $f(x, q) = \operatorname{loss}(x,q)$ where $q$ is the parameters of the model and $x$ is a training example and its label.
+\end{itemize}
+For all of the above, we can find flat error functions $E(q) = \sum_{i=1}^{k} s_i f(x_i,q)$ such that $\sup_q E(q)$ is small. 
+We argue that this gives a general mechanism for sketching in a diverse set of scenarios.
+
+\section{Density estimation}
+
+Already done by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751} in the non streaming setting.
+
 Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $\rho: \R^d \rightarrow \R$ of a point $y$ is defined as 
@@
 Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
-$$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = \frac{1}{1+\|x-y\|_2^2/\sigma^2)}$$
+$$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|_2^2/\sigma^2)^{-1}$$
 where $\sigma$ is a scaling parameter.
@@
 
-\section{General note about sketching and flat signed function}
-In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
-The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
-If $z \subset x$ this is a subset selection problem. 
-For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
-However, it is often far from being the best possible in terms of its space-accuracy tradeoff.
-
-Here are some examples:
-\begin{itemize}
-\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else.
-\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else.
-\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
-\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see above)
-\item in machine learning $f(x, q) = \operatorname{loss}(x,q)$ where $q$ is the parameters of the model and $x$ is a training example and its label.
-\end{itemize}
-For all of the above, we can find flat error functions $E(q) = \sum_{i=1}^{k} s_i f(x_i,q)$ such that $\sup_q E(q)$ is small. 
-We argue that this gives a general mechanism for sketching in a diverse set of scenarios.
-
-Let us choose the value  and assume by induction that
 \section{Row subset selection}
@@
 If this is correct, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
+
+Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
+We need to see if these hold in our setting or only hold for sampling.
+Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
+
+\bibliographystyle{plain}
+\bibliography{density}
 

### 2018-11-12 density.tex
push mid flight

@@
 If $z \subset x$ this is a subset selection problem. 
-For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
+For bounded functions $f$, uniform sampling combined with a union bound over the space of possible values for $q$ always provides a valid solution. 
+While the number of possible queries $q$ is often infinite it often reduces to a finite set through a net argument. 
+This is common practice in machine learning, specifically, PAC learning.
+
 However, it is often far from being the best possible in terms of its space-accuracy tradeoff.
@@
 \begin{itemize}
-\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else.
-\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else.
-\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$.
-\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see above)
-\item in machine learning $f(x, q) = \operatorname{loss}(x,q)$ where $q$ is the parameters of the model and $x$ is a training example and its label.
+\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
+\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits strong ordering.
+\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
+For simplicity, we will assume in this manuscript that $x$ is also unit norm.
+\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = 1/(1 + \exp(-q^T x))$. 
+Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
+\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian and $q$ is a test vector.
+\item Probably also good for matrix approx when we get entry updates. 
 \end{itemize}
-For all of the above, we can find flat error functions $E(q) = \sum_{i=1}^{k} s_i f(x_i,q)$ such that $\sup_q E(q)$ is small. 
-We argue that this gives a general mechanism for sketching in a diverse set of scenarios.
+
+We argue that we can offer a unified solution for producing coresets for all of the above problems in a unified manner. 
+Moreover, our solution created streaming algorithms with fully mergeable sketches.
+
+We begin with describing the basic operation of compaction and the notion of flat error functions.
+
+Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
+Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
+Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
+Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
+We call $E$ flat if $\min_s \max_q |E(q)| = o(n)$.
+
+\begin{definition}
+We define $E_n$ with respect to a function $f(x,q)$ to be  $\min_s \max_q \max_x \sum_{i=1}^{n} s_i f(x_i,q)$. 
+\end{definition}
+
+As a warmup exercise, consider the case where $E_n = 1$.
+This is the case for quantiles and for counting. 
+At step one, we will create a coreset of weight $2$ and size at most $n/2$ (by either adding or subtracting $E$). Here we incur an error of at most $1$.
+Then, we repeat the process and incur an error of at most $2$ resulting in a stream of length at most $n/4$. 
+We can continue the above process until we are left with $O(1/\eps)$ points in the coreset. At this point, the error adds up to at most $\eps n$.
+Similarly, when $E_n = O(\sqrt{n})$ we get a coreset of size $O(1/\eps^2)$ whose error is at most $\eps n$.
+This gives an offline algorithm.
+
+\zk{We can describe the general streaming algorithm here. I think $E_n$ is a sufficient characterization of this.}
+
+For all of the above, we argue that we can find flat signed error functions such that $E_n = O(1)$ or $E_n = O(\sqrt{n})$.
 

### 2018-11-12 density.tex

--- 2018-11-11 density.tex
@@
 \newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
+\newcommand{\el}[1]{\textcolor{blue}{ZK: #1}}
 
@@
 
+\section{Introduction}
+
+Oh no... \cite{DBLP:conf/soda/PhillipsT18}
+
 \section{Problem Definition}
@@
 $$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = \frac{1}{1+\|x-y\|_2^2/\sigma^2)}$$
+$$ K(x,y) = \max(0, 1- \|x-y\|/\sigma) $$
 where $\sigma$ is a scaling parameter.
@@
 But, in that case it's also easy to find a sequence of $s_i$ which gives $\|\sum_i s_i x_i x_i^T\| = O(1)$. Is that always possible?
-\zk{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
+\el{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
 If this is correct, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
+
+Selecting $o(1/\eps^2)$ is claimed to be impossible due to \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06} and \cite{DBLP:conf/soda/GhashamiP14}.
+
+\subsection{notes about row selection}
+The problem is 
+$$ \min_s \| \sum_i s_i x_ix_i^T\| $$
+where $\|x_i\| \leq 1$. Consider the following greedy approach: At point $x_i$, let
+$$ C_i = \sum_{j<i} s_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
+We choose $s_i = 1$ if $l_+ < l_i$, otherwise $s_i=-1$.
+
+This approach can be shown to be better than random. Random will result in an answer of up to
+
+Consider the following example. 
+$$x_1=e_1, x_2=e_2*\eps, x_3=e_2, x_4=e_1/\sqrt{2} + e_2/\sqrt{2}$$
+where $\eps \to 0$.
+We get that the covariance matrix after inserting $x_3$ has two eigenvalues of +1 and -1.
+Now when inserting $x_4$ we have to increase the magnitude of one of them and we exceed the limit of 1.
+
+\bibliographystyle{plain}
+\bibliography{density}
 

### 2018-11-14 density.tex
before merge

--- 2018-11-12 density.tex
@@
 Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
-Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
-Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
-Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
-We call $E$ flat if $\min_s \max_q |E(q)| = o(n)$.
+Now consider $\tilde F(q) = F(q) + \Delta(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
+Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | \Delta(q)|$.
+Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | \Delta(q)|$.
+We call $E$ flat if $\min_s \max_q |\Delta(q)| = o(n)$.
 

### 2018-11-14 density.tex
more stuff

@@
 \newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
+\newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
 
@@
 
-\zk{We can describe the general streaming algorithm here. I think $E_n$ is a sufficient characterization of this.}
-
+\el{We can describe the general streaming algorithm here. I think $E_n$ is a sufficient characterization of this.} 
 For all of the above, we argue that we can find flat signed error functions such that $E_n = O(1)$ or $E_n = O(\sqrt{n})$.
 
-\section{Density estimation}
-
-Already done by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751} in the non streaming setting.
+\section{Density Estimation}
 
@@
 Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
+
 $$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|_2^2/\sigma^2)^{-1}$$
+
 where $\sigma$ is a scaling parameter.
@@
 
-Our objective is obtaining a core-set $z_1,\ldots, z_\ell \in \R^d$, $\ell \ll n$ along with weights $w_1,\ldots, w_\ell$ such that for any point $y \in \R^d$
-$$ \left| \sum_{i=1}^\ell w_i \cdot K(z_i, y) - \D(y) \right| < \eps n $$
-We are interested in achieving this in the streaming setting, while bounding the amount of memory used throughout the run of the algorithm.
-
-\section{Compactor}
-We use the compactor approach. We collect $k$ data points $x_1,\ldots, x_k$ and output $m \approx k/2$ points $\tilde{x}_1,\ldots, \tilde{x}_m$ such that 
-$$ \left| \sum_{i =1}^k K(x_i,y) - 2\sum_{i=1}^m K(\tilde{x}_i, y) \right| = o(k)$$
-This can be used to transform a stream of $n$ to $n/2$, then the $n/2$ stream to $n/4$, until we have a stream we can keep in memory.
-We move to define the compactor.
-First, consider the error induced by a single compaction
-$$ \text{Err}(y) = \sum_{i =1}^k K(x_i,y) - 2\sum_{i=1}^m K(\tilde{x}_i, y) $$
-If the $\tilde{x}_i$'s are chosen as a subset of the $x_i$'s the error can be re-written as
-$$ \text{Err}(y) = \sum_{i=1}^k s_i K(x_i,y)  $$
-where $s_i \in \{-1, 1\}$ according to whether $x_i$ is in the set of $\tilde{x}$'s. It follows that our objective is the following function
-$$ \min_{s \in \{-1,1\}^k} \max_y \sum_{i=1}^k s_i K(x_i,y) $$
-
-We now exploit a property of kernel functions to reformulate the problem. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
+Using our framework, we need to bound $\Delta(y) = \sum_{i=1}^k s_i K(x_i,y)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
 $$ K(x,y) = \ip{\phi(x), \phi(y)} $$
 Using this function $\phi$ our objective function becomes
-$$\sum_{i=1}^k s_i K(x_i,y) = \sum_{i=1}^k s_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^k s_i \phi(x_i), \phi(y)} \leq $$
-$$ \|\phi(y)\| \cdot \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| $$
-This upper bound allows to optimize a much easier minimization function.
-
-We continue to solve the following problem: Given $k$ vectors $z_1,\ldots,z_k$ in an inner product space, compute signs minimizing 
-$$\| \sum_i s_i z_i \| $$
+$$\sum_{i=1}^k s_i K(x_i,y) = \sum_{i=1}^k s_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^k s_i \phi(x_i), \phi(y)} \leq \|\phi(y)\| \cdot \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| $$
+This upper bound allows us to optimize (find values for $s_i$) a simple expression.
+Given $k$ vectors $z_1,\ldots,z_k$ in an inner product space, compute signs minimizing $\| \sum_i s_i z_i \|$.
 We first notice that for i.i.d.\ uniform signs, it holds that
@@
 leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i s_i z_i \| \le 2\sum_i \|z_i\|$.
-
+%
 We can also use the method of expectation minimization to achieve this bound deterministically.
@@
 \end{eqnarray*}
-
+This completes the proof that $\| \sum_{j=1}^{k}s_j z_j\| \le \sqrt{\sum_{j=1}^{i} \|z_j\|^2}$ for our choice of values for $s$. 
+%
 Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
 The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
-$$ s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j  K(x_j, x_i)) $$
-This guarantees that for any $y \in \R^d$,
-$$ \sum_i s_i K(x_i, y) \leq \sqrt{ \sum_i \|\phi(x_i)\|^2 } = \sqrt{k} $$
+$$ s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j  K(x_j, x_i))$$
+This guarantees that 
+$$ \forall y \in \R^d \;\;\; \sum s_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{k} $$
 
-Before we extend this to a complete algorithm, it is worth getting an intuition for the meaning of this result.
+Using the framework above this provides a streaming coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that 
+$\forall \;q\;\; |\tilde \rho(q) - \rho(q)| \le \eps n$.
+This matches the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
 
-For the coreset, this means that we can choose the $\tilde{x}$'s as either the $x$ vectors with positive $s_i$'s or negative $s_i$'s.
+%
+%<<<<<<< HEAD
+%\section{General note about sketching and flat signed function}
+%In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
+%The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
+%If $z \subset x$ this is a subset selection problem. 
+%For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
+%However, it is often far from being the best possible in terms of its space-accuracy tradeoff. 
+%=======
+%
+%>>>>>>> ce3a786138737689452723acbd3980a5d8533fbe
 
-\section{Row subset selection}
+\section{Row Subset Selection}
 Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
@@
 But, in that case it's also easy to find a sequence of $s_i$ which gives $\|\sum_i s_i x_i x_i^T\| = O(1)$. Is that always possible?
-\zk{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
+\el{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
 If this is correct, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
@@
 
+\paragraph{Hard example?}
+$x_i$'s are gaussian vectors with mean zero and covariance $\sum_{i=1}^d \sqrt{i} \cdot e_i e_i^T$. It might be the case that any sign assignment here will result in $\sqrt{d}$ operator norm.
+
+\paragraph{Reduction to the Kernel case}
+This is really the Kernel density estimation problem with $K(x,y) = \ip{x,y}^2$.
+We might be able to squeeze a bit more due to the fact that $\phi(x) = xx^T$ is a very special $d \times d$ matrix: a rank $1$ matrix.
+That being said, a coreset of $1/\eps^2$ can be obtained by simply using the kernel technique.
+The special structure can either give better dependence on $\eps$ or exploit low rank structure e.g.\ if the vectors form a nearly rank $k$ matrix.
+
+\zk{The Kernel argument will get us $\sqrt{k}$ and I think we really should get $\sqrt{d}$ which is possibly better.}
+%
+%\subsection{notes about row selection}
+%The problem is 
+%$$ \min_s \| \sum_i s_i x_ix_i^T\| $$
+%where $\|x_i\| \leq 1$. Consider the following greedy approach: At point $x_i$, let
+%$$ C_i = \sum_{j<i} s_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
+%We choose $s_i = 1$ if $l_+ < l_i$, otherwise $s_i=-1$.
+%
+%This approach can be shown to be better than random. Random will result in an answer of up to 
+%
+%Consider the following example. 
+%$$x_1=e_1, x_2=e_2*\eps, x_3=e_2, x_4=e_1/\sqrt{2} + e_2/\sqrt{2}$$
+%where $\eps \to 0$.
+We get that the covariance matrix after inserting $x_3$ has two eigenvalues of +1 and -1.
+Now when inserting $x_4$ we have to increase the magnitude of one of them and we exceed the limit of 1.
+%
 \bibliographystyle{plain}

### 2018-11-15 density.tex
adds sum of signed vectors and matrices

@@
 \usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage[noend]{algorithmic}
@@
 
-%\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{conjecture}{Conjecture}[section]
 %\newtheorem{claim}[theorem]{Claim}
@@
 %\usepackage{ntheorem}
-%\usepackage{amsthm}
 
@@
 \newtheorem{claim}{Claim}
+%\newtheorem{theorem}{Theorem}
 
@@
 
+\section{Appendix 1}
+For completeness we recap a result from \cite{barany2008}.
+\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1]
+For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i x_i || \le \sqrt{d}$.
+\end{theorem}
+\begin{proof}
+Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
+This feasible region is not empty because it contains the origin. 
+Consider an extreme point $\alpha^*_i$ and set $s_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $s_i = -1$ w.p.\ $(1+\alpha^*_i)/2$.
+$$
+\E[\|\sum s_i x_i\|^2] =  \E[\|\sum (s_i - \alpha^*_i) x_i\|^2] = \sum \E[(s_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
+$$
+The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
+Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
+\end{proof}
+
+\noindent The conjectures appear to be provable in almost exactly the same manner
+\begin{conjecture}
+For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2,F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2,F} \le O(\sqrt{d_1d_2\log(d_1 + d_2) })$.
+\end{conjecture}
+\begin{conjecture}
+For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
+signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d\sqrt{\log{d}}$.
+Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. \el{This us weak. It really should be $\sqrt{d}$ or at most $\sqrt{d\log{d}}$ }
+\end{conjecture}
+
 \end{document}

### 2018-11-15 src/testLP.py
testing LP idea derivation

@@ -1,0 +1,35 @@
+from scipy.optimize import linprog
+from numpy.random import random
+from numpy.linalg import norm
+from numpy import eye, ones, zeros, vstack
+
+
+def findSigns(X):
+    (n,d) = X.shape
+    A_eq = zeros((d,n))
+    for i in range(n):
+        A_eq[:,i] = X[i,:]/norm(X[i,:])
+    b_eq = zeros(d)
+    c =random(n)
+    bounds=[(-1.0, 1.0)]*n
+    res = linprog(c, A_ub=None, b_ub=None,
+                  A_eq=A_eq, b_eq=b_eq,
+                  bounds=bounds, method='simplex',
+                  callback=None, options={"disp": True})
+
+    alpha = res.x
+    s = zeros(n)
+    for i in range(n):
+        s[i] = 1 if random() < (1+alpha[i])/2 else -1
+    return(s)
+
+
+n = 500
+d = 20
+data = random((n,d))
+for i in range(n):
+    data[i] = data[i]/norm(data[i])
+
+s = findSigns(data)
+sumNorm = norm(sum([s[i]*data[i] for i in range(n)]))
+print('Found sign assignment with total norm of', sumNorm)

### 2018-11-16 density.tex
fixed theorems

@@
 
-\noindent The conjectures appear to be provable in almost exactly the same manner
+\noindent The following theorems are provable in almost exactly the same manner
 \begin{conjecture}
-For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2,F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2,F} \le O(\sqrt{d_1d_2\log(d_1 + d_2) })$.
+For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{F} \le O(\sqrt{d_1d_2})$.
 \end{conjecture}
-\begin{conjecture}
+
+\begin{theorem}
+For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2} \le O(\sqrt{\log(d_1 + d_2) d_1d_2})$.
+Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
+\end{theorem}
+
+\begin{theorem}
 For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
-signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d\sqrt{\log{d}}$.
-Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. \el{This us weak. It really should be $\sqrt{d}$ or at most $\sqrt{d\log{d}}$ }
-\end{conjecture}
+signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d$.
+Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
+\end{theorem}
 

### 2018-11-17 density.tex
adding facts

@@
 %\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{fact}[theorem]{Fact}
+\newtheorem{fact}[theorem]{Fact}
 
@@
 The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
-If $z \subset x$ this is a subset selection problem. 
+If $z \subset x$ this is a subset selection or a coreset problem. 
 For bounded functions $f$, uniform sampling combined with a union bound over the space of possible values for $q$ always provides a valid solution. 
@@
 Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
-Now consider $\tilde F(q) = F(q) + \Delta(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
-Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | \Delta(q)|$.
-Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | \Delta(q)|$.
-We call $E$ flat if $\min_s \max_q |\Delta(q)| = o(n)$.
+Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
+Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
+Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
+\begin{definition}
+We define the discrepancy $\Delta_k$ with respect to a function $f(x,q)$ to be  
+\[\Delta_n = \min_s \max_q \max_x \sum_{i=1}^{n} s_i f(x_i,q). \] 
+\end{definition}
+\noindent We claim that a function is sketch-able if $\Delta_n = o(n)$. 
+As a warmup exercise, consider the non-streaming case.
+\begin{fact}
+For any function $f$ which a corresponding discrepancy of $\Delta_k = O(1)$ there exists a coreset of size 
+$O(1/\eps)$ whose error is at most $\eps n$.
+\end{fact}
+\begin{fact}
+For any sum of functions $f$ which a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a coreset of size 
+$O(1/\eps^2)$ whose error is at most $\eps n$.
+\end{fact}
 
-\begin{definition}
-We define $E_n$ with respect to a function $f(x,q)$ to be  $\min_s \max_q \max_x \sum_{i=1}^{n} s_i f(x_i,q)$. 
-\end{definition}
+\noindent Proving both facts is trivial. 
+At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c_1$ or $c_2 \sqrt{n}$.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c_1$ of $2\sqrt{n/2}  = \sqrt{2n}$.
+Note that the sum of errors is dominated by last iterations. 
+Halting the compression at $O(1/\eps)$ or $O(1/\eps^2)$ items respectively achieves the goal.
 
-As a warmup exercise, consider the case where $E_n = 1$.
-This is the case for quantiles and for counting. 
-At step one, we will create a coreset of weight $2$ and size at most $n/2$ (by either adding or subtracting $E$). Here we incur an error of at most $1$.
-Then, we repeat the process and incur an error of at most $2$ resulting in a stream of length at most $n/4$. 
-We can continue the above process until we are left with $O(1/\eps)$ points in the coreset. At this point, the error adds up to at most $\eps n$.
-Similarly, when $E_n = O(\sqrt{n})$ we get a coreset of size $O(1/\eps^2)$ whose error is at most $\eps n$.
-This gives an offline algorithm.
+\begin{fact}
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+$O(\log^2(\log(1/\delta))/\eps)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+\end{fact}
+\begin{fact}
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+$O(\log^2(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+\end{fact}
 
-\el{We can describe the general streaming algorithm here. I think $E_n$ is a sufficient characterization of this.} 
-For all of the above, we argue that we can find flat signed error functions such that $E_n = O(1)$ or $E_n = O(\sqrt{n})$.
+\begin{fact}
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
+$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
+\end{fact}
+\begin{fact}
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
+$O(\log^2(n)/\eps^2)$ whose error is at most $\eps n$.
+\end{fact}
 

### 2018-11-20 density.tex
adding short proof

@@
 Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
+\item Linear Classification $f(x,q) = 1$ if $x^t > 0$ and $0$ else. Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
+\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
+For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
 \item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian and $q$ is a test vector.
@@
 Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c_1$ of $2\sqrt{n/2}  = \sqrt{2n}$.
-Note that the sum of errors is dominated by last iterations. 
+Note that the sum of errors is asymptotically dominated by last iterations. 
 Halting the compression at $O(1/\eps)$ or $O(1/\eps^2)$ items respectively achieves the goal.
@@
 For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O(\log^2(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+$O(\log^3(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
 \end{fact}
+\begin{proof}
+For simplicity, assume that $n$, the length of the stream, is known in advance. This assumption will be removed later.
+We begin with an obvious observation that sampling is always a possible first step if the stream is long enough.
+Consider sampling stream items with probably $p = \log(1/\delta)/n\eps^2$ and weighting the sampled items by $w = 1/p$.
+This gives a an $\eps n$ approximation for any single query $q$ with probability at least $1-\delta$. 
+Let $Q_\eps$ denote an epsilon-net over $f$. Specifically $\max_q \min_{q' \in Q_\eps} |F(q) - F(q')| \le \eps n$.
+Setting $\delta \le 1/|Q_\eps|$ will achieve a strong corset for using the union bound. 
+Note that $|Q_\eps|$ is usually exponential in the parameters of the problem and $\log(1/\delta)$ is polynomial in those parameters.
+
+\noindent From here on, we assume $n = O(\log(1/\delta)/\eps^2)$ for some appropriately small value $\delta$.
+Let us begin with the simpler case where $\Delta_k = O(\sqrt{k})$. 
+Here, we will create $H$ buffers $B_1,...,B_H$ of size $k$ feeding one into each other. 
+The number items seen by buffer $h$ is $n_h = n/2^{h-1}$ and their weight is $w_h = 2^{h-1}$.
+The error induce by buffer $h$ is at most $w_h\frac{n_h}{k} \sqrt{k} = n/\sqrt{k}$. The total error is therefore at most $Hn/\sqrt{k}$.
+In order for the last buffer to not overflow we need to make sure that $n_H \le k$. Setting $H = \log(n/k)+1$ achieves that.
+Demanding that $Hn/\sqrt{k} \le \eps n$ and setting $k = (\log\log(1/\delta) + 1)^2/\eps^2$ we get that the total error is less than $\eps n$.
+Substituting we get that $H \le \log\log(1/\delta) + 1$. Finally, the total storage of the sketch is $Hk = O(\log\log(1/\delta) + 1)^3/\eps^2$.
 
@@
 \end{fact}
-\begin{fact}
-For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-$O(\log^2(n)/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
+\begin{proof}
+Proving this is more involved.
+It follows the same steps as the recent breakthrough result about streaming quantiles \cite{DBLP:conf/focs/KarninLL16} which exhibit $\Delta_k = O(1)$.
+The following proof can be thought of as a generalization of the proof in \cite{DBLP:conf/focs/KarninLL16}.
+\end{proof}
+
+\end{proof}
 

### 2018-11-20 density.tex
some proofs

--- 2018-11-17 density.tex
@@
 \usepackage{amsfonts}
+\usepackage{ amssymb }
 
@@
 %\newtheorem{claim}[theorem]{Claim}
-%\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{lemma}[theorem]{Lemma}
 %\newtheorem{remark}[theorem]{Remark}
@@
 %\usepackage{ntheorem}
+\newcommand{\floor}[1]{\left \lfloor #1 \right \rfloor}
+\newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
 
@@
 In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
-The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
+The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$, either for all possible queries simultaneously, for every fixed $q$ with high probability, or more complicated formulations such as weak coresets.
+
 If $z \subset x$ this is a subset selection or a coreset problem. 
@@
 \item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
-\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits strong ordering.
-\item in matrix row subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
+\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
+\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
 For simplicity, we will assume in this manuscript that $x$ is also unit norm.
@@
 Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
-\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian and $q$ is a test vector.
+\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian  corresponding to the graph with a single edge $x$ and $q$ is a test vector.
 \item Probably also good for matrix approx when we get entry updates. 
@@
 
-We argue that we can offer a unified solution for producing coresets for all of the above problems in a unified manner. 
-Moreover, our solution created streaming algorithms with fully mergeable sketches.
+We argue that we can offer a solution for producing coresets for all of the above problems in a unified manner. 
+Moreover, our solution creates streaming algorithms with fully mergeable sketches.
 
-We begin with describing the basic operation of compaction and the notion of flat error functions.
+The high level idea is the following.
+Consider a stream of the data points $x_i$.
+We wish to to maintain a buffer that can hold up to $k$ points, and output a stream of data points having half the amount of the original stream, yet at the same time maintain a similar value for
+$$ \sum_i f(x_i, q) $$
+for any query $q$.
+To do so our buffer, once collecting $k$ data points, performs a \emph{compact} operation that outputs $k/2$ data points of weight $2$ representing the original $k$ inputs.
+The compact operation partitions the $k$ points into two (roughly) sets, whose corresponding sum are very close.
+This is made formal with the following definitions: Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$ where $s_i \in \{-1,1\}$ are signs.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
+We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  | E(q)|$.
 
-Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
-Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
-Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
+%
+%We begin with describing the basic operation of compaction and the notion of flat error functions. 
+%
+%Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
+%Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
+%Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
 Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
@@
 We define the discrepancy $\Delta_k$ with respect to a function $f(x,q)$ to be  
-\[\Delta_n = \min_s \max_q \max_x \sum_{i=1}^{n} s_i f(x_i,q). \] 
+\[\Delta_k = \min_s \max_{q,x} \sum_{i=1}^{k} s_i f(x_i,q). \] 
 \end{definition}
-\noindent We claim that a function is sketch-able if $\Delta_n = o(n)$. 
-As a warmup exercise, consider the non-streaming case.
+\noindent We claim that a function is sketch-able if $\Delta_k = o(k)$. 
+As a warmup exercise, consider the non-streaming case. Throughout we discuss functions $f$ with the property $|f(x,q)| \leq 1$ for all $x,q$.
+
 \begin{fact}
@@
 
-\begin{fact}
+In what follows, we prove the following.
+\begin{theorem} \label{thm:streaming}
 For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O(\log^2(\log(1/\delta))/\eps)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
-\end{fact}
-\begin{fact}
+$O\left(\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+For $\delta=0$ this results in a deterministic algorithm.
+The algorithm must be given $\eps, \delta$ as input and does not require knowledge of the stream length $n$.
+\end{theorem}
+
+\begin{theorem}
 For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O(\log^2(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
-\end{fact}
+$O\left(\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+For $\delta=0$ this results in a deterministic algorithm.
+The algorithm must be given $\eps, \delta$ as input and does not require knowledge of the stream length $n$.
+\end{theorem}
+%
+%\begin{fact}
+%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+%$O(\log^2(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+%\end{fact}
+%
+%\begin{fact}
+%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
+%$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
+%\end{fact}
+%\begin{fact}
+%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
+%$O(\log^2(n)/\eps^2)$ whose error is at most $\eps n$.
+%\end{fact}
 
-\begin{fact}
-For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
-\end{fact}
-\begin{fact}
-For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-$O(\log^2(n)/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
+\begin{lemma} \label{lem:compactor}
+Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $s_1,\ldots,s_k$ such that
+$$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
+Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
+\begin{itemize}
+\item $\{z_i\}_i$ is a subset of $\{x_i\}$
+\item $\E[m] = n/2$
+\item For any fixed query $q$, the error associated with $q$, defined as
+$$\text{Err}(q) = 2\sum_{i=1}^m f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
+Can be decomposed as a sum
+$$\text{Err}(q) = \sum_{j=1}^{n/k} \text{Err}_j(q)$$
+where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq \rho k$
+\end{itemize}
+The last property ensures that deterministically $|\text{Err}(q)| \leq \rho n$, and that w.h.p (via Chernoff's inequality) for a fixed $q$ 
+$$|\text{Err}(q)| \lesssim \rho k\sqrt{n/k} = \rho \sqrt{kn}$$
+\end{lemma}
+\begin{proof}
+The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
+$$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
+Now, consider the set $P=\{i:s_i=1\}$ and $N=\{i:s_i=-1\}$.
+$$ \sum_i s_i f(x_i, q) = \sum_i s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
+$$ -\sum_i s_i f(x_i, q) = \sum_i -s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
+Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$.
+We call this operation a single compaction.
+Since $P,N$ form a partition of $[k]$ we get that the expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
+As for the error term w.r.t a fixed query $q$, it is clearly the sum of errors accumulated in each compaction.
+The error incurred in a compaction is either
+$\sum_i s_i f(x_i, q)$ or $-\sum_i s_i f(x_i, q)$ with equal probability. It follows that it is a Bernoulli r.v. with magnitude of at most $\rho k$ as required.
+\end{proof}
+
+\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
+Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
+The streaming algorithm operates as follows.
+At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
+The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
+In the beginning we have a single compactor at level $h=0$.
+Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
+After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
+
+The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor. For a query $q$ we analyze the error
+$$\text{Err}(q) = \sum_{h=0}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \ .$$
+Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
+The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
+The sum over $j$ is over the number of compactions at level $h$.
+Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
+
+To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the set $P$ or $N$ with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+$$ \text{Err}(q) \leq \rho(k) \log_2(n/k) n $$
+
+If however, we are interested in a high probability bound of $1-\delta$, we decompose the error to two components
+$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
+ Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later.
+Notice that the right summand contains roughly $\log(1/\delta)$ random variables.
+Since they are all Bernoulli we get that any combination of them is possible with probability $\geq \delta$ hence we must use a deterministic bound for these upper layers.
+We thus set $k_h=k$ for $h > H'$ and use the bound
+$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
+Now, for the bottom layers we use Chernoffs bound
+$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
+$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$
+
+\zk{$n_h$ being random is a problem. The weight of the stream might increase with time. The analysis now works for a completely balanced case }
+Consider the sum in the denominator. 
+$$ \sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} = O(\sum_{h=0}^{H'} 2^{2h} \rho(k_h)^2 k_h n_h ) $$
+Since $n_h \leq n_{h-1}/2$ and we have $k_h \leq k$ we have 
+$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2  ) $$
+Now, if $\rho(k_h) \geq 1/\sqrt{k_h}$ we set $k_h = 2$ for all $h \leq H'$ and obtain
+$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h  ) = O(n^2/ (k \log(1/\delta))) $$
+and we get
+$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) \right)   \right) $$
+Hence, by setting $k \geq c/\eps^2$ for sufficiently large constant $c$ the probability is upper bounded by $\delta$.
+
+Now, for $\rho(k) < 1/\sqrt{k}$ we have $\eta(k) = \rho(k)^2 k = o(1)$.
+We can exploit that to allow for $k = o(1/\eps^2)$.
+For $\eta(k)=O(k^{-p})$ we\footnote{We do not discuss other scenarios as we are not aware of any setting where they occur.
+Also, extending the analysis to them is a purely technical exercise} use $k_h = \max(2, \ceil{(2/3)^{H'-h}k})$, leading to a bound of
+$$\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2 \leq \sum_{h=0}^{H'} 2^h \eta(k) \cdot (3/2)^{H'-h} = (3/2)^{H'} \eta(k) \sum_{h=0}^{H'} (4/3)^h \leq  $$
+$$(3/2)^{H'} \eta(k) \cdot (4/3)^{H'} \cdot 3 = 3 \cdot 2^{H'} \eta(k) = O(\eta(k)n/(k\log(1/\delta))$$
+Plugging this in the probability bound gives
+$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) / \eta(k) \right)   \right) = $$
+$$ \exp \left( -O\left( \eps^2 \log(1/\delta) / \rho(k)^2 \right)   \right) $$
+Hence, setting $k$ large enough so that $\rho(k) \leq c\eps$ for some universal constant $c$ leads to the required bound.
+
+In particular for $\rho(k) = O(1/k)$ we see that $k=1/\eps$ suffices, for general $p>1/2$ with $\rho(k) = k^{-p}$ we require $k=\eps^{-1/p}$.
+
+Now, consider the overall error and memory of the entire process.
+For the bottom layers, for any $\rho(k)$ we require $O(k+H')=O(k+\log(n))$ memory.
+A closer inspection actually shows that once $k_h=2$ we are simply performing uniform sampling, and all of those layers can be done with constant memory.
+Hence, the memory footprint of the bottom layers is $O(k)$.
+The top layers require $O(\log\log(1/\delta)k)$ memory leading to a total memory usage of $O(\log\log(1/\delta)k)$.
+
+The error for the bottom layers is $O(\min\{\rho(k), 1/\sqrt{k}\} n)$.
+The error of the top layers is $O(\log\log(1/\delta) \rho(k) n)$, meaning that the overall error is $O(\log\log(1/\delta) \rho(k) n)$.
+
+Hence, if we aim for an error of $\eps n$ w.p.\ $1-\delta$ we set $k$ large enough such that $\rho(k) \leq c \eps / \log\log(1/\delta)$.
+Denoting by $\rho^{\dagger}$ the inverse function to $\rho$ this leads to a total memory requirement of
+$$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
+
+\end{proof}
 

### 2018-11-20 density.tex

@@
 Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
+\item Linear Classification $f(x,q) = 1$ if $x^t > 0$ and $0$ else. Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
+\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
+For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
 \item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian  corresponding to the graph with a single edge $x$ and $q$ is a test vector.
@@
 $$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
+%=======
+%$O(\log^3(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+%\end{fact}
+%\begin{proof}
+%For simplicity, assume that $n$, the length of the stream, is known in advance. This assumption will be removed later.
+%We begin with an obvious observation that sampling is always a possible first step if the stream is long enough.
+%Consider sampling stream items with probably $p = \log(1/\delta)/n\eps^2$ and weighting the sampled items by $w = 1/p$.
+%This gives a an $\eps n$ approximation for any single query $q$ with probability at least $1-\delta$. 
+%Let $Q_\eps$ denote an epsilon-net over $f$. Specifically $\max_q \min_{q' \in Q_\eps} |F(q) - F(q')| \le \eps n$.
+%Setting $\delta \le 1/|Q_\eps|$ will achieve a strong corset for using the union bound. 
+%Note that $|Q_\eps|$ is usually exponential in the parameters of the problem and $\log(1/\delta)$ is polynomial in those parameters. 
+%
+%\noindent From here on, we assume $n = O(\log(1/\delta)/\eps^2)$ for some appropriately small value $\delta$.
+%Let us begin with the simpler case where $\Delta_k = O(\sqrt{k})$. 
+%Here, we will create $H$ buffers $B_1,...,B_H$ of size $k$ feeding one into each other. 
+%The number items seen by buffer $h$ is $n_h = n/2^{h-1}$ and their weight is $w_h = 2^{h-1}$.
+%The error induce by buffer $h$ is at most $w_h\frac{n_h}{k} \sqrt{k} = n/\sqrt{k}$. The total error is therefore at most $Hn/\sqrt{k}$.
+%In order for the last buffer to not overflow we need to make sure that $n_H \le k$. Setting $H = \log(n/k)+1$ achieves that.
+%Demanding that $Hn/\sqrt{k} \le \eps n$ and setting $k = (\log\log(1/\delta) + 1)^2/\eps^2$ we get that the total error is less than $\eps n$.
+%Substituting we get that $H \le \log\log(1/\delta) + 1$. Finally, the total storage of the sketch is $Hk = O(\log\log(1/\delta) + 1)^3/\eps^2$.
+% 
+%\begin{fact}
+%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
+%$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
+%\end{fact}
+%\begin{proof}
+%Proving this is more involved.
+It follows the same steps as the recent breakthrough result about streaming quantiles \cite{DBLP:conf/focs/KarninLL16} which exhibit $\Delta_k = O(1)$.
+The following proof can be thought of as a generalization of the proof in \cite{DBLP:conf/focs/KarninLL16}.
+%\end{proof}
+%
+%
+%
+%
+%
+%>>>>>>> 3fb6fdab63baebeec7715bcb29d19665e3023a8c
 

### 2018-11-21 density.tex
Row Subset Selection

@@
 
-%
-%<<<<<<< HEAD
-%\section{General note about sketching and flat signed function}
-%In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
-%The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$. 
-%If $z \subset x$ this is a subset selection problem. 
-%For bounded functions $f$, uniform sampling combined with a union bound over the space of possbile values for $q$ always provides a valid solution.
-%However, it is often far from being the best possible in terms of its space-accuracy tradeoff. 
-%=======
-%
-%>>>>>>> ce3a786138737689452723acbd3980a5d8533fbe
-
 \section{Row Subset Selection}
 Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
-for simplicity, assume $x_i$ are all unit length. Moreover, assume each vector $Z$ must be one of the rows in $X$ up to some constant factor.
+For simplicity, assume $x_i$ are all unit length. Moreover, assume each vector in $Z$ must be one of the rows in $X$ up to some constant factor.
 This is called the row subset selection problem. 
 Since you are trying to minimize the quadratic form, you get that $f(x, q) = \langle x,q \rangle ^2$ and 
-$$E(y) = \sum_i s_i \langle x_i,q \rangle ^2 = q^T (\sum_i s_i x_i x_i^T ) q \le \|\sum_i s_i x_i x_i^T\|$$
-When summing rank one projections matrices $x_i x_i^T$ you can think of two extreme cases. 
-If $x_i$ are orthogonal to each other than $\|\sum_i s_i x_i x_i^T\| = 1$ independently of $s_i$.
-If $x_i$ are all equal than a random assignment would get  $\E[\|\sum_i s_i x_i x_i^T\|] = E[|\sum_i s_i|] = \Omega(\sqrt{k})$.
-But, in that case it's also easy to find a sequence of $s_i$ which gives $\|\sum_i s_i x_i x_i^T\| = O(1)$. Is that always possible?
-\el{My experiments show that behaves like polylog $d$ and $n$ but who knows. I thought I proved $O(1)$ but I think it's wrong.}
-If this is correct, it would give a covariance sketch is subset selection of size $1/\eps$ which would be an improvement over frequent directions.
+$$E(y) = \sum_i s_i \langle x_i,q \rangle ^2 = q^T (\sum_i s_i x_i x_i^T ) q \le \|\sum_i s_i x_i x_i^T\| \le c\sqrt{d}$$
 
-Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
+\noindent The last inequality is a direct application of the following Theorem.
+\begin{theorem}\label{BansalInDaHouz}
+For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
+\end{theorem}
+\begin{proof}
+First, recount Banaszczyk's theorem. 
+Let $\mathcal K$ be a convex body in $\R^d$ such that $\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is Gaussian i.i.d.
+Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
+Then, there exist signs $s_i$ such that $\sum s_i x_i \in C \mathcal K$ for some universal constant $C$.
+
+To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
+Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $10\sqrt{d_1 + d_2}$.
+More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le 10\sqrt{d_1+d_2}\}$. 
+Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
+Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices \cite{}.
+Banaszczyk's theorem says that there exist signs $s_i$ such that $\sum s_i \operatorname{flatten}(X_i) \in C \mathcal K$.
+In other words $\| \sum s_i X_i\| = \| \operatorname{stack}( \sum s_i \operatorname{flatten}(x_i x_i^T)) \| \le 10 C \sqrt{d}$. 
+\end{proof}
+
+Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
+Alternatively, we obtain a streaming mergeable algorithm for creating coresets of size $\log^{2}(\min(n, \log(1/\delta)) \sqrt{d}/\eps$.
+
+\zk{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
 We need to see if these hold in our setting or only hold for sampling.
 Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
+Their assumptions don't hold here.}
 
-\paragraph{Hard example?}
-$x_i$'s are gaussian vectors with mean zero and covariance $\sum_{i=1}^d \sqrt{i} \cdot e_i e_i^T$. It might be the case that any sign assignment here will result in $\sqrt{d}$ operator norm.
-
-\paragraph{Reduction to the Kernel case}
-This is really the Kernel density estimation problem with $K(x,y) = \ip{x,y}^2$.
+%\paragraph{Reduction to the Kernel case}
+%This is really the Kernel density estimation problem with $K(x,y) = \ip{x,y}^2$.
 We might be able to squeeze a bit more due to the fact that $\phi(x) = xx^T$ is a very special $d \times d$ matrix: a rank $1$ matrix.
@@
 
-\zk{The Kernel argument will get us $\sqrt{k}$ and I think we really should get $\sqrt{d}$ which is possibly better.}
 %
@@
 
-\noindent The following theorems are provable in almost exactly the same manner
-\begin{conjecture}
-For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{F} \le O(\sqrt{d_1d_2})$.
-\end{conjecture}
-
-\begin{theorem}
-For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{2} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2} \le O(\sqrt{\log(d_1 + d_2) d_1d_2})$.
-Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
-\end{theorem}
-
-\begin{theorem}
-For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of 
-signs $s_1,...,s_n$ such that $||\sum_i s_i x_i x^T||_2 \le d$.
-Here, $\|\cdot\|_2$ denotes the spectral norm of a matrix. 
-\end{theorem}
-
 \end{document}

### 2018-11-21 density.tex
Row Subset Selection
comment

@@
 \end{proof}
-
+The algorithm for finding the signs reduces to random choice for $s_i$ and then checking the norm of $\sum s_i x_i x_i^T$.
+This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric.
 Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
@@
 
-\zk{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
+\el{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
 We need to see if these hold in our setting or only hold for sampling.
 Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
-Their assumptions don't hold here.}
+Their assumptions don't hold here.} \zk{We can get $1/\eps^2$ though which is better than $\sqrt{d}/\eps$ as long as $\eps > 1/\sqrt{d}$.
+If $\eps < 1/\sqrt{d}$ then $\sqrt{d}/\eps > d$ - shouldn't it be trivial to get a coreset of size $d$?}
 

### 2018-11-23 density.tex
Streaming Graph Approximation

--- 2018-11-21 density.tex
@@
 
-\section{Row Subset Selection}
+\section{Row (or Column) Subset Selection}
 Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
@@
 Their assumptions don't hold here.}
+
+\section{Streaming Graph Approximation}
+Streaming graphs have received a lot of attention in the last several years \cite{}. 
+In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
+Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
+Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
+Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
+In this formulation, this problem reduced to that of row (column) subset selection. 
+Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
+Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
+The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
+$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
 

### 2018-11-23 density.tex
Small changes
 Please enter the commit message for your changes. Lines starting

@@
 \section{General framework for sketching}
-In many sketching problems our goal is to approximate a function of the of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i$ are all the stream items and and $q$ is some query point. 
-The goal is to produce a sketch of $\ell$ points $z$ and weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$, either for all possible queries simultaneously, for every fixed $q$ with high probability, or more complicated formulations such as weak coresets.
+In many sketching problems our goal is to approximate a function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are all the stream items and $q \in \mathcal Q$ is any query point from a possible set $\mathcal Q$ which is known in advance.
+The goal is to produce a sketch of $\ell$ points $z \subset \mathcal X$ and real weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$, either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with high probability at least $1-\delta$.
+There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.
 
-If $z \subset x$ this is a subset selection or a coreset problem. 
-For bounded functions $f$, uniform sampling combined with a union bound over the space of possible values for $q$ always provides a valid solution. 
-While the number of possible queries $q$ is often infinite it often reduces to a finite set through a net argument. 
+If $z \subset x$ the problem is further restricted to being a subset selection or a coreset selection problem. 
+For bounded functions $f$, uniform sampling combined with a union bound over $|\mathcal Q|$ always provides a valid solution. 
+While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit exponential) set through a net argument. 
 This is common practice in machine learning, specifically, PAC learning. 
-
 However, it is often far from being the best possible in terms of its space-accuracy tradeoff.

### 2018-11-25 density.tex
Some more stuff

@@
 \item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-\item Probably also good for matrix approx when we get entry updates. 
+\item Probably also good for matrix approximation when we get entry updates. 
 \end{itemize}
@@
 
+\section{Logistic Regression}
+The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
+This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
+
 %\paragraph{Reduction to the Kernel case}

### 2018-11-27 density.tex
asd

--- 2018-11-23 density.tex
@@
 
-\section{Row (or Column) Subset Selection}
+\section{Row Subset Selection}
 Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
@@
 
-\zk{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
+\el{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
 We need to see if these hold in our setting or only hold for sampling.
 Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
-Their assumptions don't hold here.}
+Their assumptions don't hold here.} \zk{We can get $1/\eps^2$ though which is better than $\sqrt{d}/\eps$ as long as $\eps > 1/\sqrt{d}$.
+If $\eps < 1/\sqrt{d}$ then $\sqrt{d}/\eps > d$ - shouldn't it be trivial to get a coreset of size $d$?}
 
-\section{Streaming Graph Approximation}
-Streaming graphs have received a lot of attention in the last several years \cite{}. 
-In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
-Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
-Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
-Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
-In this formulation, this problem reduced to that of row (column) subset selection. 
-Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
-Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
-The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
-$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
+\subsection{optimal design of experiments}
+We discuss the problem of linear regression with mean squared error.
+In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
+$$ \sum_i (w^Tx_i - y_i)^2 $$
+In the field of optimal design of experiments, the labels are not given with the data.
+Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
+The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
+
+The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
+$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
+%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
+%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
+%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
+%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+
+One can show that for $w_B$,
+$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
+This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.
+
+We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
+Something that is commonly practiced.
+Since we will solve the problem for the subset we choose in an optimal way for gaussian noise, we end up with an unbiased estimator for $w^*$.
+The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
+$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+This is leads to the exact same objective as in column subset selection.
+Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
+Specifically we get that we can obtain a core-set of size
+$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
+For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
+I'm not sure what statements are known already.
+
+In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
 

### 2018-11-27 density.tex

--- 2018-11-25 density.tex
@@
 \end{itemize}
-The last property ensures that deterministically $|\text{Err}(q)| \leq \rho n$, and that w.h.p (via Chernoff's inequality) for a fixed $q$ 
+The last property ensures that deterministically $|\text{Err}(q)| \leq \rho n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$ 
 $$|\text{Err}(q)| \lesssim \rho k\sqrt{n/k} = \rho \sqrt{kn}$$
@@
 $$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
-Now, consider the set $P=\{i:s_i=1\}$ and $N=\{i:s_i=-1\}$.
-$$ \sum_i s_i f(x_i, q) = \sum_i s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
-$$ -\sum_i s_i f(x_i, q) = \sum_i -s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
-Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$.
-We call this operation a single compaction.
-Since $P,N$ form a partition of $[k]$ we get that the expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
-As for the error term w.r.t a fixed query $q$, it is clearly the sum of errors accumulated in each compaction.
-The error incurred in a compaction is either
+Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; s_i = 1\}$ or $\{x_i \; | \; s_i = -1\}$ with twice the weight.
+$$\sum_{i ,\; s_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} s_i f(x_i, q)$$
+$$\sum_{i ,\; s_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} s_i f(x_i, q)$$
+
+%Now, consider the set $P=\{i:s_i=1\}$ and $N=\{i:s_i=-1\}$.
+%$$ \sum_i s_i f(x_i, q) = \sum_i s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
+%$$ -\sum_i s_i f(x_i, q) = \sum_i -s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
+%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
+%\el{this is clunky way to say this...}
+The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$. 
+As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
 $\sum_i s_i f(x_i, q)$ or $-\sum_i s_i f(x_i, q)$ with equal probability. It follows that it is a Bernoulli r.v. with magnitude of at most $\rho k$ as required.
@@
 
-To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the set $P$ or $N$ with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
 $$ \text{Err}(q) \leq \rho(k) \log_2(n/k) n $$
@@
 $$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
-%=======
-%$O(\log^3(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
-%\end{fact}
-%\begin{proof}
-%For simplicity, assume that $n$, the length of the stream, is known in advance. This assumption will be removed later.
-%We begin with an obvious observation that sampling is always a possible first step if the stream is long enough.
-%Consider sampling stream items with probably $p = \log(1/\delta)/n\eps^2$ and weighting the sampled items by $w = 1/p$.
-%This gives a an $\eps n$ approximation for any single query $q$ with probability at least $1-\delta$. 
-%Let $Q_\eps$ denote an epsilon-net over $f$. Specifically $\max_q \min_{q' \in Q_\eps} |F(q) - F(q')| \le \eps n$.
-%Setting $\delta \le 1/|Q_\eps|$ will achieve a strong corset for using the union bound. 
-%Note that $|Q_\eps|$ is usually exponential in the parameters of the problem and $\log(1/\delta)$ is polynomial in those parameters. 
-%
-%\noindent From here on, we assume $n = O(\log(1/\delta)/\eps^2)$ for some appropriately small value $\delta$.
-%Let us begin with the simpler case where $\Delta_k = O(\sqrt{k})$. 
-%Here, we will create $H$ buffers $B_1,...,B_H$ of size $k$ feeding one into each other. 
-%The number items seen by buffer $h$ is $n_h = n/2^{h-1}$ and their weight is $w_h = 2^{h-1}$.
-%The error induce by buffer $h$ is at most $w_h\frac{n_h}{k} \sqrt{k} = n/\sqrt{k}$. The total error is therefore at most $Hn/\sqrt{k}$.
-%In order for the last buffer to not overflow we need to make sure that $n_H \le k$. Setting $H = \log(n/k)+1$ achieves that.
-%Demanding that $Hn/\sqrt{k} \le \eps n$ and setting $k = (\log\log(1/\delta) + 1)^2/\eps^2$ we get that the total error is less than $\eps n$.
-%Substituting we get that $H \le \log\log(1/\delta) + 1$. Finally, the total storage of the sketch is $Hk = O(\log\log(1/\delta) + 1)^3/\eps^2$.
-% 
-%\begin{fact}
-%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-%$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
-%\end{fact}
-%\begin{proof}
-%Proving this is more involved.
-It follows the same steps as the recent breakthrough result about streaming quantiles \cite{DBLP:conf/focs/KarninLL16} which exhibit $\Delta_k = O(1)$.
-The following proof can be thought of as a generalization of the proof in \cite{DBLP:conf/focs/KarninLL16}.
-%\end{proof}
-%
-%
-%
-%
-%
-%>>>>>>> 3fb6fdab63baebeec7715bcb29d19665e3023a8c
 

### 2018-11-27 density.tex

@@
 
+\subsection{optimal design of experiments}
+We discuss the problem of linear regression with mean squared error.
+In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
+$$ \sum_i (w^Tx_i - y_i)^2 $$
+In the field of optimal design of experiments, the labels are not given with the data.
+Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
+The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
+
+The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
+$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
+%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
+%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
+%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
+%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+
+One can show that for $w_B$,
+$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
+This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.
+
+We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
+Something that is commonly practiced.
+Since we will solve the problem for the subset we choose in an optimal way for gaussian noise, we end up with an unbiased estimator for $w^*$.
+The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
+$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+This is leads to the exact same objective as in column subset selection.
+Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
+Specifically we get that we can obtain a core-set of size
+$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
+For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
+I'm not sure what statements are known already.
+
+In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
+
 \section{Streaming Graph Approximation}

### 2018-12-03 density.tex
abstract

@@
 \begin{abstract}
-abc
+We present a general framework for producing mergeable sketches based on coresets for a wide variety of streaming problems. 
+The algorithm is generic and works whenever the task exhibits a certain low discrepancy property.
+Such problems include simple tasks like frequent item counting and quantile approximation, newer results on kernel density estimation and matrix covariance approximation, and extends to machine learning in problems such at linear and logistic regression.
+For all of the above we match the state of the art or improve on it with the above generic framework.
+This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
 \end{abstract}
@@
 In many sketching problems our goal is to approximate a function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are all the stream items and $q \in \mathcal Q$ is any query point from a possible set $\mathcal Q$ which is known in advance.
-The goal is to produce a sketch of $\ell$ points $z \subset \mathcal X$ and real weights $w$ such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(z_i,q) \approx \sum_{i=1}^{n} f(x_i, q)$, either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with high probability at least $1-\delta$.
+The goal is to produce weights $w$ with at most $\ell \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(x_i,q) \approx F(q)$.
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
 There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.
 
-If $z \subset x$ the problem is further restricted to being a subset selection or a coreset selection problem. 
 For bounded functions $f$, uniform sampling combined with a union bound over $|\mathcal Q|$ always provides a valid solution. 
-While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit exponential) set through a net argument. 
+While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through an epsilon net argument. 
 This is common practice in machine learning, specifically, PAC learning. 
@@
 \item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = 1/(1 + \exp(-q^T x))$. 
+\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
 Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
-\item Linear Classification $f(x,q) = 1$ if $x^t > 0$ and $0$ else. Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
+\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
+Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
 \item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
@@
 For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
 \item Probably also good for matrix approximation when we get entry updates. 
@@
 \section{Row (or Column) Subset Selection}
-Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps n$.
-For simplicity, assume $x_i$ are all unit length. Moreover, assume each vector in $Z$ must be one of the rows in $X$ up to some constant factor.
+Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps \operatorname{Tr}(X^TX)$.
+For simplicity, assume $x_i$ are all unit length so $\eps \operatorname{Tr}(X^TX) = \eps n$. Moreover, assume each vector in $Z$ must be one of the rows in $X$ up to some constant factor.
 This is called the row subset selection problem. 

### 2018-12-05 density.tex
some changes

@@
 \newcommand{\eps}{\epsilon}
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\X}{\mathcal{X}}
 %\usepackage{ntheorem}
@@
 
-For bounded functions $f$, uniform sampling combined with a union bound over $|\mathcal Q|$ always provides a valid solution. 
-While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through an epsilon net argument. 
-This is common practice in machine learning, specifically, PAC learning. 
-However, it is often far from being the best possible in terms of its space-accuracy tradeoff.
+Generating a concise representation for $\tilde F$ allows one to optimize of $\tilde F$ instead of $F$ which more efficient. 
+Moreover, if the sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
 
@@
 
-We argue that we can offer a solution for producing coresets for all of the above problems in a unified manner. 
+For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ stream items.
+While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
+This is common practice in machine learning, specifically, PAC learning. 
+However, it is often far from being the smallest cardinality coreset possible.
+
+We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
 Moreover, our solution creates streaming algorithms with fully mergeable sketches.
@@
 Consider a stream of the data points $x_i$. 
-We wish to to maintain a buffer that can hold up to $k$ points, and output a stream of data points having half the amount of the original stream, yet at the same time maintain a similar value for
-$$ \sum_i f(x_i, q) $$
-for any query $q$.
-To do so our buffer, once collecting $k$ data points, performs a \emph{compact} operation that outputs $k/2$ data points of weight $2$ representing the original $k$ inputs.
-The compact operation partitions the $k$ points into two (roughly) sets, whose corresponding sum are very close.
-This is made formal with the following definitions: Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$ where $s_i \in \{-1,1\}$ are signs.
+We maintain a buffer that can hold up to $k$ points.
+Once collecting $k$ data points it performs a \emph{compact} operation that outputs $k/2$ data points of weight $2$ representing the original $k$ inputs.
+The compact operation partitions the $k$ points into two sets whose corresponding sum are very close.
+This is made formal with the following definitions: 
+Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$ where $s_i \in \{-1,1\}$ are signs.
 Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
@@
 
-\subsection{optimal design of experiments}
+\subsection{Optimal Design of Experiments}
 We discuss the problem of linear regression with mean squared error.
@@
 
+\section{Attempt at Cleaner Definitions}
+Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
+We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
+$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}s_i f_i (x)$$  \el{need to double check the order here...}
+
+We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
+Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
+
+In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
+The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
+Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
+Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
+
+In what follows, we subscript the function $f$ with its parametrization.
+\begin{itemize}
+\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
+\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
+\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
+\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
+Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
+\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
+Here, like in Logistic Regression, $a$ is the example point multiplied by its label and $x$ is the weights of the linear classifier.
+\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
+For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
+\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+\item Probably also good for matrix approximation when we get entry updates. 
+\end{itemize}
+
 \end{document}

### 2018-12-08 density.tex
komlos density

@@
 
+\section{Komlos Complexity}
+
+\begin{definition}
+Let $\F:\mathcal Q\rightarrow \R$ be a family of functions, $f \subset \F$, and $\sigma \in \{-1,1\}^m$ uniformly. 
+The Rademacher complexity of $\F$ is defined to be
+\[
+R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f}  \sum_{i=1}^{m}\sigma_i f_i
+\]
+\end{definition}
+\cite{Bartlett:2003:RGC:944919.944944}
+\begin{definition}
+Let $\F:\mathcal Q\rightarrow \R$ be a family of functions, $f \subset \F$, and $\sigma \in \{-1,1\}^m$.
+The Komlos complexity of $\F$ is defined as
+\[
+K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{f}  \sum_{i=1}^{m}\sigma_i f_i
+\]
+\end{definition}
+We claim that while $R_n$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution) $K_n$ is the measure more suitable for
+active learning and creating streaming coresets. 
+The name Komlos Complexity due to the Komlos Conjecture which claims the minimal value of $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
+The correctness of the Komlos Conjecture is still an important open problem in the study of discrepancy theory.
+
+It is clear that $K_m(\F) < R_m(\F)$ for every family $\F$.
+
+\newcommand{\ccc}[1]{\parbox}
+\begin{table}[htp]
+\caption{default}
+\begin{center}
+\begin{tabular}{|c|c|c|c|} \hline
+Problem				& $f$ 							& $R_m$ 		& $K_m$ \\ \hline
+Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 	& $1/\sqrt{m}$	& $1/m$ \\ \hline
+Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  	& $1/\sqrt{m}$	& $1/m$ \\ \hline
+Matrix Sketching		& $f(x, q) = \langle x,q \rangle ^2$ where $q,x\in \R^d$	& $1/\sqrt{m}$	& $\min\{\sqrt{d}/m,1/\sqrt{m}\}$ \\ \hline
+Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other positive kernel (see \cite{}) & ?	$\sqrt{m}$ ? \\ \hline
+Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 		& ?	 ? \\ \hline
+Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else	& ?	& ? \\ \hline
+Graph Laplacian 		& $f(x, q) = q^T L_x q = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$ and $q \in \R^n$ & ?	& ? \\ \hline
+Entry-wise Matrix Approximation  & $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ & ?	& ? \\ \hline
+\end{tabular}
+\end{center}
+\label{default}
+\end{table}%
+
+According to these notes \el{https://courses.cs.washington.edu/courses/cse522/11wi/scribes/lecture6.pdf find better ref} all
+linear classifiers have Rademacher complexity $O(1/\sqrt{m})$. 
+If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$)
+
 \end{document}

### 2018-12-08 density.tex
komlos density

@@
 linear classifiers have Rademacher complexity $O(1/\sqrt{m})$. 
-If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$)
+If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$) \el{I've done this in my head so it might not be right...}
 

### 2018-12-08 density.tex
cleaner table

@@
 Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Matrix Sketching		& $f(x, q) = \langle x,q \rangle ^2$ where $q,x\in \R^d$	& $1/\sqrt{m}$	& $\min\{\sqrt{d}/m,1/\sqrt{m}\}$ \\ \hline
-Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other positive kernel (see \cite{}) & ?	$\sqrt{m}$ ? \\ \hline
-Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 		& ?	 ? \\ \hline
+Column Slection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
+Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
 Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
-Graph Laplacian 		& $f(x, q) = q^T L_x q = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$ and $q \in \R^n$ & ?	& ? \\ \hline
-Entry-wise Matrix Approximation  & $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ & ?	& ? \\ \hline
+Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
+Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
 \end{tabular}

### 2018-12-09 density.tex
small changes + bugfix

@@
 This feasible region is not empty because it contains the origin. 
-Consider an extreme point $\alpha^*_i$ and set $s_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $s_i = -1$ w.p.\ $(1+\alpha^*_i)/2$.
+Consider an extreme point $\alpha^*_i$ and set $s_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $s_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
 $$
@@
 $$
+The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[s_i] = \alpha^*_i $.
 The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
@@
 
-\section{Attempt at Cleaner Definitions}
-Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
-We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
-$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}s_i f_i (x)$$  \el{need to double check the order here...}
-
-We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
-Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
-
-In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
-The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
-Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
-Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
-
-In what follows, we subscript the function $f$ with its parametrization.
-\begin{itemize}
-\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
-\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
-\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
-\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
-Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
-\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
+%\section{Attempt at Cleaner Definitions}
+%Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
+%We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
+%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}s_i f_i (x)$$  \el{need to double check the order here...}
+%
+%We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
+%Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
+%
+%In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
+%The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
+%Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
+%Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
+%
+%
+%In what follows, we subscript the function $f$ with its parametrization.
+%\begin{itemize}
+%\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
+%\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
+%\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
+%\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+%\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
+%Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
+%\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
 Here, like in Logistic Regression, $a$ is the example point multiplied by its label and $x$ is the weights of the linear classifier.
-\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
 Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
 For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-\item Probably also good for matrix approximation when we get entry updates. 
-\end{itemize}
+%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+%\item Probably also good for matrix approximation when we get entry updates. 
+%\end{itemize}
+%
 
@@
 We claim that while $R_n$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution) $K_n$ is the measure more suitable for
-active learning and creating streaming coresets. 
-The name Komlos Complexity due to the Komlos Conjecture which claims the minimal value of $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
-The correctness of the Komlos Conjecture is still an important open problem in the study of discrepancy theory.
-
-It is clear that $K_m(\F) < R_m(\F)$ for every family $\F$.
+active learning, for creating coresets, and for creating mergeable sketches.
+The name Komlos Complexity due to the Komlos Conjecture.
+It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
+The correctness of the Komlos Conjecture is still a fundamental open problem in the study of discrepancy theory.
+The definition is useful, however regardless of the correctness of the conjecture.  
+It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We claim, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
 
@@
 Column Slection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& ? 		& $\sqrt{m}$ \\ \hline
 Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline

### 2018-12-14 komlos.tex
adds komlos

--- 2018-12-09 density.tex
@@
 \begin{abstract}
-We present a general framework for producing mergeable sketches based on coresets for a wide variety of streaming problems. 
-The algorithm is generic and works whenever the task exhibits a certain low discrepancy property.
-Such problems include simple tasks like frequent item counting and quantile approximation, newer results on kernel density estimation and matrix covariance approximation, and extends to machine learning in problems such at linear and logistic regression.
+This paper presents the Komlos complexity for families of functions.
+We argue that this measure of complexity captures properties like minimal coreset sizes, streaming mergable sketches, and batch active learning.  
+We show that for many well known problems the Komlos complexity is asymptotically lower than their Rademacher complexity.
+This proves the existence smaller coresets than those achievable by random sampling. 
+These include frequent item counting, quantile approximation, kernel density estimation, matrix covariance approximation, and linear and logistic regression.
 For all of the above we match the state of the art or improve on it with the above generic framework.
 This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
+We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
 \end{abstract}
 
-\section{introduction}
-def
+\section{Introduction}
 
-\section{General framework for sketching}
-In many sketching problems our goal is to approximate a function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are all the stream items and $q \in \mathcal Q$ is any query point from a possible set $\mathcal Q$ which is known in advance.
+In many machine learning and sketching problems our goal is to approximate the sum (or expectation) of functions.
+Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\mathcal Q$ which is known in advance.
 The goal is to produce weights $w$ with at most $\ell \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(x_i,q) \approx F(q)$.
@@
 
-Generating a concise representation for $\tilde F$ allows one to optimize of $\tilde F$ instead of $F$ which more efficient. 
+Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which more efficient. 
 Moreover, if the sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
@@
 
+\newcommand{\ccc}[1]{\parbox}
+\begin{table}[htp]
+\caption{default}
+\begin{center}
+\begin{tabular}{|c|c|c|c|} \hline
+Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
+Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
+Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
+Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
+Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& ? 		& $\sqrt{m}$ \\ \hline
+Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
+Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
+Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
+\end{tabular}
+\end{center}
+\label{default}
+\end{table}%
+
 For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ stream items.
@@
 Moreover, our solution creates streaming algorithms with fully mergeable sketches. 
+The size of the coreset above appears to be intimately tied to the discrepancy properties of the associated functions.
+This is captured by its Komlos complexity.
+
+\section{Komlos Complexity}
+We begin by formally defining the Komols complexity and by giving some general results about for problems with low Komols complexity.
+The Komols complexity of a sequence set is defined similarly to it Rademacher complexity.
+\begin{definition}
+Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$ uniformly. 
+The Rademacher complexity of $\F$ is 
+\[
+R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
+\]
+\end{definition}
+
+\begin{definition}
+Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$. 
+The Komlos complexity of $A$ is 
+\[
+K_m(A) =  \frac{1}{m}\min_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
+\]
+\end{definition}
+\noindent It well known that $R_n$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions complexity and relationships between them.
+We claim that $K_n$ is the measure more suitable for active learning, for creating coresets, and for creating mergeable sketches.
+
+The name Komlos Complexity is due to the Komlos Conjecture.
+It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
+The correctness of the Komlos Conjecture is still a fundamental open problem in the study of discrepancy theory.
+The definition is useful, however, regardless of the correctness or provability of the conjecture.
+It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We show later that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+
+\begin{theorem}
+Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
+There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
+$$
+\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
+$$
+\end{theorem}
+\begin{proof}
+By halving the points repeatedly \el{TODO}.
+\end{proof}
+
+\begin{theorem}
+Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
+There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
+That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+$$
+\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+$$
+\end{theorem}
+
+\begin{theorem}
+Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
+There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
+That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+$$
+\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+$$
+\end{theorem}
+
+\section{General Framework for Sketching}
 
@@
 
-\section{Density Estimation}
+\section{Connections to streaming Counting and Quantiles}
+
+\section{Kernel Density Estimation}
 
@@
 
-$$ K(x,y) = \exp(- \|x-y\|_2^2/\sigma^2)\;\;\; K(x,y) = \exp(-\lambda \|x-y\|/\sigma) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|_2^2/\sigma^2)^{-1}$$
+$$ K(x,y) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,y) = \exp(- \|x-y\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|/_2^2/\lambda^2)^{-1}$$
 
-where $\sigma$ is a scaling parameter.
-What we discuss in what follows applies for any kernel, an depends on a bound on $K(x,x)$.
+where $\lambda$ is a scaling parameter.
+What we discuss in what follows applies for any positive definite kernel, an depends on a bound on $K(x,x)$.
 For simplicity we assume that $K(x,x) \leq 1$ for all datapoints.
@@
 
-Using our framework, we need to bound $\Delta(y) = \sum_{i=1}^k s_i K(x_i,y)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
+Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,y)$.
+For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that
 $$ K(x,y) = \ip{\phi(x), \phi(y)} $$
@@
 This guarantees that 
-$$ \forall y \in \R^d \;\;\; \sum s_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{k} $$
+$$ \forall y \in \R^d \;\;\; \sum s_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
 
@@
 \end{proof}
-The algorithm for finding the signs reduces to random choice for $s_i$ and then checking the norm of $\sum s_i x_i x_i^T$.
-This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric.
+\el{The algorithm for finding the signs reduces to random choice for $s_i$ and then checking the norm of $\sum s_i x_i x_i^T$.
+This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric. TODO Replace with Bansal's paper}
 Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
@@
 
-\subsection{Optimal Design of Experiments}
+\subsection{Streaming Graph Approximation}
+Streaming graphs have received a lot of attention in the last several years \cite{}. 
+In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
+Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
+Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
+Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
+In this formulation, this problem reduced to that of row (column) subset selection. 
+Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
+Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
+The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
+$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
+
+\section{Linear Regression}
+
+\section{Optimal Design of Experiments}
 We discuss the problem of linear regression with mean squared error.
@@
 $$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
-This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.
+\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
 
@@
 $$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-This is leads to the exact same objective as in column subset selection.
+This leads to the exact same objective as in column subset selection.
 Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
@@
 In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
-
-\section{Streaming Graph Approximation}
-Streaming graphs have received a lot of attention in the last several years \cite{}. 
-In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
-Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
-Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
-Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
-In this formulation, this problem reduced to that of row (column) subset selection. 
-Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
-Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
-The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
-$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
 
@@
 
-\section{Komlos Complexity}
-
-\begin{definition}
-Let $\F:\mathcal Q\rightarrow \R$ be a family of functions, $f \subset \F$, and $\sigma \in \{-1,1\}^m$ uniformly. 
-The Rademacher complexity of $\F$ is defined to be
-\[
-R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f}  \sum_{i=1}^{m}\sigma_i f_i
-\]
-\end{definition}
-\cite{Bartlett:2003:RGC:944919.944944}
-\begin{definition}
-Let $\F:\mathcal Q\rightarrow \R$ be a family of functions, $f \subset \F$, and $\sigma \in \{-1,1\}^m$.
-The Komlos complexity of $\F$ is defined as
-\[
-K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{f}  \sum_{i=1}^{m}\sigma_i f_i
-\]
-\end{definition}
-We claim that while $R_n$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution) $K_n$ is the measure more suitable for
-active learning, for creating coresets, and for creating mergeable sketches.
-The name Komlos Complexity due to the Komlos Conjecture.
-It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
-The correctness of the Komlos Conjecture is still a fundamental open problem in the study of discrepancy theory.
-The definition is useful, however regardless of the correctness of the conjecture.  
-It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We claim, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
-
-\newcommand{\ccc}[1]{\parbox}
-\begin{table}[htp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|c|c|c|c|} \hline
-Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
-Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Column Slection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& ? 		& $\sqrt{m}$ \\ \hline
-Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
-Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
-Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
-\end{tabular}
-\end{center}
-\label{default}
-\end{table}%
-
-According to these notes \el{https://courses.cs.washington.edu/courses/cse522/11wi/scribes/lecture6.pdf find better ref} all
-linear classifiers have Rademacher complexity $O(1/\sqrt{m})$. 
-If we look at the proof in the last page, it is clear we can get also $K_m = \sqrt{d}/m$ which is better whenever $m>d$ which is pretty much always the case for linear classification (number of examples greater than $d$) \el{I've done this in my head so it might not be right...}
-
 \end{document}

### 2018-12-14 komlos.tex
more changes

@@
 \newcommand{\X}{\mathcal{X}}
+\newcommand{\Q}{\mathcal{Q}}
 %\usepackage{ntheorem}
@@
 
-In many machine learning and sketching problems our goal is to approximate the sum (or expectation) of functions.
-Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\mathcal Q$ which is known in advance.
-The goal is to produce weights $w$ with at most $\ell \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(x_i,q) \approx F(q)$.
+In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
+Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance.
+For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
+The goal is to produce weights $w$ with at most $k \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{n}w_i f(x_i,q)$ approximates $F(q)$.
 Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
@@
 
-Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which more efficient. 
-Moreover, if the sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
+Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
+Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
 
-Here are some examples:
-\begin{itemize}
-\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
-\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
-\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
+%Here are some examples:
+%\begin{itemize}
+%\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
+%\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
+%\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
 For simplicity, we will assume in this manuscript that $x$ is also unit norm.
-\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
-Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
-\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
+%\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+%\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
+%Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
+%\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
 Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
-\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
 Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
 For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-\item Probably also good for matrix approximation when we get entry updates. 
-\end{itemize}
+%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+%\item Probably also good for matrix approximation when we get entry updates. 
+%\end{itemize}
 
@@
 \begin{table}[htp]
-\caption{default}
 \begin{center}
@@
 Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& ? 		& $\sqrt{m}$ \\ \hline
-Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
+Gaussian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\lambda^2)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
+Laplacian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2/\lambda)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
+Positive Kernel Density 			& $f(x, q) = k(x,q)$ for any positive kernel $k$ and $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
+
+%Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ where  $q,x\in \R^d$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+%Hinge Regression     		& $f(x, q) = [1-q^T x]_+$ where  $q,x\in \R^d$							& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Linear Regression		& $f(x,q) = (z^Tq - y)^2$ where $x = (z\in\R^d,y\in \R)$ and $q\in \R^d$					& ?				& ? \\ \hline
+Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else. $q,x\in \R^d$					& ?				& ? \\ \hline
 Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
-Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
+Matrix Approximation  	& $f(x, q) = a_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
 \end{tabular}
+\caption{Example problems in machine learning and sketching that fall into this framework.}
 \end{center}
@@
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
-This is common practice in machine learning, specifically, PAC learning. 
-However, it is often far from being the smallest cardinality coreset possible.
-
+%This is common practice in machine learning, specifically, PAC learning. However, it is often far from being the smallest cardinality coreset possible.
 We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
@@
 
-\begin{theorem}
-Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
-There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
-$$
-\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
-$$
-\end{theorem}
-\begin{proof}
-By halving the points repeatedly \el{TODO}.
-\end{proof}
+%\begin{theorem}
+%Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
+%There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
+%$$
+%\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
+%$$
+%\end{theorem}
+%\begin{proof}
+%By halving the points repeatedly \el{TODO}.
+%\end{proof}
 
-\begin{theorem}
-Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
-There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
-That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-$$
-\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-$$
-\end{theorem}
+\begin{fact}
+For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
+$O(c/\eps)$ whose error is at most $\eps n$.
+\end{fact}
+\begin{fact}
+For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
+$O(c/\eps^2)$ whose error is at most $\eps n$.
+\end{fact}
 
-\begin{theorem}
-Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
-There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
-That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-$$
-\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-$$
-\end{theorem}
+\noindent Proving both facts is trivial. 
+At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ of $2\sqrt{n/2}  = \sqrt{2n}$.
+Note that the sum of errors is asymptotically dominated by last iterations. 
+Halting the compression at $\Theta(1/\eps)$ or $\Theta(1/\eps^2)$ items respectively achieves the goal.
+
+%\begin{theorem}
+%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
+%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
+%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+%$$
+%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+%$$
+%\end{theorem}
+%
+%
+%\begin{theorem}
+%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
+%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
+%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+%$$
+%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+%$$
+%\end{theorem}
 
@@
 Consider a stream of the data points $x_i$. 
-We maintain a buffer that can hold up to $k$ points.
-Once collecting $k$ data points it performs a \emph{compact} operation that outputs $k/2$ data points of weight $2$ representing the original $k$ inputs.
-The compact operation partitions the $k$ points into two sets whose corresponding sum are very close.
+We maintain a buffer that can hold up to $m$ points.
+Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
+The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
 This is made formal with the following definitions: 
-Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$ where $s_i \in \{-1,1\}$ are signs.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
-We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  | E(q)|$.
+Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
+We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  |E(q)|$.
 
@@
 %Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
-Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
-\begin{definition}
-We define the discrepancy $\Delta_k$ with respect to a function $f(x,q)$ to be  
-\[\Delta_k = \min_s \max_{q,x} \sum_{i=1}^{k} s_i f(x_i,q). \] 
-\end{definition}
-\noindent We claim that a function is sketch-able if $\Delta_k = o(k)$. 
-As a warmup exercise, consider the non-streaming case. Throughout we discuss functions $f$ with the property $|f(x,q)| \leq 1$ for all $x,q$.
-
-\begin{fact}
-For any function $f$ which a corresponding discrepancy of $\Delta_k = O(1)$ there exists a coreset of size 
-$O(1/\eps)$ whose error is at most $\eps n$.
-\end{fact}
-\begin{fact}
-For any sum of functions $f$ which a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a coreset of size 
-$O(1/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
-
-\noindent Proving both facts is trivial. 
-At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c_1$ or $c_2 \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c_1$ of $2\sqrt{n/2}  = \sqrt{2n}$.
-Note that the sum of errors is asymptotically dominated by last iterations. 
-Halting the compression at $O(1/\eps)$ or $O(1/\eps^2)$ items respectively achieves the goal.
+Note that the above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
+Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
+We claim that a function is sketch-able if $K_m(\F) = O(m^\gamma)$ for any constant $\gamma \in [0,1)$.
 
@@
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding cthere exists an unbiased fully-mergeable streaming coreset algorithms of size 
 $O\left(\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \begin{theorem}
-For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding omlos Complexity of $K_m = O(1/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
 $O\left(\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \begin{lemma} \label{lem:compactor}
-Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $s_1,\ldots,s_k$ such that
-$$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
+Let $k$ be an integer and assume we have black box access to a solver that for any $m$ inputs $x_1,\ldots,x_m$ obtains $m$ signs $\sigma_1,\ldots,\sigma_m$ such that
+$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_m$$
+\el{I need to think about this absolute value here. Is it needed?}
 Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties

### 2018-12-14 komlos.tex
more changes

@@
 %
-%Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
-%Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
+%Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} \sigma_i f(x_i,q)$.
+%Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$.
 %Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
@@
 The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
-$$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
-Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; s_i = 1\}$ or $\{x_i \; | \; s_i = -1\}$ with twice the weight.
-$$\sum_{i ,\; s_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} s_i f(x_i, q)$$
-$$\sum_{i ,\; s_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} s_i f(x_i, q)$$
+$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq \rho k$$
+Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
+$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
+$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
 
-%Now, consider the set $P=\{i:s_i=1\}$ and $N=\{i:s_i=-1\}$.
-%$$ \sum_i s_i f(x_i, q) = \sum_i s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
-%$$ -\sum_i s_i f(x_i, q) = \sum_i -s_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
+%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
+%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
+%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
 %Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
@@
 As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-$\sum_i s_i f(x_i, q)$ or $-\sum_i s_i f(x_i, q)$ with equal probability. It follows that it is a Bernoulli r.v. with magnitude of at most $\rho k$ as required.
+$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Bernoulli r.v. with magnitude of at most $\rho k$ as required.
 \end{proof}
@@
 Using this function $\phi$ our objective function becomes
-$$\sum_{i=1}^k s_i K(x_i,y) = \sum_{i=1}^k s_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^k s_i \phi(x_i), \phi(y)} \leq \|\phi(y)\| \cdot \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^k s_i \phi(x_i) \right\| $$
-This upper bound allows us to optimize (find values for $s_i$) a simple expression.
-Given $k$ vectors $z_1,\ldots,z_k$ in an inner product space, compute signs minimizing $\| \sum_i s_i z_i \|$.
+$$\sum_{i=1}^m \sigma_i K(x_i,y) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(y)} \leq \|\phi(y)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| $$
+This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
+Given $m$ vectors $z_1,\ldots,z_m$ in an inner product space, compute signs minimizing $\| \sum_i \sigma_i z_i \|$.
 We first notice that for i.i.d.\ uniform signs, it holds that
-$$\E[\| \sum_i s_i z_i \|^2] = \E[\sum_{i,j} s_i s_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
-leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i s_i z_i \| \le 2\sum_i \|z_i\|$.
+$$\E[\| \sum_i \sigma_i z_i \|^2] = \E[\sum_{i,j} \sigma_i \sigma_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
+leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i \sigma_i z_i \| \le 2\sqrt{\sum_i \|z_i\|^2}$.
 %
 We can also use the method of expectation minimization to achieve this bound deterministically.
-Specifically, we will guaranty that $\| \sum_{j=1}^i s_j z_j \|^2 \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
+Specifically, we will guaranty that $\| \sum_{j=1}^i \sigma_j z_j \|^2 \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
 This is trivially true for $i=1$. 
-For another value $i$ set $s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle z_j, z_i \rangle)$ 
-and  assume by induction that $\| \sum_{j=1}^{i-1} s_j z_j\|^2 \le \sum_{j=1}^{i-1} \|z_j\|^2$.
+For another value $i$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle z_j, z_i \rangle)$ 
+and  assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j z_j\|^2 \le \sum_{j=1}^{i-1} \|z_j\|^2$.
 
 \begin{eqnarray*}
-\| \sum_{j=1}^{i}s_j z_j\|^2 &=& \|\sum_{j=1}^{i-1}s_j z_j\|^2 + \|z_i\|^2 + \langle \sum_{j=1}^{i-1}s_j z_j, s_i z_i\rangle \\
-&\le& \sum_{j=1}^{i-1} \|z_j\|^2 + \|z_i\|^2 + s_i \sum_{j=1}^{i-1}s_j \langle  z_j,  z_i\rangle \mbox{\;\;\; by the induction assumption}\\ 
-&=& \sum_{j=1}^{i} \|z_j\|^2 - |\sum_{j=1}^{i-1}s_j \langle  z_j,  z_i\rangle| \le \sum_{j=1}^{i} \|z_j\|^2
+\| \sum_{j=1}^{i}\sigma_j z_j\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j z_j\|^2 + \|z_i\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j z_j, \sigma_i z_i\rangle \\
+&\le& \sum_{j=1}^{i-1} \|z_j\|^2 + \|z_i\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle \mbox{\;\;\; by the induction assumption}\\ 
+&=& \sum_{j=1}^{i} \|z_j\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle| \le \sum_{j=1}^{i} \|z_j\|^2
 \end{eqnarray*}
-This completes the proof that $\| \sum_{j=1}^{k}s_j z_j\| \le \sqrt{\sum_{j=1}^{i} \|z_j\|^2}$ for our choice of values for $s$. 
+This completes the proof that $\| \sum_{j=1}^{k}\sigma_j z_j\| \le \sqrt{\sum_{j=1}^{i} \|z_j\|^2}$ for our choice of values for $\sigma$. 
 %
@@
 The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
-$$ s_i = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}s_j  K(x_j, x_i))$$
+$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
 This guarantees that 
-$$ \forall y \in \R^d \;\;\; \sum s_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
+$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
 
@@
 Since you are trying to minimize the quadratic form, you get that $f(x, q) = \langle x,q \rangle ^2$ and 
-$$E(y) = \sum_i s_i \langle x_i,q \rangle ^2 = q^T (\sum_i s_i x_i x_i^T ) q \le \|\sum_i s_i x_i x_i^T\| \le c\sqrt{d}$$
+$$E(q) = \sum_i \sigma_i \langle x_i,q \rangle ^2 = q^T (\sum_i \sigma_i x_i x_i^T ) q \le \|\sum_i \sigma_i x_i x_i^T\| \le c\sqrt{d}$$
 
@@
 \begin{theorem}\label{BansalInDaHouz}
-For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
+For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
 \end{theorem}
@@
 First, recount Banaszczyk's theorem. 
-Let $\mathcal K$ be a convex body in $\R^d$ such that $\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is Gaussian i.i.d.
+Let $\mathcal K$ be a convex body in $\R^d$ with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
 Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
-Then, there exist signs $s_i$ such that $\sum s_i x_i \in C \mathcal K$ for some universal constant $C$.
+Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some universal constant $C$.
 
 To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
-Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $10\sqrt{d_1 + d_2}$.
-More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le 10\sqrt{d_1+d_2}\}$. 
+Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $c\sqrt{d_1 + d_2}$.
+More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le c\sqrt{d_1+d_2}\}$. 
 Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
-Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices \cite{}.
-Banaszczyk's theorem says that there exist signs $s_i$ such that $\sum s_i \operatorname{flatten}(X_i) \in C \mathcal K$.
-In other words $\| \sum s_i X_i\| = \| \operatorname{stack}( \sum s_i \operatorname{flatten}(x_i x_i^T)) \| \le 10 C \sqrt{d}$. 
+Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices \el{add citation \cite{}}.
+Banaszczyk's theorem says that there exist signs $\sigma_i$ such that $\sum \sigma_i \operatorname{flatten}(X_i) \in C \mathcal K$.
+In other words $\| \sum \sigma_i X_i\| = \| \operatorname{stack}( \sum \sigma_i \operatorname{flatten}(x_i x_i^T)) \| \le C \sqrt{d}$. 
 \end{proof}
-\el{The algorithm for finding the signs reduces to random choice for $s_i$ and then checking the norm of $\sum s_i x_i x_i^T$.
-This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric. TODO Replace with Bansal's paper}
+The algorithm for finding the signs above is, unfortunately, not as simple as with kernels. 
+In fact, Banaszczyk's theorem was not constructive and a matching algorithms is a very recent breakthrough result by Bansal, Dadush, Garg, and Lovett \cite{DBLP:conf/stoc/BansalDGL18}.
 Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
@@
 %The problem is 
-%$$ \min_s \| \sum_i s_i x_ix_i^T\| $$
+%$$ \min_s \| \sum_i \sigma_i x_ix_i^T\| $$
 %where $\|x_i\| \leq 1$. Consider the following greedy approach: At point $x_i$, let
-%$$ C_i = \sum_{j<i} s_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
-%We choose $s_i = 1$ if $l_+ < l_i$, otherwise $s_i=-1$.
+%$$ C_i = \sum_{j<i} \sigma_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
+%We choose $\sigma_i = 1$ if $l_+ < l_i$, otherwise $\sigma_i=-1$.
 %
@@
 \begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1]
-For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i s_i x_i || \le \sqrt{d}$.
+For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
 \end{theorem}
@@
 This feasible region is not empty because it contains the origin. 
-Consider an extreme point $\alpha^*_i$ and set $s_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $s_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
+Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
 $$
-\E[\|\sum s_i x_i\|^2] =  \E[\|\sum (s_i - \alpha^*_i) x_i\|^2] = \sum \E[(s_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
+\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
 $$
-The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[s_i] = \alpha^*_i $.
+The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
 The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
@@
 %We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
-%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}s_i f_i (x)$$  \el{need to double check the order here...}
+%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}\sigma_i f_i (x)$$  \el{need to double check the order here...}
 %
@@
 
-%Specifically, we set $s_i$ sequentially for $i$ while minimizing the expectation. 
-%We prove by induction on $i$ that for the fixed $s_j$'s up to and not including $i$,
-%$$\E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
-%For $i=1$ this is trivial. For $i>1$ let $v=\sum_{j=1}^{i-1} s_j z_j$.
-%$$ \E_{s_i,\ldots,s_k}[\| \sum_{j=1}^k s_j z_j \|^2] = \E[\| v + \sum_{j=i}^k s_j z_j \|^2] = \|v\|^2 + \sum_{j=i}^k \|z_j\|^2$$
-%It follows that by fixing $s_i$ deterministically,
-%$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] = \|v\|^2 + \|z_i\|^2 - \|v + s_i z_i\|^2  $$
+%Specifically, we set $\sigma_i$ sequentially for $i$ while minimizing the expectation. 
+%We prove by induction on $i$ that for the fixed $\sigma_j$'s up to and not including $i$,
+%$$\E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
+%For $i=1$ this is trivial. For $i>1$ let $v=\sum_{j=1}^{i-1} \sigma_j z_j$.
+%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_{j=1}^k \sigma_j z_j \|^2] = \E[\| v + \sum_{j=i}^k \sigma_j z_j \|^2] = \|v\|^2 + \sum_{j=i}^k \|z_j\|^2$$
+%It follows that by fixing $\sigma_i$ deterministically,
+%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] = \|v\|^2 + \|z_i\|^2 - \|v + \sigma_i z_i\|^2  $$
 %so in order to make sure that 
-%$$ \E_{s_i,\ldots,s_k}[\| \sum_j s_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j s_j z_j \|^2] $$
+%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] $$
 %we need
-%$$ 2\ip{m,s_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + s_i z_i\|^2 \geq 0 $$
+%$$ 2\ip{m,\sigma_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + \sigma_i z_i\|^2 \geq 0 $$
 %We thus set 
-%$$ s_i = -\text{sign} \ip{m,z_i}$$
+%$$ \sigma_i = -\text{sign} \ip{m,z_i}$$

### 2018-12-17 komlos.tex
changing definitions

@@
 The Komols complexity of a sequence set is defined similarly to it Rademacher complexity.
+%\begin{definition}
+%Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$ uniformly. 
+%The Rademacher complexity of $\F$ is 
+%\[
+%R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
+%\]
+%\end{definition}
+%
+%\begin{definition}
+%Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$. 
+%The Komlos complexity of $A$ is 
+%\[
+%K_m(A) =  \frac{1}{m}\min_{\sigma} \sup_{a \in A}  \left|\sum_{i=1}^{m}\sigma_i a_i\right|
+%\]
+%\end{definition}
+
 \begin{definition}
-Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$ uniformly. 
-The Rademacher complexity of $\F$ is 
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$ uniformly. 
+The Rademacher complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
 \[
-R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
+R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f \in \F}  \sum_{i=1}^{m}\sigma_i f(x_i)
 \]
 \end{definition}
+%
+\begin{definition}
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The Komlos complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+\[
+K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
+\]
+The Komlos Complexity $K_m(\F)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+\end{definition}
 
-\begin{definition}
-Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$. 
-The Komlos complexity of $A$ is 
-\[
-K_m(A) =  \frac{1}{m}\min_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
-\]
-\end{definition}
-\noindent It well known that $R_n$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions complexity and relationships between them.
-We claim that $K_n$ is the measure more suitable for active learning, for creating coresets, and for creating mergeable sketches.
+\noindent It well known that $R_m$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
+We claim that $K_m$ is the measure more suitable for active learning, for creating coresets, and for creating mergeable sketches.
 
-The name Komlos Complexity is due to the Komlos Conjecture.
+\el{Add a much longer explanation about the connection to discrepancy and the ideas behind this construction} The name Komlos Complexity is due to the Komlos Conjecture.
 It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
@@
 %\end{proof}
+\subsection{General Framework for Coresets}
+Consider the function $F = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}$.
+We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+%
+The above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
+Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
+A function is sketch-able if $K_m(\F) = O(m^\gamma)$ for any constant $\gamma \in [0,1)$.
+Typically we see that $K_m(\F) = O(c/m)$ or $K_m(\F)= c/\sqrt{m}$ for some $c$ which does not depend on $m$.
 
@@
 At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ of $2\sqrt{n/2}  = \sqrt{2n}$.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = \sqrt{2n}$.
 Note that the sum of errors is asymptotically dominated by last iterations. 
-Halting the compression at $\Theta(1/\eps)$ or $\Theta(1/\eps^2)$ items respectively achieves the goal.
+Halting the compression at $\Theta(c/\eps)$ or $\Theta(c/\eps^2)$ items respectively achieves the goal.
 
@@
 
-\section{General Framework for Sketching}
+\el{I believe we that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets.
+Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}
+
+\subsection{General Framework for Sketching}
 
@@
 This is made formal with the following definitions:
-Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
-We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  |E(q)|$.
 
  %
-%We begin with describing the basic operation of compaction and the notion of flat error functions. 
-%
-%Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} \sigma_i f(x_i,q)$.
-%Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$.
-%Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
-Note that the above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
-Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
-We claim that a function is sketch-able if $K_m(\F) = O(m^\gamma)$ for any constant $\gamma \in [0,1)$.
-
 In what follows, we prove the following.
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding cthere exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O\left(\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+$O\left(c\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
 For $\delta=0$ this results in a deterministic algorithm.
-The algorithm must be given $\eps, \delta$ as input and does not require knowledge of the stream length $n$.
+The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
 \end{theorem}
@@
 \begin{theorem}
-For any function $f$ with a corresponding omlos Complexity of $K_m = O(1/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O\left(\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+$O\left(c\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
 For $\delta=0$ this results in a deterministic algorithm.
-The algorithm must be given $\eps, \delta$ as input and does not require knowledge of the stream length $n$.
+The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
 \end{theorem}
@@
 \begin{lemma} \label{lem:compactor}
-Let $k$ be an integer and assume we have black box access to a solver that for any $m$ inputs $x_1,\ldots,x_m$ obtains $m$ signs $\sigma_1,\ldots,\sigma_m$ such that
-$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_m$$
-\el{I need to think about this absolute value here. Is it needed?}
+Let $m$ be an integer and assume we have black box access to a solver that for any $m$ inputs $x_1,\ldots,x_m$ obtains $m$ signs $\sigma_1,\ldots,\sigma_m$ such that
+$$\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \in O(K_m)$$
+Note that such signs are guarantied to exist by the definition of the Komols Complexity. 
+In fact, the quantity above is likely much smaller than $K_m$ because it is computed for a specific set of points $x_i$ and the worst such possible set.
+
 Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties

### 2018-12-18 komlos.tex
random stuff

--- 2018-12-14 komlos.tex
@@
 \newcommand{\X}{\mathcal{X}}
-\newcommand{\Q}{\mathcal{Q}}
 %\usepackage{ntheorem}
@@
 
-In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
-Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance.
-For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
-The goal is to produce weights $w$ with at most $k \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{n}w_i f(x_i,q)$ approximates $F(q)$.
+In many machine learning and sketching problems our goal is to approximate the sum (or expectation) of functions.
+Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\mathcal Q$ which is known in advance.
+The goal is to produce weights $w$ with at most $\ell \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{\ell}w_i f(x_i,q) \approx F(q)$.
 Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
@@
 
-Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
-Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
+Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which more efficient. 
+Moreover, if the sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
 
-%Here are some examples:
-%\begin{itemize}
-%\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
-%\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
-%\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
+Here are some examples:
+\begin{itemize}
+\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
+\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
+\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
 For simplicity, we will assume in this manuscript that $x$ is also unit norm.
-%\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-%\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
-%Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
-%\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
+\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
+Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
+\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
 Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
-%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
 Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
 For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-%\item Probably also good for matrix approximation when we get entry updates. 
-%\end{itemize}
+\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+\item Probably also good for matrix approximation when we get entry updates. 
+\end{itemize}
 
@@
 \begin{table}[htp]
+\caption{default}
 \begin{center}
@@
 Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Gaussian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\lambda^2)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Laplacian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2/\lambda)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Positive Kernel Density 			& $f(x, q) = k(x,q)$ for any positive kernel $k$ and $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-
-%Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ where  $q,x\in \R^d$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-%Hinge Regression     		& $f(x, q) = [1-q^T x]_+$ where  $q,x\in \R^d$							& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Linear Regression		& $f(x,q) = (z^Tq - y)^2$ where $x = (z\in\R^d,y\in \R)$ and $q\in \R^d$					& ?				& ? \\ \hline
-Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else. $q,x\in \R^d$					& ?				& ? \\ \hline
+Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& ? 		& $\sqrt{m}$ \\ \hline
+Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
 Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
-Matrix Approximation  	& $f(x, q) = a_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
+Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
 \end{tabular}
-\caption{Example problems in machine learning and sketching that fall into this framework.}
 \end{center}
@@
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
-%This is common practice in machine learning, specifically, PAC learning. However, it is often far from being the smallest cardinality coreset possible.
+This is common practice in machine learning, specifically, PAC learning. 
+However, it is often far from being the smallest cardinality coreset possible.
+
 We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
@@
 
-%\begin{theorem}
-%Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
-%There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
-%$$
-%\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
-%$$
-%\end{theorem}
-%\begin{proof}
-%By halving the points repeatedly \el{TODO}.
-%\end{proof}
+\begin{theorem}
+Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
+There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
+$$
+\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
+$$
+\end{theorem}
+\begin{proof}
+By halving the points repeatedly \el{TODO}.
+\end{proof}
 
-\begin{fact}
-For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
-$O(c/\eps)$ whose error is at most $\eps n$.
-\end{fact}
-\begin{fact}
-For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
-$O(c/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
+\begin{theorem}
+Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
+There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
+That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+$$
+\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+$$
+\end{theorem}
 
-\noindent Proving both facts is trivial. 
-At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ of $2\sqrt{n/2}  = \sqrt{2n}$.
-Note that the sum of errors is asymptotically dominated by last iterations. 
-Halting the compression at $\Theta(1/\eps)$ or $\Theta(1/\eps^2)$ items respectively achieves the goal.
-
-%\begin{theorem}
-%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
-%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
-%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-%$$
-%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-%$$
-%\end{theorem}
-%
-%
-%\begin{theorem}
-%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
-%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
-%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-%$$
-%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-%$$
-%\end{theorem}
+\begin{theorem}
+Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
+There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
+That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
+$$
+\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
+$$
+\end{theorem}
 
@@
 Consider a stream of the data points $x_i$. 
-We maintain a buffer that can hold up to $m$ points.
-Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
-The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
+We maintain a buffer that can hold up to $k$ points.
+Once collecting $k$ data points it performs a \emph{compact} operation that outputs $k/2$ data points of weight $2$ representing the original $k$ inputs.
+The compact operation partitions the $k$ points into two sets whose corresponding sum are very close.
 This is made formal with the following definitions: 
-Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
-We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  |E(q)|$.
+Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$ where $s_i \in \{-1,1\}$ are signs.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$ and the corresponding $F_{-1}$.
+We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| \le  | E(q)|$.
 
@@
 %Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
-Note that the above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
-Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
-We claim that a function is sketch-able if $K_m(\F) = O(m^\gamma)$ for any constant $\gamma \in [0,1)$.
+Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
+\begin{definition}
+We define the discrepancy $\Delta_k$ with respect to a function $f(x,q)$ to be  
+\[\Delta_k = \min_s \max_{q,x} \sum_{i=1}^{k} s_i f(x_i,q). \] 
+\end{definition}
+\noindent We claim that a function is sketch-able if $\Delta_k = o(k)$. 
+As a warmup exercise, consider the non-streaming case. Throughout we discuss functions $f$ with the property $|f(x,q)| \leq 1$ for all $x,q$.
+
+\begin{fact}
+For any function $f$ which a corresponding discrepancy of $\Delta_k = O(1)$ there exists a coreset of size 
+$O(1/\eps)$ whose error is at most $\eps n$.
+\end{fact}
+\begin{fact}
+For any sum of functions $f$ which a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a coreset of size 
+$O(1/\eps^2)$ whose error is at most $\eps n$.
+\end{fact}
+
+\noindent Proving both facts is trivial. 
+At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c_1$ or $c_2 \sqrt{n}$.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c_1$ of $2\sqrt{n/2}  = \sqrt{2n}$.
+Note that the sum of errors is asymptotically dominated by last iterations. 
+Halting the compression at $O(1/\eps)$ or $O(1/\eps^2)$ items respectively achieves the goal.
 
@@
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding cthere exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
 $O\left(\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \begin{theorem}
-For any function $f$ with a corresponding omlos Complexity of $K_m = O(1/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
 $O\left(\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \begin{lemma} \label{lem:compactor}
-Let $k$ be an integer and assume we have black box access to a solver that for any $m$ inputs $x_1,\ldots,x_m$ obtains $m$ signs $\sigma_1,\ldots,\sigma_m$ such that
-$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_m$$
-\el{I need to think about this absolute value here. Is it needed?}
+Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $s_1,\ldots,s_k$ such that
+$$\max_q \left| \sum_i s_i f(x_i, q)\right| \leq \rho k$$
 Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
@@
 \el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
+\zk{We actually ended up using the Radamacher complexity, at least for the bound.
+Namely, we used random signs.
+Perhaps there is a kernel for which it is easy to prove something better?
+One that comes to mind is apx low rank data.
+By low rank I mean in the kernel space, meaning the $z_i$'s.
+To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$.
+Then, we use theory on the sum of unit vectors of low dimension giving $\sqrt{k}/\eps$ where $k$ is the dimension we got.
+In the worst case if the kernel matrix is isotropic we will get $k \approx n$ and gain nothing, but this way we can squeeze something from the data that wasn't squeezed before..
+We can take this further and look into the details of the proof that we can balance unit vectors to have a norm of $\sqrt{d}$ regardless of the number of vectors.
+The key in that proof is that by considering continuous $s_i$'s we can have the sum equal to zero while keeping only $d$ points with non $\{-1,1\}$ $s_i$'s.
+Consider a split of top $k$ and bottom rest directions.
+If we restrict the $s_i$'s to only have the sum to be zero in the top $k$ we get $k$ non integral $s_i$'s but possibly horrible performance on the bottom $k$.
+What if only restrict $d-2k$ and not $d-k$ points?
+Then we get some freedom in choosing the integer $s_i$'s.
+The bound on the bottom singular values can become smaller than the trivial one.}
 
@@
 \el{The algorithm for finding the signs reduces to random choice for $s_i$ and then checking the norm of $\sum s_i x_i x_i^T$.
-This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric. TODO Replace with Bansal's paper}
+This suffices according to \cite{DBLP:conf/approx/DadushGLN16} and the corresponding convex body $\mathcal K$ being symmetric.
+TODO Replace with Bansal's paper} \zk{Taking random $s_i$'s cannot be enough.
+If $d=1$ and we have $n \gg 1$ vectors this fails miserably.
+Does Bansal have a paper giving a constructive proof of this Theorem?}
 Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
@@
 Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
-Their assumptions don't hold here.} \zk{We can get $1/\eps^2$ though which is better than $\sqrt{d}/\eps$ as long as $\eps > 1/\sqrt{d}$.
-If $\eps < 1/\sqrt{d}$ then $\sqrt{d}/\eps > d$ - shouldn't it be trivial to get a coreset of size $d$?}
+Their assumptions don't hold here.}
 
@@
 
+Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
+The dimension of $x$'s is $d$ and of $y$'s is infinite.
+Both $\|x_i\|, \|y\| \leq 1$.
+However, the overall norm of the $y$'s is bounded $\sum \|y_i\|^2 \leq \rho n$.
+Naively we can ignore the $y$'s and get a bound on the norm of $\sqrt{d + \sqrt{\rho} n}$ or something like that.
+If $y$ is obtained as the low components of PCA we can squeeze some more.
+Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
+Let $\alpha^{(1)}$ be a feasible point.
+Let $\alpha^{(2)}$ be another feasible point that is restricted to being orthogonal to $\alpha^{(1)}$, and so on up to $\alpha^{(d)}$.
+For all these $\alpha$'s we have a bound of $2d$ to their rounding w.r.t to $x$.
+Now, for the $y$'s we can choose any one of these $\alpha$'s
+
+However, we can search for $\alpha \in [-1,1]^n$ minimizing
+
 %\section{Attempt at Cleaner Definitions}

### 2018-12-18 komlos.tex

--- 2018-12-17 komlos.tex
@@
 In fact, Banaszczyk's theorem was not constructive and a matching algorithms is a very recent breakthrough result by Bansal, Dadush, Garg, and Lovett \cite{DBLP:conf/stoc/BansalDGL18}.
+
 Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
@@
 
+In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
+The do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
+Calling that matrix $A$, $A_{q,x} = K(q,x)$.
+They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound
+$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
+Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
+$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
+They prove that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
+Now, back to our case.
+For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$.
+Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$.
+It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$.
+The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
+
 %\paragraph{Reduction to the Kernel case}
@@
 \end{proof}
+
+Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
+The dimension of $x$'s is $d$ and of $y$'s is infinite.
+Both $\|x_i\|, \|y\| \leq 1$.
+However, the overall norm of the $y$'s is bounded $\sum \|y_i\|^2 \leq \rho n$.
+Naively we can ignore the $y$'s and get a bound on the norm of $\sqrt{d + \sqrt{\rho} n}$ or something like that.
+If $y$ is obtained as the low components of PCA we can squeeze some more.
+Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
+Let $\alpha^{(1)}$ be a feasible point.
+Let $\alpha^{(2)}$ be another feasible point that is restricted to being orthogonal to $\alpha^{(1)}$, and so on up to $\alpha^{(d)}$.
+For all these $\alpha$'s we have a bound of $2d$ to their rounding w.r.t to $x$.
+Now, for the $y$'s we can choose any one of these $\alpha$'s
+
+However, we can search for $\alpha \in [-1,1]^n$ minimizing
 

### 2018-12-18 komlos.tex
before changes
colt style

@@
-\documentclass{article} % For LaTeX2e
+\documentclass[anon,12pt]{colt2019} % Anonymized submission
+% \documentclass[12pt]{colt2019} % Include author names
+
+% The following packages will be automatically loaded:
+% amsmath, amssymb, natbib, graphicx, url, algorithm2e
+
+\title[Komols Complexity, Coresets, and Sketches in Machine Learning]{Komols Complexity, Coresets, and Sketches in Machine Learning}
+\usepackage{times}
+% Use \Name{Author Name} to specify the name.
+% If the surname contains spaces, enclose the surname
+% in braces, e.g. \Name{John {Smith Jones}} similarly
+% if the name has a "von" part, e.g \Name{Jane {de Winter}}.
+% If the first letter in the forenames is a diacritic
+% enclose the diacritic in braces, e.g. \Name{{\'E}louise Smith}
+
+% Two authors with the same address
+% \coltauthor{\Name{Author Name1} \Email{abc@sample.com}\and
+%  \Name{Author Name2} \Email{xyz@sample.com}\\
+%  \addr Address}
+
+% Three or more authors with the same address:
+% \coltauthor{\Name{Author Name1} \Email{an1@sample.com}\\
+%  \Name{Author Name2} \Email{an2@sample.com}\\
+%  \Name{Author Name3} \Email{an3@sample.com}\\
+%  \addr Address}
+
 \usepackage{amsmath}
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage[noend]{algorithmic}
 \usepackage{algorithm}
-\usepackage[margin=1in]{geometry}
+%\usepackage[margin=1in]{geometry}
 \usepackage{xcolor}
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}{Conjecture}[section]
+%\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{conjecture}{Conjecture}[section]
 %\newtheorem{claim}[theorem]{Claim}
-\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{lemma}[theorem]{Lemma}
 %\newtheorem{remark}[theorem]{Remark}
@@
 \newtheorem{fact}[theorem]{Fact}
+%\newtheorem*{definition*}{Definition}
+%\newtheorem{definition}{Definition}
+%\newtheorem{claim}{Claim}
+%\newtheorem{theorem}{Theorem}
 
@@
 
-%\newtheorem*{definition*}{Definition}
-\newtheorem{definition}{Definition}
-\newtheorem{claim}{Claim}
-%\newtheorem{theorem}{Theorem}
-
-\title{Sketching for Density Estimation}
-\date{\nonumber}
-
-\author{
-Zohar Karnin\\Amazon\\zkarnin@amazon.com
-\and
-Edo Liberty\\Amazon\\libertye@amazon.com
+% Authors with different addresses:
+\coltauthor{%
+ \Name{Zohar Karnin} \Email{zkarnin@amazon.com}%\\ \addr Address 1
+ \AND
+ \Name{Edo Liberty} \Email{libertye@amazon.com}%\\ \addr Address 2%
 }
@@
 
-\el{I believe we that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets.
+\el{I believe that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets.
 Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}
@@
 In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
-The do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
+They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
 Calling that matrix $A$, $A_{q,x} = K(q,x)$.

### 2018-12-21 komlos.tex
gamma_2

--- 2018-12-18 komlos.tex
@@
 %\newtheorem{observation}[theorem]{Observation}
-%\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{corollary}[theorem]{Corollary}
 %\newtheorem{proposition}[theorem]{Proposition}
@@
 \newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
+\newcommand{\disc}{\text{disc}}
 
@@
 
+A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
+This is proven in \cite{tomczak1989banach}.
+In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
+
 %\paragraph{Reduction to the Kernel case}
@@
 %
+
+\section{Active Learning for linear functions (based on $\gamma_2$ norm)}
+
+Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
+$$\min_w \sum_{i=1}^n L(K(x_i, w), y_i)$$
+
+For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
+The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
+
+\begin{definition}
+For a matrix $A$,
+$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
+is the $\gamma_2$ norm of $A$. 
+\end{definition}
+ \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
+ $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
+
+\begin{lemma} \label{lem:powers}
+For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
+\end{lemma}
+\begin{proof}
+For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
+$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
+Furthermore, 
+$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
+Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
+\end{proof}
+
+\begin{lemma}
+Let $L:\R \to \R$ be a function that can be written as 
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
+with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
+$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
+\end{lemma}
+\begin{proof}
+This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
+\end{proof}
+
+This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
+In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
+\begin{corollary}
+For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
+\end{corollary}
+
+\begin{definition}
+For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
+$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
+\end{definition}
+In \cite{matouvsek2014factorization} they prove that 
+$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
+This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
+$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
+where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
+$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}/\eps) $$
+
+Let's discuss what this means.
+For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
+
+Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
+$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
+meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
+By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
+Then, for the matrix $A_{K,f_L}$ with
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
+we have 
+$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
+
+\begin{corollary}
+For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
+$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
+and
+$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}/\eps) $$ 
+\end{corollary}
+
+%Let's discuss what this means.
+For a logistic regression problem, by observing the weights we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
+This has a limitation where we need the labels to determine the coreset.
+We now proceed to see how we can remove that need.
+%
+%We will require an assumption regarding the labels of the data: We assume that for some $q \in Q$, there exist at most $\rho n$ data point label pairs $(x,y) \in X \times \{-1,1\}$ such that $\text{sign}(\ip{q,x}) \neq y$.
+
 \bibliographystyle{plain}

### 2018-12-22 komlos.tex
adding proof for RBF

--- 2018-12-18 komlos.tex
@@
 \newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
+%\newcommand{\Pr}{\operatorname{Pr}}
 
@@
 \begin{fact}
-For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
+For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
 $O(c/\eps)$ whose error is at most $\eps n$.
@@
 \begin{fact}
-For any function family $\F$ which a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
+For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
 $O(c/\eps^2)$ whose error is at most $\eps n$.
@@
 
+\section{Universal Coresets for Functions of Inner Products}
+
+\begin{lemma}\label{uc}
+For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\|\sum_i \sigma_i x_i^{\otimes k}\| \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
+Here
+$\|X\| = \max_{q, \|q\|=1} \langle X, q^{\otimes k}\rangle$.
+
+\end{lemma}
+\begin{proof}
+The proof will use Banaszczyk's theorem. 
+Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
+Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
+Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
+
+To use Banaszczyk's theorem we begin with defining our convex body.
+Define the norm $\|\psi\|_T$ of a vector $\psi$ as follows.
+Look at the first $d$ coordinates of $\psi$ as a vector $\psi_1$, the next $d^2$ coordinates of $\psi$ as a matrix $\psi_2$ the next $d^3$ coordinates as a three tensor $\psi_3$ etc.
+We define $\|\psi\|_T = \max_k \|\psi_k\|/\sqrt{\log(k)}$. 
+Here, $\|\cdot\|$ is a special spectral norm defined by 
+$$\|\psi\| = \max_{q, \|q\|=1} \langle   \psi_k,q^{\otimes k}\rangle  = \max_{q, \|q\|=1} \sum_{i_1,\ldots,i_k=1}^d \psi_k(i_1,\ldots,i_k)\Pi_{k'=1}^{k}q(i_{k'})$$
+%
+Since $\|\cdot\|_T$ is a norm the set $\mathcal K  = \{\psi \; | \; \|\psi\|_T \le c\sqrt{d}\}$ is convex. 
+We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
+That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
+
+Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
+A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\| \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
+The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$.
+The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+
+We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
+$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
+Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\| = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+
+We are now ready to apply Banaszczyk's theorem. 
+There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
+Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\| \le \sqrt{d k \log^{3}(k)}$
+
+\begin{lemma}
+Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
+The Komlos Complexity of the Family of functions $f$ (indexed by $q$) is bouded by
+\[
+K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}
+\]
+\end{lemma}
+\begin{proof}
+The proof follows from combining the above.
+$$
+\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|
+$$
+By Lemma \ref{uc} we can find signs $\sigma$ such that 
+$\| \sum_i \sigma_i x_i^{\otimes k}\| \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
+\end{proof}
+
+\begin{lemma}
+The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d})$.
+\end{lemma}
+\begin{proof}
+The sum converged to a constant.
+\end{proof}
+\begin{lemma}
+The Komlos complexity of the Logistic function in dimension $d$ is $O(\sqrt{d})$.
+\end{lemma}
+\begin{proof}
+The sum converged to a constant.
+\end{proof}
+
+\end{proof}
+
 \section{Row (or Column) Subset Selection}
@@
 
-\section{Optimal Design of Experiments}
-We discuss the problem of linear regression with mean squared error.
+%\section{Optimal Design of Experiments}
+%We discuss the problem of linear regression with mean squared error.
 In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
-$$ \sum_i (w^Tx_i - y_i)^2 $$
-In the field of optimal design of experiments, the labels are not given with the data.
+%$$ \sum_i (w^Tx_i - y_i)^2 $$
+%In the field of optimal design of experiments, the labels are not given with the data.
 Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
 The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
-
-The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
-$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
-%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
-%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
-%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
-%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-
-One can show that for $w_B$,
-$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
-\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
-
-We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
+%
+%The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
+%$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
+%%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
+%%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
+%%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
+%%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+%
+%
+%One can show that for $w_B$,
+%$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
+%\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
+%
+%We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
 Something that is commonly practiced.
@@
 The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
-$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-This leads to the exact same objective as in column subset selection.
+%$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+%This leads to the exact same objective as in column subset selection.
 Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
 Specifically we get that we can obtain a core-set of size
-$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
-For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
+%$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
+%For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
 I'm not sure what statements are known already.
-
-In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
+%
+%In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
 

### 2018-12-26 komlos.tex
draft gammma2

--- 2018-12-21 komlos.tex
@@
 %\newtheorem{observation}[theorem]{Observation}
-\newtheorem{corollary}[theorem]{Corollary}
+%\newtheorem{corollary}[theorem]{Corollary}
 %\newtheorem{proposition}[theorem]{Proposition}
@@
 $$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
-They prove that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
+They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
 Now, back to our case.
@@
 
-\section{Active Learning for linear functions (based on $\gamma_2$ norm)}
+\section{Coreset for linear functions (based on $\gamma_2$ norm)}
 
 Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
-$$\min_w \sum_{i=1}^n L(K(x_i, w), y_i)$$
+$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
+
+Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
+$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
 
@@
 where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
-$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}/\eps) $$
+$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
 
@@
 and
-$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}/\eps) $$ 
+$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
 \end{corollary}
-
-%Let's discuss what this means.
-For a logistic regression problem, by observing the weights we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
-This has a limitation where we need the labels to determine the coreset.
-We now proceed to see how we can remove that need.
-%
-%We will require an assumption regarding the labels of the data: We assume that for some $q \in Q$, there exist at most $\rho n$ data point label pairs $(x,y) \in X \times \{-1,1\}$ such that $\text{sign}(\ip{q,x}) \neq y$.
 

### 2018-12-26 komlos.tex

--- 2018-12-22 komlos.tex
@@
 \newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
-%\newcommand{\Pr}{\operatorname{Pr}}
+\newcommand{\disc}{\text{disc}}
 
@@
 The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
+
+A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
+This is proven in \cite{tomczak1989banach}.
+In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
 
@@
 %
+
+\section{Coreset for linear functions (based on $\gamma_2$ norm)}
+
+Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
+$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
+
+Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
+$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
+
+For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
+The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
+
+\begin{definition}
+For a matrix $A$,
+$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
+is the $\gamma_2$ norm of $A$. 
+\end{definition}
+ \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
+ $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
+
+\begin{lemma} \label{lem:powers}
+For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
+\end{lemma}
+\begin{proof}
+For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
+$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
+Furthermore, 
+$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
+Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
+\end{proof}
+
+\begin{lemma}
+Let $L:\R \to \R$ be a function that can be written as 
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
+with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
+$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
+\end{lemma}
+\begin{proof}
+This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
+\end{proof}
+
+This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
+In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
+\begin{corollary}
+For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
+\end{corollary}
+
+\begin{definition}
+For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
+$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
+\end{definition}
+In \cite{matouvsek2014factorization} they prove that 
+$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
+This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
+$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
+where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
+$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
+
+Let's discuss what this means.
+For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
+
+Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
+$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
+meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
+By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
+Then, for the matrix $A_{K,f_L}$ with
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
+we have 
+$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
+
+\begin{corollary}
+For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
+$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
+and
+$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
+\end{corollary}
+
 \bibliographystyle{plain}

### 2018-12-26 komlos.tex
cleanup

@@
 \newcommand{\disc}{\text{disc}}
+\renewcommand{\Pr}{\operatorname{Pr}}
 
@@
 
-\section{Universal Coresets for Functions of Inner Products}
+\section{Universal Coresets for Analytical Functions}
+
+We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$.
+The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors $q$.
+By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
+It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$.
+
+We start some notation and trivial properties.
+For a vector $q \in \R^d$ let $q^{\otimes k}$ to represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself in all the dimensions.
+For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
+$\|X\| = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
+\begin{lemma}
+$\|X\|$ is a norm
+\end{lemma}
+\begin{proof}
+Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
+It follows that there must be $q$ for which it's value is non-zero.
+This means that $\|X\|=0$ iff $X=0$.
+For a scalar $a$, we clearly have by definition that
+$$ \|aX\| = |a|\|X\| $$
+Lastly, by the max definition we clearly have
+$$ \|X+Y\| =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\| + \|Y\|$$
+\end{proof}
+
+We are now ready for the lemma controlling all powers of inner products simultaneously.
 
@@
 For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\|\sum_i \sigma_i x_i^{\otimes k}\| \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
-Here
-$\|X\| = \max_{q, \|q\|=1} \langle X, q^{\otimes k}\rangle$.
-
 \end{lemma}
@@
 Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
-Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
+Let $x_1,\ldots,x_n$ be vectors with $\|x_i\|_2 =O(1)$. 
 Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
@@
 We define $\|\psi\|_T = \max_k \|\psi_k\|/\sqrt{\log(k)}$. 
-Here, $\|\cdot\|$ is a special spectral norm defined by 
-$$\|\psi\| = \max_{q, \|q\|=1} \langle   \psi_k,q^{\otimes k}\rangle  = \max_{q, \|q\|=1} \sum_{i_1,\ldots,i_k=1}^d \psi_k(i_1,\ldots,i_k)\Pi_{k'=1}^{k}q(i_{k'})$$
+Here, $\|\cdot\|$ is the special spectral norm defined in the beginning of the section 
+%$$\|\psi\| = \max_{q, \|q\|=1} \langle   \psi_k,q^{\otimes k}\rangle  = \max_{q, \|q\|=1} \sum_{i_1,\ldots,i_k=1}^d \psi_k(i_1,\ldots,i_k)\Pi_{k'=1}^{k}q(i_{k'})$$
 %
-Since $\|\cdot\|_T$ is a norm the set $\mathcal K  = \{\psi \; | \; \|\psi\|_T \le c\sqrt{d}\}$ is convex. 
+The maximum over norms of subvectors is clearly a norm in itself, meaning that $\|\cdot \|_T$ is indeed a norm.
+It follows that  the set $\mathcal K  = \{\psi \; | \; \|\psi\|_T \le c\sqrt{d}\}$ is convex.
+
 We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
 That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
-
 Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
 A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\| \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
-The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$.
+The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
 Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$.
@@
 $$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
-Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\| = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+Finally, note that for $\|x\|_2 \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
 
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:komlos anl}
 Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
-The Komlos Complexity of the Family of functions $f$ (indexed by $q$) is bouded by
+The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\|_2 \leq 1$, is bounded by
 \[
 K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}
+\]
+For general $\|q\|_2 \leq R$ we get
+\[
+K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}
 \]
@@
 $$
-\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|
+\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\| \cdot \|q\|_2^k
 $$
@@
 
-\begin{lemma}
+\begin{theorem}
+Let $\tilde{f}$ be an analytical one dimension function over $\R$.
+There exist a radius $R$ such that for $\|q\|_2 \leq R$ the function family of functions $f_q(x) = \tilde{f}(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d})$
+\end{theorem}
+\begin{proof}
+Recall that for analytical functions $f$ we have 
+$$\left| \frac{d^k \tilde{f}}{dx^k}(x) \right| / k! \leq C^{k+1} $$
+for some constant $C$. Considering the taylor expansion of $\tilde{f}$ near zero we get that for $R < 1/C$, the sum
+$$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} $$
+corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
+\end{proof}
+
+\begin{corollary}
+The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\|_2 \leq 1$ is $O(\sqrt{d})$.
+\end{corollary}
+
+Notice that by transforming $x$ to $\tilde{x} = (-x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$.
+This implies that our results for functions of $\ip{q,x}$ apply for functions of $\|q-x\|^2$.
+In particular we get
+\begin{corollary}
 The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d})$.
-\end{lemma}
-\begin{proof}
-The sum converged to a constant.
-\end{proof}
-\begin{lemma}
-The Komlos complexity of the Logistic function in dimension $d$ is $O(\sqrt{d})$.
-\end{lemma}
-\begin{proof}
-The sum converged to a constant.
-\end{proof}
+\end{corollary}
 
@@
 Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
-Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices \el{add citation \cite{}}.
+Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices (see Theorem~\ref{thm:random tensor}).
 Banaszczyk's theorem says that there exist signs $\sigma_i$ such that $\sum \sigma_i \operatorname{flatten}(X_i) \in C \mathcal K$.
@@
 
-\bibliographystyle{plain}
+%\bibliographystyle{plain}
 \bibliography{density}
@@
 For completeness we recap a result from \cite{barany2008}.
-\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1]
+\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
 For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.

### 2018-12-26 komlos.tex
minor fix

@@
 For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
-$\|X\| = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
+$\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
 \begin{lemma}
-$\|X\|$ is a norm
+$\|X\|_{T_k}$ is a norm
 \end{lemma}
 \begin{proof}
+We prove the claim directly from the definition of a norm.
 Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
-It follows that there must be $q$ for which it's value is non-zero.
-This means that $\|X\|=0$ iff $X=0$.
+It follows that there must be $q$ for which it's value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
 For a scalar $a$, we clearly have by definition that
-$$ \|aX\| = |a|\|X\| $$
+$$ \|aX\|_{T_k} = |a|\|X\|_{T_k} $$
 Lastly, by the max definition we clearly have
-$$ \|X+Y\| =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\| + \|Y\|$$
+$$ \|X+Y\|_{T_k} =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq $$
+$$\max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$$
 \end{proof}
@@
 \begin{lemma}\label{uc}
-For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\|\sum_i \sigma_i x_i^{\otimes k}\| \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
+For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
 \end{lemma}
@@
 Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
-Let $x_1,\ldots,x_n$ be vectors with $\|x_i\|_2 =O(1)$. 
+Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
 Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
@@
 Look at the first $d$ coordinates of $\psi$ as a vector $\psi_1$, the next $d^2$ coordinates of $\psi$ as a matrix $\psi_2$ the next $d^3$ coordinates as a three tensor $\psi_3$ etc.
-We define $\|\psi\|_T = \max_k \|\psi_k\|/\sqrt{\log(k)}$. 
-Here, $\|\cdot\|$ is the special spectral norm defined in the beginning of the section 
-%$$\|\psi\| = \max_{q, \|q\|=1} \langle   \psi_k,q^{\otimes k}\rangle  = \max_{q, \|q\|=1} \sum_{i_1,\ldots,i_k=1}^d \psi_k(i_1,\ldots,i_k)\Pi_{k'=1}^{k}q(i_{k'})$$
-%
+We define $\|\psi\|_T = \max_k \|\psi_k\|_{T_k} /\sqrt{\log(k)}$. 
+Here, $\|\cdot\|_{T_k}$ is the special spectral norm defined in the beginning of the section 
 The maximum over norms of subvectors is clearly a norm in itself, meaning that $\|\cdot \|_T$ is indeed a norm.
@@
 Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
-A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\| \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
+A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
 The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
@@
 $$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
-Finally, note that for $\|x\|_2 \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
 
@@
 There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
-Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\| \le \sqrt{d k \log^{3}(k)}$
+Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$
 
@@
 Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
-The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\|_2 \leq 1$, is bounded by
+The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
 \[
@@
 \]
-For general $\|q\|_2 \leq R$ we get
+For general $\|q\| \leq R$ we get
 \[
@@
 $$
-\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\| \cdot \|q\|_2^k
+\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
 $$
 By Lemma \ref{uc} we can find signs $\sigma$ such that 
-$\| \sum_i \sigma_i x_i^{\otimes k}\| \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
+$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
 \end{proof}
@@
 Let $\tilde{f}$ be an analytical one dimension function over $\R$.
-There exist a radius $R$ such that for $\|q\|_2 \leq R$ the function family of functions $f_q(x) = \tilde{f}(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d})$
+There exist a radius $R$ such that for $\|q\| \leq R$ the function family of functions $f_q(x) = \tilde{f}(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d})$
 \end{theorem}
@@
 Recall that for analytical functions $f$ we have 
-$$\left| \frac{d^k \tilde{f}}{dx^k}(x) \right| / k! \leq C^{k+1} $$
+$$\left| \frac{d^k \tilde{f}}{dz^k}(z) \right|  \leq C^{k+1} k! $$
 for some constant $C$. Considering the taylor expansion of $\tilde{f}$ near zero we get that for $R < 1/C$, the sum
-$$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} $$
+$$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$$
 corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
@@
 \begin{corollary}
-The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\|_2 \leq 1$ is $O(\sqrt{d})$.
+The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d})$.
 \end{corollary}

### 2018-12-28 komlos.tex
commit before pull

--- 2018-12-26 komlos.tex
@@
 \newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
-\newcommand{\disc}{\text{disc}}
+%\newcommand{\Pr}{\operatorname{Pr}}
 
@@
 \begin{abstract}
-This paper presents the Komlos complexity for families of functions.
-We argue that this measure of complexity captures properties like minimal coreset sizes, streaming mergable sketches, and batch active learning.  
+This paper defines the Komlos complexity for families of functions which is intimately related to its discrepancy properties.
+We argue that this measure of complexity captures properties like minimal coreset sizes for different problems in machine learning.
 We show that for many well known problems the Komlos complexity is asymptotically lower than their Rademacher complexity.
 This proves the existence smaller coresets than those achievable by random sampling.
-These include frequent item counting, quantile approximation, kernel density estimation, matrix covariance approximation, and linear and logistic regression.
-For all of the above we match the state of the art or improve on it with the above generic framework.
+New results for coresets for kernel density estimation, matrix covariance approximation, and logistic regression are presented both as examples of for providing mechanisms to compute the Komlos complexity of other classes.
+For all of the above we match the state of the art or improve on it.
 This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
-We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
+%We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
 \end{abstract}
@@
 The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
-
+%
 We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
 $$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
-Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\| = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
-
+Note that for $\|x\| \le 1$ we have $\|\psi(x)\| = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+%
 We are now ready to apply Banaszczyk's theorem. 
@@
 $$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
-They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
+They prove that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
 Now, back to our case.
@@
 The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
-
-A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
-This is proven in \cite{tomczak1989banach}.
-In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
 
@@
 %
-
-\section{Coreset for linear functions (based on $\gamma_2$ norm)}
-
-Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
-$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
-
-Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
-$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
-
-For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
-The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
-
-\begin{definition}
-For a matrix $A$,
-$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
-is the $\gamma_2$ norm of $A$. 
-\end{definition}
- \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
- $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
-
-\begin{lemma} \label{lem:powers}
-For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
-\end{lemma}
-\begin{proof}
-For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
-$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
-Furthermore, 
-$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
-Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
-\end{proof}
-
-\begin{lemma}
-Let $L:\R \to \R$ be a function that can be written as 
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
-with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
-$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
-\end{lemma}
-\begin{proof}
-This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
-\end{proof}
-
-This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
-In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
-\begin{corollary}
-For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
-\end{corollary}
-
-\begin{definition}
-For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
-$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
-\end{definition}
-In \cite{matouvsek2014factorization} they prove that 
-$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
-This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
-$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
-where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
-$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
-
-Let's discuss what this means.
-For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
-
-Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
-$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
-meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
-By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
-Then, for the matrix $A_{K,f_L}$ with
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
-we have 
-$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
-
-\begin{corollary}
-For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
-$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
-and
-$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
-\end{corollary}
-
 \bibliographystyle{plain}

### 2018-12-28 komlos.tex
fixed sketch proof

--- 2018-12-26 komlos.tex
@@
 \begin{lemma} \label{lem:compactor}
-Let $m$ be an integer and assume we have black box access to a solver that for any $m$ inputs $x_1,\ldots,x_m$ obtains $m$ signs $\sigma_1,\ldots,\sigma_m$ such that
-$$\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \in O(K_m)$$
+Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $\sigma_1,\ldots,\sigma_k$ such that
+$$\max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$$
 Note that such signs are guarantied to exist by the definition of the Komols Complexity. 
-In fact, the quantity above is likely much smaller than $K_m$ because it is computed for a specific set of points $x_i$ and the worst such possible set.
+In fact, the quantity above is potentially much smaller than the Komlos Complexity because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
 
@@
 \item $\E[m] = n/2$
+\item $\Pr[m \geq (1+1/\log^2(n))n/2] \leq \exp \left( -O\left(\frac{n}{k\log(n)^4}\right)\right)$
 \item For any fixed query $q$, the error associated with $q$, defined as
@@
 $$\text{Err}(q) = \sum_{j=1}^{n/k} \text{Err}_j(q)$$
-where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq \rho k$
+where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
 \end{itemize}
-The last property ensures that deterministically $|\text{Err}(q)| \leq \rho n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$ 
+The last property ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$ 
 $$|\text{Err}(q)| \lesssim \rho k\sqrt{n/k} = \rho \sqrt{kn}$$
@@
 The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
-$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq \rho k$$
+$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
 Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
@@
 The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
+Moreover, the output length is a sum of $n/k$ independent random variables with mean $k/2$ and a maximum value of $k$.
+Chernoff-Hoeffding's bound can guarantee the stated concentration around $\E[m]$.
 As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Bernoulli r.v. with magnitude of at most $\rho k$ as required.
+$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Radamacher r.v. scaled by a magnitude of at most $K_k$ as required.
 \end{proof}
@@
 
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+%
+
+\subsubsection{take 3}
+
+\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
+Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
+The streaming algorithm operates as follows.
+At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
+The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
+In the beginning we have a single compactor at level $h=0$.
+Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
+After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
+
+The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
+For a query $q$ and hierarchy level $h$ we analyze the error
+$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
+Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
+The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
+The sum over $j$ is over the number of compactions at level $h$.
+$K_h$ is used to denote the discrepancy of each compaction using a buffer of $k_h$ points.
+Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
+The overall error for the query $q$ is the sum over all levels of its errors
+$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
+
+To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
+
+We are however interested in a high probability bound.
+Specifically we would like to guarantee for $\delta_1,\delta_2 > 0$ that for any set of queries $Q$ the error is bounded by $\eps n$ w.p.\ $\delta_1|Q| + \delta_2$.
+To this end we consider a different analysis for the top and bottom layers.
+For the top layers, the length of the stream can be arbitrarily short so we will use the deterministic analysis as above.
+For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
+
+The bottom layers will be those of height $h=0$ up to $h=H'$ with 
+\begin{equation} \label{eq:Htag}
+H' = \ceil{\log\left( \frac{n}{k\log\left(1/\left(c \delta_1 \delta_2 \log^3(n)\right)\right)} \right)}
+\end{equation}
+for some constant $c$ that will be determined later.
+
+According to Lemma~\ref{lem:compactor} we have for $ h\geq 0$ that irrespective of $q$,
+$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -O\left(\frac{n_{h}}{k \log^2(n)} \right) \right) = \delta_2 / H' $$
+for a sufficiently small constant $c$ in Equation~\eqref{eq:Htag}. 
+It follows by taking a union bound and noticing that $H' \leq \log(n)$ that irrespective of $q$ we have w.p. at least $1-\delta_2$ that 
+$$\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}$$
+
+Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
+$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
+$$
+We now make use of the above union bound applied to the bound on $n_h$.
+Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
+We get that since $n_h \leq 3n/2^h$
+$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
+\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
+$$
+In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta_1)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
+$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta_1/(H'-h+1)^2$$
+and a union bound ensures that with probability at least $1-\delta_1$, for any fixed query $q$ it holds for all $h \leq H'$ that
+$$\left| \text{Err}_h(q) \right| \geq \eps_h n$$
+and 
+$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
+
+We start by dealing with the setting where $K_k = \min\{d,k\}$ where $d$ is independent of $k$.
+We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$.
+Since $k_{H'} = k$ by using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
+$$\eps_h \leq \sqrt{\frac{2c \cdot K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'} k_{h}}} \cdot \sqrt{\frac{2^{H'} K_{H'}^2 \log(1/\delta_1)}{k_{H'} n}} = $$
+$$
+\frac{K_k}{k} \cdot O\left( \sqrt{\frac{K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'}^2 k_{h}}}  \right)
+$$ 
+We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$
+$$
+\frac{K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'}^2 k_{h}} \leq \frac{d^2 k\log(H'-h+1)}{2^{H'-h} d^2 (2/3)^{H'-h}k} =
+\frac{\log(H'-h+1)}{ (4/3)^{H'-h}}
+$$
+If follows that 
+$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(d/k) $$
+and we have a bound of $O(d/k)$ for the bottom layers.
+
+For the top layers we set $k_h=k$ and obtain the deterministic bound of 
+$$ \sum_{h=H'+1}^H \text{Err}_h(q) \leq (H-H')(d/k)n $$
+Since we $n_{h+1} \leq n_h$ for $h \geq H'$ we get that $H-H' \leq \log(n/(kn_{H'}))$.
+According to our analysis above we are in an event (of probability $1-\delta_2$) where $n_{H'} \leq 3 \cdot n/2^{H'}  $ meaning that
+$$ n/(kn_{H'}) = O\left((\log\left(1/\left(c \delta_1 \delta_2 \log^3(n)\right)\right)\right) $$
+leading to the bound of 
+$$ \sum_{h=H'+1}^H \text{Err}_h(q) \leq O\left( \log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right)(d/k)n \right)$$
+The latter is the bound for the total sum of errors $\text{Err}(q)$ as well.
+
+To conclude the case of $K_k=d$ we obtain an error of 
+$$O\left( \log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right)(d/k)n \right)$$
+by using $O(k\log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right))$ memory.
+The memory analysis follows from a trivial bound to the upper layers, and noticing that for the smaller layers, all layers with $k=2$ can be implemented in $O(1)$ memory by uniformly sampling.
+By setting $\delta=\delta_1=\delta_2 < 1/\log(n)$ we get that for
+$$ k=O(d\log\log(1/\delta)/\eps) $$
+the overall error is bounded by $\eps n$ and the memory is bounded by 
+$$ O(d\log\log(1/\delta)^2/\eps) $$
+
+Let's now consider the case where $K_k = d\sqrt{k}$ with $d$ independent of $k$. Here, we set $k_{H'}=k$ and $k_h=2$ for all $h<H'$.
+
+\zk{need to finish the analysis for the above $K_k$..}
+\end{proof}
+
 \section{Connections to streaming Counting and Quantiles}
@@
 Using this function $\phi$ our objective function becomes
-$$\sum_{i=1}^m \sigma_i K(x_i,y) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(y)} \leq \|\phi(y)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| \leq  \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| $$
+$$\sum_{i=1}^m \sigma_i K(x_i,y) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(y)} \leq $$
+$$ \|\phi(y)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| \leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| $$
 This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
@@
 
-We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$.
+We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or distance $\|q-x\|$.
 The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors $q$.
 By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
-It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$.
+It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
 
@@
 We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
-$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
+$$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
 Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
@@
 \subsection{Streaming Graph Approximation}
-Streaming graphs have received a lot of attention in the last several years \cite{}. 
+Streaming graphs have received a lot of attention in the last several years \zk{cite something here \cite{}}. 
 In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.

### 2018-12-28 komlos.tex

--- 2018-12-26 komlos.tex
@@
 
-\section{Universal Coresets for Analytical Functions}
+\section{Universal Coresets for Analytic Functions of Dot Products}
 
+%<<<<<<< HEAD
+%\begin{lemma}\label{uc}
+%For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\|\sum_i \sigma_i x_i^{\otimes k}\| \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
+Here
+%$\|X\| = \max_{q, \|q\|=1} \langle X, q^{\otimes k}\rangle$.
+%=======
 We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$.
@@
 
-We start some notation and trivial properties.
-For a vector $q \in \R^d$ let $q^{\otimes k}$ to represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself in all the dimensions.
+We start with some notation and trivial properties. 
+For a vector $q \in \R^d$ let $q^{\otimes k}$ represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself $k$ times.
 For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
 $\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
-\begin{lemma}
+\begin{fact}
 $\|X\|_{T_k}$ is a norm
-\end{lemma}
+\end{fact}
 \begin{proof}
@@
 Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
-It follows that there must be $q$ for which it's value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
+It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
 For a scalar $a$, we clearly have by definition that
-$$ \|aX\|_{T_k} = |a|\|X\|_{T_k} $$
-Lastly, by the max definition we clearly have
-$$ \|X+Y\|_{T_k} =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq $$
-$$\max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$$
+$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
+$ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
+\max_q \left| \langle X, q^{\otimes k}\rangle \right| + \max_q\left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$
 \end{proof}
+%>>>>>>> 56549e52bc0636f8545357647f053d28b3c0c7df
 
@@
 The proof will use Banaszczyk's theorem. 
-Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
+Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
 Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
@@
 That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
-Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
+Consider a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
+%<<<<<<< HEAD
+%A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\| \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
+The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$.
+The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+%%
+%We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
+%$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
+%Note that for $\|x\| \le 1$ we have $\|\psi(x)\| = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+%
+%=======
 A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
 The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
-Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$.
-The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$.
 
-We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
+We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
 $$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
@@
 
+%>>>>>>> 56549e52bc0636f8545357647f053d28b3c0c7df
 We are now ready to apply Banaszczyk's theorem. 

### 2018-12-30 komlos.tex

--- 2018-12-28 komlos.tex
@@
 For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
-The goal is to produce weights $w$ with at most $k \ll n$ non-zero such that $\tilde F(q) = \sum_{i=1}^{n}w_i f(x_i,q)$ approximates $F(q)$.
+The goal is to produce weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
 Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
@@
 
-Generating a concise representation for $\tilde F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
+Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
 Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
@@
 
-\el{I believe that the correctness of the Komlos conjecture implies equivalence between coresets limited to the input and general coresets.
-Specifically, a constructive positive resolution will give an algorithm for converting any coresets to signs $\sigma$ and select inputs from a sequence.}
-
 \subsection{General Framework for Sketching}
@@
 
-If however, we are interested in a high probability bound of $1-\delta$, we decompose the error to two components
+If however, we are interested in a smaller sketch with high probability of success of $1-\delta$, we decompose the error to two components
 $$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
@@
 
-Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
 $$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
@@
 
-\section{Connections to streaming Counting and Quantiles}
+\section{A Simple Algorithm for Kernel Density Estimation}
 
-\section{Kernel Density Estimation}
-
-Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $\rho: \R^d \rightarrow \R$ of a point $y$ is defined as 
-$$ \rho(y) = \sum_{i=1}^{n} K(x_i,y) $$
+From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
+Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
+This bound is better when the $d > m$.
+More importantly though, there is a very simple and deterministic algorithm for computing the signs $\sigma$.
+Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
+$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
 Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
-
-$$ K(x,y) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,y) = \exp(- \|x-y\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-y\|/_2^2/\lambda^2)^{-1}$$
-
+$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
 where $\lambda$ is a scaling parameter.
-What we discuss in what follows applies for any positive definite kernel, an depends on a bound on $K(x,x)$.
-For simplicity we assume that $K(x,x) \leq 1$ for all datapoints.
+For simplicity, we assume that $K(x,x) \leq 1$ for all data points.
 Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.
 
-Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,y)$.
+Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$.
 For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that
-$$ K(x,y) = \ip{\phi(x), \phi(y)} $$
+$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
 Using this function $\phi$ our objective function becomes
-$$\sum_{i=1}^m \sigma_i K(x_i,y) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(y)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(y)} \leq $$
-$$ \|\phi(y)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| \leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| $$
+\[
+\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
+\]
 This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
-Given $m$ vectors $z_1,\ldots,z_m$ in an inner product space, compute signs minimizing $\| \sum_i \sigma_i z_i \|$.
-We first notice that for i.i.d.\ uniform signs, it holds that
-$$\E[\| \sum_i \sigma_i z_i \|^2] = \E[\sum_{i,j} \sigma_i \sigma_j \ip{z_i, z_j}] = \sum_i \|z_i\|^2 $$
-leading to a randomized approach. By Markov with probability at least $3/4$ we have $\| \sum_i \sigma_i z_i \| \le 2\sqrt{\sum_i \|z_i\|^2}$.
-%
-We can also use the method of expectation minimization to achieve this bound deterministically.
-Specifically, we will guaranty that $\| \sum_{j=1}^i \sigma_j z_j \|^2 \le \sum_{j=1}^i \|z_j\|^2$ for all $i$.
+Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
+We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
 This is trivially true for $i=1$. 
-For another value $i$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle z_j, z_i \rangle)$ 
-and  assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j z_j\|^2 \le \sum_{j=1}^{i-1} \|z_j\|^2$.
+For another value assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
 
 \begin{eqnarray*}
-\| \sum_{j=1}^{i}\sigma_j z_j\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j z_j\|^2 + \|z_i\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j z_j, \sigma_i z_i\rangle \\
-&\le& \sum_{j=1}^{i-1} \|z_j\|^2 + \|z_i\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle \mbox{\;\;\; by the induction assumption}\\ 
-&=& \sum_{j=1}^{i} \|z_j\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j \langle  z_j,  z_i\rangle| \le \sum_{j=1}^{i} \|z_j\|^2
+\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
+&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
+&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
 \end{eqnarray*}
-This completes the proof that $\| \sum_{j=1}^{k}\sigma_j z_j\| \le \sqrt{\sum_{j=1}^{i} \|z_j\|^2}$ for our choice of values for $\sigma$. 
+This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
 %
-Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
-The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
-$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
-This guarantees that 
-$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
+%Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
+%The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
+%$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
+%This guarantees that 
+%$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
 
-Using the framework above this provides a streaming coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that 
-$\forall \;q\;\; |\tilde \rho(q) - \rho(q)| \le \eps n$.
-This matches the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
-\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
-\zk{We actually ended up using the Radamacher complexity, at least for the bound.
+Using the framework above this provides a coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$.
+This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+%\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
+%\zk{We actually ended up using the Radamacher complexity, at least for the bound.
 Namely, we used random signs.
@@
 One that comes to mind is apx low rank data.
-By low rank I mean in the kernel space, meaning the $z_i$'s.
+By low rank I mean in the kernel space, meaning the $\phi(x_j)$'s.
 To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$.
@@
 
-\section{Universal Coresets for Analytical Functions}
+\section{Universal Coresets for Analytic Functions of Dot Products}
 
@@
 Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
-It follows that there must be $q$ for which it's value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
+It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
 For a scalar $a$, we clearly have by definition that
-$$ \|aX\|_{T_k} = |a|\|X\|_{T_k} $$
-Lastly, by the max definition we clearly have
-$$ \|X+Y\|_{T_k} =  \max_{q \in \R^d, \|q\|=1} \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq $$
-$$\max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right| + \max_{q \in \R^d, \|q\|=1} \left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$$
+$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
+$ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
+\max_q \left| \langle X, q^{\otimes k}\rangle \right| + \max_q\left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$
 \end{proof}
@@
 That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
-Considering a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$. 
+Consider a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$.
+
 A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
 The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
-Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability al least $1/2$.
-The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$.
+%
+We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
 
-We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
-$$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
 Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.

### 2018-12-30 komlos.tex
reorder and organize

@@
 \begin{abstract}
+\el{I need to rewrite the abstract}
 This paper defines the Komlos complexity for families of functions which is intimately related to its discrepancy properties.
@@
 
+\el{I need to rewrite this section.}
 In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
@@
 %\end{itemize}
-
-\newcommand{\ccc}[1]{\parbox}
-\begin{table}[htp]
-\begin{center}
-\begin{tabular}{|c|c|c|c|} \hline
-Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
-Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Gaussian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\lambda^2)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Laplacian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2/\lambda)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Positive Kernel Density 			& $f(x, q) = k(x,q)$ for any positive kernel $k$ and $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-
-%Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ where  $q,x\in \R^d$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-%Hinge Regression     		& $f(x, q) = [1-q^T x]_+$ where  $q,x\in \R^d$							& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Linear Regression		& $f(x,q) = (z^Tq - y)^2$ where $x = (z\in\R^d,y\in \R)$ and $q\in \R^d$					& ?				& ? \\ \hline
-Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else. $q,x\in \R^d$					& ?				& ? \\ \hline
-Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
-Matrix Approximation  	& $f(x, q) = a_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
-\end{tabular}
-\caption{Example problems in machine learning and sketching that fall into this framework.}
-\end{center}
-\label{default}
-\end{table}%
 
@@
 %\end{fact}
+
+\section{The Complexity of Analytic Functions of Dot Products}
+
+We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or distance $\|q-x\|$.
+The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors $q$.
+By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
+It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
+
+We start with some notation and trivial properties. 
+For a vector $q \in \R^d$ let $q^{\otimes k}$ represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself $k$ times.
+For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
+$\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
+\begin{fact}
+$\|X\|_{T_k}$ is a norm
+\end{fact}
+\begin{proof}
+We prove the claim directly from the definition of a norm.
+Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
+It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
+For a scalar $a$, we clearly have by definition that
+$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
+$ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
+\max_q \left| \langle X, q^{\otimes k}\rangle \right| + \max_q\left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$
+\end{proof}
+
+We are now ready for the lemma controlling all powers of inner products simultaneously.
+
+\begin{lemma}\label{uc}
+For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
+\end{lemma}
+\begin{proof}
+The proof will use Banaszczyk's theorem. 
+Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
+Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
+Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
+
+To use Banaszczyk's theorem we begin with defining our convex body.
+Define the norm $\|\psi\|_T$ of a vector $\psi$ as follows.
+Look at the first $d$ coordinates of $\psi$ as a vector $\psi_1$, the next $d^2$ coordinates of $\psi$ as a matrix $\psi_2$ the next $d^3$ coordinates as a three tensor $\psi_3$ etc.
+We define $\|\psi\|_T = \max_k \|\psi_k\|_{T_k} /\sqrt{\log(k)}$. 
+Here, $\|\cdot\|_{T_k}$ is the special spectral norm defined in the beginning of the section 
+The maximum over norms of subvectors is clearly a norm in itself, meaning that $\|\cdot \|_T$ is indeed a norm.
+It follows that  the set $\mathcal K  = \{\psi \; | \; \|\psi\|_T \le c\sqrt{d}\}$ is convex.
+
+We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
+That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
+Consider a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$.
+
+A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
+The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$.
+%
+We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
+
+Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+
+We are now ready to apply Banaszczyk's theorem. 
+There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
+Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$
+\end{proof}
+
+\begin{lemma} \label{lem:komlos anl}
+Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
+The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
+\[
+K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
+\]
+For general $\|q\| \leq R$ we get
+\[
+K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
+\]
+\end{lemma}
+\begin{proof}
+The proof follows from combining the above.
+$$
+\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
+$$
+By Lemma \ref{uc} we can find signs $\sigma$ such that 
+$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
+\end{proof}
+
+\begin{theorem}\label{analitic1}
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d}/m)$. 
+\end{theorem}
+\begin{proof}
+Recall that for analytic functions $f$ we have $\left| \frac{d^k f}{dz^k}(z) \right|  \leq C^{k+1} k! $
+for some constant $C$. Considering the taylor expansion of $f$ near zero. For $R < 1/C$, the sum
+$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$
+corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
+\end{proof}
+
+\begin{corollary}
+The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+\end{corollary}
+
+\begin{corollary}
+The Komlos complexity of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescales columns of the matrix $X$.
+\end{corollary}
+
+\begin{theorem}
+Let $f:\R\rightarrow\R$ be analytic.
+There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq \sqrt{R}$, has Komlos complexity of $O(\sqrt{d}/m)$.
+\end{theorem}
+\begin{proof}
+By transforming $x$ to $\tilde{x} = (x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (-2q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$.
+Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$.
+The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$ apply for functions of $\|q-x\|^2$.
+\end{proof}
+
+\begin{corollary}
+The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d}/m)$.
+This improves upon the recent result of \el{\cite{??}} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density.
+This resolves the open problem raised by \el{\cite{??}} and matches their lower bound.   
+\end{corollary}
+%\end{proof}
+
+\section{A Simple Algorithm for Kernel Density Estimation}
+
+From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
+Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
+This bound is better when $d > m$.
+More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
+Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
+$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
+Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
+$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
+where $\lambda$ is a scaling parameter.
+For simplicity, we assume that $K(x,x) \leq 1$ for all data points.
+Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.
+
+Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$.
+For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that
+$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
+Using this function $\phi$ our objective function becomes
+\[
+\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
+\]
+This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
+Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
+We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
+This is trivially true for $i=1$. 
+Assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
+
+\begin{eqnarray*}
+\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
+&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
+&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
+\end{eqnarray*}
+This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
+
+Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$.
+This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+
+\section{Linear Regression}
+
+%\section{Optimal Design of Experiments}
+%We discuss the problem of linear regression with mean squared error.
+In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
+%$$ \sum_i (w^Tx_i - y_i)^2 $$
+%In the field of optimal design of experiments, the labels are not given with the data.
+Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
+The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
+%
+%The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
+%$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
+%%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
+%%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
+%%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
+%%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+%
+%
+%One can show that for $w_B$,
+%$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
+%\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
+%
+%We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
+Something that is commonly practiced.
+Since we will solve the problem for the subset we choose in an optimal way for gaussian noise, we end up with an unbiased estimator for $w^*$.
+The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
+%$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
+%This leads to the exact same objective as in column subset selection.
+Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
+Specifically we get that we can obtain a core-set of size
+%$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
+%For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
+I'm not sure what statements are known already.
+%
+%In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
+
+\section{Logistic Regression}
+The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
+This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
+
+In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
+They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
+Calling that matrix $A$, $A_{q,x} = K(q,x)$.
+They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound
+$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
+Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
+$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
+They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
+Now, back to our case.
+For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$.
+Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$.
+It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$.
+The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
+
+A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
+This is proven in \cite{tomczak1989banach}.
+In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
+
+\section{Coreset for linear functions (based on $\gamma_2$ norm)}
+
+Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
+$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
+
+Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
+$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
+
+For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
+The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
+
+\begin{definition}
+For a matrix $A$,
+$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
+is the $\gamma_2$ norm of $A$. 
+\end{definition}
+ \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
+ $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
+
+\begin{lemma} \label{lem:powers}
+For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
+\end{lemma}
+\begin{proof}
+For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
+$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
+Furthermore, 
+$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
+Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
+\end{proof}
+
+\begin{lemma}
+Let $L:\R \to \R$ be a function that can be written as 
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
+with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
+$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
+\end{lemma}
+\begin{proof}
+This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
+\end{proof}
+
+This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
+In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
+\begin{corollary}
+For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
+\end{corollary}
+
+\begin{definition}
+For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
+$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
+\end{definition}
+In \cite{matouvsek2014factorization} they prove that 
+$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
+This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
+$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
+where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
+$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
+
+Let's discuss what this means.
+For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
+
+Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
+$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
+meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
+By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
+Then, for the matrix $A_{K,f_L}$ with
+$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
+we have 
+$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
+
+\begin{corollary}
+For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
+$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
+and
+$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
+\end{corollary}
+
+%\bibliographystyle{plain}
+\bibliography{density}
+
+\section{Appendix 1}
+For completeness we recap a result from \cite{barany2008}.
+\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
+For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
+\end{theorem}
+\begin{proof}
+Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
+This feasible region is not empty because it contains the origin. 
+Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
+$$
+\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
+$$
+The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
+The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
+Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
+\end{proof}
+
+Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
+The dimension of $x$'s is $d$ and of $y$'s is infinite.
+Both $\|x_i\|, \|y\| \leq 1$.
+However, the overall norm of the $y$'s is bounded $\sum \|y_i\|^2 \leq \rho n$.
+Naively we can ignore the $y$'s and get a bound on the norm of $\sqrt{d + \sqrt{\rho} n}$ or something like that.
+If $y$ is obtained as the low components of PCA we can squeeze some more.
+Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
+Let $\alpha^{(1)}$ be a feasible point.
+Let $\alpha^{(2)}$ be another feasible point that is restricted to being orthogonal to $\alpha^{(1)}$, and so on up to $\alpha^{(d)}$.
+For all these $\alpha$'s we have a bound of $2d$ to their rounding w.r.t to $x$.
+Now, for the $y$'s we can choose any one of these $\alpha$'s
+
+However, we can search for $\alpha \in [-1,1]^n$ minimizing
+
+%\section{Attempt at Cleaner Definitions}
+%Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
+%We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
+%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}\sigma_i f_i (x)$$  \el{need to double check the order here...}
+%
+%We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
+%Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
+%
+%In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
+%The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
+%Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
+%Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
+%
+%
+%In what follows, we subscript the function $f$ with its parametrization.
+%\begin{itemize}
+%\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
+%\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
+%\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
+%\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
+%\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
+%Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
+%\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
+Here, like in Logistic Regression, $a$ is the example point multiplied by its label and $x$ is the weights of the linear classifier.
+%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
+Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
+For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
+%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
+%\item Probably also good for matrix approximation when we get entry updates. 
+%\end{itemize}
+%
+
+\appendix
+
+\section{Proofs for Streaming Coresets}
 
@@
 
-\zk{need to finish the analysis for the above $K_k$..}
+\zk{need to finish the analysis for the above $K_k$.}
 \end{proof}
 
-\section{A Simple Algorithm for Kernel Density Estimation}
+\section{Table of Complexities for Common Classes}
 
-From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
-Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
-This bound is better when the $d > m$.
-More importantly though, there is a very simple and deterministic algorithm for computing the signs $\sigma$.
-Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
-$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
-Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
-$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
-where $\lambda$ is a scaling parameter.
-For simplicity, we assume that $K(x,x) \leq 1$ for all data points.
-Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.
+\newcommand{\ccc}[1]{\parbox}
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{|c|c|c|c|} \hline
+Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
+Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
+Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
+Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
+Gaussian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\lambda^2)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
+Laplacian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2/\lambda)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
+Positive Kernel Density 			& $f(x, q) = k(x,q)$ for any positive kernel $k$ and $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
 
-Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$.
-For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that
-$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
-Using this function $\phi$ our objective function becomes
-\[
-\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
-\]
-This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
-Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
-We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
-This is trivially true for $i=1$. 
-For another value assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
-
-\begin{eqnarray*}
-\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
-&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
-&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
-\end{eqnarray*}
-This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
-%
-%Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
-%The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
-%$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
-%This guarantees that 
-%$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$
-
-Using the framework above this provides a coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$.
-This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
-%\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
-%\zk{We actually ended up using the Radamacher complexity, at least for the bound.
-Namely, we used random signs.
-Perhaps there is a kernel for which it is easy to prove something better?
-One that comes to mind is apx low rank data.
-By low rank I mean in the kernel space, meaning the $\phi(x_j)$'s.
-To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$.
-Then, we use theory on the sum of unit vectors of low dimension giving $\sqrt{k}/\eps$ where $k$ is the dimension we got.
-In the worst case if the kernel matrix is isotropic we will get $k \approx n$ and gain nothing, but this way we can squeeze something from the data that wasn't squeezed before..
-We can take this further and look into the details of the proof that we can balance unit vectors to have a norm of $\sqrt{d}$ regardless of the number of vectors.
-The key in that proof is that by considering continuous $s_i$'s we can have the sum equal to zero while keeping only $d$ points with non $\{-1,1\}$ $s_i$'s.
-Consider a split of top $k$ and bottom rest directions.
-If we restrict the $s_i$'s to only have the sum to be zero in the top $k$ we get $k$ non integral $s_i$'s but possibly horrible performance on the bottom $k$.
-What if only restrict $d-2k$ and not $d-k$ points?
-Then we get some freedom in choosing the integer $s_i$'s.
-The bound on the bottom singular values can become smaller than the trivial one.}
-
-\section{Universal Coresets for Analytic Functions of Dot Products}
-
-We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or distance $\|q-x\|$.
-The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors $q$.
-By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
-It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
-
-We start with some notation and trivial properties. 
-For a vector $q \in \R^d$ let $q^{\otimes k}$ represent the $k$-dimensional tensor obtained from the outer product of $q$ with itself $k$ times.
-For a $k$ dimensional tensor with $d^k$ entries $X$ we consider the measure
-$\|X\|_{T_k} = \max_{q \in \R^d, \|q\|=1} \left| \langle X, q^{\otimes k}\rangle \right|$.
-\begin{fact}
-$\|X\|_{T_k}$ is a norm
-\end{fact}
-\begin{proof}
-We prove the claim directly from the definition of a norm.
-Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
-It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.
-For a scalar $a$, we clearly have by definition that
-$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
-$ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
-\max_q \left| \langle X, q^{\otimes k}\rangle \right| + \max_q\left| \langle Y, q^{\otimes k}\rangle \right| = \|X\|_{T_k} + \|Y\|_{T_k}$
-\end{proof}
-
-We are now ready for the lemma controlling all powers of inner products simultaneously.
-
-\begin{lemma}\label{uc}
-For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
-\end{lemma}
-\begin{proof}
-The proof will use Banaszczyk's theorem. 
-Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
-Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
-Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
-
-To use Banaszczyk's theorem we begin with defining our convex body.
-Define the norm $\|\psi\|_T$ of a vector $\psi$ as follows.
-Look at the first $d$ coordinates of $\psi$ as a vector $\psi_1$, the next $d^2$ coordinates of $\psi$ as a matrix $\psi_2$ the next $d^3$ coordinates as a three tensor $\psi_3$ etc.
-We define $\|\psi\|_T = \max_k \|\psi_k\|_{T_k} /\sqrt{\log(k)}$. 
-Here, $\|\cdot\|_{T_k}$ is the special spectral norm defined in the beginning of the section 
-The maximum over norms of subvectors is clearly a norm in itself, meaning that $\|\cdot \|_T$ is indeed a norm.
-It follows that  the set $\mathcal K  = \{\psi \; | \; \|\psi\|_T \le c\sqrt{d}\}$ is convex.
-
-We now need to show that the Gaussian measure of $\mathcal K$ is at least $1/2$. 
-That is, with probability at least $1/2$ a vector of random Gaussian entrees $g$ belongs to $\mathcal K$.
-Consider a random i.i.d.\ Gaussian Tensor $g_k \in \R^{d^k}$.
-
-A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
-The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
-Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$.
-%
-We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
-$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
-
-Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
-
-We are now ready to apply Banaszczyk's theorem. 
-There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
-Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$
-
-\begin{lemma} \label{lem:komlos anl}
-Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
-The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
-\[
-K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}
-\]
-For general $\|q\| \leq R$ we get
-\[
-K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}
-\]
-\end{lemma}
-\begin{proof}
-The proof follows from combining the above.
-$$
-\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
-$$
-By Lemma \ref{uc} we can find signs $\sigma$ such that 
-$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
-\end{proof}
-
-\begin{theorem}
-Let $\tilde{f}$ be an analytical one dimension function over $\R$.
-There exist a radius $R$ such that for $\|q\| \leq R$ the function family of functions $f_q(x) = \tilde{f}(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d})$
-\end{theorem}
-\begin{proof}
-Recall that for analytical functions $f$ we have 
-$$\left| \frac{d^k \tilde{f}}{dz^k}(z) \right|  \leq C^{k+1} k! $$
-for some constant $C$. Considering the taylor expansion of $\tilde{f}$ near zero we get that for $R < 1/C$, the sum
-$$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$$
-corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
-\end{proof}
-
-\begin{corollary}
-The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d})$.
-\end{corollary}
-
-Notice that by transforming $x$ to $\tilde{x} = (-x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$.
-This implies that our results for functions of $\ip{q,x}$ apply for functions of $\|q-x\|^2$.
-In particular we get
-\begin{corollary}
-The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d})$.
-\end{corollary}
-
-\end{proof}
+%Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ where  $q,x\in \R^d$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+%Hinge Regression     		& $f(x, q) = [1-q^T x]_+$ where  $q,x\in \R^d$							& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
+Linear Regression		& $f(x,q) = (z^Tq - y)^2$ where $x = (z\in\R^d,y\in \R)$ and $q\in \R^d$					& ?				& ? \\ \hline
+Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else. $q,x\in \R^d$					& ?				& ? \\ \hline
+Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
+Matrix Approximation  	& $f(x, q) = a_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
+\end{tabular}
+\caption{Example problems in machine learning and sketching that fall into this framework.}
+\end{center}
+\label{default}
+\end{table}%
 
@@
 In other words $\| \sum \sigma_i X_i\| = \| \operatorname{stack}( \sum \sigma_i \operatorname{flatten}(x_i x_i^T)) \| \le C \sqrt{d}$.
+
 \end{proof}
+
 The algorithm for finding the signs above is, unfortunately, not as simple as with kernels. 
@@
 
-\subsection{Streaming Graph Approximation}
+\section{Streaming Graph Approximation}
 Streaming graphs have received a lot of attention in the last several years \zk{cite something here \cite{}}. 
@@
 $|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
-
-\section{Linear Regression}
-
-%\section{Optimal Design of Experiments}
-%We discuss the problem of linear regression with mean squared error.
-In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
-%$$ \sum_i (w^Tx_i - y_i)^2 $$
-%In the field of optimal design of experiments, the labels are not given with the data.
-Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
-The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
-%
-%The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
-%$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
-%%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
-%%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
-%%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
-%%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-%
-%
-%One can show that for $w_B$,
-%$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
-%\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
-%
-%We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
-Something that is commonly practiced.
-Since we will solve the problem for the subset we choose in an optimal way for gaussian noise, we end up with an unbiased estimator for $w^*$.
-The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
-%$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-%This leads to the exact same objective as in column subset selection.
-Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
-Specifically we get that we can obtain a core-set of size
-%$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
-%For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
-I'm not sure what statements are known already.
-%
-%In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
-
-\section{Logistic Regression}
-The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
-This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
-
-In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
-They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
-Calling that matrix $A$, $A_{q,x} = K(q,x)$.
-They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound
-$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
-Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
-$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
-They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
-Now, back to our case.
-For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$.
-Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$.
-It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$.
-The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
-
-A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
-This is proven in \cite{tomczak1989banach}.
-In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
-
-%\paragraph{Reduction to the Kernel case}
-%This is really the Kernel density estimation problem with $K(x,y) = \ip{x,y}^2$.
-We might be able to squeeze a bit more due to the fact that $\phi(x) = xx^T$ is a very special $d \times d$ matrix: a rank $1$ matrix.
-That being said, a coreset of $1/\eps^2$ can be obtained by simply using the kernel technique.
-The special structure can either give better dependence on $\eps$ or exploit low rank structure e.g.\ if the vectors form a nearly rank $k$ matrix.
-
-%
-%\subsection{notes about row selection}
-%The problem is 
-%$$ \min_s \| \sum_i \sigma_i x_ix_i^T\| $$
-%where $\|x_i\| \leq 1$. Consider the following greedy approach: At point $x_i$, let
-%$$ C_i = \sum_{j<i} \sigma_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
-%We choose $\sigma_i = 1$ if $l_+ < l_i$, otherwise $\sigma_i=-1$.
-%
-%This approach can be shown to be better than random. Random will result in an answer of up to 
-%
-%Consider the following example. 
-%$$x_1=e_1, x_2=e_2*\eps, x_3=e_2, x_4=e_1/\sqrt{2} + e_2/\sqrt{2}$$
-%where $\eps \to 0$.
-We get that the covariance matrix after inserting $x_3$ has two eigenvalues of +1 and -1.
-Now when inserting $x_4$ we have to increase the magnitude of one of them and we exceed the limit of 1.
-%
-
-\section{Coreset for linear functions (based on $\gamma_2$ norm)}
-
-Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
-$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
-
-Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
-$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
-
-For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
-The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
-
-\begin{definition}
-For a matrix $A$,
-$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
-is the $\gamma_2$ norm of $A$. 
-\end{definition}
- \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
- $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
-
-\begin{lemma} \label{lem:powers}
-For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
-\end{lemma}
-\begin{proof}
-For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
-$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
-Furthermore, 
-$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
-Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
-\end{proof}
-
-\begin{lemma}
-Let $L:\R \to \R$ be a function that can be written as 
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
-with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
-$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
-\end{lemma}
-\begin{proof}
-This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
-\end{proof}
-
-This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
-In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
-\begin{corollary}
-For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
-\end{corollary}
-
-\begin{definition}
-For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
-$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
-\end{definition}
-In \cite{matouvsek2014factorization} they prove that 
-$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
-This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
-$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
-where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
-$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
-
-Let's discuss what this means.
-For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
-
-Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
-$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
-meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
-By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
-Then, for the matrix $A_{K,f_L}$ with
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
-we have 
-$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
-
-\begin{corollary}
-For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
-$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
-and
-$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
-\end{corollary}
-
-%\bibliographystyle{plain}
-\bibliography{density}
-
-\section{Appendix 1}
-For completeness we recap a result from \cite{barany2008}.
-\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
-For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
-\end{theorem}
-\begin{proof}
-Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
-This feasible region is not empty because it contains the origin. 
-Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
-$$
-\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
-$$
-The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
-The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
-Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
-\end{proof}
-
-Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
-The dimension of $x$'s is $d$ and of $y$'s is infinite.
-Both $\|x_i\|, \|y\| \leq 1$.
-However, the overall norm of the $y$'s is bounded $\sum \|y_i\|^2 \leq \rho n$.
-Naively we can ignore the $y$'s and get a bound on the norm of $\sqrt{d + \sqrt{\rho} n}$ or something like that.
-If $y$ is obtained as the low components of PCA we can squeeze some more.
-Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
-Let $\alpha^{(1)}$ be a feasible point.
-Let $\alpha^{(2)}$ be another feasible point that is restricted to being orthogonal to $\alpha^{(1)}$, and so on up to $\alpha^{(d)}$.
-For all these $\alpha$'s we have a bound of $2d$ to their rounding w.r.t to $x$.
-Now, for the $y$'s we can choose any one of these $\alpha$'s
-
-However, we can search for $\alpha \in [-1,1]^n$ minimizing
-
-%\section{Attempt at Cleaner Definitions}
-%Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
-%We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
-%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}\sigma_i f_i (x)$$  \el{need to double check the order here...}
-%
-%We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
-%Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
-%
-%In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
-%The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
-%Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
-%Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
-%
-%
-%In what follows, we subscript the function $f$ with its parametrization.
-%\begin{itemize}
-%\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
-%\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
-%\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
-%\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-%\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
-%Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
-%\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
-Here, like in Logistic Regression, $a$ is the example point multiplied by its label and $x$ is the weights of the linear classifier.
-%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
-Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
-For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-%\item Probably also good for matrix approximation when we get entry updates. 
-%\end{itemize}
-%
 

### 2019-01-02 komlos.tex
citation

@@
 By Lemma \ref{uc} we can find signs $\sigma$ such that 
-$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
+$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above, the lemma follows.
 \end{proof}
@@
 \begin{proof}
-By transforming $x$ to $\tilde{x} = (x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (-2q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$.
+By transforming $x$ to $\tilde{x} = (1, x, \|x\|^2)$ and $q$ to $\tilde{q} = (\|q\|^2, -2q, 1)$ we get $\ip{\tilde{x},\tilde{q}} = \|q-x\|^2$.
 Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$.
-The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$ apply for functions of $\|q-x\|^2$.
+The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$.
 \end{proof}
@@
 
-\section{Linear Regression}
+%\section{Linear Regression}
 
@@
 \begin{proof}
-First, recount Banaszczyk's theorem. 
+First, recount Banaszczyk's Theorem~\cite{Banaszczyk}.
 Let $\mathcal K$ be a convex body in $\R^d$ with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).

### 2019-01-02 komlos.tex
fixed stream proof

@@
 Recall that for analytic functions $f$ we have $\left| \frac{d^k f}{dz^k}(z) \right|  \leq C^{k+1} k! $
-for some constant $C$. Considering the taylor expansion of $f$ near zero. For $R < 1/C$, the sum
+for some constant $C$. Considering the taylor expansion of $f$ near zero, for $R < 1/C$ the sum
 $ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$
@@
 
-\begin{theorem}
+\begin{theorem} \label{thm:analytic2}
 Let $f:\R\rightarrow\R$ be analytic.
@@
 \begin{proof}
-By transforming $x$ to $\tilde{x} = (1, x, \|x\|^2)$ and $q$ to $\tilde{q} = (\|q\|^2, -2q, 1)$ we get $\ip{\tilde{x},\tilde{q}} = \|q-x\|^2$.
-Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$.
+By transforming $x$ to $\tilde{x} = (1, \sqrt{2}x, \|x\|^2)$ and $q$ to $\tilde{q} = (\|q\|^2, -\sqrt{2}q, 1)$ we get $\ip{\tilde{x},\tilde{q}} = \|q-x\|^2$.
+Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R+1$.
 The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$.
@@
 \begin{corollary}
-The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d}/m)$.
-This improves upon the recent result of \el{\cite{??}} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density.
-This resolves the open problem raised by \el{\cite{??}} and matches their lower bound.   
+The Komlos complexity of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
+This improves upon the recent result of \cite{DBLP:journals/corr/abs-1802-01751} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density, in the case where $\gamma$ is constant.
+For the constant $\gamma$ setting this resolves the open problem raised by \cite{DBLP:journals/corr/abs-1802-01751} and matches their lower bound.
 \end{corollary} 
+\begin{proof}
+W.l.o.g. the maximum distance $\|q-x\|$ is 1. The taylor series of $K$ becomes
+$$ \sum_{k=0}^\infty \frac{(-\gamma)^k}{k!} $$
+Plugging into the equation in the proof of Theorem~\ref{thm:analytic2} we get that the sum determining the constant is upper bounded by
+$$ \sum_{k=0}^\infty \frac{\gamma^{k}\sqrt{ k\log^3(k)}}{k!} = O\left((1+\gamma) \exp(\gamma)\right)$$
+\end{proof}
 %\end{proof}
@@
 We are however interested in a high probability bound.
-Specifically we would like to guarantee for $\delta_1,\delta_2 > 0$ that for any set of queries $Q$ the error is bounded by $\eps n$ w.p.\ $\delta_1|Q| + \delta_2$.
+Specifically we would like to guarantee for $\delta > 0$ that for any query $q$ the error is bounded by $\eps n$ w.p.\ at least $1-\delta$.
 To this end we consider a different analysis for the top and bottom layers.
-For the top layers, the length of the stream can be arbitrarily short so we will use the deterministic analysis as above.
+For the top layers, the stream can be arbitrarily short so we will use the deterministic analysis as above.
 For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
 
-The bottom layers will be those of height $h=0$ up to $h=H'$ with 
+The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
+\begin{equation} \label{eq:Htag_nh}
+ \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(1/(c_2 \delta \log(n)))
+\end{equation}
+for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
+
+According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
+$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta / \log(n) $$
+We can now union bound over all 
+$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
+and conclude that w.p.\ at least $1-\delta/2$
 \begin{equation} \label{eq:Htag}
-H' = \ceil{\log\left( \frac{n}{k\log\left(1/\left(c \delta_1 \delta_2 \log^3(n)\right)\right)} \right)}
+H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
 \end{equation}
-for some constant $c$ that will be determined later.
-
-According to Lemma~\ref{lem:compactor} we have for $ h\geq 0$ that irrespective of $q$,
-$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -O\left(\frac{n_{h}}{k \log^2(n)} \right) \right) = \delta_2 / H' $$
-for a sufficiently small constant $c$ in Equation~\eqref{eq:Htag}. 
-It follows by taking a union bound and noticing that $H' \leq \log(n)$ that irrespective of $q$ we have w.p. at least $1-\delta_2$ that 
-$$\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}$$
+and
+\begin{equation} \label{eq:nh small}
+\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
+\end{equation}
 
@@
 $$
-We now make use of the above union bound applied to the bound on $n_h$.
+We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
 Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
@@
 $$
-In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta_1)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
-$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta_1/(H'-h+1)^2$$
-and a union bound ensures that with probability at least $1-\delta_1$, for any fixed query $q$ it holds for all $h \leq H'$ that
-$$\left| \text{Err}_h(q) \right| \geq \eps_h n$$
+In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
+$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
+and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
+$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
 and 
@@
 
-We start by dealing with the setting where $K_k = \min\{d,k\}$ where $d$ is independent of $k$.
-We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$.
-Since $k_{H'} = k$ by using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
-$$\eps_h \leq \sqrt{\frac{2c \cdot K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'} k_{h}}} \cdot \sqrt{\frac{2^{H'} K_{H'}^2 \log(1/\delta_1)}{k_{H'} n}} = $$
+Let's proceed to bound the error on the top layers $H'+1$ to $H$.
+In these top layers we use a deterministic algorithm guaranteeing the stream is cut at least times 2 from layer to layer.
+We assign all top layers a budget of $k_h=k$ for the compactors.
+Since $2^{H+1} < n/k$ this gives a bound of
 $$
-\frac{K_k}{k} \cdot O\left( \sqrt{\frac{K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'}^2 k_{h}}}  \right)
+H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
 $$
-We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$
 $$
-\frac{K_h^2 k_{H'}\log(H'-h+1)}{2^{H'-h} K_{H'}^2 k_{h}} \leq \frac{d^2 k\log(H'-h+1)}{2^{H'-h} d^2 (2/3)^{H'-h}k} =
-\frac{\log(H'-h+1)}{ (4/3)^{H'-h}}
+O\left( \log \log(n/\delta) \right)
 $$
+leading to a bound of 
+$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
+and an overall bound of
+\begin{equation}
+|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
+\end{equation}
+
+We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
+Recall that we aim to deal with two settings.
+In the first $K_k=\min\{d,k\}$ and in the second $K_k=\min\{d\sqrt{k}, k\}$.
+In both cases  $d$ is independent of $k$.
+We start by dealing with the first scenario.
+
+We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. Since $k_{H'} = k$ by using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
+\begin{align*}
+\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
+  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right)  \\
+    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
+\end{align*}
+We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq d$
+$$
+\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{d^2 k}{2^{H'-h} d^2 (2/3)^{H'-h}k} =
+(3/4)^{H'-h}
+$$
+For $k_h \leq d$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq d/k$, meaning that $2^{H'-H''} \geq k/d$. For such $h$ we get
+\begin{align*}
+ \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} d^2 } \right) =  \\
+    	   &  O\left( \frac{ k_h k}{2^{H''-h} kd } \right) = & k_h \leq d\\
+	   &  O\left( (1/2)^{H''-h}   \right) 
+\end{align*}
+
 If follows that 
 $$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(d/k) $$
-and we have a bound of $O(d/k)$ for the bottom layers.
+translating to an overall bound for the error of
+$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(d/k)  \right)$$
+The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
+The top layers require $O(\log\log(n/\delta)k)$ memory.
+If follows that by setting $k=c d \log\log(n/\delta) / \eps$ for sufficiently large $c$, the error is bounded by $\eps n$ w.p.
+$1-\delta$ and the overall memory requirement is
+$$ O\left( \log \log(n/\delta)^2 (d/\eps)  \right) $$
 
-For the top layers we set $k_h=k$ and obtain the deterministic bound of 
-$$ \sum_{h=H'+1}^H \text{Err}_h(q) \leq (H-H')(d/k)n $$
-Since we $n_{h+1} \leq n_h$ for $h \geq H'$ we get that $H-H' \leq \log(n/(kn_{H'}))$.
-According to our analysis above we are in an event (of probability $1-\delta_2$) where $n_{H'} \leq 3 \cdot n/2^{H'}  $ meaning that
-$$ n/(kn_{H'}) = O\left((\log\left(1/\left(c \delta_1 \delta_2 \log^3(n)\right)\right)\right) $$
-leading to the bound of 
-$$ \sum_{h=H'+1}^H \text{Err}_h(q) \leq O\left( \log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right)(d/k)n \right)$$
-The latter is the bound for the total sum of errors $\text{Err}(q)$ as well.
-
-To conclude the case of $K_k=d$ we obtain an error of 
-$$O\left( \log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right)(d/k)n \right)$$
-by using $O(k\log \log\left( 1/\left( \delta_1\delta_2\log(n) \right)\right))$ memory.
-The memory analysis follows from a trivial bound to the upper layers, and noticing that for the smaller layers, all layers with $k=2$ can be implemented in $O(1)$ memory by uniformly sampling.
-By setting $\delta=\delta_1=\delta_2 < 1/\log(n)$ we get that for
-$$ k=O(d\log\log(1/\delta)/\eps) $$
-the overall error is bounded by $\eps n$ and the memory is bounded by 
-$$ O(d\log\log(1/\delta)^2/\eps) $$
-
-Let's now consider the case where $K_k = d\sqrt{k}$ with $d$ independent of $k$. Here, we set $k_{H'}=k$ and $k_h=2$ for all $h<H'$.
-
-\zk{need to finish the analysis for the above $K_k$.}
+We are now ready for the case where $K_k = d\sqrt{k}$.
+We assume that $\sqrt{k} > d$ as otherwise we can result to a random sample.
+Here we set $H'' = H' - \ceil{\log_2(k/d^2)}$.
+For $h \geq H''$ we set $k_h=k$ and for $k \leq H''$ we set $k_h=2$.
+For $k \leq H''$ we have
+\begin{align*}
+\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ k_h=k=2 \\
+  	   &  O\left( \sqrt{2^{h-H'}} \right)  = & 2^{H'-H''} \geq k/d^2 \\
+    	   &  O\left(\frac{\sqrt{k}}{d} \sqrt{2^{h-H''}} \right)  
+\end{align*}
+and 
+$$ \sum_{h=0}^{H''} \eps_h= O(\sqrt{k}/d) $$
 \end{proof}
+For $H'' \leq h \leq H'$ we use the deterministic algorithm and its error bound of
+$$\sum_{h=H''}^{H'} |\text{Err}_h(q)| \leq O(\log(k/d^2) d/\sqrt{k})$$
+Summing the errors of all layers we obtain a bound of
+$$|\text{Err}(q)| \leq \frac{d}{\sqrt{k}} \cdot O(\log(k/d^2) + \log\log(n/\delta))$$
+The memory requirement is $k \cdot O(\log(k/d^2) + \log\log(n/\delta))$ hence by setting 
+$$k \approx \frac{d^2\left(\log^2(1/\eps)+ \log^2\log(n/\delta) \right)}{\eps^2}$$ 
+we get a bound of $\eps n$ for the error and a memory usage of 
+$$ O\left( \frac{d^2\left( \log^3(1/\eps) + \log^3\log(n/\delta) \right)}{\eps^2}\right) $$
 

### 2019-01-03 komlos.tex
fixed streaming

@@
 \begin{equation} \label{eq:Htag_nh}
- \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(1/(c_2 \delta \log(n)))
+ \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
 \end{equation}
@@
 According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
-$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta / \log(n) $$
+$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
 We can now union bound over all 
@@
 Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
 $$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
@@
 and an overall bound of
-\begin{equation}
+\begin{equation} \label{eq:err total}
 |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
@@
 
-We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. Since $k_{H'} = k$ by using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
+We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
 \begin{align*}
 \eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
-  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right)  \\
+  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
     	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
@@
 
-We are now ready for the case where $K_k = d\sqrt{k}$.
-We assume that $\sqrt{k} > d$ as otherwise we can result to a random sample.
-Here we set $H'' = H' - \ceil{\log_2(k/d^2)}$.
-For $h \geq H''$ we set $k_h=k$ and for $k \leq H''$ we set $k_h=2$.
-For $k \leq H''$ we have
+We are now ready for the case where $K_k = \min\{k, d\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
 \begin{align*}
-\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ k_h=k=2 \\
-  	   &  O\left( \sqrt{2^{h-H'}} \right)  = & 2^{H'-H''} \geq k/d^2 \\
-    	   &  O\left(\frac{\sqrt{k}}{d} \sqrt{2^{h-H''}} \right)  
+\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
+  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
 \end{align*}
 and 
-$$ \sum_{h=0}^{H''} \eps_h= O(\sqrt{k}/d) $$
+$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
+Plugging this to the overall error in Equation~\eqref{eq:err total} we get
+$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)d + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)d }{\sqrt{k}}  \right) $$
+
+Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
+$$k \approx \frac{d^2 \log^2\log(n/\delta)}{\eps^2}$$ 
+we get a bound of $\eps n$ for the error and a memory usage of 
+$$ O\left( \frac{d^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
 \end{proof}
-For $H'' \leq h \leq H'$ we use the deterministic algorithm and its error bound of
-$$\sum_{h=H''}^{H'} |\text{Err}_h(q)| \leq O(\log(k/d^2) d/\sqrt{k})$$
-Summing the errors of all layers we obtain a bound of
-$$|\text{Err}(q)| \leq \frac{d}{\sqrt{k}} \cdot O(\log(k/d^2) + \log\log(n/\delta))$$
-The memory requirement is $k \cdot O(\log(k/d^2) + \log\log(n/\delta))$ hence by setting 
-$$k \approx \frac{d^2\left(\log^2(1/\eps)+ \log^2\log(n/\delta) \right)}{\eps^2}$$ 
-we get a bound of $\eps n$ for the error and a memory usage of 
-$$ O\left( \frac{d^2\left( \log^3(1/\eps) + \log^3\log(n/\delta) \right)}{\eps^2}\right) $$
 

### 2019-01-03 komlos.tex
sorting main body

@@
 \renewcommand{\Pr}{\operatorname{Pr}}
+
+\newcommand{\komconstant}{c}
 
@@
 For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O\left(c\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+$$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
+whose error is at most $\eps n$ and failure probability at most $\delta$.
 For $\delta=0$ this results in a deterministic algorithm.
@@
 
-\begin{theorem}
+\begin{theorem} \label{thm:streaming2}
 For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$O\left(c\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
+$$O\left(c\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
+whose error is at most $\eps n$ and failure probability at most $\delta$.
 For $\delta=0$ this results in a deterministic algorithm.
@@
 
-\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
-Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
+%
+%\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
+%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
 The streaming algorithm operates as follows.
@@
 After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
-
-The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor. For a query $q$ we analyze the error
-$$\text{Err}(q) = \sum_{h=0}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \ .$$
-Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
+%
+%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor. For a query $q$ we analyze the error
+%$$\text{Err}(q) = \sum_{h=0}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \ .$$
+%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
 The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
@@
 Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
-
-To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
-$$ \text{Err}(q) \leq \rho(k) \log_2(n/k) n $$
-
-If however, we are interested in a smaller sketch with high probability of success of $1-\delta$, we decompose the error to two components
-$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
- Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later.
+%
+%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+%$$ \text{Err}(q) \leq \rho(k) \log_2(n/k) n $$
+%
+%If however, we are interested in a smaller sketch with high probability of success of $1-\delta$, we decompose the error to two components
+%$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
+% Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later.
 Notice that the right summand contains roughly $\log(1/\delta)$ random variables.
@@
 We thus set $k_h=k$ for $h > H'$ and use the bound
-$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
-Now, for the bottom layers we use Chernoffs bound
-$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
-$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$
-
-\zk{$n_h$ being random is a problem. The weight of the stream might increase with time. The analysis now works for a completely balanced case }
-Consider the sum in the denominator. 
-$$ \sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} = O(\sum_{h=0}^{H'} 2^{2h} \rho(k_h)^2 k_h n_h ) $$
-Since $n_h \leq n_{h-1}/2$ and we have $k_h \leq k$ we have 
-$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2  ) $$
-Now, if $\rho(k_h) \geq 1/\sqrt{k_h}$ we set $k_h = 2$ for all $h \leq H'$ and obtain
-$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h  ) = O(n^2/ (k \log(1/\delta))) $$
-and we get
-$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) \right)   \right) $$
-Hence, by setting $k \geq c/\eps^2$ for sufficiently large constant $c$ the probability is upper bounded by $\delta$.
-
-Now, for $\rho(k) < 1/\sqrt{k}$ we have $\eta(k) = \rho(k)^2 k = o(1)$.
+%$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
+%Now, for the bottom layers we use Chernoffs bound
+%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
+%$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$
+%
+%\zk{$n_h$ being random is a problem. The weight of the stream might increase with time. The analysis now works for a completely balanced case }
+%Consider the sum in the denominator. 
+%$$ \sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} = O(\sum_{h=0}^{H'} 2^{2h} \rho(k_h)^2 k_h n_h ) $$
+%Since $n_h \leq n_{h-1}/2$ and we have $k_h \leq k$ we have 
+%$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2  ) $$
+%Now, if $\rho(k_h) \geq 1/\sqrt{k_h}$ we set $k_h = 2$ for all $h \leq H'$ and obtain
+%$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h  ) = O(n^2/ (k \log(1/\delta))) $$
+%and we get
+%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) \right)   \right) $$
+%Hence, by setting $k \geq c/\eps^2$ for sufficiently large constant $c$ the probability is upper bounded by $\delta$.
+%
+%Now, for $\rho(k) < 1/\sqrt{k}$ we have $\eta(k) = \rho(k)^2 k = o(1)$.
 We can exploit that to allow for $k = o(1/\eps^2)$.
@@
 Also, extending the analysis to them is a purely technical exercise} use $k_h = \max(2, \ceil{(2/3)^{H'-h}k})$, leading to a bound of
-$$\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2 \leq \sum_{h=0}^{H'} 2^h \eta(k) \cdot (3/2)^{H'-h} = (3/2)^{H'} \eta(k) \sum_{h=0}^{H'} (4/3)^h \leq  $$
-$$(3/2)^{H'} \eta(k) \cdot (4/3)^{H'} \cdot 3 = 3 \cdot 2^{H'} \eta(k) = O(\eta(k)n/(k\log(1/\delta))$$
-Plugging this in the probability bound gives
-$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) / \eta(k) \right)   \right) = $$
-$$ \exp \left( -O\left( \eps^2 \log(1/\delta) / \rho(k)^2 \right)   \right) $$
-Hence, setting $k$ large enough so that $\rho(k) \leq c\eps$ for some universal constant $c$ leads to the required bound.
-
-In particular for $\rho(k) = O(1/k)$ we see that $k=1/\eps$ suffices, for general $p>1/2$ with $\rho(k) = k^{-p}$ we require $k=\eps^{-1/p}$.
-
-Now, consider the overall error and memory of the entire process.
+%$$\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2 \leq \sum_{h=0}^{H'} 2^h \eta(k) \cdot (3/2)^{H'-h} = (3/2)^{H'} \eta(k) \sum_{h=0}^{H'} (4/3)^h \leq  $$
+%$$(3/2)^{H'} \eta(k) \cdot (4/3)^{H'} \cdot 3 = 3 \cdot 2^{H'} \eta(k) = O(\eta(k)n/(k\log(1/\delta))$$
+%Plugging this in the probability bound gives
+%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) / \eta(k) \right)   \right) = $$
+%$$ \exp \left( -O\left( \eps^2 \log(1/\delta) / \rho(k)^2 \right)   \right) $$
+%Hence, setting $k$ large enough so that $\rho(k) \leq c\eps$ for some universal constant $c$ leads to the required bound.
+%
+%In particular for $\rho(k) = O(1/k)$ we see that $k=1/\eps$ suffices, for general $p>1/2$ with $\rho(k) = k^{-p}$ we require $k=\eps^{-1/p}$.
+%
+%
+%Now, consider the overall error and memory of the entire process.
 For the bottom layers, for any $\rho(k)$ we require $O(k+H')=O(k+\log(n))$ memory.
@@
 The top layers require $O(\log\log(1/\delta)k)$ memory leading to a total memory usage of $O(\log\log(1/\delta)k)$.
-
-The error for the bottom layers is $O(\min\{\rho(k), 1/\sqrt{k}\} n)$.
+%
+%The error for the bottom layers is $O(\min\{\rho(k), 1/\sqrt{k}\} n)$.
 The error of the top layers is $O(\log\log(1/\delta) \rho(k) n)$, meaning that the overall error is $O(\log\log(1/\delta) \rho(k) n)$.
-
-Hence, if we aim for an error of $\eps n$ w.p.\ $1-\delta$ we set $k$ large enough such that $\rho(k) \leq c \eps / \log\log(1/\delta)$.
+%
+%Hence, if we aim for an error of $\eps n$ w.p.\ $1-\delta$ we set $k$ large enough such that $\rho(k) \leq c \eps / \log\log(1/\delta)$.
 Denoting by $\rho^{\dagger}$ the inverse function to $\rho$ this leads to a total memory requirement of
-$$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
-
-\end{proof}
-
+%$$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
+%
+%\end{proof}
 %
 %
+%%
+%%
+%%
+%%
+%%
+%%
+%%
+%%
+%%
+%%
+%%
 %
 %
-%
-%
-%
-%
-%
-%
+%\subsubsection{take 3}
 %
 
-\subsubsection{take 3}
-
-\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
+\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
 Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
@@
 $$
-In particular, for $\eps_h = \sqrt{\frac{c 2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}}$ for some sufficiently large constant $c$ it holds that
+In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
 $$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
@@
 Recall that we aim to deal with two settings.
-In the first $K_k=\min\{d,k\}$ and in the second $K_k=\min\{d\sqrt{k}, k\}$.
-In both cases  $d$ is independent of $k$.
+In the first $K_k=\min\{\komconstant,k\}$ and in the second $K_k=\min\{\komconstant \sqrt{k}, k\}$.
+In both cases  $\komconstant$ is independent of $k$.
 We start by dealing with the first scenario.
@@
 \end{align*}
-We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq d$
+We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
 $$
-\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{d^2 k}{2^{H'-h} d^2 (2/3)^{H'-h}k} =
+\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
 (3/4)^{H'-h}
 $$
-For $k_h \leq d$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq d/k$, meaning that $2^{H'-H''} \geq k/d$. For such $h$ we get
+For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
 \begin{align*}
- \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} d^2 } \right) =  \\
-    	   &  O\left( \frac{ k_h k}{2^{H''-h} kd } \right) = & k_h \leq d\\
+ \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
+    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
 	   &  O\left( (1/2)^{H''-h}   \right) 
@@
 If follows that 
-$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(d/k) $$
+$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
 translating to an overall bound for the error of
-$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(d/k)  \right)$$
+$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
 The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
 The top layers require $O(\log\log(n/\delta)k)$ memory.
-If follows that by setting $k=c d \log\log(n/\delta) / \eps$ for sufficiently large $c$, the error is bounded by $\eps n$ w.p.
+If follows that by setting $k= O\left(\komconstant \log\log(n/\delta) / \eps\right)$ the error is bounded by $\eps n$ w.p.
 $1-\delta$ and the overall memory requirement is
-$$ O\left( \log \log(n/\delta)^2 (d/\eps)  \right) $$
+$$ O\left( \log \log(n/\delta)^2 (\komconstant/\eps)  \right) $$
 
-We are now ready for the case where $K_k = \min\{k, d\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
+We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
 \begin{align*}
@@
 Plugging this to the overall error in Equation~\eqref{eq:err total} we get
-$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)d + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)d }{\sqrt{k}}  \right) $$
+$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
 
 Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
-$$k \approx \frac{d^2 \log^2\log(n/\delta)}{\eps^2}$$ 
+$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
 we get a bound of $\eps n$ for the error and a memory usage of 
-$$ O\left( \frac{d^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
+$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
 \end{proof}

### 2019-01-06 komlos.tex
before merge

--- 2019-01-02 komlos.tex
@@
 \begin{definition}
-Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$ uniformly. 
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$ uniformly at random. 
 The Rademacher complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
@@
 
-%\begin{theorem}
-%Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
-%There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
-%$$
-%\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
-%$$
-%\end{theorem}
-%\begin{proof}
-%By halving the points repeatedly \el{TODO}.
-%\end{proof}
 \subsection{General Framework for Coresets}
-Consider the function $F = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}$.
-We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+Consider the function $F = \sum_{i=1}^{m} f(x_i,q)$ and the error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $\tilde F(q) = F(q) + E(q) =  \sum_{i | \sigma_i=1} 2f(x_i,q)$ 
+or alternatively $\tilde F(q) = F(q) - E(q) = \sum_{i | \sigma_i=-1} 2f(x_i,q)$.
+We have that $\tilde F(q)$ is an approximation for $F(q)$ obtained by a coreset of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
 %
@@
 \begin{fact}
-For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
-$O(c/\eps)$ whose error is at most $\eps n$.
+Let $\F$ be a function family with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$.
+Let $F(q) = \sum_{i=1}^{n}f_i(q)$ where $f_i \in \F$.
+There exists a coreset for $F$ of size $k = O(c/\eps)$ whose error is at most $\eps n$.
 \end{fact}
 \begin{fact}
-For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
-$O(c/\eps^2)$ whose error is at most $\eps n$.
+Let $\F$ be a function family with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$.
+Let $F(q) = \sum_{i=1}^{n}f_i(q)$ where $f_i \in \F$.
+There exists a coreset for $F$ of size $k = O(c/\eps^2)$ whose error is at most $\eps n$.
 \end{fact}
 
-\noindent Proving both facts is trivial. 
+\noindent Proving both facts is trivial and known in the folklore as ``the halving trick". 
 At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = \sqrt{2n}$.
-Note that the sum of errors is asymptotically dominated by last iterations. 
+Then, repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = \sqrt{2n}$.
+Note that the sum of errors is asymptotically dominated by last iteration. 
 Halting the compression at $\Theta(c/\eps)$ or $\Theta(c/\eps^2)$ items respectively achieves the goal.
@@
 \subsection{General Framework for Sketching}
-
-The high level idea is the following. 
-Consider a stream of the data points $x_i$. 
-We maintain a buffer that can hold up to $m$ points.
-Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
-The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
-This is made formal with the following definitions:
+We claim that low Komlos complexity implies concise streaming mergeable coresets. 
+This assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
+A trivial way to obtain such a construction is known as the merge-reduce trick \el{\cite{??} Har Peled?}.
+\el{What do we get from merge-reduce here? $\log(n)/\eps^2$ or $\log^2(n)/\eps^2$? Is it like MRL?)}
+The following theorems claim that a better construction is also possible.
 
 %
-In what follows, we prove the following.
+%of function family $\F$ is low, 
+%and one has an 
+%
+%The high level idea is the following. 
+%Consider a stream of the data points $x_i$. 
+%We maintain a buffer that can hold up to $m$ points.
+%Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
+The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
+%This is made formal with the following definitions: 
+%
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists a fully-mergeable streaming coreset algorithm of size 
 $O\left(c\log^2\left(\min(n, \log(1/\delta)) \right)/\eps\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \begin{theorem}
-For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset algorithm of size 
 $O\left(c\log^3\left(\min(n, \log(1/\delta)) \right)/\eps^2\right)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 \end{theorem}
+
+The proofs of the above two theorems are quite technical and not very illuminating.
+Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
 %

### 2019-01-07 komlos.tex
edits

--- 2019-01-03 komlos.tex
@@
 \[
-R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f \in \F}  \sum_{i=1}^{m}\sigma_i f(x_i)
+R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f \in \F}  \left| \sum_{i=1}^{m}\sigma_i f(x_i) \right|
 \]
@@
 %
+In other words, the Radamacher complexity of a family function $\F$ measures how much a function in the family can skew the values when weighted with random signs.
+The Komlos complexity measures the ability of the family function to skew an adversarial set of signs.
+
 \begin{definition}
@@
 See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
-We claim that $K_m$ is the measure more suitable for active learning, for creating coresets, and for creating mergeable sketches.
+We claim that $K_m$ is the measure more suitable for \zk{I think we should remove `active learning' from the list} creating coresets, and for creating mergeable sketches.
 
@@
 It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We show later that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+
+ \zk{I actually am still having problems with justifying the name Komlos complexity.
+It might as well be called Banaszczyk's complexity or simply discrepancy complexity.
+In particular if you could prove Komlos' conjecture it wouldn't affect any of our results, nor simplify our proofs..
+Either way, below is my suggested motivation for the definition}
+To understand the motivation of the the Komlos Complexity, consider the following informal explanation of Radamacher Complexity applied to ML problems.
+In this ML problem there exists a distribution over $(x,y)$ pairs where we aim to predict $y$ given $x$.
+Our goal is to find a predictor from a family of prediction functions that suffers the least loss.
+A predictor maps to a loss value on each $x,y$ pair so we can discuss the problem of finding a function $f$ from a family $\F$ minimizing $\E_{x,y} f(x,y)$ where $f$ is the loss associated with the corresponding predictor on the $x,y$ pairs.
+Having a low Radamacher complexity means that if we sample $m$ pairs, split them into two uniformly at random and find the function $f$ minimizing the loss over the first half, the loss over the second half is bounded.
+This translates to a generalization bound stating that the function $f$ minimizing the loss over a uniform random sample of $(x,y)$ pairs, will perform well on the entire distribution.
+In other words, the Radamacher complexity gives a guarantee for the distribution loss of the minimizer of a finite set of pairs chosen uniformly at random.
+
+Coming back to Komlos Complexity, having the ability to choose the signs in a non-uniform way lets us choose a subset of pairs $(x,y)$ such that the minimizer $f$ over the subset is guaranteed to have (roughly) the same performance on the entire set.
+This allows us to obtain a guarantee for the distribution loss of a minimizer of a finite set of pairs chosen in an adaptive way to the family function $\F$.
+This set is in fact a core-set and the Komlos complexity helps us determine that possible size of a coreset.
+The tradeoff of considering a coreset vs.\ a random sample is that on one hand, it is clearly much simpler to obtain a random sample.
+On the other hand we will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
+This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
 
@@
 \subsection{General Framework for Coresets}
-Consider the function $F = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}$.
+In what follows it will be convenient to represent the function family as a family of vectors representing the functions.
+The vector family will be denoted as $Q$, where we use $q$ to denote a single vector corresponding to a function.
+We a universal function $f$ such that $f(x,q)$ corresponds to the value of the function matching $q$ when applied to $x$.
+We will assume from hereon that for any $x,q$ $|f(x,q)| \leq 1$; this allows to simplify the presentation.
+Our results can extend to $|f(x,q)| \leq R$ and will have dependencies on the bound $R$.
+Achieving these bounds is a purely technical task that we defer for the sake of readability.
+
+Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}(q)$.
 We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
@@
 Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
-A function is sketch-able if $K_m(\F) = O(m^\gamma)$ for any constant $\gamma \in [0,1)$.
+A function is sketch-able if $K_m(\F) = o(m)$.
 Typically we see that $K_m(\F) = O(c/m)$ or $K_m(\F)= c/\sqrt{m}$ for some $c$ which does not depend on $m$.
@@
 For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
-$O(c/\eps^2)$ whose error is at most $\eps n$.
+$O(c^2/\eps^2)$ whose error is at most $\eps n$.
 \end{fact}
@@
 At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = \sqrt{2n}$.
-Note that the sum of errors is asymptotically dominated by last iterations. 
-Halting the compression at $\Theta(c/\eps)$ or $\Theta(c/\eps^2)$ items respectively achieves the goal.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
+Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
+Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
 
@@
 
-\subsection{General Framework for Sketching}
+\subsection{General Framework for Sketching} \label{sec:sketch}
 
@@
 For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-$$O\left(c\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
+$$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
 whose error is at most $\eps n$ and failure probability at most $\delta$.
@@
 
-\section{The Complexity of Analytic Functions of Dot Products}
+\section{The Complexity of Analytic Functions of Dot Products} \label{sec:analytic}
 
-We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or distance $\|q-x\|$.
-The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors $q$.
+Now that we proved the usefulness of the Komlos Complexity we move to upper bound it for interesting family functions.
+We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or Euclidean distance $\|q-x\|$.
+
+The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors\footnote{We Assume that $\|x\|,\|q\| \leq 1$ for ease of presentation.
+As above our results extend to generic bounds on the radius of $q$} $q$.
 By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
@@
 For a scalar $a$, we clearly have by definition that
-$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we clearly have
+$\|aX\|_{T_k} = |a|\|X\|_{T_k}$.  Lastly, by the max definition we  have
 $ \|X+Y\|_{T_k} =  \max_q \left| \langle X+Y, q^{\otimes k}\rangle \right| \leq 
@@
 \begin{lemma}\label{uc}
-For any set of vectors $x_i \in \R^d$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
+For any set of vectors $x_i \in \R^d$ with $\|x_i\| \leq 1$ there exist a set of signs $\sigma_i$ such that for all $k$ simultaneously $\left\| \sum_i \sigma_i x_i^{\otimes k} \right\|_{T_k} \le O(\sqrt{d k\log^{3}{k}})$ (the $3$ power of the term $\log(k)$ can be reduced to any constant power larger than $2$).
 \end{lemma}
 \begin{proof}
-The proof will use Banaszczyk's theorem. 
+The proof will use Banaszczyk's theorem \cite{Banaszczyk}. 
 Let $\mathcal K$ be a convex body in Euclidean space with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ when $g$ is i.i.d.\ Gaussian).
-Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| =O(1)$. 
+Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| \leq 1$. 
 Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
@@
 The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
-Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$.
+Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$, where $\operatorname{flat}(g_k)$ is the flattening of the tensor into a one dimensional vector.
 %
 We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
-$$\psi(x) = [x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots]$$
+$$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
 
@@
 There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
-Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$
+Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that 
+$$\max_k \frac{\|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k}}{\sqrt{k \log^{3}(k)}} \le O\left( \sqrt{d} \right)$$
 \end{proof}
@@
 $$
-\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
+\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \ip{ x_i,q}^k =  \sum_k \alpha_k  \ip{  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}} \le $$
+$$\sum_k |\alpha_k| \cdot \left\| \sum_i \sigma_i x_i^{\otimes k}\right\|_{T_k} \cdot \|q\|^k
 $$
 By Lemma \ref{uc} we can find signs $\sigma$ such that 
-$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above, the lemma follows.
+$\left\| \sum_i \sigma_i x_i^{\otimes k}\right\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above, the lemma follows.
 \end{proof}
@@
 \begin{theorem} \label{thm:analytic2}
-Let $f:\R\rightarrow\R$ be analytic.
-There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq \sqrt{R}$, has Komlos complexity of $O(\sqrt{d}/m)$.
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 By transforming $x$ to $\tilde{x} = (1, \sqrt{2}x, \|x\|^2)$ and $q$ to $\tilde{q} = (\|q\|^2, -\sqrt{2}q, 1)$ we get $\ip{\tilde{x},\tilde{q}} = \|q-x\|^2$.
-Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R+1$.
+Moreover, $\|q\| \le R$ gives $\|\tilde q\| \le R^2+1$.
 The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$.
@@
 The Komlos complexity of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
+\end{corollary} 
 This improves upon the recent result of \cite{DBLP:journals/corr/abs-1802-01751} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density, in the case where $\gamma$ is constant.
 For the constant $\gamma$ setting this resolves the open problem raised by \cite{DBLP:journals/corr/abs-1802-01751} and matches their lower bound.
-\end{corollary} 
+
 \begin{proof}
@@
 
-From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
-Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
-This bound is better when $d > m$.
+From section \ref{sec:analytic} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
+The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently.
+Here, we provide a computationally efficient bound that can be achieved with a straightforward algorithm of complexity $O(m^2)$.
+Together with the results of Section~\ref{sec:sketch} this provides an efficient sketching algorithm for Kernel Density Estimation.
+We show that for any positive kernel $K_m = O(1/\sqrt{m})$.
+This bound is superior to that of the previous section when $d > \sqrt{m}$.
 More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
@@
 
-Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$.
+The algorithm we proposed works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
+\begin{theorem}
+The algorithm above achieves a set of signs $\sigma_1,\ldots,\sigma_m$ such that for any $q$,
+$$ \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q) \leq \sqrt{m} $$
+\end{theorem}
+
+\begin{proof}
+%Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$. 
 For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
@@
 \]
-This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
-Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
-We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
-This is trivially true for $i=1$. 
-Assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
-
+Since $\|\phi(q)\| \leq 1$ we reduced the problem to bounding the norm of $ \sum_{i=1}^m \sigma_i \phi(x_i) $.
+%
+%This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
+%Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
+We will show by induction on $i$ that 
+$$\left\| \sum_{j=1}^i \sigma_j \phi(x_j) \right\|^2 \le \sum_{j=1}^i \left\|\phi(x_j)\right\|^2 \leq i$$
+This is trivially true for $i=1$ since $\|\phi(x)\| \leq 1$. 
+%Assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
+Using our induction assumption we get
 \begin{eqnarray*}
-\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
-&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
-&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
+\left\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\right\|^2 =& \left\|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\right\|^2 + \|\phi(x_i)\|^2 + 2\ip{ \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)} \leq & \text{induction assumption}\\
+& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) = & \text{choice of } \sigma_i \\
+& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2 \\
 \end{eqnarray*}
-This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
+%\begin{eqnarray*}
+%\left\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\right\|^2 &=& \left\|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\right\|^2 + \|\phi(x_i)\|^2 + 2\ip{ \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)} \\
+%&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
+%&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
+%\end{eqnarray*}
+%This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
+\end{proof}
 
@@
 This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+Along with an $\eps$-net argument, it also gives rise to a streaming algorithm for kernel density estimation with a memory requirement of $O\left(\log\left(d\log(1/\eps)\right)^3/\eps^2\right)$ vectors.
+
+\paragraph{Note} The Theorem above provides an upper bound of $\sqrt{m}$ for the sign discrepancy.
+One can in fact construct an example where this upper bound is indeed what the algorithm achieves.
+However, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
+We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
 
@@
 
-\section{Logistic Regression}
-The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
-This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
-
-In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
+%\section{Logistic Regression}
+%The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
+%This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
+%
+%In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
 They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
@@
 They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound
-$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
-Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
-$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
-They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
+%$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
+%Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
+%$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
+%They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
 Now, back to our case.
@@
 The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
-
-A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
+%
+%A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
 This is proven in \cite{tomczak1989banach}.
 In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
-
-\section{Coreset for linear functions (based on $\gamma_2$ norm)}
-
-Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
-$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
-
-Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
-$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
-
-For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
+%
+%
+%
+%
+%
+%\section{Coreset for linear functions (based on $\gamma_2$ norm)}
+%
+%Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
+%$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
+%
+%Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
+%$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
+%
+%For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
 The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
-
-\begin{definition}
-For a matrix $A$,
-$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
-is the $\gamma_2$ norm of $A$. 
-\end{definition}
- \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
- $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$.
-
-\begin{lemma} \label{lem:powers}
-For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
-\end{lemma}
-\begin{proof}
-For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
-$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
-Furthermore, 
-$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
-Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
-\end{proof}
-
-\begin{lemma}
-Let $L:\R \to \R$ be a function that can be written as 
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
-with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
-$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
-\end{lemma}
-\begin{proof}
-This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
-\end{proof}
-
-This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
+%
+%\begin{definition}
+%For a matrix $A$,
+%$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
+%is the $\gamma_2$ norm of $A$. 
+%\end{definition}
+% \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
+% $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$. 
+%
+%
+%\begin{lemma} \label{lem:powers}
+%For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
+%\end{lemma}
+%\begin{proof}
+%For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
+%$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
+%Furthermore, 
+%$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
+%Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
+%\end{proof}
+%
+%\begin{lemma}
+%Let $L:\R \to \R$ be a function that can be written as 
+%$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
+%with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
+%$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
+%\end{lemma}
+%\begin{proof}
+%This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
+%\end{proof}
+%
+%This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
 In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
-\begin{corollary}
-For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
-\end{corollary}
-
-\begin{definition}
-For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
-$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
-\end{definition}
-In \cite{matouvsek2014factorization} they prove that 
-$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
-This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
-$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
-where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
-$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
-
-Let's discuss what this means.
+%\begin{corollary}
+%For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
+%\end{corollary}
+%
+%\begin{definition}
+%For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
+%$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
+%\end{definition}
+%In \cite{matouvsek2014factorization} they prove that 
+%$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
+%This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
+%$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
+%where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
+%$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
+%
+%Let's discuss what this means.
 For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
-
-Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
-$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
-meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
+%
+%Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
+%$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
+%meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
 By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
 Then, for the matrix $A_{K,f_L}$ with
-$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
-we have 
-$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
-
-\begin{corollary}
-For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
-$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
-and
-$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
-\end{corollary}
+%$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
+%we have 
+%$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
+%
+%\begin{corollary}
+%For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
+%$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
+%and
+%$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
+%\end{corollary}
+%
 
@@
 
-\section{Appendix 1}
-For completeness we recap a result from \cite{barany2008}.
-\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
-For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
-\end{theorem}
-\begin{proof}
-Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
-This feasible region is not empty because it contains the origin. 
-Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
-$$
-\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
-$$
-The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
-The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
-Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
-\end{proof}
-
-Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
+%\section{Appendix 1}
+%For completeness we recap a result from \cite{barany2008}.
+%\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
+%For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
+%\end{theorem}
+%\begin{proof}
+%Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
+%This feasible region is not empty because it contains the origin. 
+%Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
+%$$
+%\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
+%$$
+%The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
+%The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
+%Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
+%\end{proof}
+%
+%Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
 The dimension of $x$'s is $d$ and of $y$'s is infinite.
@@
 If $y$ is obtained as the low components of PCA we can squeeze some more.
-Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
+%Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
 Let $\alpha^{(1)}$ be a feasible point.
@@
 Now, for the $y$'s we can choose any one of these $\alpha$'s
-
-However, we can search for $\alpha \in [-1,1]^n$ minimizing
+%
+%However, we can search for $\alpha \in [-1,1]^n$ minimizing
 
@@
 
-\section{Proofs for Streaming Coresets}
+\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets}
 
@@
 $$\max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$$
-Note that such signs are guarantied to exist by the definition of the Komols Complexity. 
-In fact, the quantity above is potentially much smaller than the Komlos Complexity because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
-
 Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
@@
 \item $\E[m] = n/2$
-\item $\Pr[m \geq (1+1/\log^2(n))n/2] \leq \exp \left( -O\left(\frac{n}{k\log(n)^4}\right)\right)$
+\item For $\rho >0$, $\Pr[m \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{k}\right)\right)$
 \item For any fixed query $q$, the error associated with $q$, defined as
@@
 \end{itemize}
-The last property ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$ 
-$$|\text{Err}(q)| \lesssim \rho k\sqrt{n/k} = \rho \sqrt{kn}$$
 \end{lemma}
+
+Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the Komols Complexity.
+In fact, the quantity above is potentially much smaller than the Komlos Complexity because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
+
 \begin{proof}
@@
 
-%
-%\begin{proof} [Proof of Theorem~\ref{thm:streaming}]
-%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
-The streaming algorithm operates as follows.
-At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
-The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
-In the beginning we have a single compactor at level $h=0$.
-Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
-After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
-%
-%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor. For a query $q$ we analyze the error
-%$$\text{Err}(q) = \sum_{h=0}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \ .$$
-%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
-The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
-The sum over $j$ is over the number of compactions at level $h$.
-Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
-%
-%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
-%$$ \text{Err}(q) \leq \rho(k) \log_2(n/k) n $$
-%
-%If however, we are interested in a smaller sketch with high probability of success of $1-\delta$, we decompose the error to two components
-%$$\text{Err}(q) = \sum_{h=0}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho k_h Y_{ij} + \sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}$$
-% Here, $H' = H - \ceil{\log(c \log(1/ \delta))}$ where $c$ is some universal constant we set later.
-Notice that the right summand contains roughly $\log(1/\delta)$ random variables.
-Since they are all Bernoulli we get that any combination of them is possible with probability $\geq \delta$ hence we must use a deterministic bound for these upper layers.
-We thus set $k_h=k$ for $h > H'$ and use the bound
-%$$ \text{Err}^{\text{top}}(q) = \left|\sum_{h=H'+1}^H 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij}\right| \leq O\left( \rho(k) \left(H-H'\right) n \right) =  O\left( \rho(k) \log \log(1/ \delta) n \right) $$
-%Now, for the bottom layers we use Chernoffs bound
-%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h)^2 k_h^2}   \right) =$$
-%$$\exp \left( -\frac{c' \eps^2 n^2}{\sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} } \right) $$
-%
-%\zk{$n_h$ being random is a problem. The weight of the stream might increase with time. The analysis now works for a completely balanced case }
-%Consider the sum in the denominator. 
-%$$ \sum_{h=h}^{H'} 2^{2h} \rho(k_h)^2 k_h^2 \floor{n_h/k_h} = O(\sum_{h=0}^{H'} 2^{2h} \rho(k_h)^2 k_h n_h ) $$
-%Since $n_h \leq n_{h-1}/2$ and we have $k_h \leq k$ we have 
-%$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2  ) $$
-%Now, if $\rho(k_h) \geq 1/\sqrt{k_h}$ we set $k_h = 2$ for all $h \leq H'$ and obtain
-%$$  = n  \cdot O(\sum_{h=0}^{H'} 2^h  ) = O(n^2/ (k \log(1/\delta))) $$
-%and we get
-%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) \right)   \right) $$
-%Hence, by setting $k \geq c/\eps^2$ for sufficiently large constant $c$ the probability is upper bounded by $\delta$.
-%
-%Now, for $\rho(k) < 1/\sqrt{k}$ we have $\eta(k) = \rho(k)^2 k = o(1)$.
-We can exploit that to allow for $k = o(1/\eps^2)$.
-For $\eta(k)=O(k^{-p})$ we\footnote{We do not discuss other scenarios as we are not aware of any setting where they occur.
-Also, extending the analysis to them is a purely technical exercise} use $k_h = \max(2, \ceil{(2/3)^{H'-h}k})$, leading to a bound of
-%$$\sum_{h=0}^{H'} 2^h k_h \rho(k_h)^2 \leq \sum_{h=0}^{H'} 2^h \eta(k) \cdot (3/2)^{H'-h} = (3/2)^{H'} \eta(k) \sum_{h=0}^{H'} (4/3)^h \leq  $$
-%$$(3/2)^{H'} \eta(k) \cdot (4/3)^{H'} \cdot 3 = 3 \cdot 2^{H'} \eta(k) = O(\eta(k)n/(k\log(1/\delta))$$
-%Plugging this in the probability bound gives
-%$$ \Pr\left[   \left|\sum_{h=h}^{H'} 2^h \sum_{j=1}^{\floor{n_h/k_h} } \rho(k_h) k_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( -O\left( \eps^2 k \log(1/\delta) / \eta(k) \right)   \right) = $$
-%$$ \exp \left( -O\left( \eps^2 \log(1/\delta) / \rho(k)^2 \right)   \right) $$
-%Hence, setting $k$ large enough so that $\rho(k) \leq c\eps$ for some universal constant $c$ leads to the required bound.
-%
-%In particular for $\rho(k) = O(1/k)$ we see that $k=1/\eps$ suffices, for general $p>1/2$ with $\rho(k) = k^{-p}$ we require $k=\eps^{-1/p}$.
-%
-%
-%Now, consider the overall error and memory of the entire process.
-For the bottom layers, for any $\rho(k)$ we require $O(k+H')=O(k+\log(n))$ memory.
-A closer inspection actually shows that once $k_h=2$ we are simply performing uniform sampling, and all of those layers can be done with constant memory.
-Hence, the memory footprint of the bottom layers is $O(k)$.
-The top layers require $O(\log\log(1/\delta)k)$ memory leading to a total memory usage of $O(\log\log(1/\delta)k)$.
-%
-%The error for the bottom layers is $O(\min\{\rho(k), 1/\sqrt{k}\} n)$.
-The error of the top layers is $O(\log\log(1/\delta) \rho(k) n)$, meaning that the overall error is $O(\log\log(1/\delta) \rho(k) n)$.
-%
-%Hence, if we aim for an error of $\eps n$ w.p.\ $1-\delta$ we set $k$ large enough such that $\rho(k) \leq c \eps / \log\log(1/\delta)$.
-Denoting by $\rho^{\dagger}$ the inverse function to $\rho$ this leads to a total memory requirement of
-%$$ \rho^{\dagger}(c \eps / \log\log(1/\delta)) \log\log(1/\delta) $$
-%
-%\end{proof}
-%
-%
-%%
-%%
-%%
-%%
-%%
-%%
-%%
-%%
-%%
-%%
-%%
-%
-%
-%\subsubsection{take 3}
-%
+Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
+$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} = \sqrt{\frac{K_k^2 n}{k}}$$
+This high probability bound will be used below for our streaming algorithm.
+In high level the idea is to have a sequence of streaming boxes that we call compactors, each receiving an input stream and outputting a stream that is of half the size of the input (in expectation).
+Eventually we will get to a stream that is small enough to store in memory.
+The randomized bound above shows that for the compactors that handle a large stream, we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$ even if all they do is uniformly sample half of the stream.
+However, for the compactors that observe the shorter streams that high probability bound is no longer as strong and we will have to make use of the fact that $K_k \ll k$.
 
@@
 \section{Table of Complexities for Common Classes}
+\zk{Not sure where to put this table - also we need to update it if we use it. Either way, beyond this point we can throw away the sections below}
 

### 2019-01-08 komlos.tex

--- 2019-01-03 komlos.tex
@@
 \begin{abstract}
-\el{I need to rewrite the abstract}
-This paper defines the Komlos complexity for families of functions which is intimately related to its discrepancy properties.
-We argue that this measure of complexity captures properties like minimal coreset sizes for different problems in machine learning.
-We show that for many well known problems the Komlos complexity is asymptotically lower than their Rademacher complexity.
-This proves the existence smaller coresets than those achievable by random sampling.
-New results for coresets for kernel density estimation, matrix covariance approximation, and logistic regression are presented both as examples of for providing mechanisms to compute the Komlos complexity of other classes.
-For all of the above we match the state of the art or improve on it.
-This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
-%We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
+This paper defines the Komlos complexity for families of functions and conjectures that it governs minimal coreset sizes for different problems in machine learning.
+Our result resolves a long standing open question regarding minimal cardinality coresets for kernel density estimation.
+It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the the dot product.
+The results leverage new tools and algorithms from discrepancy theory and provide tools for improving coreset sizes for other problems.
+Independently of the above, we show that any problem with low Komlos complexity admits a small merge-able streaming sketch.
+The result is an exponential improvement over the widely known and simple merge-and-reduce trick.
+This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
 \end{abstract}
@@
 \subsection{General Framework for Sketching}
-
-The high level idea is the following. 
-Consider a stream of the data points $x_i$. 
-We maintain a buffer that can hold up to $m$ points.
-Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
-The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
-This is made formal with the following definitions:
+We claim that low Komlos complexity implies concise streaming mergeable coresets. 
+This assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
+A trivial way to obtain such a construction is known as the merge-reduce trick \el{\cite{??} Har Peled?}.
+\el{What do we get from merge-reduce here? $\log(n)/\eps^2$ or $\log^2(n)/\eps^2$? Is it like MRL?)}
+The following theorems claim that a better construction is also possible.
 
 %
-In what follows, we prove the following.
+%of function family $\F$ is low, 
+%and one has an 
+%
+%The high level idea is the following. 
+%Consider a stream of the data points $x_i$. 
+%We maintain a buffer that can hold up to $m$ points.
+%Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
+The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
+%This is made formal with the following definitions: 
+%
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithms of size 
 $$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
@@
 \begin{theorem} \label{thm:streaming2}
-For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an fully-mergeable streaming coreset algorithms of size 
 $$O\left(c\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
@@
 More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
-Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
-$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
+Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $F: \R^d \rightarrow \R$ of a point $q$ is defined as 
+$$ F(q) = \sum_{i=1}^{n} K(x_i,q) $$
 Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
@@
 \]
-This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
+This upper bound allows us to find values for $\sigma_i$ which bound $K_m$ using a simple algorithm.
 Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
@@
 
-Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$.
+Using the framework above this provides a deterministic coreset construction for any positive kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
 This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.

### 2019-01-08 komlos.tex

--- 2019-01-07 komlos.tex
@@
 
-\title[Komols Complexity, Coresets, and Sketches in Machine Learning]{Komols Complexity, Coresets, and Sketches in Machine Learning}
+\title[Discrepancy, Coresets, and Sketches in Machine Learning]{Discrepancy, Coresets, and Sketches in Machine Learning}
 \usepackage{times}
@@
 See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
-We claim that $K_m$ is the measure more suitable for \zk{I think we should remove `active learning' from the list} creating coresets, and for creating mergeable sketches.
+We claim that $K_m$ is the measure more suitable for creating coresets, and for creating mergeable sketches.
 
@@
 Either way, below is my suggested motivation for the definition}
+ \el{You are right about the name.
+In fact, I've been thinking about it myself.
+The discrepancy we get is actually much lower than what Komlos conjecture says...
+So, I am happy with with calling it simple \it{the discrepancy.}}
 To understand the motivation of the the Komlos Complexity, consider the following informal explanation of Radamacher Complexity applied to ML problems.
@@
 This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
+\el{I like this explanation, I'm just not sure why it talks about pairs...}
 
-%\begin{theorem}
-%Let $F(a) = \sum_i a_i$ for $a \in A$ and let $K_m(A) = O(c/m^\gamma)$ for any constant $\gamma \in (0,1]$.
-%There exist a coreset for $A$ such that $\tilde{F}(a) = \sum_{i} w_i a_i$, $\operatorname{supp}(w) \le m$ and 
-%$$
-%\forall \; a \in A \;\;\;  |F(a) - \tilde F(a)| \le \eps n
-%$$
-%\end{theorem}
-%\begin{proof}
-%By halving the points repeatedly \el{TODO}.
-%\end{proof}
 \subsection{General Framework for Coresets}
+
 In what follows it will be convenient to represent the function family as a family of vectors representing the functions.
@@
 We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+
 %
@@
 \begin{fact}
-For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$ there exists a coreset of size 
-$O(c/\eps)$ whose error is at most $\eps n$.
+Let $\F$ be a function family with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$.
+Let $F(q) = \sum_{i=1}^{n}f_i(q)$ where $f_i \in \F$.
+There exists a coreset for $F$ of size $k = O(c/\eps)$ whose error is at most $\eps n$.
 \end{fact}
 \begin{fact}
+
 For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
 $O(c^2/\eps^2)$ whose error is at most $\eps n$.
+
 \end{fact}
 
-\noindent Proving both facts is trivial. 
+\noindent Proving both facts is trivial and known in the folklore as ``the halving trick". 
 At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
@@
 
-%\begin{theorem}
-%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/\sqrt{m})$.
-%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{3}\log(1/\delta)/\eps^2)$.
-%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-%$$
-%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-%$$
-%\end{theorem}
-%
-%
-%\begin{theorem}
-%Let $A$ be of the special form $a_i = f(x_i,q) \in [0,1]$ and $K_m(A) = O(c/m)$.
-%There exist and streaming mergeable coreset for $A$ with cardinality at most $\ell = O(c\log^{2}\log(1/\delta)/\eps)$.
-%That is, let $F(q) = \sum_i f(x_i,q)$. One can process a stream of item $x_1,\ldots,x_n$ and produce $\tilde{F}(q) = \sum_{i} w_i a_i$ with $\operatorname{supp}(w) \le \ell$ such that 
-%$$
-%\forall \; q \in Q \text{\;\;with probability\;\;} 1-\delta  \;\;\;  |F(q) - \tilde F(q)| \le \eps n
-%$$
-%\end{theorem}
+\subsection{General Framework for Sketching}\label{sec:sketch}
+We claim that low Komlos complexity implies concise streaming mergeable coresets. 
+This section assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
 
-\subsection{General Framework for Sketching} \label{sec:sketch}
-
-The high level idea is the following. 
-Consider a stream of the data points $x_i$. 
-We maintain a buffer that can hold up to $m$ points.
-Once collecting $m$ data points it performs a \emph{compact} operation that outputs at most $m/2$ data points of weight $2$ representing the original $m$ inputs.
-The compact operation partitions the $m$ points into two sets whose corresponding sums are very close.
-This is made formal with the following definitions:
-
- %
-In what follows, we prove the following.
 \begin{theorem} \label{thm:streaming}
-For any function $f$ with a corresponding Komlos Complexity $K_m = O(c/m)$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function family $\F$ with a corresponding Komlos Complexity with $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithms of size 
 $$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
@@
 \begin{theorem} \label{thm:streaming2}
-For any function $f$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function family $\F$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
 $$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
@@
 \end{theorem}
-%
-%\begin{fact}
-%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
-%$O(\log^2(\log(1/\delta))/\eps^2)$ whose error is at most $\eps n$ and failure probability at most $\delta$.
-%\end{fact}
-%
-%\begin{fact}
-%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(1)$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-%$O(\log^2(n)/\eps)$ whose error is at most $\eps n$.
-%\end{fact}
-%\begin{fact}
-%For any function $f$ with a corresponding discrepancy of $\Delta_k = O(\sqrt{k})$ there exists a fully-mergeable deterministic streaming coreset algorithms of size 
-%$O(\log^2(n)/\eps^2)$ whose error is at most $\eps n$.
-%\end{fact}
+
+The proofs of the above two theorems are quite technical and not very illuminating.
+Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
 
@@
 \section{A Simple Algorithm for Kernel Density Estimation}
-
 From section \ref{sec:analytic} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
@@
 \begin{proof}
-%Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$. 
 For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
@@
 \[
-\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
+\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
 \]
@@
 %
-%This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
-%Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
 We will show by induction on $i$ that 
@@
 This is trivially true for $i=1$ since $\|\phi(x)\| \leq 1$. 
-%Assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.
 Using our induction assumption we get
@@
 \end{eqnarray*}
-%\begin{eqnarray*}
-%\left\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\right\|^2 &=& \left\|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\right\|^2 + \|\phi(x_i)\|^2 + 2\ip{ \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)} \\
-%&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
-%&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
-%\end{eqnarray*}
-%This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.
 \end{proof}
@@
 
-%\section{Linear Regression}
-
-%\section{Optimal Design of Experiments}
-%We discuss the problem of linear regression with mean squared error.
-In the classic setting we are given $n$ points $x_1,\ldots,x_n \in \R^d$ along with $n$ labels $y_1,\ldots,y_n \in \R$ and wish to find $w \in \R^d$ minimizing
-%$$ \sum_i (w^Tx_i - y_i)^2 $$
-%In the field of optimal design of experiments, the labels are not given with the data.
-Instead, the learner must choose in advance a subset of datapoints for which they query the labels.
-The subset is chosen to provide the least error in a generalization bound, assuming $(x_1,y_1),\ldots,(x_n,y_n)$ are i.i.d from an unknown distribution.
-%
-%The way this is done in optimal design of experiments is as follows. Let $X$ be the set of $n$ points and consider a subset $B \subseteq X$. The empirical risk minimizer (ERM) for $B$ is 
-%$$ w_B = \left( \sum_{x \in B} xx^T \right)^{\dagger} y_B $$
-%%It is known that $w_B$ is an unbiased estimator of $w^*$, the optimal regressor for the distribution, where the noise comes from the realizations of the $y_i$'s. It follows that to minimize 
-%%$$ E_{x \sim {\cal D}} \ip{w-w^*,x}^2 $$
-%%which is the variance of $w$ measured by the distribution of data points, it suffice to minimize the second moment
-%%$$ E_{x \sim {\cal D}} \ip{w,x}^2  \approx w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-%
-%
-%One can show that for $w_B$,
-%$$ \sum_i (w_B^Tx_i - y_i)^2 = C \cdot \text{Tr} \left(\left( \sum_{x \in B} xx^T \right)^{\dagger} \right) $$
-%\zk{This only works when $\sum_{x \in B} xx^T$ is full rank, otherwise we need to introduce some regularization and then things get messy.}
-%
-%We can use the results above for optimal design in the case where $w$ is restricted to have a unit Euclidean norm.
-Something that is commonly practiced.
-Since we will solve the problem for the subset we choose in an optimal way for gaussian noise, we end up with an unbiased estimator for $w^*$.
-The error is the variance of that unbiased estimator and minimizing the variance for an unbiased estimator is the same as minimizing its second moment we can aim to minimize
-%$$ F(w) = w^T \left( \frac{1}{n} \sum_{i=1}^n x_ix_i^T \right) w $$
-%This leads to the exact same objective as in column subset selection.
-Meaning that an $\eps$ core-set for the $x$'s gives a guaranteed error for a subset in the optimal design setting.
-Specifically we get that we can obtain a core-set of size
-%$$ \min(1/\eps^2, \sqrt{d}/\eps)$$
-%For the case of $\eps < 1/\sqrt{d}$, which is an interesting case in linear regression, a random sample of $\sqrt{d}/\eps$ points will not give a generalization bound of $\eps$ (there are known lower bounds, http://jmlr.org/papers/volume16/shamir15a/shamir15a.pdf contradicting this), meaning that we have a provable non-trivial guarantee for active learning.
-I'm not sure what statements are known already.
-%
-%In the optimal design setting, they require keeping the covariance matrix. We could come up with a hueristic or even sketching algorithm that avoids maintaining $d^2$ points.
-
-%\section{Logistic Regression}
-%The following paper claims no streaming algorithms or coresets are available \cite{DBLP:journals/corr/abs-1805-08571}.
-%This paper claims to have done that \cite{DBLP:conf/nips/HugginsCB16}.
-%
-%In \cite{DBLP:journals/corr/abs-1802-01751} (see paragraph before Lemma 2.2) they manage to obtain a coreset (with equal weights) of size $\sqrt{d \log(1/\eps)}/\eps$ for any kernel with certain properties.
-They do so by considering a matrix whose rows correspond to all the vectors in an $\eps$-net over the space, and columns correspond to the $n$ data points.
-Calling that matrix $A$, $A_{q,x} = K(q,x)$.
-They bound the discrepancy of the matrix defined as $\min_s \|As\|_\infty$ where $s$ is a sign vector by using a bound
-%$$ \min_s \|As\|_\infty \leq \sqrt{\log(N)} \|A\|_{\gamma_2} $$
-%Here, $N$ is the size of the $\eps$ net and the $\gamma_2$ norm is 
-%$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \text{max norm of a row of B or C}$$
-%They use the fact that for psd kernel $K$, $\|A\|_{\gamma_2} \leq 1$ (in fact it is equal to 1).
-Now, back to our case.
-For any fixed power $k$ we know that $K(x,q)=\ip{x,q}^k$ is a psd kernel, hence its corresponding matrix $A_k$ has $\gamma_2$ norm bounded by $1$.
-Now, the logistic function can be written in a taylor expansion whose coefficients, in absolute value, sum to a constant $C$.
-It follows that the $A$ matrix for the logistic function has a $\gamma_2$ norm bounded by $C$.
-The same arguments as in  \cite{DBLP:journals/corr/abs-1802-01751} can now prove that its discrepancy is bounded by $\sqrt{\log(N)} \approx \sqrt{d\log(1/\eps)}$
-%
-%A useful fact about the $\gamma_2$ norm is that it is indeed a norm.
-This is proven in \cite{tomczak1989banach}.
-In \cite{matouvsek2014factorization} this is listed in Section 2, Proposition 2.2 along with other known properties of the $\gamma_2$ norm.
-%
-%
-%
-%
-%
-%\section{Coreset for linear functions (based on $\gamma_2$ norm)}
-%
-%Let $x_1,\ldots,x_n \in R^d$ be and $y_1,\ldots,y_n$ be labels associated to the data points. Let $K$ be a psd kernel. Consider a problem of learning a linear function aiming to minimize the loss of 
-%$$\min_q \sum_{i=1}^n L(K(x_i, q), y_i)$$
-%
-%Our objective is to find a core-set of the $n$ data points. That is, we aim to find a set $S \subseteq [n]$ such that for every $q$ it holds that 
-%$$ \left| \sum_{i=1}^n L(K(x_i, q), y_i) - \frac{n}{|S|} \sum_{i \in S} L(K(x_i, q), y_i) \right| \leq \eps n $$
-%
-%For a function $f(q,x)$, let $A_f$ be a matrix whose rows are an $\eps$-net over the Euclidean unit ball of $R^d$, and columns correspond to the different $x_i$'s.
-The value of $A_f$ at an entry corresponding to $(q,x)$ if $f(q,x)$.
-%
-%\begin{definition}
-%For a matrix $A$,
-%$$ \|A\|_{\gamma_2} = \min_{B,C: A=BC^T} \|B\|_{2 \to \infty} \|C\|_{2 \to \infty}$$
-%is the $\gamma_2$ norm of $A$. 
-%\end{definition}
-% \cite{tomczak1989banach} prove that this is indeed a norm, in particular that 
-% $\|A_1+A_2\|_{\gamma_2} \leq \|A_1\|_{\gamma_2} + \|A_2\|_{\gamma_2}$. 
-%
-%
-%\begin{lemma} \label{lem:powers}
-%For $k \geq 0$ let $f_k(q,x) = \ip{q,x}^k$. If holds that $\|A_{f_k}\|_{\gamma_2} \leq 1$
-%\end{lemma}
-%\begin{proof}
-%For $k=0$ the statement is obvious. For $k>0$, notice that $f_k$ is a kernel, and in particular there exists a mapping $\phi_k: \R^d \to \R^{d^k}$ such that
-%$$ \ip{q,x}^k = \ip{\phi_k(q), \phi_k(x)} $$
-%Furthermore, 
-%$$ \|\phi_k(x)\| = \sqrt{\ip{\phi_k(x), \phi_k(x)}} = \sqrt{\|x\|^{2k}} = \|x\|^k \leq 1 $$
-%Since all $x,q$ have at most unit norm we get a bound over the $\gamma_2$ norm by viewing the $B,C$ matrices obtained from the $\phi_k$ embeddings of the different $x,q$'s
-%\end{proof}
-%
-%\begin{lemma}
-%Let $L:\R \to \R$ be a function that can be written as 
-%$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k$$
-%with $\sum_{k=0}^{\infty} |\alpha_k| \leq C$. For $f_L(q,x) = L(\ip{q,x})$ it holds that 
-%$$ \|A_{f_L}\|_{\gamma_2} \leq C $$
-%\end{lemma}
-%\begin{proof}
-%This is a direct corollary from $\gamma_2$ being a norm, and Lemma~\ref{lem:powers}
-%\end{proof}
-%
-%This lemma in particular holds for the logistic function as its Taylor series has elements that converge.
-In particular, evaluating the function at $i$ and summing the real and imaginary parts of the result gives the sum of the absolute values of the coefficients, which is (roughly) $0.461$
-%\begin{corollary}
-%For $L(z) = \log(1+e^z)$ we have $\|A_{f_L}\|_{\gamma_2} \leq 0.5$
-%\end{corollary}
-%
-%\begin{definition}
-%For a matrix $A$ of dimensions $m \times n$, $\disc(A)$ is defined as 
-%$$ \min_{s \in \{-1,1\}^n} \|As\|_\infty $$
-%\end{definition}
-%In \cite{matouvsek2014factorization} they prove that 
-%$$\|A\|_{\gamma_2} / \log(m) \leq \disc(A) \leq \|A\|_{\gamma_2}  \sqrt{\log(m)}$$
-%This gives a way to control the discrepancy of a matrix by representing it as a sum of matrices with known discrepency or $\gamma_2$ norm. In particular, for the logistic function we get that 
-%$$\disc(A_{f_L}) \leq \sqrt{\log(|Q|)} $$
-%where $Q$ is an $\eps$-net over the Euclidean unit sphere. This gives the bound of 
-%$$\disc(A_{f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$
-%
-%Let's discuss what this means.
-For a logistic regression problem, by observing the weights and labels we can change the signs of the inputs so that the logistic loss is always $\log(1+\exp(\ip{q,x}))$, and we can now convert the discrepancy result into a coreset of size $\sqrt{d\log(1/\eps)}/\eps$, as opposed to a random sample of $1/\eps^2$.
-%
-%Let $K$ be a psd kernel, meaning for $x,q \in \R^d$ we have for some mapping $\phi$ into a Hilbert space $K(q,x) = \ip{\phi_K(q), \phi_K(x)}$. Notice that for $\phi_k$ defined above
-%$$ \ip{\phi_k(\phi_K(q)), \phi_k(\phi_K(x))} = \ip{\phi_K(q), \phi_K(x)}^k = K(q,x)^k $$
-%meaning that $K^k(q,x)$ is a psd kernel for all $k \geq 0$.
-By using the exact same arguments before we can define $A_{K,k} \in \R^{|Q|,n}$ with $A_{K,k}(q,i) = K(q, x_i)^k$ and conclude that $\|A_{K,k}\|_{\gamma_2} \leq 1$.
-Then, for the matrix $A_{K,f_L}$ with
-%$$ L(z) = \sum_{k=0}^\infty \alpha_k z^k, A_{K,f_L}(q,i) = L(K(q,x_i))$$
-%we have 
-%$$\|A_{K,f_L}\|_{\gamma_2} \leq \sum_{k=0}^{\infty} |\alpha_k| $$
-%
-%\begin{corollary}
-%For $L(z)=\log(1+\exp(z))$ and $L(z) = z^2$, and any psd kernel $K:\R^d \times \R^d \to \R$ we have
-%$$\|A_{K,f_L}\|_{\gamma_2} \leq 1 $$ 
-%and
-%$$\disc(A_{K,f_L}) \leq O(\sqrt{d\log(1/\eps)}) $$ 
-%\end{corollary}
-%
-
-%\bibliographystyle{plain}
 \bibliography{density}
-
-%\section{Appendix 1}
-%For completeness we recap a result from \cite{barany2008}.
-%\begin{theorem}[Simplified from B\'ar\'any \cite{barany2008} Theorem 4.1] \label{thm:random tensor}
-%For any set of vector $x_1,...,x_n$ in $\R^d$ such that $\|x_i\| \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i x_i || \le \sqrt{d}$.
-%\end{theorem}
-%\begin{proof}
-%Consider the feasible region for $\sum_i \alpha_i x_i = 0$ and all $\alpha_i \in [-1,1]$.
-%This feasible region is not empty because it contains the origin. 
-%Consider an extreme point $\alpha^*_i$ and set $\sigma_i = 1$ w.p.\ $(1+\alpha^*_i)/2$ and $\sigma_i = -1$ w.p.\ $(1-\alpha^*_i)/2$.
-%$$
-%\E[\|\sum \sigma_i x_i\|^2] =  \E[\|\sum (\sigma_i - \alpha^*_i) x_i\|^2] = \sum \E[(\sigma_i - \alpha^*_i)^2] \|x_i\|^2= \sum (1-(\alpha_i^*)^2) \le d
-%$$
-%The first equality is due to $\sum_i \alpha_i x_i = 0$. The second used $\E[\sigma_i] = \alpha^*_i $.
-%The last inequality holds because the values $\alpha^*_i$ are non-integer in at most $d$ places. 
-%Assuming otherwise would entail more than $d$ linearly independent vectors in $\R^d$ due to $\alpha^*$ being an extreme point.
-%\end{proof}
-%
-%Extension to the apx low rank case: The vectors are $[x_1,y_1],\ldots,[x_n,y_n]$.
-The dimension of $x$'s is $d$ and of $y$'s is infinite.
-Both $\|x_i\|, \|y\| \leq 1$.
-However, the overall norm of the $y$'s is bounded $\sum \|y_i\|^2 \leq \rho n$.
-Naively we can ignore the $y$'s and get a bound on the norm of $\sqrt{d + \sqrt{\rho} n}$ or something like that.
-If $y$ is obtained as the low components of PCA we can squeeze some more.
-%Consider another approach: Asking for $\sum x_i \alpha_i =0 $ gives $d$ linear restrictions.
-Let $\alpha^{(1)}$ be a feasible point.
-Let $\alpha^{(2)}$ be another feasible point that is restricted to being orthogonal to $\alpha^{(1)}$, and so on up to $\alpha^{(d)}$.
-For all these $\alpha$'s we have a bound of $2d$ to their rounding w.r.t to $x$.
-Now, for the $y$'s we can choose any one of these $\alpha$'s
-%
-%However, we can search for $\alpha \in [-1,1]^n$ minimizing
-
-%\section{Attempt at Cleaner Definitions}
-%Let $\mathcal F$ be a family functions from a domain $\X$ to $\R$.
-%We define the discrepancy of $\F$. Let $f \subset{\F}$ to a subset of $\F$.
-%$$\mathcal D_m(\F) := \sup_{x\in\X} \min_{s\in \{0,1\}^m} \sup_{f\subset \F, |f|=m}  \sum_{i}\sigma_i f_i (x)$$  \el{need to double check the order here...}
-%
-%We claim that a very common task is to approximate the function $F = \sum_i f_i$ using a concise representation.  
-%Specifically, using coresets we can approximate $F$ with $\tilde F = \sum_i w_i f_i$ where $w$ is non-zero in at most $k$ places.
-%
-%In this paper we show that if a family of functions exhibits low discrepancy then finding a good coreset is always possible.
-%The size of the coresets we find with the proposed algorithm is always smaller than that achievable by uniform sampling.
-%Moreover, we show that this framework includes a wide variety of problems including quantile approximation, approximate counting, machine learning classification and regressing, kernel density estimation and many more.
-%Finally, we show that coresets can always be created in a streaming fashion using fully mergable sketches with only a $\operatorname{poly}\log\log$ factor loss in space.
-%
-%
-%In what follows, we subscript the function $f$ with its parametrization.
-%\begin{itemize}
-%\item In approximate counting we have $f_a(x) = 1$ if $a=x$ and zero else. Here both $a$ and $x$ belong to some finite domain.
-%\item In quantile approximation we have $f_a(x) = 1$ if $a<x$ and zero else. Here, $a$ and $x$ belong to a set which exhibits total ordering.
-%\item In matrix column subset selection we have $f_z(a,q) = \langle z,x \rangle ^2$ where $a,x \R^d$. For simplicity, we assume $\|a\| = \|x\| = 1$.
-%\item In density estimation $f_a(x) = \exp(- \|a-x\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-%\item In logistic regression $f_a(x) = \operatorname{loss}(a,x) = \log(1 + \exp(-a^T x))$. 
-%Here $x$ is the parameters of the linear model and $a$ is a training example vector multiplied by its label ($1$ or $-1$).
-%\item Linear Classification $f_a(x) = 1$ if $a^Tx > 0$ and $0$ else.
-Here, like in Logistic Regression, $a$ is the example point multiplied by its label and $x$ is the weights of the linear classifier.
-%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
-Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
-For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-%\item Probably also good for matrix approximation when we get entry updates. 
-%\end{itemize}
-%
 
@@
 
-\section{Table of Complexities for Common Classes}
-\zk{Not sure where to put this table - also we need to update it if we use it. Either way, beyond this point we can throw away the sections below}
-
-\newcommand{\ccc}[1]{\parbox}
-\begin{table}[htp]
-\begin{center}
-\begin{tabular}{|c|c|c|c|} \hline
-Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
-Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
-Column Selection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
-Gaussian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\lambda^2)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Laplacian Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2/\lambda)$ where  $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-Positive Kernel Density 			& $f(x, q) = k(x,q)$ for any positive kernel $k$ and $q,x\in \R^d$				& ? 		& $1/\sqrt{m}$ \\ \hline
-
-%Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ where  $q,x\in \R^d$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-%Hinge Regression     		& $f(x, q) = [1-q^T x]_+$ where  $q,x\in \R^d$							& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
-Linear Regression		& $f(x,q) = (z^Tq - y)^2$ where $x = (z\in\R^d,y\in \R)$ and $q\in \R^d$					& ?				& ? \\ \hline
-Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else. $q,x\in \R^d$					& ?				& ? \\ \hline
-Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
-Matrix Approximation  	& $f(x, q) = a_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
-\end{tabular}
-\caption{Example problems in machine learning and sketching that fall into this framework.}
-\end{center}
-\label{default}
-\end{table}%
-
-\section{Row (or Column) Subset Selection}
-Assume you are getting the rows $x_i$  of matrix $X$ in a stream and you want to compute $Z$ such that $\|Z^TZ - X^TX\| \le \eps \operatorname{Tr}(X^TX)$.
-For simplicity, assume $x_i$ are all unit length so $\eps \operatorname{Tr}(X^TX) = \eps n$. Moreover, assume each vector in $Z$ must be one of the rows in $X$ up to some constant factor.
-This is called the row subset selection problem. 
-Since you are trying to minimize the quadratic form, you get that $f(x, q) = \langle x,q \rangle ^2$ and 
-$$E(q) = \sum_i \sigma_i \langle x_i,q \rangle ^2 = q^T (\sum_i \sigma_i x_i x_i^T ) q \le \|\sum_i \sigma_i x_i x_i^T\| \le c\sqrt{d}$$
-
-\noindent The last inequality is a direct application of the following Theorem.
-\begin{theorem}\label{BansalInDaHouz}
-For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
-\end{theorem}
-\begin{proof}
-First, recount Banaszczyk's Theorem~\cite{Banaszczyk}.
-Let $\mathcal K$ be a convex body in $\R^d$ with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
-Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
-Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some universal constant $C$.
-
-To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
-Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $c\sqrt{d_1 + d_2}$.
-More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le c\sqrt{d_1+d_2}\}$. 
-Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
-Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices (see Theorem~\ref{thm:random tensor}).
-Banaszczyk's theorem says that there exist signs $\sigma_i$ such that $\sum \sigma_i \operatorname{flatten}(X_i) \in C \mathcal K$.
-In other words $\| \sum \sigma_i X_i\| = \| \operatorname{stack}( \sum \sigma_i \operatorname{flatten}(x_i x_i^T)) \| \le C \sqrt{d}$.
-
-\end{proof}
-
-The algorithm for finding the signs above is, unfortunately, not as simple as with kernels. 
-In fact, Banaszczyk's theorem was not constructive and a matching algorithms is a very recent breakthrough result by Bansal, Dadush, Garg, and Lovett \cite{DBLP:conf/stoc/BansalDGL18}.
-
-Using the general framework above gives a matrix covariance coreset of cardinality $O(\sqrt{d}/\eps)$.
-Alternatively, we obtain a streaming mergeable algorithm for creating coresets of size $\log^{2}(\min(n, \log(1/\delta)) \sqrt{d}/\eps$.
-
-\el{Selecting $o(1/\eps^2)$ is claimed to be hard by \cite{DBLP:conf/focs/DeshpandeR10} and \cite{DBLP:conf/soda/DeshpandeRVW06}.
-We need to see if these hold in our setting or only hold for sampling.
-Also, \cite{DBLP:conf/soda/GhashamiP14} showed that the impossibility result is limited to frequent directions like settings.
-Their assumptions don't hold here.}
-
-\section{Streaming Graph Approximation}
-Streaming graphs have received a lot of attention in the last several years \zk{cite something here \cite{}}. 
-In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
-Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
-Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
-Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
-In this formulation, this problem reduced to that of row (column) subset selection. 
-Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
-Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
-The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
-$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
-
 \end{document}
-
-%Specifically, we set $\sigma_i$ sequentially for $i$ while minimizing the expectation. 
-%We prove by induction on $i$ that for the fixed $\sigma_j$'s up to and not including $i$,
-%$$\E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] \leq \sum_j \|z_j\|^2$$
-%For $i=1$ this is trivial. For $i>1$ let $v=\sum_{j=1}^{i-1} \sigma_j z_j$.
-%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_{j=1}^k \sigma_j z_j \|^2] = \E[\| v + \sum_{j=i}^k \sigma_j z_j \|^2] = \|v\|^2 + \sum_{j=i}^k \|z_j\|^2$$
-%It follows that by fixing $\sigma_i$ deterministically,
-%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] - \E_{s_{i+1},\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] = \|v\|^2 + \|z_i\|^2 - \|v + \sigma_i z_i\|^2  $$
-%so in order to make sure that 
-%$$ \E_{\sigma_i,\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] \geq \E_{s_{i+1},\ldots,s_k}[\| \sum_j \sigma_j z_j \|^2] $$
-%we need
-%$$ 2\ip{m,\sigma_i z_i} = \|m\|^2 + \|z_i\|^2 - \|m + \sigma_i z_i\|^2 \geq 0 $$
-%We thus set 
-%$$ \sigma_i = -\text{sign} \ip{m,z_i}$$

### 2019-01-09 komlos.tex
related work

@@
 \newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
+
+%\newcommand{\zk}[1]{}
+%\newcommand{\el}[1]{}
 
@@
 This is captured by its Komlos complexity.
+
+\section{Related Work}
+\begin{itemize}
+\item coresets - motivation, some papers, streaming algorithms for coresets
+
+\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
+However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
+
+\item Kernel density estimation.
+The state-of-the-art is by \cite{DBLP:journals/corr/abs-1802-01751} giving a $\sqrt{d\log(1/\eps)}/\eps$ coreset for kernel density, for Lipchitz psd kernels.
+The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
+The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
+
+\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
+Give multiplicative approximation.
+This is impossible in general so they depend on a different restriction on the regressor or dataset.
+Based on sensitivity scores.
+\cite{DBLP:conf/nips/HugginsCB16} use a heuristic of using $k$-means to approximate sensitivity scores and prove that given good sensitivity scores they get a good coreset.
+\cite{tolochinsky2018coresets} gives a generic coreset construction for any monotonic function as long as it comes with an $\ell_2^2$ regularization.
+The dependence they get is, ignoring polynomial factors, $d/\eps^2$.
+\cite{DBLP:journals/corr/abs-1805-08571} have a different method, relying on a measure of complexity of the dataset and obtain roughly $\sqrt{n}d^{3/2}/\eps^2$ sized dataset.
+\end{itemize}
 

### 2019-01-09 komlos.tex
more related work

--- 2019-01-08 komlos.tex
@@
 This is captured by its Komlos complexity.
+
+\section{Related Work}
+\begin{itemize}
+\item coresets - motivation, some papers, streaming algorithms for coresets
+
+\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
+We are not aware of any analog to Radamacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
+However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+%
+% There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
+However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
+
+\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
+However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
+
+\item Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
+Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}.
+A thorough survey could be found in \cite{silverman2018density}.
+Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
+The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that
+$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$.
+For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
+Their result holds for Lipchitz psd kernels.
+The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
+The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
+
+\item Logistic Regression is an extremely popular technique for classification task.
+In it, we are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
+The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$.
+A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$.
+A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset.
+They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$.
+The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.
+\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
+The dependence they get is, ignoring logarithmic factors, is $d/\eps^2$.
+
+%\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
+Give multiplicative approximation.
+This is impossible in general so they depend on a different restriction on the regressor or dataset.
+Based on sensitivity scores.
+\cite{DBLP:conf/nips/HugginsCB16} use a heuristic of using $k$-means to approximate sensitivity scores and prove that given good sensitivity scores they get a good coreset.
+\cite{tolochinsky2018coresets} gives a generic coreset construction for any monotonic function as long as it comes with an $\ell_2^2$ regularization.
+The dependence they get is, ignoring polynomial factors, $d/\eps^2$.
+\cite{DBLP:journals/corr/abs-1805-08571} have a different method, relying on a measure of complexity of the dataset and obtain roughly $\sqrt{n}d^{3/2}/\eps^2$ sized dataset.
+\end{itemize}
 

### 2019-01-09 komlos.tex
intro start

--- 2019-01-08 komlos.tex
@@
 \section{Introduction}
-
-\el{I need to rewrite this section.}
-In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
-Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance.
-For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
-The goal is to produce weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
+In both machine learning and in streaming and sketching problems our goal is (usually) to approximate the sums or expectations of functions.
+Specifically, approximate $F = \sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either training examples or stream items.
+In this paper it will often be convenient to consider an equivalent formulation.
+$F(q) = \sum_{i=1}^{n} f(x_i, q)$  and $q \in \mathcal Q$ is either the model parameters (which acts as an ``index'' into $\F$) or a query from a possible set $\Q$. 
+Clearly, the two formulations are identical. In this manuscript we use both interchangeably.  
+For simplicity and throughout this manuscript we assume the range of $f$ is $[0,1]$.
+The goal is to produce a coreset. This is a set of weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
 Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
@@
 
-%Here are some examples:
-%\begin{itemize}
-%\item in approximate counting we have $f(x, q) = 1$ if $x=q$ and zero else. Here both $x$ and $q$ belong to some finite domain.
-%\item in quantile approximation we have $f(x, q) = 1$ if $x<q$ and zero else. Here, $x$ and $q$ belong to a set which exhibits total ordering.
-%\item in matrix column subset selection we have $f(x, q) = \langle x,q \rangle ^2$ where $q$ is any unit vector in $\R^d$ and $x$ are matrix rows.
-For simplicity, we will assume in this manuscript that $x$ is also unit norm.
-%\item in density estimation $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other kernel (see \cite{})
-%\item in logistic regression $f(x, q) = \operatorname{loss}(x,q) = \log(1 + \exp(-q^T x))$. 
-%Here $q$ is the parameters of the linear model and $x$ is a training example vector multiplied by its label ($1$ or $-1$).
-%\item Linear Classification $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else.
-Here, like in Logistic Regression, $x$ is the example point multiplied by its label and $q$ is the weights of the linear classifier.
-%\item Fractional Satisfiability $f(x,q)$ if $q$ satisfies $f$ and $0$ otherwise.
-Here $x$ in a clause in conjunctive normal form and $q$ is a boolean value assignment to the variables.
-For example $f(x,q) = 1$ iff $(q_1 \vee q_5  \vee \neg q_8)$ is true.
-%\item Quadratic forms of the graph Laplacian are $f(x, q) = q^T L_x q = \sum_{i,j\in E} (q_i - q_i)^2$ where $x$ is an edge and $L_x$ is the graph laplacian corresponding to the graph with a single edge $x$ and $q$ is a test vector.
-%\item Probably also good for matrix approximation when we get entry updates. 
-%\end{itemize}
-
-For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ stream items.
+For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ items.
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
-%This is common practice in machine learning, specifically, PAC learning. However, it is often far from being the smallest cardinality coreset possible.
+%
 We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
@@
 The Komols complexity of a sequence set is defined similarly to it Rademacher complexity.
-%\begin{definition}
-%Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$ uniformly. 
-%The Rademacher complexity of $\F$ is 
-%\[
-%R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{a \in A}  \sum_{i=1}^{m}\sigma_i a_i
-%\]
-%\end{definition}
-%
-%\begin{definition}
-%Let $A \subset [0,1]^m$ and $\sigma \in \{-1,1\}^m$. 
-%The Komlos complexity of $A$ is 
-%\[
-%K_m(A) =  \frac{1}{m}\min_{\sigma} \sup_{a \in A}  \left|\sum_{i=1}^{m}\sigma_i a_i\right|
-%\]
-%\end{definition}
 

### 2019-01-09 komlos.tex
intro edits

@@
 \section{Introduction}
-In both machine learning and in streaming and sketching problems our goal is (usually) to approximate the sums or expectations of functions.
-Specifically, approximate $F = \sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either training examples or stream items.
-In this paper it will often be convenient to consider an equivalent formulation.
-$F(q) = \sum_{i=1}^{n} f(x_i, q)$  and $q \in \mathcal Q$ is either the model parameters (which acts as an ``index'' into $\F$) or a query from a possible set $\Q$. 
-Clearly, the two formulations are identical. In this manuscript we use both interchangeably.  
-For simplicity and throughout this manuscript we assume the range of $f$ is $[0,1]$.
+In both machine learning and in streaming and sketching problems our goal is (usually) to approximate the sums or expectations of well behaved functions.
+Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either training examples or stream items.
+Standard generalization results show that for a large enough $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn from underlying distribution.
+We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
+For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ .
+It is convenient to think about $q$ as either the model parameters or a query for the sketch.
+
 The goal is to produce a coreset. This is a set of weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
 There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
+Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient.
+Moreover, if the resulting coresets are mergeable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
 
-Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient.
-Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
-
-For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ items.
+For bounded functions $f$ uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
 %
-We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
+We argue that we can offer a solution for producing smaller coresets for a large class of problems in a unified manner. 
 Moreover, our solution creates streaming algorithms with fully mergeable sketches. 
 The size of the coreset above appears to be intimately tied to the discrepancy properties of the associated functions.
-This is captured by its Komlos complexity.
 
-\section{Related Work}
-\begin{itemize}
-\item coresets - motivation, some papers, streaming algorithms for coresets
-
-\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
-A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of any analog to Radamacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
-There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
-However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-%
-% There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
-For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
-However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
-
-\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
-For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
-However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
-
-\item Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
-Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}.
-A thorough survey could be found in \cite{silverman2018density}.
-Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
-The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that
-$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$.
-For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
-Their result holds for Lipchitz psd kernels.
-The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
-The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
-
-\item Logistic Regression is an extremely popular technique for classification task.
-In it, we are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
-The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$.
-A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$.
-A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset.
-They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$.
-The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.
-\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
-The dependence they get is, ignoring logarithmic factors, is $d/\eps^2$.
-
-%\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
-Give multiplicative approximation.
-This is impossible in general so they depend on a different restriction on the regressor or dataset.
-Based on sensitivity scores.
-\cite{DBLP:conf/nips/HugginsCB16} use a heuristic of using $k$-means to approximate sensitivity scores and prove that given good sensitivity scores they get a good coreset.
-\cite{tolochinsky2018coresets} gives a generic coreset construction for any monotonic function as long as it comes with an $\ell_2^2$ regularization.
-The dependence they get is, ignoring polynomial factors, $d/\eps^2$.
-\cite{DBLP:journals/corr/abs-1805-08571} have a different method, relying on a measure of complexity of the dataset and obtain roughly $\sqrt{n}d^{3/2}/\eps^2$ sized dataset.
-\end{itemize}
-
-\section{Komlos Complexity}
-We begin by formally defining the Komols complexity and by giving some general results about for problems with low Komols complexity.
-The Komols complexity of a sequence set is defined similarly to it Rademacher complexity.
+\section{Discrepancy of a Function Class}
+We begin by formally defining the discrepancy complexity and by giving some general results about for problems with low discrepancy. We remind the reader the definition of the Rademacher complexity.
 
@@
 In other words, the Radamacher complexity of a family function $\F$ measures how much a function in the family can skew the values when weighted with random signs.
-The Komlos complexity measures the ability of the family function to skew an adversarial set of signs.
+The discrepancy complexity measures the ability of the family of functions to skew an adversarial set of signs.
 
@@
 Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The Komlos complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+The discrepancyof $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
 \[
@@
 \]
-The Komlos Complexity $K_m(\F)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+The discrepancy $K_m(\F)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+\end{definition}
+The following is an alternative and equivalent definition:
+\begin{definition}
+Let $f:\X,\Q\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+\[
+K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{q \in \Q}  \left|\sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
+\]
+The Komlos Complexity $K_m(f)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
 \end{definition}
 
-\noindent It well known that $R_m$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
+\noindent It is well known that $R_m$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
 See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
-We claim that $K_m$ is the measure more suitable for creating coresets, and for creating mergeable sketches.
+We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
+Trivially,  $K_m \le R_m$. We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
 
-\el{Add a much longer explanation about the connection to discrepancy and the ideas behind this construction} The name Komlos Complexity is due to the Komlos Conjecture.
-It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
-The correctness of the Komlos Conjecture is still a fundamental open problem in the study of discrepancy theory.
-The definition is useful, however, regardless of the correctness or provability of the conjecture.
-It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We show later that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+To understand our motivation, consider the following informal explanation of the Radamacher Complexity applied to ML problems. 
+In PAC learning there exists a set of examples (with labels).
+We aim to find a predictor/classifier from a given family that suffers the least loss on the set. 
+Having a low Radamacher complexity means that if we
 
- \zk{I actually am still having problems with justifying the name Komlos complexity.
-It might as well be called Banaszczyk's complexity or simply discrepancy complexity.
-In particular if you could prove Komlos' conjecture it wouldn't affect any of our results, nor simplify our proofs..
-Either way, below is my suggested motivation for the definition}
- \el{You are right about the name.
-In fact, I've been thinking about it myself.
-The discrepancy we get is actually much lower than what Komlos conjecture says...
-So, I am happy with with calling it simple \it{the discrepancy.}}
-To understand the motivation of the the Komlos Complexity, consider the following informal explanation of Radamacher Complexity applied to ML problems.
-In this ML problem there exists a distribution over $(x,y)$ pairs where we aim to predict $y$ given $x$.
-Our goal is to find a predictor from a family of prediction functions that suffers the least loss.
-A predictor maps to a loss value on each $x,y$ pair so we can discuss the problem of finding a function $f$ from a family $\F$ minimizing $\E_{x,y} f(x,y)$ where $f$ is the loss associated with the corresponding predictor on the $x,y$ pairs.
-Having a low Radamacher complexity means that if we sample $m$ pairs, split them into two uniformly at random and find the function $f$ minimizing the loss over the first half, the loss over the second half is bounded.
-This translates to a generalization bound stating that the function $f$ minimizing the loss over a uniform random sample of $(x,y)$ pairs, will perform well on the entire distribution.
-In other words, the Radamacher complexity gives a guarantee for the distribution loss of the minimizer of a finite set of pairs chosen uniformly at random.
+Consider optimizing over a sample of roughly half the examples at random (each w.p.\ $1/2$).
+Low Rademacher complexity guaranties that twice the loss on the sample is roughly the same as the loss on the entire set.
+This translates to a generalization bound. 
+In other words, the Radamacher complexity gives a guarantee for the loss of corests chosen uniformly at random.
 
-Coming back to Komlos Complexity, having the ability to choose the signs in a non-uniform way lets us choose a subset of pairs $(x,y)$ such that the minimizer $f$ over the subset is guaranteed to have (roughly) the same performance on the entire set.
-This allows us to obtain a guarantee for the distribution loss of a minimizer of a finite set of pairs chosen in an adaptive way to the family function $\F$.
-This set is in fact a core-set and the Komlos complexity helps us determine that possible size of a coreset.
-The tradeoff of considering a coreset vs.\ a random sample is that on one hand, it is clearly much simpler to obtain a random sample.
-On the other hand we will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
+Coming back to Discrepancy. Having the ability to choose the signs algorithmically (non-uniform) lets us choose an advantageous subset of examples.
+We can actively choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
+This set is in fact a core-set. The Discrepancy complexity helps us determine possible sizes of a coresets. 
+We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
 This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
-\el{I like this explanation, I'm just not sure why it talks about pairs...}
 
@@
 Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
+
+\section{Related Work}
+\begin{itemize}
+\item coresets - motivation, some papers, streaming algorithms for coresets
+
+\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
+We are not aware of any analog to Radamacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
+However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+%
+% There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
+However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
+
+\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
+However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
+
+\item Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
+Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}.
+A thorough survey could be found in \cite{silverman2018density}.
+Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
+The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that
+$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$.
+For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
+Their result holds for Lipchitz bounded positive semi-definite kernels.
+The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
+The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
+
+\item Logistic Regression is an extremely popular technique for classification.
+We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
+The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$.
+A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$.
+A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset.
+They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$.
+The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.
+\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
+The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
+
+%\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
+Give multiplicative approximation.
+This is impossible in general so they depend on a different restriction on the regressor or dataset.
+Based on sensitivity scores.
+\cite{DBLP:conf/nips/HugginsCB16} use a heuristic of using $k$-means to approximate sensitivity scores and prove that given good sensitivity scores they get a good coreset.
+\cite{tolochinsky2018coresets} gives a generic coreset construction for any monotonic function as long as it comes with an $\ell_2^2$ regularization.
+The dependence they get is, ignoring polynomial factors, $d/\eps^2$.
+\cite{DBLP:journals/corr/abs-1805-08571} have a different method, relying on a measure of complexity of the dataset and obtain roughly $\sqrt{n}d^{3/2}/\eps^2$ sized dataset.
+\end{itemize}
 

### 2019-01-13 komlos.tex
some edits to intro

@@
 Our result resolves a long standing open question regarding minimal cardinality coresets for kernel density estimation.
-It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the the dot product.
+It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the dot product or the squared distance.
 The results leverage new tools and algorithms from discrepancy theory and provide tools for improving coreset sizes for other problems.
 Independently of the above, we show that any problem with low Komlos complexity admits a small merge-able streaming sketch.
-The result is an exponential improvement over the widely known and simple merge-and-reduce trick.
+The result is an exponential improvement over the widely known merge-and-reduce construction.
 This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
@@
 \section{Introduction}
-In both machine learning and in streaming and sketching problems our goal is (usually) to approximate the sums or expectations of well behaved functions.
-Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either training examples or stream items.
-Standard generalization results show that for a large enough $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn from underlying distribution.
+In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
+Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either sampled training examples or an arbitrary set of stream items.
+Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are i.i.d.\ drawn from underlying distribution.
 We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
 For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ .
-It is convenient to think about $q$ as either the model parameters or a query for the sketch.
+One should think about $q$ as either the model parameters or a query for the sketch.
 
-The goal is to produce a coreset. This is a set of weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
+The goal is to produce a coreset. This is a set of weights $w$ with at small number of non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
 Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
@@
 Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
-Moreover, if the resulting coresets are mergeable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
+Moreover, if the resulting coresets are mergeable, this could be done on separate streams without the need for communication or assuming randomness in the partitioning.
 
@@
 \section{Discrepancy of a Function Class}
-We begin by formally defining the discrepancy complexity and by giving some general results about for problems with low discrepancy. We remind the reader the definition of the Rademacher complexity.
+We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
 
 \begin{definition}
-Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$ uniformly at random. 
-The Rademacher complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the discrepancy of $A$ is 
 \[
-R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f \in \F}  \left| \sum_{i=1}^{m}\sigma_i f(x_i) \right|
+K_m(A)  = \min_\sigma \max_{a\in A} \frac{1}{m}|\sum_i  \sigma_i  a_i| 
 \]
@@
 %
-In other words, the Radamacher complexity of a family function $\F$ measures how much a function in the family can skew the values when weighted with random signs.
-The discrepancy complexity measures the ability of the family of functions to skew an adversarial set of signs.
-
-\begin{definition}
-Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The discrepancyof $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
-\[
-K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
-\]
-The discrepancy $K_m(\F)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
-\end{definition}
-The following is an alternative and equivalent definition:
 \begin{definition}
@@
 \[
-K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{q \in \Q}  \left|\sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
+K_m(f) =  \frac{1}{m}\min_{\sigma} \max_{q \in \Q}  \left|\sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
 \]
-The Komlos Complexity $K_m(f)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
 \end{definition}
+%
+\begin{definition}
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+\[
+K_m(\F) =  \frac{1}{m}\min_{\sigma} \max_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
+\]
+\end{definition}
+The discrepancy of $f$ or $\F$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
 
-\noindent It is well known that $R_m$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
+\noindent Notice that these definition are very similar to $R_m(\F)$ the Rademacher complexity.
+The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a random $\sigma$.
+Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{Bartlet et al \cite{Bartlett:2003:RGC:944919.944944} use the same ``discrepancy'' to define a different quantity than the one above.}
  We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
@@
 In PAC learning there exists a set of examples (with labels).
-We aim to find a predictor/classifier from a given family that suffers the least loss on the set. 
-Having a low Radamacher complexity means that if we
-
-Consider optimizing over a sample of roughly half the examples at random (each w.p.\ $1/2$).
+We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
+Having a low Radamacher complexity means that if we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
 Low Rademacher complexity guaranties that twice the loss on the sample is roughly the same as the loss on the entire set.
@@
 
-Coming back to Discrepancy. Having the ability to choose the signs algorithmically (non-uniform) lets us choose an advantageous subset of examples.
-We can actively choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is in fact a core-set. The Discrepancy complexity helps us determine possible sizes of a coresets. 
+Coming back to discrepancy. Having the ability to choose the signs arbitrarily lets us choose an advantageous subset of examples.
+We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
+This set is in fact a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.

### 2019-01-13 komlos.tex
section 2

@@
 The discrepancy of $f$ or $\F$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
+Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$. This is an obvious equivalence when one thinks about $q$ is the model parameters.
 
@@
 This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
+This intuition is restated more explicitly in the next section.
 
 \subsection{General Framework for Coresets}
-
-In what follows it will be convenient to represent the function family as a family of vectors representing the functions.
+In what follows it will be convenient to use the notation $f(x,q)$ and consider $K_m(f)$.
+%
+%to represent the function family as a family of vectors representing the functions.
 The vector family will be denoted as $Q$, where we use $q$ to denote a single vector corresponding to a function.
@@
 Achieving these bounds is a purely technical task that we defer for the sake of readability.
-
 Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}(q)$.
-We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+Now consider $F_1(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $F_{-1}(q) = F(q) - E(q)   = \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
+We have that both $F_1(q)$ and $F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
 
 %
-The above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
-Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
-A function is sketch-able if $K_m(\F) = o(m)$.
-Typically we see that $K_m(\F) = O(c/m)$ or $K_m(\F)= c/\sqrt{m}$ for some $c$ which does not depend on $m$.
+The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
+Note that we can select signs such that $|E(q)| \le m K_m(f)$.
+Typically we can show that $K_m = O(c/m)$ or $K_m = c/\sqrt{m}$ for some $c$ which does not depend on $m$.
 
 \begin{fact}
-Let $\F$ be a function family with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$.
-Let $F(q) = \sum_{i=1}^{n}f_i(q)$ where $f_i \in \F$.
-There exists a coreset for $F$ of size $k = O(c/\eps)$ whose error is at most $\eps n$.
+Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/m)$.
+Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
+There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
 \end{fact}
 \begin{fact}
-
-For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
-$O(c^2/\eps^2)$ whose error is at most $\eps n$.
-
+Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
+Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
+There exists a coreset for $F$ of size $O(c^2/\eps^2)$ whose error is at most $\eps n$.
 \end{fact}
@@
 \subsection{General Framework for Sketching}\label{sec:sketch}
-We claim that low Komlos complexity implies concise streaming mergeable coresets. 
+We claim that low discrepancy implies concise streaming mergeable coresets as well. 
 This section assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
@@
 \begin{theorem} \label{thm:streaming}
-For any function family $\F$ with a corresponding Komlos Complexity with $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithms of size 
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithm of size 
 $$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
-whose error is at most $\eps n$ and failure probability at most $\delta$.
-For $\delta=0$ this results in a deterministic algorithm.
-The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
+whose error is at most $\eps n$ with probability at least $1-\delta$. 
 \end{theorem}
@@
 \begin{theorem} \label{thm:streaming2}
-For any function family $\F$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithm of size 
 $$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
-whose error is at most $\eps n$ and failure probability at most $\delta$.
-For $\delta=0$ this results in a deterministic algorithm.
-The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
+whose error is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
+For both statements above, setting $\delta=0$ yields a deterministic algorithm. The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance.
 
-The proofs of the above two theorems are quite technical and not very illuminating.
+The proofs of the above two theorems are quite technical and delegated to the appendix.
 Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
+Generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
+The main ideas are as follows.
+In the last section we argued that both $F_1$ and $F_{-1}$ are good approximations for $F$.
+We can also take $F'$ which is $F_1$ or $F_{-1}$ equally likely.
+Clearly $|F' - F| \le |E|$ as before.
+But now, $\E[F'] = F$ as well.
+In the streaming algorithm, we apply this compaction (converting $F$ to $F'$) many times which allows us to use standard concentration results to bound the overall error.
+The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $F'$ no longer has exactly $1/2$ the size $F$.
+In the general setting, this only true in expectation.
 

### 2019-01-13 komlos.tex
section 2

@@
 \usepackage{ amssymb }
+
+\usepackage[]{algorithm2e}
 
@@
 \begin{abstract}
-This paper defines the Komlos complexity for families of functions and conjectures that it governs minimal coreset sizes for different problems in machine learning.
-Our result resolves a long standing open question regarding minimal cardinality coresets for kernel density estimation.
-It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the dot product or the squared distance.
-The results leverage new tools and algorithms from discrepancy theory and provide tools for improving coreset sizes for other problems.
-Independently of the above, we show that any problem with low Komlos complexity admits a small merge-able streaming sketch.
-The result is an exponential improvement over the widely known merge-and-reduce construction.
+This paper defines the discrepancy for families of functions.  It shows that low discrepancy classes admit small offline and streaming coresets.
+We provide general techniques for bounding the discrepancy of machine learning problems and specifically does so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
+Our result resolves a long standing open question regarding minimal cardinality coresets for Gaussian kernel density estimation.  
+We provide two more related but independent results. 
+First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
+Second, an extremely simple algorithm for finding coresets (low discrepancy sequences) for any positive kernel density estimation problem. 
 This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
@@
 
-Now that we proved the usefulness of the Komlos Complexity we move to upper bound it for interesting family functions.
-We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or Euclidean distance $\|q-x\|$.
+Now that we proved the usefulness of discrepancy we move to upper bound it for common family functions.
+We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or squared Euclidean distance $\|q-x\|^2$.
 
@@
 We define $\|\psi\|_T = \max_k \|\psi_k\|_{T_k} /\sqrt{\log(k)}$. 
-Here, $\|\cdot\|_{T_k}$ is the special spectral norm defined in the beginning of the section 
+Here, $\|\cdot\|_{T_k}$ is the special spectral norm defined in the beginning of the section.
 The maximum over norms of subvectors is clearly a norm in itself, meaning that $\|\cdot \|_T$ is indeed a norm.
@@
 A trivial modification of Theorem 1 from \cite{tomioka2014spectral} shows that $\Pr[\|g_k\|_{T_k} \ge c\sqrt{d\log(k)}] \le 1/10k^2$ for some constant $c$.
-The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$, where the reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
+The only change needed in the proof is the size of the epsilon net which changes from $(2\log(3/2)/k)^{kd}$ for \cite{tomioka2014spectral} to $(2\log(3/2)/k)^d$.
+The reason we require a net over a smaller space is due to us bounding the inner product with a rank one tensor rather than rank $k$.
 Union bounding on all values of $k$ we get $\sum_k 1/10k^2 \le 1/2$ which shows $g = [g_1, \operatorname{flat}(g_2), \operatorname{flat}(g_3), \ldots]$ belongs to $\mathcal K$ with probability at least $1/2$, where $\operatorname{flat}(g_k)$ is the flattening of the tensor into a one dimensional vector.
 %
-We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
+We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
+%The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
 $$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
 
-Finally, note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
+\noindent Note that for $\|x\| \le 1$ we have $\|\psi(x)\|_2 = (\sum_k  1/k\log^2(k))^{1/2} = O(1)$.
 
@@
 \begin{lemma} \label{lem:komlos anl}
-Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion.
-The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
+Let $f$ be a function of the inner product $f(x,q) = f(\langle x,q\rangle)$ and let $f = \sum_k \alpha_k \langle x,q\rangle^k$ be its Taylor expansion. 
+The discrepancy of $f$ indexed by $\|q\| \leq 1$ is bounded by
 \[
@@
 \begin{theorem}\label{analitic1}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 \begin{corollary}
-The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+The discrepancy of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
 \end{corollary}
@@
 \begin{corollary}
-The Komlos complexity of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
-This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescales columns of the matrix $X$.
+The discrepancy of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescaled columns of the matrix $X$.
+\el{Is this result new?
+Hard to say...}
 \end{corollary}
@@
 \begin{theorem} \label{thm:analytic2}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 \begin{corollary}
-The Komlos complexity of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
+The discrepancy of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
 \end{corollary} 
 This improves upon the recent result of \cite{DBLP:journals/corr/abs-1802-01751} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density, in the case where $\gamma$ is constant.
-For the constant $\gamma$ setting this resolves the open problem raised by \cite{DBLP:journals/corr/abs-1802-01751} and matches their lower bound.
+This also resolves the open problem raised by \cite{DBLP:journals/corr/abs-1802-01751} and matches their lower bound.
 
 \begin{proof}
-W.l.o.g. the maximum distance $\|q-x\|$ is 1. The taylor series of $K$ becomes
-$$ \sum_{k=0}^\infty \frac{(-\gamma)^k}{k!} $$
+W.l.o.g. the maximum distance $\|q-x\|$ is 1. The Taylor series of the Gaussian kernel $K$ becomes
+$ \sum_{k=0}^\infty \frac{(-\gamma)^k}{k!} $.
 Plugging into the equation in the proof of Theorem~\ref{thm:analytic2} we get that the sum determining the constant is upper bounded by
-$$ \sum_{k=0}^\infty \frac{\gamma^{k}\sqrt{ k\log^3(k)}}{k!} = O\left((1+\gamma) \exp(\gamma)\right)$$
+$ \sum_{k=0}^\infty \frac{\gamma^{k}\sqrt{ k\log^3(k)}}{k!} = O\left((1+\gamma) \exp(\gamma)\right)$.
 \end{proof}
@@
 \section{A Simple Algorithm for Kernel Density Estimation}
-From section \ref{sec:analytic} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$.
-The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently.
+From section \ref{sec:analytic} we know that the discrepancy of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. 
+%The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently. 
 Here, we provide a computationally efficient bound that can be achieved with a straightforward algorithm of complexity $O(m^2)$.
 Together with the results of Section~\ref{sec:sketch} this provides an efficient sketching algorithm for Kernel Density Estimation.
-We show that for any positive kernel $K_m = O(1/\sqrt{m})$.
-This bound is superior to that of the previous section when $d > \sqrt{m}$.
+In fact, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
+This bound is superior to that of the previous section for high dimensions $d > \sqrt{m}$.
 More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
 Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
-$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
+$$ F(q) = \sum_{i=1}^{n} K(x_i,q) $$
 Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
@@
 
-The algorithm we proposed works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
+\begin{algorithm}[H]
+ \KwData{Kernel function $K:(\R^d,\R^d)\rightarrow[0,1]$, points  $x_1,\ldots,x_m$}
+ \KwResult{$\sigma \in \{-1,1\}^m$ such that $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$}
+ $\sigma_1 = 1$;\\
+ \For{$i = 2,\ldots,m$}
+ {$\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$}
+% \EndFor
+ \caption{Low Discrepancy Algorithm for Positive Kernels}
+\end{algorithm}
+
+%The algorithm works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
 \begin{theorem}
-The algorithm above achieves a set of signs $\sigma_1,\ldots,\sigma_m$ such that for any $q$,
-$$ \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q) \leq \sqrt{m} $$
+The algorithm above achieves $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$.
 \end{theorem}
@@
 For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
-$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
+$ K(x,q) = \ip{\phi(x), \phi(q)} $.
 Using this function $\phi$ our objective function becomes
 \[
-\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
+|\sum_{i=1}^m \sigma_i K(x_i,q)| = |\sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} | = | \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)}| \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
 \]
@@
 %
-We will show by induction on $i$ that 
+We show by induction on $i$ that 
 $$\left\| \sum_{j=1}^i \sigma_j \phi(x_j) \right\|^2 \le \sum_{j=1}^i \left\|\phi(x_j)\right\|^2 \leq i$$
@@
 \begin{eqnarray*}
-\left\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\right\|^2 =& \left\|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\right\|^2 + \|\phi(x_i)\|^2 + 2\ip{ \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)} \leq & \text{induction assumption}\\
-& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) = & \text{choice of } \sigma_i \\
-& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2 \\
+\left\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\right\|^2 &=& \left\|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\right\|^2 + \|\phi(x_i)\|^2 + 2\ip{ \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)} \\
+&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)\\
+&\le& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2 \\
 \end{eqnarray*}
+The first equality simply unpacks the squared vector norm, the second transition is due to the induction assumption and the last substitutes our choice of %$\sigma$.
+This completes the proof that $|\sum_{i=1}^m \sigma_i K(x_i,q)| \le \sqrt{m}$ for all $q$.
 \end{proof}
 
-Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$.
+Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
 This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
 Along with an $\eps$-net argument, it also gives rise to a streaming algorithm for kernel density estimation with a memory requirement of $O\left(\log\left(d\log(1/\eps)\right)^3/\eps^2\right)$ vectors.
+\el{We should confirm this statement. I believe the Lipshitz constant of $m$ kernels can be $m$ so we might need another $d$ inside the inner $log$.}
 
@@
 
-Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the Komols Complexity.
-In fact, the quantity above is potentially much smaller than the Komlos Complexity because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
+Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the discrepancy.
+In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
 

### 2019-01-14 komlos.tex
section 2

@@
 
+\el{I am thinking about removing the $1/m$ from the definition. Pro: Its cleaner. Con: It's less like the Rademacher complexity. What do you think?}
 \begin{definition}
@@
 \[
-K_m(A)  = \min_\sigma \max_{a\in A} \frac{1}{m}|\sum_i  \sigma_i  a_i| 
+K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_i  \sigma_i  a_i\right| 
 \]
@@
 \[
-K_m(f) =  \frac{1}{m}\min_{\sigma} \max_{q \in \Q}  \left|\sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
+K_m(f) =  \min_{\sigma} \max_{q \in \Q}  \left|\frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
 \]
@@
 \[
-K_m(\F) =  \frac{1}{m}\min_{\sigma} \max_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
+K_m(\F) =  \min_{\sigma} \max_{f \in \F}  \left| \frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i)\right|
 \]
@@
 
-\begin{theorem} \label{thm:streaming}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithm of size 
-$$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
-whose error is at most $\eps n$ with probability at least $1-\delta$. 
+\begin{theorem} \label{thm:streaming12}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+\end{theorem}
+\begin{theorem} \label{thm:streaming11}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
+\el{for a single query?}
 \end{theorem}
 
-\begin{theorem} \label{thm:streaming2}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithm of size 
-$$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
-whose error is at most $\eps n$ with probability at least $1-\delta$.
+\begin{theorem} \label{thm:streaming21}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \end{theorem}
-For both statements above, setting $\delta=0$ yields a deterministic algorithm. The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance.
+\begin{theorem} \label{thm:streaming22}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
+\el{for a single query?}
+\end{theorem}
 
+The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
 The proofs of the above two theorems are quite technical and delegated to the appendix.
@@
 The main ideas are as follows.
-In the last section we argued that both $F_1$ and $F_{-1}$ are good approximations for $F$.
+In the last section we argued that both $F_1$ and $F_{-1}$ are both good approximations for $F$.
 We can also take $F'$ which is $F_1$ or $F_{-1}$ equally likely.
@@
 But now, $\E[F'] = F$ as well.
-In the streaming algorithm, we apply this compaction (converting $F$ to $F'$) many times which allows us to use standard concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $F'$ no longer has exactly $1/2$ the size $F$.
+In the streaming algorithm, we apply this compaction (converting $F$ to $F'$) many times over small subset of items from the stream.
+This allows us to use standard concentration results to bound the overall error.
+The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $F'$ no longer has exactly half the size $F$.
 In the general setting, this only true in expectation.
@@
 
+%\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} 
+%
+%\begin{lemma} \label{lem:compactor}
+%Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $\sigma_1,\ldots,\sigma_k$ such that
+%$$\max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$$
+%Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
+%\begin{itemize}
+%\item $\{z_i\}_i$ is a subset of $\{x_i\}$
+%\item $\E[m] = n/2$
+%\item For $\rho >0$, $\Pr[m \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{k}\right)\right)$
+%\item For any fixed query $q$, the error associated with $q$, defined as
+%$$\text{Err}(q) = 2\sum_{i=1}^m f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
+%Can be decomposed as a sum
+%$$\text{Err}(q) = \sum_{j=1}^{n/k} \text{Err}_j(q)$$
+%where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
+%\end{itemize}
+%\end{lemma}
+%
+%Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the discrepancy.
+In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
+%
+%\begin{proof}
+%The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
+%$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
+%Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
+%$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
+%$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
+%
+%%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
+%%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
+%%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
+%%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
+%%\el{this is clunky way to say this...}
+%The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
+Moreover, the output length is a sum of $n/k$ independent random variables with mean $k/2$ and a maximum value of $k$.
+Chernoff-Hoeffding's bound can guarantee the stated concentration around $\E[m]$.
+%As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
+%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Radamacher r.v. scaled by a magnitude of at most $K_k$ as required.
+%\end{proof}
+%
+%Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
+%$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} = \sqrt{\frac{K_k^2 n}{k}}$$
+%This high probability bound will be used below for our streaming algorithm.
+In high level the idea is to have a sequence of streaming boxes that we call compactors, each receiving an input stream and outputting a stream that is of half the size of the input (in expectation).
+Eventually we will get to a stream that is small enough to store in memory.
+The randomized bound above shows that for the compactors that handle a large stream, we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$ even if all they do is uniformly sample half of the stream.
+However, for the compactors that observe the shorter streams that high probability bound is no longer as strong and we will have to make use of the fact that $K_k \ll k$.
+%
+%
+%\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
+%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
+The streaming algorithm operates as follows.
+At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
+The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
+In the beginning we have a single compactor at level $h=0$.
+Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
+After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
+%
+%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
+For a query $q$ and hierarchy level $h$ we analyze the error
+%$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
+%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
+The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
+The sum over $j$ is over the number of compactions at level $h$.
+$K_h$ is used to denote the discrepancy of each compaction using a buffer of $k_h$ points.
+Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
+The overall error for the query $q$ is the sum over all levels of its errors
+%$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
+%
+%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+%$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
+%
+%We are however interested in a high probability bound.
+Specifically we would like to guarantee for $\delta > 0$ that for any query $q$ the error is bounded by $\eps n$ w.p.\ at least $1-\delta$.
+To this end we consider a different analysis for the top and bottom layers.
+For the top layers, the stream can be arbitrarily short so we will use the deterministic analysis as above.
+For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
+%
+%The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
+%\begin{equation} \label{eq:Htag_nh}
+% \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
+%\end{equation}
+%for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
+%
+%According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
+%$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
+%We can now union bound over all 
+%$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
+%and conclude that w.p.\ at least $1-\delta/2$
+%\begin{equation} \label{eq:Htag}
+%H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
+%\end{equation}
+%and
+%\begin{equation} \label{eq:nh small}
+%\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
+%\end{equation}
+%
+%
+%Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
+%$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
+%$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
+%$$
+%We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
+Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
+We get that since $n_h \leq 3n/2^h$
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
+%\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
+%$$
+%In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
+%and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
+%$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
+%and 
+%$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
+%
+%Let's proceed to bound the error on the top layers $H'+1$ to $H$.
+In these top layers we use a deterministic algorithm guaranteeing the stream is cut at least times 2 from layer to layer.
+We assign all top layers a budget of $k_h=k$ for the compactors.
+Since $2^{H+1} < n/k$ this gives a bound of
+%$$
+%H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
+%$$
+%$$
+%O\left( \log \log(n/\delta) \right)
+%$$
+%leading to a bound of 
+%$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
+%and an overall bound of
+%\begin{equation} \label{eq:err total}
+%|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
+%\end{equation}
+%
+%We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
+Recall that we aim to deal with two settings.
+In the first $K_k=\min\{\komconstant,k\}$ and in the second $K_k=\min\{\komconstant \sqrt{k}, k\}$.
+In both cases  $\komconstant$ is independent of $k$.
+We start by dealing with the first scenario.
+%
+%We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
+%\begin{align*}
+%\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
+%  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
+%    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
+%\end{align*}
+%We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
+%$$
+%\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
+%(3/4)^{H'-h}
+%$$
+%For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
+%\begin{align*}
+% \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
+%    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
+%	   &  O\left( (1/2)^{H''-h}   \right) 
+%\end{align*}
+%
+%If follows that 
+%$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
+%translating to an overall bound for the error of
+%$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
+%The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
+The top layers require $O(\log\log(n/\delta)k)$ memory.
+If follows that by setting $k= O\left(\komconstant \log\log(n/\delta) / \eps\right)$ the error is bounded by $\eps n$ w.p.
+$1-\delta$ and the overall memory requirement is
+%$$ O\left( \log \log(n/\delta)^2 (\komconstant/\eps)  \right) $$
+%
+%
+%We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
+%\begin{align*}
+%\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
+%  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
+%\end{align*}
+%and 
+%$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
+%Plugging this to the overall error in Equation~\eqref{eq:err total} we get
+%$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
+%
+%Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
+%$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
+%we get a bound of $\eps n$ for the error and a memory usage of 
+%$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
+%\end{proof}
+%
+
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets}
@@
 \begin{lemma} \label{lem:compactor}
-Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $\sigma_1,\ldots,\sigma_k$ such that
-$$\max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$$
-Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
+Assume we have black box access to a solver that for any integer $m$ and inputs $x_1,\ldots,x_m$ obtains signs $\sigma_1,\ldots,\sigma_m$ such that $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ for some function $f$ whose discrepancy is $K_m$.\footnote{An constant factor approximation algorithm achieving $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| = O(K_m)$ would also clearly suffice.}
+Then there exist a streaming algorithm requiring a memory buffer of $m$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_{n'}$ with the following properties
 \begin{itemize}
 \item $\{z_i\}_i$ is a subset of $\{x_i\}$
-\item $\E[m] = n/2$
-\item For $\rho >0$, $\Pr[m \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{k}\right)\right)$
+\item $\E[n'] = n/2$
+\item For $\rho >0$, $\Pr[n' \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{m}\right)\right)$
 \item For any fixed query $q$, the error associated with $q$, defined as
-$$\text{Err}(q) = 2\sum_{i=1}^m f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
+$$\text{Err}(q) = 2\sum_{i=1}^{n'} f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
 Can be decomposed as a sum
-$$\text{Err}(q) = \sum_{j=1}^{n/k} \text{Err}_j(q)$$
+$$\text{Err}(q) = \sum_{j=1}^{n/m} \text{Err}_j(q)$$
 where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
@@
 
-Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the discrepancy.
+Note that signs achieving $max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ are guarantied to exist by the definition of the discrepancy.
 In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
 
+\el{changed notation until here...}
 \begin{proof}
@@
 Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
-$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} = \sqrt{\frac{K_k^2 n}{k}}$$
+$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} $$
 This high probability bound will be used below for our streaming algorithm. 
-In high level the idea is to have a sequence of streaming boxes that we call compactors, each receiving an input stream and outputting a stream that is of half the size of the input (in expectation).
-Eventually we will get to a stream that is small enough to store in memory.
-The randomized bound above shows that for the compactors that handle a large stream, we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$ even if all they do is uniformly sample half of the stream.
-However, for the compactors that observe the shorter streams that high probability bound is no longer as strong and we will have to make use of the fact that $K_k \ll k$.
+The high level idea is to have a sequence of streaming objects that we call compactors. 
+Each compactor receives an input stream and outputs a stream that is of half the size of the input (in expectation). 
+Eventually we get to a stream that is small enough to store in memory. 
+The randomized bound above shows that for the compactors that handle a large stream, 
+we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$. 
+That is true even if all they do is uniformly sample half of the stream. 
+However, for the compactors that observe the shorter streams, a high probability bound is no longer strong enough. 
+For those we will make use of the fact that $K_k \ll k$.
 
@@
 
-Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+We proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
 $$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
@@
 
-Let's proceed to bound the error on the top layers $H'+1$ to $H$.
-In these top layers we use a deterministic algorithm guaranteeing the stream is cut at least times 2 from layer to layer.
+We proceed to bound the error on the top layers $H'+1$ to $H$.
+In these top layers we use a deterministic algorithm guaranteeing the stream is cut in half from layer to layer.
 We assign all top layers a budget of $k_h=k$ for the compactors.
@@
 $1-\delta$ and the overall memory requirement is
-$$ O\left( \log \log(n/\delta)^2 (\komconstant/\eps)  \right) $$
+$$ O\left( \log^2 \log(n/\delta) (\komconstant/\eps)  \right) $$
 

### 2019-01-14 komlos.tex
minor changes

--- 2019-01-13 komlos.tex
@@
 Our result resolves a long standing open question regarding minimal cardinality coresets for kernel density estimation.
-It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the dot product or the squared distance.
+It provides improved coreset for matrix covariance approximation, logistic regression, and any analytic function of the the dot product.
 The results leverage new tools and algorithms from discrepancy theory and provide tools for improving coreset sizes for other problems.
 Independently of the above, we show that any problem with low Komlos complexity admits a small merge-able streaming sketch.
-The result is an exponential improvement over the widely known merge-and-reduce construction.
+The result is an exponential improvement over the widely known and simple merge-and-reduce trick.
 This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
@@
 \section{Introduction}
-In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
-Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either sampled training examples or an arbitrary set of stream items.
-Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are i.i.d.\ drawn from underlying distribution.
-We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ .
-One should think about $q$ as either the model parameters or a query for the sketch.
+In both machine learning and in streaming and sketching problems our goal is (usually) to approximate the sums or expectations of functions.
+Specifically, approximate $F = \sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either training examples or stream items.
+In this paper it will often be convenient to consider an equivalent formulation.
+$F(q) = \sum_{i=1}^{n} f(x_i, q)$  and $q \in \mathcal Q$ is either the model parameters (which acts as an ``index'' into $\F$) or a query from a possible set $\Q$. 
+Clearly, the two formulations are identical. In this manuscript we use both interchangeably.  
+For simplicity and throughout this manuscript we assume the range of $f$ is $[0,1]$.
+The goal is to produce a coreset. This is a set of weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
+There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.
 
-The goal is to produce a coreset. This is a set of weights $w$ with at small number of non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
-There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
 Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient.
-Moreover, if the resulting coresets are mergeable, this could be done on separate streams without the need for communication or assuming randomness in the partitioning.
+Moreover, if the resulting sketches or coresets are mergable, this could be done on separate machines without the need for communication or assuming randomness in the partitioning.
 
-For bounded functions $f$ uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
+For bounded functions $f$ like above, uniform sampling of $\ell = O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $\ell = O(\log(|\mathcal Q|)/\eps^2)$ items.
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
 %
-We argue that we can offer a solution for producing smaller coresets for a large class of problems in a unified manner. 
+We argue that we can offer a solution for producing smaller coresets for all of the above problems in a unified manner. 
 Moreover, our solution creates streaming algorithms with fully mergeable sketches. 
 The size of the coreset above appears to be intimately tied to the discrepancy properties of the associated functions.
-
-\section{Discrepancy of a Function Class}
-We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
-
-\begin{definition}
-Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the discrepancy of $A$ is 
-\[
-K_m(A)  = \min_\sigma \max_{a\in A} \frac{1}{m}|\sum_i  \sigma_i  a_i| 
-\]
-\end{definition}
-%
-\begin{definition}
-Let $f:\X,\Q\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
-\[
-K_m(f) =  \frac{1}{m}\min_{\sigma} \max_{q \in \Q}  \left|\sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
-\]
-\end{definition}
-%
-\begin{definition}
-Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
-\[
-K_m(\F) =  \frac{1}{m}\min_{\sigma} \max_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
-\]
-\end{definition}
-The discrepancy of $f$ or $\F$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
-Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$. This is an obvious equivalence when one thinks about $q$ is the model parameters.
-
-\noindent Notice that these definition are very similar to $R_m(\F)$ the Rademacher complexity.
-The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a random $\sigma$.
-Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{Bartlet et al \cite{Bartlett:2003:RGC:944919.944944} use the same ``discrepancy'' to define a different quantity than the one above.}
- We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
-Trivially,  $K_m \le R_m$. We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
-
-To understand our motivation, consider the following informal explanation of the Radamacher Complexity applied to ML problems. 
-In PAC learning there exists a set of examples (with labels).
-We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
-Having a low Radamacher complexity means that if we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
-Low Rademacher complexity guaranties that twice the loss on the sample is roughly the same as the loss on the entire set.
-This translates to a generalization bound. 
-In other words, the Radamacher complexity gives a guarantee for the loss of corests chosen uniformly at random.
-
-Coming back to discrepancy. Having the ability to choose the signs arbitrarily lets us choose an advantageous subset of examples.
-We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is in fact a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
-We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
-This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
-This intuition is restated more explicitly in the next section.
-
-\subsection{General Framework for Coresets}
-In what follows it will be convenient to use the notation $f(x,q)$ and consider $K_m(f)$.
-%
-%to represent the function family as a family of vectors representing the functions.
-The vector family will be denoted as $Q$, where we use $q$ to denote a single vector corresponding to a function.
-We a universal function $f$ such that $f(x,q)$ corresponds to the value of the function matching $q$ when applied to $x$.
-We will assume from hereon that for any $x,q$ $|f(x,q)| \leq 1$; this allows to simplify the presentation.
-Our results can extend to $|f(x,q)| \leq R$ and will have dependencies on the bound $R$.
-Achieving these bounds is a purely technical task that we defer for the sake of readability.
-Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $F_{-1}(q) = F(q) - E(q)   = \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
-We have that both $F_1(q)$ and $F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
-
-%
-The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-Note that we can select signs such that $|E(q)| \le m K_m(f)$.
-Typically we can show that $K_m = O(c/m)$ or $K_m = c/\sqrt{m}$ for some $c$ which does not depend on $m$.
-
-\begin{fact}
-Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/m)$.
-Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
-There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
-\end{fact}
-\begin{fact}
-Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
-Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
-There exists a coreset for $F$ of size $O(c^2/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
-
-\noindent Proving both facts is trivial and known in the folklore as ``the halving trick". 
-At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
-Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
-Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
-
-\subsection{General Framework for Sketching}\label{sec:sketch}
-We claim that low discrepancy implies concise streaming mergeable coresets as well. 
-This section assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
-
-\begin{theorem} \label{thm:streaming}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithm of size 
-$$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
-whose error is at most $\eps n$ with probability at least $1-\delta$. 
-\end{theorem}
-
-\begin{theorem} \label{thm:streaming2}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithm of size 
-$$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
-whose error is at most $\eps n$ with probability at least $1-\delta$.
-\end{theorem}
-For both statements above, setting $\delta=0$ yields a deterministic algorithm. The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance.
-
-The proofs of the above two theorems are quite technical and delegated to the appendix.
-Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
-Generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
-The main ideas are as follows.
-In the last section we argued that both $F_1$ and $F_{-1}$ are good approximations for $F$.
-We can also take $F'$ which is $F_1$ or $F_{-1}$ equally likely.
-Clearly $|F' - F| \le |E|$ as before.
-But now, $\E[F'] = F$ as well.
-In the streaming algorithm, we apply this compaction (converting $F$ to $F'$) many times which allows us to use standard concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $F'$ no longer has exactly $1/2$ the size $F$.
-In the general setting, this only true in expectation.
+This is captured by its Komlos complexity.
 
@@
 For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
-Their result holds for Lipchitz bounded positive semi-definite kernels.
+Their result holds for Lipchitz psd kernels.
 The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
@@
 
-\item Logistic Regression is an extremely popular technique for classification.
-We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
+\item Logistic Regression is an extremely popular technique for classification task.
+In it, we are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
 The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$.
@@
 \cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
-The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
+The dependence they get is, ignoring logarithmic factors, is $d/\eps^2$.
 
@@
 \end{itemize}
+
+\section{Komlos Complexity}
+We begin by formally defining the Komols complexity and by giving some general results about for problems with low Komols complexity.
+The Komols complexity of a sequence set is defined similarly to it Rademacher complexity.
+
+\begin{definition}
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$ uniformly at random. 
+The Rademacher complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+\[
+R_m(\F) =  \frac{1}{m}\E_{\sigma} \sup_{f \in \F}  \left| \sum_{i=1}^{m}\sigma_i f(x_i) \right|
+\]
+\end{definition}
+%
+In other words, the Radamacher complexity of a family function $\F$ measures how much a function in the family can skew the values when weighted with random signs.
+The Komlos complexity measures the ability of the family function to skew an adversarial set of signs.
+
+\begin{definition}
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The Komlos complexity of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+\[
+K_m(\F) =  \frac{1}{m}\min_{\sigma} \sup_{f \in \F}  \left|\sum_{i=1}^{m}\sigma_i f(x_i)\right|
+\]
+The Komlos Complexity $K_m(\F)$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+\end{definition}
+
+\noindent It well known that $R_m$ is a good measure for generalization when data is chosen uniformly at random (or drawn from an unknown distribution).
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.
+We claim that $K_m$ is the measure more suitable for creating coresets, and for creating mergeable sketches.
+
+\el{Add a much longer explanation about the connection to discrepancy and the ideas behind this construction} The name Komlos Complexity is due to the Komlos Conjecture.
+It claims that $\min_\sigma \max_f \|\sum_i \sigma_i f_i\|_\infty = O(1)$ for unit vectors $f$.
+The correctness of the Komlos Conjecture is still a fundamental open problem in the study of discrepancy theory.
+The definition is useful, however, regardless of the correctness or provability of the conjecture.
+It is obvious that  $K_m(\F) \le R_m(\F)$ for any family $\F$. We show later that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+
+ \zk{I actually am still having problems with justifying the name Komlos complexity.
+It might as well be called Banaszczyk's complexity or simply discrepancy complexity.
+In particular if you could prove Komlos' conjecture it wouldn't affect any of our results, nor simplify our proofs..
+Either way, below is my suggested motivation for the definition}
+ \el{You are right about the name.
+In fact, I've been thinking about it myself.
+The discrepancy we get is actually much lower than what Komlos conjecture says...
+So, I am happy with with calling it simple \it{the discrepancy.}}
+To understand the motivation of the the Komlos Complexity, consider the following informal explanation of Radamacher Complexity applied to ML problems.
+In this ML problem there exists a distribution over $(x,y)$ pairs where we aim to predict $y$ given $x$.
+Our goal is to find a predictor from a family of prediction functions that suffers the least loss.
+To simplify our discussion and make it applicable for unsupervised learning we can consider the features and label as a single input vector $x$, and consider a prediction function as one that maps this new input vector $x$ to a loss in $\R$.
+Formally, for a family of function $\F$ we wish to find $f \in \F$ minimizing $\E_x f(x)$.
+Having a low Radamacher complexity means that if we sample $m$ data points, split them into two uniformly at random and find the function $f$ minimizing the loss over the first half, the loss over the second half is bounded.
+This translates to a generalization bound stating that the function $f$ minimizing the loss over a uniform random sample of points will perform well on the entire distribution.
+In other words, the Radamacher complexity gives a guarantee for the distribution loss of the minimizer of a finite set of points chosen in an i.i.d.\ fashion.
+
+Coming back to Komlos Complexity, having the ability to choose the signs in a non-uniform way lets us choose a subset of data points such that the minimizer $f$ over the subset is guaranteed to have (roughly) the same performance on the entire set.
+This allows us to obtain a guarantee for the distribution loss of a minimizer of a finite set chosen in an adaptive way to the family function $\F$.
+This set is in fact a core-set and the Komlos complexity helps us determine the possible size of a coreset.
+The tradeoff of considering a coreset vs.\ a random sample is that on one hand, it is clearly much simpler to obtain a random sample.
+On the other hand, as we will prove in what follows, there are multiple useful examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
+In other words, in what follows we show that for a wide range of interesting function families in machine learning that $K_m(\F) = o(R_m(\F))$.
+\el{I like this explanation, I'm just not sure why it talks about pairs...} \zk{changed to data points}
+
+\subsection{General Framework for Coresets}
+
+In what follows it will be convenient to represent the function family as a family of vectors representing the functions.
+The vector family will be denoted as $Q$, where we use $q$ to denote a single vector corresponding to a function.
+We define a universal function $f$ such that $f(x,q)$ corresponds to the value of the function matching $q$ when applied to $x$.
+We assume that for any $x,q$ $|f(x,q)| \leq 1$; this allows to simplify the presentation.
+Our results can extend to $|f(x,q)| \leq R$ and will have dependencies on the bound $R$.
+Achieving these bounds is a purely technical task that we defer for the sake of readability.
+
+Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $F_1(q) = F(q) + E(q) = \sum_{i=1}^{m} f(x_i,q)  + \sum_{i=1}^{m} \sigma_i f(x_i,q)  = 2 \sum_{i | \sigma_i=1} f(x_i,q)$ and similarly $F_{-1}(q)$.
+We have that both $F_1(q), F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+
+%
+The above is true for any choice of signs $\sigma_i$, specifically, for those minimizing $\max_q | E(q)|$.
+Note that we can select signs such that $|E(q)| \le m K_m(\F)$.
+A function is sketch-able if $K_m(\F) = o(1)$.
+Typically we see that $K_m(\F) = O(c/m)$ or $K_m(\F)= c/\sqrt{m}$ for some $c$ which does not depend on $m$.
+
+\begin{fact}
+Let $\F$ be a function family with a corresponding Komlos Complexity $K_m(\F) = O(c/m)$.
+Let $F(q) = \sum_{i=1}^{n}f_i(q)$ where $f_i \in \F$.
+There exists a coreset for $F$ of size $k = O(c/\eps)$ whose error is at most $\eps n$.
+\end{fact}
+\begin{fact}
+For any function family $\F$ with a corresponding Komlos Complexity $K_m(\F) = O(c/\sqrt{m})$ there exists a coreset of size 
+$O(c^2/\eps^2)$ whose error is at most $\eps n$.
+\end{fact}
+
+\noindent Proving both facts is trivial and known in the folklore as ``the halving trick". 
+At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
+Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
+Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
+Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
+
+\subsection{General Framework for Sketching}\label{sec:sketch}
+We claim that low Komlos complexity implies concise streaming mergeable coresets. 
+This section assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
+
+\begin{theorem} \label{thm:streaming}
+For any function family $\F$ with a corresponding Komlos Complexity with $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset algorithms of size 
+$$O\left(c\log^2\left(\min(\eps n/c, \log(n/\delta)) \right)/\eps\right)$$ 
+whose error is at most $\eps n$ and failure probability at most $\delta$.
+For $\delta=0$ this results in a deterministic algorithm.
+The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
+\end{theorem}
+
+\begin{theorem} \label{thm:streaming2}
+For any function family $\F$ with a corresponding Komlos Complexity of $K_m = O(c/\sqrt{m})$ there exists an unbiased fully-mergeable streaming coreset algorithms of size 
+$$O\left(c^2\log^3\left(\min(\eps^2 n/c, \log(n/\delta)) \right)/\eps^2\right)$$ 
+whose error is at most $\eps n$ and failure probability at most $\delta$.
+For $\delta=0$ this results in a deterministic algorithm.
+The algorithm must be given $\eps, \delta$ as input and does not require a priori knowledge of the stream length $n$.
+\end{theorem}
+
+The proofs of the above two theorems are given in Appendix~\ref{app:sketch proof} as they are quite technical and not very illuminating.
+Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
+Still, we note that the guarantees they provide go beyond what one would obtain with a standard merge and reduce framework as in \zk{Is this the name, is there a reference to the `known' way to convert an offline coreset algorithm to a streaming one?}.
+In particular, the dependence on the error probability $\delta$ is \emph{doubly} logarithmic rather than logarithmic.
+This is key since typically we require a union bound over an $\eps$-net that is exponentially large.
 
@@
 
-\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets}
+\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
 

### 2019-01-14 komlos.tex

--- 2019-01-14 komlos.tex
@@
 \begin{theorem} \label{thm:streaming11}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
-\el{for a single query?}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
@@
 \begin{theorem} \label{thm:streaming22}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
-\el{for a single query?}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
 
+Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
+Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
+Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provide a coreset for entire family that matches the non-streaming version up to poly-logarithmic terms.
+
 The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
-The proofs of the above two theorems are quite technical and delegated to the appendix.
+The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
 Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
@@
 
-\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+%
+%\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
 For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
@@
 
+\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets}

### 2019-01-15 komlos.tex
appendinx MRL

--- 2019-01-14 komlos.tex
@@
 First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
-Second, an extremely simple algorithm for finding coresets (low discrepancy sequences) for any positive kernel density estimation problem. 
+Second, an extremely simple algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
 This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
@@
 Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either sampled training examples or an arbitrary set of stream items.
-Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are i.i.d.\ drawn from underlying distribution.
+Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn i.i.d.\ from underlying distribution.
 We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ .
+For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$.
 One should think about $q$ as either the model parameters or a query for the sketch.
@@
 
-\begin{theorem} \label{thm:streaming12}
+\begin{theorem} \label{thm:streaming11}
 For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
 \end{theorem}
-\begin{theorem} \label{thm:streaming11}
+\begin{theorem} \label{thm:streaming12}
 For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
@@
 
+\section{Appendix Appendix Appendix...}
+
+The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
+A compactor consumes a stream of items and outputs another stream.
+The output stream contains roughly half the items from the input stream with double the weight. 
+It does so by keeping a buffer of a certain capacity $k$. When a new item is inserted into the compactor it is added to its buffer. 
+If the buffer is full, a compaction operation takes place. 
+The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
+$\max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
+Note that such a sequence is guarantied to exist by the definition of the discrepancy. 
+However, an algorithm for finding such a sequence might not exist. 
+From this point onwards, we assume the existence of such an algorithm.
+In other words, our theorems hold for problems which admit such a solution.
+The compactor then outputs either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ with double the weight.
+
+We begin with showing some basic properties of deterministic compactor, which always output the smaller of the two set  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
+Consider a single compaction and let $\tilde F$ denote the function evaluated on the output set.
+Let $E(q) = \sum_i \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above. 
+$$\tilde F(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
+$$\tilde F(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
+Note that $|\tilde F(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
+Now, aggregating over the $n/m$ compactions we get that $|\tilde F(q) - F(q)| \le n K_m$. Moreover, the stream length is clearly cut (at least) in half.
+
+These facts alone already allow us to prove Theorem~\ref{thm:streaming11}. 
+\paragraph{Theorem~\ref{thm:streaming11}}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+\begin{proof}
+Consider feeding the output of the first compactor into a second one etc. Number the compactors $0,\ldots,H$.
+The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
+Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ we know that $H \le log(n/m)$.
+The total error is therefore $H n K_m \le log(n/m) n K_m$. 
+Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
+Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $c\log^2(\eps n/c)/\eps$.
+\end{proof}
+
+This algorithm is a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
+Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
+A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
+The above gives a discrepancy of $1/m$ for quantile approximation.
+
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} 
-
 \begin{lemma} \label{lem:compactor}

### 2019-01-15 komlos.tex

@@
 \end{theorem}
+
 \begin{theorem} \label{thm:streaming12}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error is at most $\eps n$ with probability at least $1-\delta$.
-\el{for a single query?}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+
 \end{theorem}
@@
 
+\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
+
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} 

### 2019-01-15 komlos.tex
More in the appendix

@@
 
-\begin{theorem} \label{thm:streaming12}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
-
-\end{theorem}
-
 \begin{theorem} \label{thm:streaming21}
@@
 \end{theorem}
+
+\begin{theorem} \label{thm:streaming12}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+\end{theorem}
+
 \begin{theorem} \label{thm:streaming22}
@@
 A compactor consumes a stream of items and outputs another stream.
-The output stream contains roughly half the items from the input stream with double the weight. 
-It does so by keeping a buffer of a certain capacity $k$. When a new item is inserted into the compactor it is added to its buffer. 
+The output stream contains at most half (in expectation) the items from the input stream with double the weight. 
+It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
 If the buffer is full, a compaction operation takes place. 
@@
 From this point onwards, we assume the existence of such an algorithm.
-In other words, our theorems hold for problems which admit such a solution.
+%In other words, our theorems hold for problems which admit such a solution.
 The compactor then outputs either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ with double the weight.
 
-We begin with showing some basic properties of deterministic compactor, which always output the smaller of the two set  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
-Consider a single compaction and let $\tilde F$ denote the function evaluated on the output set.
+We begin with showing some basic properties of deterministic compactors which always output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
+Consider a single compaction and let $\tilde F_{+}$ denote the function evaluated on $\{ x_i | \sigma_i = 1\}$ (similarly $\tilde F_{-}$).
 Let $E(q) = \sum_i \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above. 
-$$\tilde F(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
-$$\tilde F(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
-Note that $|\tilde F(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
+$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
+$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
+Note that $|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
 Now, aggregating over the $n/m$ compactions we get that $|\tilde F(q) - F(q)| \le n K_m$. Moreover, the stream length is clearly cut (at least) in half.
 
-These facts alone already allow us to prove Theorem~\ref{thm:streaming11}. 
+These facts alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
+The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
+Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
+A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
+The above gives a discrepancy of $1/m$ for quantile approximation.
+Below we generalize this algorithm to any low discrepancy class.
+
 \paragraph{Theorem~\ref{thm:streaming11}}
@@
 Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $c\log^2(\eps n/c)/\eps$.
+Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \el{TODO: double check the math.}
 \end{proof}
 
-This algorithm is a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
-Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
-A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
-The above gives a discrepancy of $1/m$ for quantile approximation.
+\paragraph{Theorem~\ref{thm:streaming21}}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+\begin{proof}
+The proof is identical to the one above except for the variable setting of
+Setting $m \ge c^2\log^2(\eps^2 n/c^2)/\eps^2$ and replacing $K_m = c/\sqrt{m}$. 
+We get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
+Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \el{TODO: double check the math.}
+\end{proof}
+
+Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
+Consider again a single compactor of capacity $m$ and
 
@@
 
-\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} 
 \begin{lemma} \label{lem:compactor}

### 2019-01-15 komlos.tex
More in the appendix
small edits

@@
 
-For bounded functions $f$ uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
+For bounded functions $f$, uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
 While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
 %
-We argue that we can offer a solution for producing smaller coresets for a large class of problems in a unified manner. 
+We present a mechanism for producing coresets which are much smaller than those achieved by sampling for a large class of problems in a unified manner. 
 Moreover, our solution creates streaming algorithms with fully mergeable sketches. 
@@
 \end{definition}
-The discrepancy of $f$ or $\F$ without a reference set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+The discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
 Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
@@
 Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{Bartlet et al \cite{Bartlett:2003:RGC:944919.944944} use the same ``discrepancy'' to define a different quantity than the one above.}
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the same ``discrepancy'' to define a different quantity than the one above.}
  We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
@@
 We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
-Having a low Radamacher complexity means that if we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
-Low Rademacher complexity guaranties that twice the loss on the sample is roughly the same as the loss on the entire set.
+Having a low Radamacher complexity means that we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
+Low Rademacher complexity guaranties that, in expectation, twice the loss on the sample is roughly the same as the loss on the entire set.
 This translates to a generalization bound. 
-In other words, the Radamacher complexity gives a guarantee for the loss of corests chosen uniformly at random.
+In other words, the Radamacher complexity gives a guarantee for the loss of coresets chosen uniformly at random.
 
@@
 Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $F_1(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $F_{-1}(q) = F(q) - E(q)   = \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
-We have that both $F_1(q)$ and $F_{-1}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|F_1(q) - F(q)| =  |E(q)|$.
+Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
+We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}- F(q)| =  |E(q)|$.
 
@@
 Note that we can select signs such that $|E(q)| \le m K_m(f)$.
-Typically we can show that $K_m = O(c/m)$ or $K_m = c/\sqrt{m}$ for some $c$ which does not depend on $m$.
+The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
+The constant $c$ does not depend on $m$ but could depend on other parameters of the problem.
 
 \begin{fact}
-Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/m)$.
-Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
-There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
+Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/m)$. Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$. There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
 \end{fact}
 \begin{fact}
-Let $\F$ be a function family with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
+Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
 Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
@@
 Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
-Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provide a coreset for entire family that matches the non-streaming version up to poly-logarithmic terms.
+Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provides a coreset for an entire family that matches the non-streaming version up to poly-logarithmic terms.
 
@@
 
+\item Linear Regression \cite{DBLP:journals/jmlr/DerezinskiW18}
 %\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
@@
 Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
-Consider again a single compactor of capacity $m$ and
+\el{Add the description of the randomized algorithms.}
 

### 2019-01-16 komlos.tex
appendix appendix

@@
 
-\el{I am thinking about removing the $1/m$ from the definition. Pro: Its cleaner. Con: It's less like the Rademacher complexity. What do you think?}
+\el{I am thinking about removing the $1/m$ from the definition. Pro: Its cleaner. Con: It's less like the Rademacher complexity. What do you think?} \zk{think of term in stead of complexity}
 \begin{definition}
@@
 %The algorithm works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
-\begin{theorem}
+\begin{theorem} \label{thm:disc simple kernel}
 The algorithm above achieves $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$.
@@
 Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
-This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
-Along with an $\eps$-net argument, it also gives rise to a streaming algorithm for kernel density estimation with a memory requirement of $O\left(\log\left(d\log(1/\eps)\right)^3/\eps^2\right)$ vectors.
-\el{We should confirm this statement. I believe the Lipshitz constant of $m$ kernels can be $m$ so we might need another $d$ inside the inner $log$.}
+This matches and simplifies the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+Theorem~\ref{thm:streaming21} leads to a deterministic streaming algorithm with a memory complexity of $O(\log^3(\eps^2 n)/\eps^2)$.
+For $L$-Lipchitz kernels, meaning $K$ such that $|K(x,q+h) - K(x,q)|/\|h\| \leq L$ for all $h \neq 0$, Theorem~\ref{thm:streaming22} leads to a randomized streaming algorithm with a memory complexity of $O\left(\log^3 \left( d \log\left(RLn/\delta\eps\right) \right) / \eps^2 \right)$ that succeeds finding a coreset with probability $1-\delta$.
+The parameter $R$ is the maximum norm of a query.
+The argument goes through a union bound over an $\eps/L$-net over vectors of norm at most $R$, the size of which is $(RL/\eps)^{O(d)}$.
 
-\paragraph{Note} The Theorem above provides an upper bound of $\sqrt{m}$ for the sign discrepancy.
-One can in fact construct an example where this upper bound is indeed what the algorithm achieves.
-However, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
+\paragraph{Note} Theorem~\ref{thm:disc simple kernel} provides an upper bound of $\sqrt{m}$ for the sign discrepancy.
+Even if this upper bound is tight, meaning there exist a set of vectors that achieve it, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
 We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
@@
 
+\zk{define compactor in an algorithm for thm about $\sqrt{m}$}
+
+%%%%%%%%%%%%%%
+%%%
+%%%
+%%%
+%%%%%%%%%%%%%%
+
+\section{yet another  Appendix...}
+
+The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
+A compactor consumes a stream of items and outputs another stream.
+The output stream contains at most half the items from the input stream with double the weight. 
+It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
+If the buffer is full, a compaction operation takes place. 
+The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
+$\max_q |\sum_i \sigma_i f(x_i,q)| \leq m K_m$. 
+Note that such a sequence is guarantied to exist by the definition of the discrepancy.
+For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
+That is, if it is possible to obtain a bound of $K_m$ yet we can only find signs obtaining a bound of $\tilde{K}_m$, our results for the obtainable signs apply for $\tilde{K}_m$.
+Given the sign vector $\sigma$, the compactor appends either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ to the output stream.
+
+Consider a stream of data points $x_1,\ldots,x_n$ and the output stream of a compactor $z_1,\ldots,z_{\tilde{n}}$. The error associated with the new stream w.r.t.\ a query $q$ is defined as
+$$ \sum_{i=1}^n f(x_i,q) - 2\sum_j f(z_j,q) \ .$$
+This is the difference between the value of $q$ on the original stream and the output stream.
+For a compactor we would like to bound both the length of the output stream, and the absolute value of its error.
+
+\begin{lemma} \label{lem:det compactor}
+A deterministic compactor output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
+Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $K_m n$
+\end{lemma}
+\begin{proof}
+We note that the argument about the length is obvious, so we proceed to bound the error.
+Consider a single compaction operation done on $m$ vectors $x_1,\ldots,x_m$.
+For a query $q$, let $F(q)=\sum_{i=1}^m f(x_i,q)$ be the evaluation on the items of the buffer.
+Let $\tilde F_{+}$ denote the function evaluated on $\{ x_i | \sigma_i = 1\}_{i=1}^m$ (similarly $\tilde F_{-}$ defined for negative signs).
+Also, let $E(q) = \sum_{i=1}^m \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above.
+We have that
+$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
+$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
+meaning that the error for the items of the single compaction is bounded by
+$$|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = mK_m$$
+Summing over all $n/m$ compactions we get that the overall error is bounded, in absolute value, by $nK_m$.
+\end{proof}
+
+Lemma~\ref{lem:det compactor} alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
+The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
+Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
+A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
+The above gives a discrepancy of $1/m$ for quantile approximation.
+Below we generalize this algorithm to any low discrepancy class.
+
+\paragraph{Theorem~\ref{thm:streaming11}}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+\begin{proof}
+Consider feeding the output of the first compactor into a second one etc.
+Specifically, we start with a single compactor and open a second once it produced any output, then open a third compactor once the second produced output, etc.
+Number the compactors $0,\ldots,H$. The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
+Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
+The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 
+Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $K_m = c/m$ we get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $m_0$, as required.
+Since we have $H = O(log(\eps n/c))$ compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. 
+\end{proof}
+
+\paragraph{Theorem~\ref{thm:streaming21}}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+\begin{proof}
+The proof is identical to the one above except for the variable setting of
+Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $K_m = c/\sqrt{m}$. 
+We get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $_0$, as required. 
+Since we have $H = O(log(\eps^2 n/c^2))$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c^2) /\eps^2\right)$. 
+\end{proof}
+
+We proceed to prove Theorem~\ref{thm:streaming22}.
+To understand the motivation consider first an easier setting where the overall stream length $n$ is known to us in advance.
+Since $|f(x,q)| \leq 1$, standard concentration bounds will show that by sampling each item w.p.\ $\log(1/\delta)/n\eps^2$ we get an output stream of length $\log(1/\delta)/\eps^2$, that for any fixed query $q$, with probability at least $1-\delta$ suffers an error of $\eps n$ for that query.
+We can feed this output stream into a deterministic sketch, and given that the input length for the deterministic sketch is $\log(1/\delta)/\eps^2$, Theorem~\ref{thm:streaming21} leads to the required guarantee.
+
+Because we do not know the stream length in advance, we operate as in the deterministic case with compactors.
+The difference will be that each compactor will keep a count of how many items it has seen.
+Once a compactor observed more than $\tilde{n} = O(\log(1/\delta)/\eps^2)$ items, it will no longer use a buffer of size $m$ but rather a buffer of size 2.
+For every two items observed it will output a single one uniformly at random.
+It is easy to see that a sequence of such compactors can in fact be implemented with $O(1)$ memory via reservoir sampling.
+The memory of this process is therefor identical, at least asymptotically, to
+
+\paragraph{Theorem~\ref{thm:streaming22}}
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+\begin{proof}
+As in the deterministic setting we maintain a sequence of compactors of levels $h=0,\ldots,H$.
+Notice that the value of $H$ is increasing as the stream grows longer.
+Recall that a compactor of level $h$ observes elements of weight $2^h$ and outputs elements of weight $2^{h+1}$.
+As before we use a buffer of $m$ and get that $H \leq  \floor{log_2(n/m)}+1$.
+The difference is that for a compactor of level $h$, once $h \leq H' = H - \log(\log(1/\delta)/m\eps^2)$, meaning we know that the number of items observed by the $h$'th compactor, $n_h \geq \tilde{n} = O(\log(1/\delta)/\eps^2)$, we change the mode of operation for this compactor.
+Rather than using a buffer of size $m$ the compactor uses a buffer of size 2 and for every two observed items it outputs one of them uniformly at random.
+
+To analyze the memory requirement, notice that the compactors of levels $h=0,\ldots,H'$ are in fact performing reservoir sampling for every $2^{H'+1}$ items, meaning that they can be implemented in $O(1)$ memory.
+This means that the overall memory requirement is $O(m\log(\log(1/\delta)/m\eps^2))$.
+
+As for the error, for the layers of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n K_m$.
+Let us bound the error for the compactor of level $h \leq H'$.
+For the first $\tilde{n}$ items it observed, the error is bounded by $2^h\tilde{n}K_m \leq 2^{h-H'}nK_m$.
+Fix a query $q$; for the items following the first $\tilde{n}$ items the compactor is operating in the sampling mode.
+For every pair, the associated error w.r.t $q$ is a random variable, of mean zero and absolute value of at most $w_h=2^{h+1}$.
+There are $(n_h-\tilde{n})/2 \leq n_h$ such pairs and the overall error w.r.t.\ $q$ is the sum of these independent random variables.
+Chernoff bound implies that with probability $1-\delta$, the overall error is bounded by $E_h = O(w_h\sqrt{n_h\log(1/\delta)})$.
+Since $n_h \geq \tilde{n}2^{H'-h} = O(2^{H'-h}\log(1/\delta)/\eps^2)$ we get that
+$$ E_h = O\left(2^h n_h\frac{\eps}{2^{(H'-h)/2}}\right) = O(\eps n 2^{(h-H')/2}) $$
+We get that the sum of errors associated with the compactors of level $h=0,\ldots,H'$ for a geometric sequence dominated by the error of the $H'$ compactor, which is in turn $O(\eps n)$.
+For proper constants in $\tilde{n}$ we get a bound of $\eps n/2$ for the bottom compactors.
+For a budget of $m = \Omega(c^2(H-H')^2/\eps^2)$ for the buffers of the top compactors we guarantee an overall error of $\eps n/2$ for the top compactors.
+Since $H-H'$ by definition is
+$$ H-H' = O(\log(\log(1/\delta)/m\eps^2)) =  O(\log(\log(1/\delta)/c^2(H-H')^2)) $$
+we get that 
+$$ H-H' = O(\log(\log(1/\delta)/c^2)), \ \  m=O(c^2\log^2(\log(1/\delta))/\eps^2) $$
+Plugging in $m$ to the bound on the memory leads to the required claim.
+\end{proof}
+
+\zk{Still missing, Theorem~\ref{thm:streaming12} ...}
+
+%%%%%%%%%%%%%%
+%%%
+%%%
+%%%
+%%%%%%%%%%%%%%
+
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}

### 2019-01-16 komlos.tex
motivation for big thm

@@
 \begin{theorem} \label{thm:streaming22}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
@@
 As before we use a buffer of $m$ and get that $H \leq  \floor{log_2(n/m)}+1$.
-The difference is that for a compactor of level $h$, once $h \leq H' = H - \log(\log(1/\delta)/m\eps^2)$, meaning we know that the number of items observed by the $h$'th compactor, $n_h \geq \tilde{n} = O(\log(1/\delta)/\eps^2)$, we change the mode of operation for this compactor.
+The difference is that for a compactor of level $h$, once $h \leq H' = H - \log(\tilde{n}/m)$, where $\tilde{n} = O(\log(1/\delta)/\eps^2)$ with a constant in the $O()$ term that will be determined later, we change the mode of operation for this compactor.
+Notice that the requirement for $h$ ensures that the number of items observed by the $h$'th compactor is at least $n_h \geq \tilde{n}$.
 Rather than using a buffer of size $m$ the compactor uses a buffer of size 2 and for every two observed items it outputs one of them uniformly at random.
@@
 To analyze the memory requirement, notice that the compactors of levels $h=0,\ldots,H'$ are in fact performing reservoir sampling for every $2^{H'+1}$ items, meaning that they can be implemented in $O(1)$ memory.
-This means that the overall memory requirement is $O(m\log(\log(1/\delta)/m\eps^2))$.
-
-As for the error, for the layers of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n K_m$.
-Let us bound the error for the compactor of level $h \leq H'$.
+This means that the overall memory requirement is $O(m\log(\log(1/\delta)/m\eps^2))$; for $m \geq 1/\eps^2$ this is $O(m\log\log(1/\delta))$.
+
+We continue to bound the error.
+For the top compactors of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n K_m$.
+Since we will use $m \geq 1/\eps^2$ we get that the error for all top compactors is $O(nK_m\log\log(1/\delta))$.
+Consider now a compactor of level $h \leq H'$.
 For the first $\tilde{n}$ items it observed, the error is bounded by $2^h\tilde{n}K_m \leq 2^{h-H'}nK_m$.
@@
 $$ E_h = O\left(2^h n_h\frac{\eps}{2^{(H'-h)/2}}\right) = O(\eps n 2^{(h-H')/2}) $$
-We get that the sum of errors associated with the compactors of level $h=0,\ldots,H'$ for a geometric sequence dominated by the error of the $H'$ compactor, which is in turn $O(\eps n)$.
+We get that the sum of errors associated with the compactors of level $h=0,\ldots,H'$ form a geometric sequence dominated by the error of the $H'$ compactor, which is in turn $O(\eps n)$.
 For proper constants in $\tilde{n}$ we get a bound of $\eps n/2$ for the bottom compactors.
-For a budget of $m = \Omega(c^2(H-H')^2/\eps^2)$ for the buffers of the top compactors we guarantee an overall error of $\eps n/2$ for the top compactors.
-Since $H-H'$ by definition is
-$$ H-H' = O(\log(\log(1/\delta)/m\eps^2)) =  O(\log(\log(1/\delta)/c^2(H-H')^2)) $$
-we get that 
-$$ H-H' = O(\log(\log(1/\delta)/c^2)), \ \  m=O(c^2\log^2(\log(1/\delta))/\eps^2) $$
-Plugging in $m$ to the bound on the memory leads to the required claim.
-\end{proof}
+For a budget of $m = \Omega(c^2\log^2(\log(1/\delta))/\eps^2)$ for the buffers of the top compactors we guarantee an overall error of $\eps n/2$ for the top compactors.
+
+To conclude, we get an error of $\eps n$ w.p. $1-\delta$ for any fixed $q$ with a memory budget of
+$$O(m\log\log(1/\delta)) = O\left(c^2\log^3(\log(1/\delta))/\eps^2\right)$$
+as required.
+\end{proof}
+
+We are now ready for the proof of Theorem~\ref{thm:streaming12}.
+Here we extend the idea of \cite{DBLP:conf/focs/KarninLL16} applied for quantiles to general coresets.
+To explain the high level idea consider again the easier setting where we know $n$, the length of the stream in advance.
+As in the $K_m=c/\sqrt{m}$ case, we will split the compactor into top compactors acting deterministically and bottom compactors yielding random outputs.
+The issue comes from the choice of $m$.
+To handle the error of the top compactors we can choose $m=c/\eps \ll 1/\eps^2$.
+The fact that $m \ll 1/\eps^2$ means that the top random compactors observe a stream that is shorter than before and having a buffer of size 2 will result in a large error.
+To mitigate this we assign the compactors an exponentially decreasing buffer size starting from $m_h=m$, until reaching $m_h=2$.
+A careful analysis of the error will show that the bottom compactors have the required $\eps n$ error, while the overall memory they require is $O(m)$.
 
 \zk{Still missing, Theorem~\ref{thm:streaming12} ...}
+
+\paragraph{Theorem~\ref{thm:streaming12}} 
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+\begin{proof}
+\end{proof}
 

### 2019-01-17 komlos.tex
better appendix

@@
 
-\section{Appendix Appendix Appendix...}
-
-The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
+%\section{Appendix Appendix Appendix...}
+%
+%
+%The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
 A compactor consumes a stream of items and outputs another stream.
-The output stream contains at most half (in expectation) the items from the input stream with double the weight. 
-It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
-If the buffer is full, a compaction operation takes place. 
-The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
-$\max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
-Note that such a sequence is guarantied to exist by the definition of the discrepancy. 
-However, an algorithm for finding such a sequence might not exist. 
-From this point onwards, we assume the existence of such an algorithm.
-%In other words, our theorems hold for problems which admit such a solution.
-The compactor then outputs either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ with double the weight.
-
-We begin with showing some basic properties of deterministic compactors which always output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
+%The output stream contains at most half (in expectation) the items from the input stream with double the weight. 
+%It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
+%If the buffer is full, a compaction operation takes place. 
+%The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
+%$\max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
+%Note that such a sequence is guarantied to exist by the definition of the discrepancy. 
+%However, an algorithm for finding such a sequence might not exist. 
+%From this point onwards, we assume the existence of such an algorithm.
+%%In other words, our theorems hold for problems which admit such a solution.
+%The compactor then outputs either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ with double the weight.
+%
+%We begin with showing some basic properties of deterministic compactors which always output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
 Consider a single compaction and let $\tilde F_{+}$ denote the function evaluated on $\{ x_i | \sigma_i = 1\}$ (similarly $\tilde F_{-}$).
-Let $E(q) = \sum_i \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above. 
-$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
-$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
-Note that $|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
-Now, aggregating over the $n/m$ compactions we get that $|\tilde F(q) - F(q)| \le n K_m$. Moreover, the stream length is clearly cut (at least) in half.
-
-These facts alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
-The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
-Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
-A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
+%Let $E(q) = \sum_i \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above. 
+%$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
+%$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
+%Note that $|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
+%Now, aggregating over the $n/m$ compactions we get that $|\tilde F(q) - F(q)| \le n K_m$. Moreover, the stream length is clearly cut (at least) in half.
+%
+%These facts alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
+%The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
+%Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
+%A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
 The above gives a discrepancy of $1/m$ for quantile approximation.
-Below we generalize this algorithm to any low discrepancy class.
-
-\paragraph{Theorem~\ref{thm:streaming11}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
-\begin{proof}
-Consider feeding the output of the first compactor into a second one etc. Number the compactors $0,\ldots,H$.
-The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ we know that $H \le log(n/m)$.
-The total error is therefore $H n K_m \le log(n/m) n K_m$. 
-Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \el{TODO: double check the math.}
-\end{proof}
-
-\paragraph{Theorem~\ref{thm:streaming21}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
-\begin{proof}
-The proof is identical to the one above except for the variable setting of
-Setting $m \ge c^2\log^2(\eps^2 n/c^2)/\eps^2$ and replacing $K_m = c/\sqrt{m}$. 
-We get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \el{TODO: double check the math.}
-\end{proof}
-
-Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
-\el{Add the description of the randomized algorithms.}
-
-\zk{define compactor in an algorithm for thm about $\sqrt{m}$}
+%Below we generalize this algorithm to any low discrepancy class.
+%
+%\paragraph{Theorem~\ref{thm:streaming11}}
+%For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+%\begin{proof}
+%Consider feeding the output of the first compactor into a second one etc. Number the compactors $0,\ldots,H$.
+%The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
+%Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ we know that $H \le log(n/m)$.
+%The total error is therefore $H n K_m \le log(n/m) n K_m$. 
+%Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
+%Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \el{TODO: double check the math.}
+%\end{proof}
+%
+%\paragraph{Theorem~\ref{thm:streaming21}}
+%For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+%\begin{proof}
+%The proof is identical to the one above except for the variable setting of
+%Setting $m \ge c^2\log^2(\eps^2 n/c^2)/\eps^2$ and replacing $K_m = c/\sqrt{m}$. 
+%We get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
+%Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \el{TODO: double check the math.}
+%\end{proof}
+%
+%Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
+%\el{Add the description of the randomized algorithms.}
+%
+%\zk{define compactor in an algorithm for thm about $\sqrt{m}$}
 
@@
 
-\section{yet another  Appendix...}
+\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
 
@@
 To explain the high level idea consider again the easier setting where we know $n$, the length of the stream in advance.
-As in the $K_m=c/\sqrt{m}$ case, we will split the compactor into top compactors acting deterministically and bottom compactors yielding random outputs.
+As in the $K_m=c/\sqrt{m}$ case, we will split the compactors into the top $\log\log(1/\delta)$ ones acting deterministically and bottom compactors yielding random outputs.
 The issue comes from the choice of $m$.
-To handle the error of the top compactors we can choose $m=c/\eps \ll 1/\eps^2$.
+To handle the error of the top compactors it suffices to set $m=c/\eps \ll 1/\eps^2$.
 The fact that $m \ll 1/\eps^2$ means that the top random compactors observe a stream that is shorter than before and having a buffer of size 2 will result in a large error.
-To mitigate this we assign the compactors an exponentially decreasing buffer size starting from $m_h=m$, until reaching $m_h=2$.
-A careful analysis of the error will show that the bottom compactors have the required $\eps n$ error, while the overall memory they require is $O(m)$.
-
-\zk{Still missing, Theorem~\ref{thm:streaming12} ...}
+We can mitigate this by adding $\log(1/\eps)$ more deterministic compactors and replace the $\log\log(1/\delta)^2$ term in the memory requirement with $\left(\log\log(1/\delta)/\eps\right)^2$.
+If $\log(1/\delta) \gg 1/\eps$ then this is a good solution.
+However, for cases where $\eps$ is small we can avoid the $\log(1/\eps)$ term altogether.
+To do that, the random compactors will not have a buffer of size 2, but a buffer size of $m_h$ depending on their level.
+Specifically the sequence of $m_h$ starting from the top random level $h= H-\log\log(1/\delta)$ and ending with $h=0$ is exponentially decreasing until hitting the minimal buffer size of $2$.
+
+The memory requirement is now $O(m)$ and a careful analysis of the error will lead to an $\eps n$ term coming from the bottom layers.
+One subtle issue we will need to take into account is that for random compactors with budget $m_h>2$ the output stream is only half as long as the input stream in expectation.
+Luckily, the output stream length is sharply concentrated around its mean so a union bound can ensure that w.p.
+$1-\delta$ the output stream is not much longer than its expectation.
 
@@
 \begin{proof}
+We start by describing the algorithm, from the perspective of a compactor of level $h$.
+The compactor observes an input stream of items with weight $2^h$ and outputs a stream of weight $2^{h+1}$.
+When created the compactor has a budget of $m_h=m$.
+Once it outputs items to an output stream for the first time, a new compactor of level $h+1$ is created.
+We keep track of $H$, the level of the top compactor, that did not yet output any items.
+When $H$ is updated, compactors of level $h<H$ might restrict their budget.
+Specifically, for some $H'=H-O(\log\log(n/\delta))$ where we set the constant of the $O()$ term later, a compactor of level $h \leq H'$ sets its buffer size to
+$$ m_h = \max\left\{2, \ceil{(2/3)^{h-H'}m} \right\} $$
+compactors of level $h >H'$ have a buffer size of $m$.
+We note that although $n$ is present in the definition of $H'$ we can use a crude upper bound.
+Given that the dependence is doubly logarithmic the upper bound can be extremely crude.
+Furthermore, $\delta$ is typically set to be exponentially small, so we ignore this issue.
+
+Compactors of level $h >H'$ act in a deterministic manner.
+Namely, once the buffer is full with items $x_1,\ldots,x_m$ we find the sign assignment $\sigma$ giving $\left|\max_q \sum \sigma_i f(x_i, q)\right| < m_hK_{m_h}=mK_m$ and output the smallest of the sets $X_+=\{x_i | \sigma_i > 0 \}$, $X_- = \{x_i | \sigma_i < 0 \}$.
+Compactors of level $h \leq H'$ act in a random manner; they output either the items of $X_-$ or $X_+$ with equal probability.
+When the stream is finished the coreset consists of all the items in the buffers, along with their corresponding weight.
+
+Let's begin by analyzing the memory complexity of the algorithm.
+The top layers each require a buffer of size $m$, and there are $\log\log(n/\delta)$ such buffers.
+It follows that they require $O(\log\log(n/\delta)m)$ memory.
+The bottom layers are exponentially decreasing until hitting $m_h=2$.
+All layers with $m_h=2$ are stacked in a consecutive way so they are in fact doing reservoir sampling and can be implemented with $O(1)$ memory.
+The layers with $m_h>2$ are have exponentially growing weights ending at $m$, so the overall memory they require is $O(m)$.
+Concluding, the overall memory requirement is $O(\log\log(n/\delta)m)$.
+
+We are now ready to bound the error, starting with the bottom layers.
+Fix a query $q$.
+For a layer $h$ we will provide a high probability bound to both $E_h(q)$, the error associated to its output stream and the length of the output stream.
+Let $n_h$ be the overall number of items layer $h$ observes.
+Let $m_h$ be the buffer size of level $h$ at the end of the stream.
+Since having a larger buffer size only improves the error bound, we analyze the error as if the budget was set as $m_h$ to begin with.
+
+With the assumption of all compactions being done with a buffer of size $m_h$, the number of compactions is $n_h/m_h$ and the error associated with each compaction is a zero mean random variable, with an absolute value of $2^h m_h K_{m_h}$.
+The overall error $E_h(q)$ is the sum of these independent random variables.
+It follows from Chernoff-Hoeffding bound that for any $\eps_h > 0$,
+\begin{equation} \label{eq:err low1}
+\Pr\left[ E_h(q) > 2^h m_h K_{m_h} \eps_h n_h \right] = \exp \left( -\Omega\left( \eps_h^2 n_h m_h \right) \right)
+\end{equation}
+
+For a bound on the output length we will analyze the behavior of the compactor with the assumption that all compactions are done to $m$ elements.
+This is not the case but an upper bound for this scenario also bounds the scenario where $m_h$ is decreasing with time.
+Every compaction outputs a random number of items between $0$ and $m$, with an expected value of $m/2$.
+Again, using Chernoff-Hoeffding we get
+\begin{equation} \label{eq:outlen}
+\Pr\left[ n_{h+1} > n_h(1/2+1/\log(n)) \right] = \exp \left( -\Omega\left( \frac{n_h}{m \log^2(n)} \right) \right) 
+\end{equation}
+To bound this expression we derive a lower bounding on $n_h$. Notice that the compactors of levels $H'+1,\ldots,H$ are acting in a deterministic manner meaning that 
+$$n_h \geq n_{H'} \geq 2^{H-H'-1}n_{H-1} \geq 2^{H-H'-1}m = \Omega(\log^2(n)\log(\log(n)/\delta)m)$$
+where the constant in the $\Omega$ term can be controlled via constant defining $H'$. Plugging into Equation~\eqref{eq:outlen} leads to
+\begin{equation*} 
+\Pr\left[ n_{h+1} > n_h(1/2+1/\log(n)) \right] \leq \delta/2(\log_2(n)+3)
+\end{equation*}
+A union bound over $h=0,\ldots,\log_2(n)+2$ indicates that w.p. $1-\delta/2$, $n_h \leq 3n/2^h$ for all mentioned $h$ values. In particular this means that $H \leq \log_2(n)+2$ meaning that 
+\begin{equation} \label{eq:outlen2}
+\Pr\left[ \forall h, n_h \leq 3n/2^h \right] \geq 1-\delta/2
+\end{equation}
+
+We can now plug the upper bound for $n_h$ to Equation~\ref{eq:err low1} and achieve 
+\begin{equation} \label{eq:err low2}
+\Pr\left[ E_h(q) > m_h K_{m_h} \eps_h n \right] = \exp \left( -\Omega\left( \frac{\eps_h^2 m_h n}{2^h} \right) \right)
+\end{equation}
+Recall that $2^{H-H'-1} = \Omega(\log^2(n)\log(\log(n)/\delta))$ and $n \geq 2^{H-1}m$. Combining the two leads to $n = \Omega(2^{H'}\log(n/\delta)m)$. Now, since $m_h \geq (2/3)^{H'-h}m$ we have that
+$$
+\frac{\eps_h^2 n m_h}{2^h} = \Omega\left( (2/3)^{H'-h} \frac{\eps_h^2 2^{H'} \log(n/\delta) m^2}{2^h} \right) = \Omega\left( (4/3)^{H'-h} \eps_h^2 \log(n/\delta) m^2 \right)
+$$
+Plugging this into Equation~\eqref{eq:err low2}, with $\eps_h = (3/4)^{h-H'}/m$ and using $m_h K_{m_h} \leq c$ we get
+\begin{equation} \label{eq:err low3}
+\Pr\left[ E_h(q) > \frac{(3/4)^{h-H'} c}{m} n \right]  \leq \delta/2n
+\end{equation}
+Since $H' < n$ we get that w.p.\ $1-\delta/2$
+$$ \sum_{h=1}^H E_h(q) \leq (4c/m) n $$
+
+Concluding the analysis for the bottom $H'$ layers, w.p.\ at least $1-\delta$ their error is $(4c/m) n$ and the output stream of the $H'$ compactor outputs at most $3n/2^{H'+1}$ items, each having a weight of $2^{H'+1}$.
+With the length of the output stream we use the fact that the top layers are deterministic and can apply Lemma~\ref{lem:det compactor} to bound their error of each of these layers by
+$$ 3K_m n \leq (3c/m) n $$
+Since there are $O(\log\log(n/\delta))$ such layers, we conclude that for $m=\Omega(\log\log(n/\delta) c/\eps)$ with appropriate constant it holds for a fixed $q$, w.p.\ at least $1-\delta$ that the overall error of the sketch is bounded by $\eps n$.
+The resulting memory requirement $O(\log^2\log(n/\delta) c/\eps)$, as claimed.
+
+%According to Lemma~\ref{lem:det compactor} we know that for a compactor observing $n_h$ items of weight $w_h=2^h$, the error associated with the compactor will be deterministically bounded by $n_hw_hK_{m_h}$, and the number of items it outputs is in expectation $n_h/2$.
 \end{proof}
@@
 
-\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
-
-\begin{lemma} \label{lem:compactor}
-Assume we have black box access to a solver that for any integer $m$ and inputs $x_1,\ldots,x_m$ obtains signs $\sigma_1,\ldots,\sigma_m$ such that $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ for some function $f$ whose discrepancy is $K_m$.\footnote{An constant factor approximation algorithm achieving $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| = O(K_m)$ would also clearly suffice.}
-Then there exist a streaming algorithm requiring a memory buffer of $m$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_{n'}$ with the following properties
-\begin{itemize}
-\item $\{z_i\}_i$ is a subset of $\{x_i\}$
-\item $\E[n'] = n/2$
-\item For $\rho >0$, $\Pr[n' \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{m}\right)\right)$
-\item For any fixed query $q$, the error associated with $q$, defined as
-$$\text{Err}(q) = 2\sum_{i=1}^{n'} f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
-Can be decomposed as a sum
-$$\text{Err}(q) = \sum_{j=1}^{n/m} \text{Err}_j(q)$$
-where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
-\end{itemize}
-\end{lemma}
-
-Note that signs achieving $max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ are guarantied to exist by the definition of the discrepancy.
+%
+%\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
+%
+%\begin{lemma} \label{lem:compactor}
+%Assume we have black box access to a solver that for any integer $m$ and inputs $x_1,\ldots,x_m$ obtains signs $\sigma_1,\ldots,\sigma_m$ such that $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ for some function $f$ whose discrepancy is $K_m$.\footnote{An constant factor approximation algorithm achieving $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| = O(K_m)$ would also clearly suffice.}
+%Then there exist a streaming algorithm requiring a memory buffer of $m$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_{n'}$ with the following properties
+%\begin{itemize}
+%\item $\{z_i\}_i$ is a subset of $\{x_i\}$
+%\item $\E[n'] = n/2$
+%\item For $\rho >0$, $\Pr[n' \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{m}\right)\right)$
+%\item For any fixed query $q$, the error associated with $q$, defined as
+%$$\text{Err}(q) = 2\sum_{i=1}^{n'} f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
+%Can be decomposed as a sum
+%$$\text{Err}(q) = \sum_{j=1}^{n/m} \text{Err}_j(q)$$
+%where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
+%\end{itemize}
+%\end{lemma}
+%
+%Note that signs achieving $max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ are guarantied to exist by the definition of the discrepancy.
 In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
-
-\el{changed notation until here...}
-\begin{proof}
-The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
-$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
-Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
-$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
-$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
-
-%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
-%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
-%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
-%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
-%\el{this is clunky way to say this...}
-The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
+%
+%
+%\el{changed notation until here...}
+%\begin{proof}
+%The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
+%$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
+%Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
+%$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
+%$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
+%
+%%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
+%%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
+%%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
+%%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
+%%\el{this is clunky way to say this...}
+%The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
 Moreover, the output length is a sum of $n/k$ independent random variables with mean $k/2$ and a maximum value of $k$.
 Chernoff-Hoeffding's bound can guarantee the stated concentration around $\E[m]$.
-As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Radamacher r.v. scaled by a magnitude of at most $K_k$ as required.
-\end{proof}
-
-Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
-$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} $$
-This high probability bound will be used below for our streaming algorithm. 
-The high level idea is to have a sequence of streaming objects that we call compactors. 
-Each compactor receives an input stream and outputs a stream that is of half the size of the input (in expectation). 
-Eventually we get to a stream that is small enough to store in memory. 
-The randomized bound above shows that for the compactors that handle a large stream, 
-we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$. 
-That is true even if all they do is uniformly sample half of the stream. 
-However, for the compactors that observe the shorter streams, a high probability bound is no longer strong enough. 
-For those we will make use of the fact that $K_k \ll k$.
-
-\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
-Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
+%As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
+%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Radamacher r.v. scaled by a magnitude of at most $K_k$ as required.
+%\end{proof}
+%
+%Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
+%$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} $$
+%This high probability bound will be used below for our streaming algorithm. 
+%The high level idea is to have a sequence of streaming objects that we call compactors. 
+%Each compactor receives an input stream and outputs a stream that is of half the size of the input (in expectation). 
+%Eventually we get to a stream that is small enough to store in memory. 
+%The randomized bound above shows that for the compactors that handle a large stream, 
+%we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$. 
+%That is true even if all they do is uniformly sample half of the stream. 
+%However, for the compactors that observe the shorter streams, a high probability bound is no longer strong enough. 
+%For those we will make use of the fact that $K_k \ll k$.
+%
+%
+%\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
+%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
 The streaming algorithm operates as follows.
@@
 After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
-
-The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
+%
+%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
 For a query $q$ and hierarchy level $h$ we analyze the error
-$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
-Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
+%$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
+%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
 The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
@@
 The overall error for the query $q$ is the sum over all levels of its errors
-$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
-
-To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
-$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
-
-We are however interested in a high probability bound.
+%$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
+%
+%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
+%$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
+%
+%We are however interested in a high probability bound.
 Specifically we would like to guarantee for $\delta > 0$ that for any query $q$ the error is bounded by $\eps n$ w.p.\ at least $1-\delta$.
@@
 For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
-
-The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
-\begin{equation} \label{eq:Htag_nh}
- \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
-\end{equation}
-for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
-
-According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
-$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
-We can now union bound over all 
-$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
-and conclude that w.p.\ at least $1-\delta/2$
-\begin{equation} \label{eq:Htag}
-H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
-\end{equation}
-and
-\begin{equation} \label{eq:nh small}
-\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
-\end{equation}
-
-We proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
-$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
-$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
-$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
-$$
-We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
+%
+%The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
+%\begin{equation} \label{eq:Htag_nh}
+% \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
+%\end{equation}
+%for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
+%
+%According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
+%$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
+%We can now union bound over all 
+%$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
+%and conclude that w.p.\ at least $1-\delta/2$
+%\begin{equation} \label{eq:Htag}
+%H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
+%\end{equation}
+%and
+%\begin{equation} \label{eq:nh small}
+%\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
+%\end{equation}
+%
+%
+%We proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
+%$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
+%$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
+%$$
+%We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
 Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
 We get that since $n_h \leq 3n/2^h$
-$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
-\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
-$$
-In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
-$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
-and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
-$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
-and 
-$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
-
-We proceed to bound the error on the top layers $H'+1$ to $H$.
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
+%\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
+%$$
+%In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
+%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
+%and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
+%$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
+%and 
+%$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
+%
+%We proceed to bound the error on the top layers $H'+1$ to $H$.
 In these top layers we use a deterministic algorithm guaranteeing the stream is cut in half from layer to layer.
@@
 Since $2^{H+1} < n/k$ this gives a bound of
-$$
-H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
-$$
-$$
-O\left( \log \log(n/\delta) \right)
-$$
-leading to a bound of 
-$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
-and an overall bound of
-\begin{equation} \label{eq:err total}
-|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
-\end{equation}
-
-We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
+%$$
+%H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
+%$$
+%$$
+%O\left( \log \log(n/\delta) \right)
+%$$
+%leading to a bound of 
+%$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
+%and an overall bound of
+%\begin{equation} \label{eq:err total}
+%|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
+%\end{equation}
+%
+%We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
 Recall that we aim to deal with two settings.
@@
 We start by dealing with the first scenario.
-
-We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
-\begin{align*}
-\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
-  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
-    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
-\end{align*}
-We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
-$$
-\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
-(3/4)^{H'-h}
-$$
-For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
-\begin{align*}
- \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
-    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
-	   &  O\left( (1/2)^{H''-h}   \right) 
-\end{align*}
-
-If follows that 
-$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
-translating to an overall bound for the error of
-$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
-The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
+%
+%We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
+%\begin{align*}
+%\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
+%  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
+%    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
+%\end{align*}
+%We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
+%$$
+%\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
+%(3/4)^{H'-h}
+%$$
+%For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
+%\begin{align*}
+% \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
+%    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
+%	   &  O\left( (1/2)^{H''-h}   \right) 
+%\end{align*}
+%
+%If follows that 
+%$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
+%translating to an overall bound for the error of
+%$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
+%The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
 The top layers require $O(\log\log(n/\delta)k)$ memory.
@@
 $1-\delta$ and the overall memory requirement is
-$$ O\left( \log^2 \log(n/\delta) (\komconstant/\eps)  \right) $$
-
-We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
-\begin{align*}
-\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
-  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
-\end{align*}
-and 
-$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
-Plugging this to the overall error in Equation~\eqref{eq:err total} we get
-$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
-
-Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
-$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
-we get a bound of $\eps n$ for the error and a memory usage of 
-$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
-\end{proof}
+%$$ O\left( \log^2 \log(n/\delta) (\komconstant/\eps)  \right) $$
+%
+%
+%We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
+%\begin{align*}
+%\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
+%  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
+%\end{align*}
+%and 
+%$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
+%Plugging this to the overall error in Equation~\eqref{eq:err total} we get
+%$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
+%
+%Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
+%$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
+%we get a bound of $\eps n$ for the error and a memory usage of 
+%$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
+%\end{proof}
 

### 2019-01-17 komlos.tex
before merge

--- 2019-01-16 komlos.tex
@@
 We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
-
-\el{I am thinking about removing the $1/m$ from the definition. Pro: Its cleaner. Con: It's less like the Rademacher complexity. What do you think?} \zk{think of term in stead of complexity}
 \begin{definition}
@@
 This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescaled columns of the matrix $X$.
-\el{Is this result new?
-Hard to say...}
 \end{corollary}
@@
 %The algorithm works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
-\begin{theorem} \label{thm:disc simple kernel}
+\begin{theorem}
 The algorithm above achieves $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$.
@@
 \[
-|\sum_{i=1}^m \sigma_i K(x_i,q)| = |\sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} | = | \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)}| \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
+|\sum_{i=1}^m \sigma_i K(x_i,q)| = |\sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} | = \left| \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)}\right| \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\|
 \]
@@
 Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
-This matches and simplifies the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
-Theorem~\ref{thm:streaming21} leads to a deterministic streaming algorithm with a memory complexity of $O(\log^3(\eps^2 n)/\eps^2)$.
-For $L$-Lipchitz kernels, meaning $K$ such that $|K(x,q+h) - K(x,q)|/\|h\| \leq L$ for all $h \neq 0$, Theorem~\ref{thm:streaming22} leads to a randomized streaming algorithm with a memory complexity of $O\left(\log^3 \left( d \log\left(RLn/\delta\eps\right) \right) / \eps^2 \right)$ that succeeds finding a coreset with probability $1-\delta$.
-The parameter $R$ is the maximum norm of a query.
-The argument goes through a union bound over an $\eps/L$-net over vectors of norm at most $R$, the size of which is $(RL/\eps)^{O(d)}$.
+This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
+Along with an $\eps$-net argument, it also gives rise to a streaming algorithm for kernel density estimation with a memory requirement of $O\left(\log\left(d\log(1/\eps)\right)^3/\eps^2\right)$ vectors.
+\el{We should confirm this statement. I believe the Lipshitz constant of $m$ kernels can be $m$ so we might need another $d$ inside the inner $log$.}
 
-\paragraph{Note} Theorem~\ref{thm:disc simple kernel} provides an upper bound of $\sqrt{m}$ for the sign discrepancy.
-Even if this upper bound is tight, meaning there exist a set of vectors that achieve it, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
+\paragraph{Note} The Theorem above provides an upper bound of $\sqrt{m}$ for the sign discrepancy.
+One can in fact construct an example where this upper bound is indeed what the algorithm achieves.
+However, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
 We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
@@
 
-\zk{define compactor in an algorithm for thm about $\sqrt{m}$}
-
-%%%%%%%%%%%%%%
-%%%
-%%%
-%%%
-%%%%%%%%%%%%%%
-
-\section{yet another  Appendix...}
-
-The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
-A compactor consumes a stream of items and outputs another stream.
-The output stream contains at most half the items from the input stream with double the weight. 
-It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
-If the buffer is full, a compaction operation takes place. 
-The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
-$\max_q |\sum_i \sigma_i f(x_i,q)| \leq m K_m$. 
-Note that such a sequence is guarantied to exist by the definition of the discrepancy.
-For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
-That is, if it is possible to obtain a bound of $K_m$ yet we can only find signs obtaining a bound of $\tilde{K}_m$, our results for the obtainable signs apply for $\tilde{K}_m$.
-Given the sign vector $\sigma$, the compactor appends either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ to the output stream.
-
-Consider a stream of data points $x_1,\ldots,x_n$ and the output stream of a compactor $z_1,\ldots,z_{\tilde{n}}$. The error associated with the new stream w.r.t.\ a query $q$ is defined as
-$$ \sum_{i=1}^n f(x_i,q) - 2\sum_j f(z_j,q) \ .$$
-This is the difference between the value of $q$ on the original stream and the output stream.
-For a compactor we would like to bound both the length of the output stream, and the absolute value of its error.
-
-\begin{lemma} \label{lem:det compactor}
-A deterministic compactor output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
-Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $K_m n$
-\end{lemma}
-\begin{proof}
-We note that the argument about the length is obvious, so we proceed to bound the error.
-Consider a single compaction operation done on $m$ vectors $x_1,\ldots,x_m$.
-For a query $q$, let $F(q)=\sum_{i=1}^m f(x_i,q)$ be the evaluation on the items of the buffer.
-Let $\tilde F_{+}$ denote the function evaluated on $\{ x_i | \sigma_i = 1\}_{i=1}^m$ (similarly $\tilde F_{-}$ defined for negative signs).
-Also, let $E(q) = \sum_{i=1}^m \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above.
-We have that
-$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
-$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
-meaning that the error for the items of the single compaction is bounded by
-$$|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = mK_m$$
-Summing over all $n/m$ compactions we get that the overall error is bounded, in absolute value, by $nK_m$.
-\end{proof}
-
-Lemma~\ref{lem:det compactor} alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
-The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
-Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
-A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
-The above gives a discrepancy of $1/m$ for quantile approximation.
-Below we generalize this algorithm to any low discrepancy class.
-
-\paragraph{Theorem~\ref{thm:streaming11}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
-\begin{proof}
-Consider feeding the output of the first compactor into a second one etc.
-Specifically, we start with a single compactor and open a second once it produced any output, then open a third compactor once the second produced output, etc.
-Number the compactors $0,\ldots,H$. The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
-The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 
-Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $K_m = c/m$ we get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $m_0$, as required.
-Since we have $H = O(log(\eps n/c))$ compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. 
-\end{proof}
-
-\paragraph{Theorem~\ref{thm:streaming21}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
-\begin{proof}
-The proof is identical to the one above except for the variable setting of
-Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $K_m = c/\sqrt{m}$. 
-We get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $_0$, as required. 
-Since we have $H = O(log(\eps^2 n/c^2))$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c^2) /\eps^2\right)$. 
-\end{proof}
-
-We proceed to prove Theorem~\ref{thm:streaming22}.
-To understand the motivation consider first an easier setting where the overall stream length $n$ is known to us in advance.
-Since $|f(x,q)| \leq 1$, standard concentration bounds will show that by sampling each item w.p.\ $\log(1/\delta)/n\eps^2$ we get an output stream of length $\log(1/\delta)/\eps^2$, that for any fixed query $q$, with probability at least $1-\delta$ suffers an error of $\eps n$ for that query.
-We can feed this output stream into a deterministic sketch, and given that the input length for the deterministic sketch is $\log(1/\delta)/\eps^2$, Theorem~\ref{thm:streaming21} leads to the required guarantee.
-
-Because we do not know the stream length in advance, we operate as in the deterministic case with compactors.
-The difference will be that each compactor will keep a count of how many items it has seen.
-Once a compactor observed more than $\tilde{n} = O(\log(1/\delta)/\eps^2)$ items, it will no longer use a buffer of size $m$ but rather a buffer of size 2.
-For every two items observed it will output a single one uniformly at random.
-It is easy to see that a sequence of such compactors can in fact be implemented with $O(1)$ memory via reservoir sampling.
-The memory of this process is therefor identical, at least asymptotically, to
-
-\paragraph{Theorem~\ref{thm:streaming22}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
-\begin{proof}
-As in the deterministic setting we maintain a sequence of compactors of levels $h=0,\ldots,H$.
-Notice that the value of $H$ is increasing as the stream grows longer.
-Recall that a compactor of level $h$ observes elements of weight $2^h$ and outputs elements of weight $2^{h+1}$.
-As before we use a buffer of $m$ and get that $H \leq  \floor{log_2(n/m)}+1$.
-The difference is that for a compactor of level $h$, once $h \leq H' = H - \log(\log(1/\delta)/m\eps^2)$, meaning we know that the number of items observed by the $h$'th compactor, $n_h \geq \tilde{n} = O(\log(1/\delta)/\eps^2)$, we change the mode of operation for this compactor.
-Rather than using a buffer of size $m$ the compactor uses a buffer of size 2 and for every two observed items it outputs one of them uniformly at random.
-
-To analyze the memory requirement, notice that the compactors of levels $h=0,\ldots,H'$ are in fact performing reservoir sampling for every $2^{H'+1}$ items, meaning that they can be implemented in $O(1)$ memory.
-This means that the overall memory requirement is $O(m\log(\log(1/\delta)/m\eps^2))$.
-
-As for the error, for the layers of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n K_m$.
-Let us bound the error for the compactor of level $h \leq H'$.
-For the first $\tilde{n}$ items it observed, the error is bounded by $2^h\tilde{n}K_m \leq 2^{h-H'}nK_m$.
-Fix a query $q$; for the items following the first $\tilde{n}$ items the compactor is operating in the sampling mode.
-For every pair, the associated error w.r.t $q$ is a random variable, of mean zero and absolute value of at most $w_h=2^{h+1}$.
-There are $(n_h-\tilde{n})/2 \leq n_h$ such pairs and the overall error w.r.t.\ $q$ is the sum of these independent random variables.
-Chernoff bound implies that with probability $1-\delta$, the overall error is bounded by $E_h = O(w_h\sqrt{n_h\log(1/\delta)})$.
-Since $n_h \geq \tilde{n}2^{H'-h} = O(2^{H'-h}\log(1/\delta)/\eps^2)$ we get that
-$$ E_h = O\left(2^h n_h\frac{\eps}{2^{(H'-h)/2}}\right) = O(\eps n 2^{(h-H')/2}) $$
-We get that the sum of errors associated with the compactors of level $h=0,\ldots,H'$ for a geometric sequence dominated by the error of the $H'$ compactor, which is in turn $O(\eps n)$.
-For proper constants in $\tilde{n}$ we get a bound of $\eps n/2$ for the bottom compactors.
-For a budget of $m = \Omega(c^2(H-H')^2/\eps^2)$ for the buffers of the top compactors we guarantee an overall error of $\eps n/2$ for the top compactors.
-Since $H-H'$ by definition is
-$$ H-H' = O(\log(\log(1/\delta)/m\eps^2)) =  O(\log(\log(1/\delta)/c^2(H-H')^2)) $$
-we get that 
-$$ H-H' = O(\log(\log(1/\delta)/c^2)), \ \  m=O(c^2\log^2(\log(1/\delta))/\eps^2) $$
-Plugging in $m$ to the bound on the memory leads to the required claim.
-\end{proof}
-
-\zk{Still missing, Theorem~\ref{thm:streaming12} ...}
-
-%%%%%%%%%%%%%%
-%%%
-%%%
-%%%
-%%%%%%%%%%%%%%
-
 \section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}

### 2019-01-20 komlos.tex

--- 2019-01-17 komlos.tex
@@
 This paper defines the discrepancy for families of functions.  It shows that low discrepancy classes admit small offline and streaming coresets.
-We provide general techniques for bounding the discrepancy of machine learning problems and specifically does so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
+We provide general techniques for bounding the discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
 Our result resolves a long standing open question regarding minimal cardinality coresets for Gaussian kernel density estimation.  
@@
 
-\el{I am thinking about removing the $1/m$ from the definition. Pro: Its cleaner. Con: It's less like the Rademacher complexity. What do you think?} \zk{think of term in stead of complexity}
 \begin{definition}
@@
 Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$. This is an obvious equivalence when one thinks about $q$ is the model parameters.
-
-\noindent Notice that these definition are very similar to $R_m(\F)$ the Rademacher complexity.
-The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a random $\sigma$.
+Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$. 
+In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
+The set $A$ is the set of possible induces losses. Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
+The equivalence between the definitions is therefore straight forward.
+
+These definition are very similar to the Rademacher complexity $R_m(\F)$.
+The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
 Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the same ``discrepancy'' to define a different quantity than the one above.}
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the name ``discrepancy'' to define a different quantity than the one above.}
  We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
@@
 We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is in fact a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
+This set is, in fact, a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
@@
 Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
-We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}- F(q)| =  |E(q)|$.
+We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$.
 
@@
 We claim that low discrepancy implies concise streaming mergeable coresets as well. 
-This section assumes the existence of an algorithm for finding low discrepancy signs $\sigma$.
+Surprisingly, the space complexity of the streaming algorithms is only poly-logarithmically larger than the best offline coreset.
+This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
 
@@
 \begin{theorem} \label{thm:streaming22}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ \el{$O\left(c^2\log^3\log(n?/\delta) /\eps^2\right)$}whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
@@
 The main ideas are as follows.
-In the last section we argued that both $F_1$ and $F_{-1}$ are both good approximations for $F$.
-We can also take $F'$ which is $F_1$ or $F_{-1}$ equally likely.
-Clearly $|F' - F| \le |E|$ as before.
-But now, $\E[F'] = F$ as well.
-In the streaming algorithm, we apply this compaction (converting $F$ to $F'$) many times over small subset of items from the stream.
-This allows us to use standard concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $F'$ no longer has exactly half the size $F$.
+In the last section we argued that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
+We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
+Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
+In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
+This allows us to use concentration results to bound the overall error.
+The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ no longer has exactly half the size $F$.
 In the general setting, this only true in expectation.
@@
 \paragraph{Note} Theorem~\ref{thm:disc simple kernel} provides an upper bound of $\sqrt{m}$ for the sign discrepancy. 
-Even if this upper bound is tight, meaning there exist a set of vectors that achieve it, for real data with vectors clustered together, as one should expect when requiring a density estimation algorithm, we expect this algorithm to perform much better than the worst-case bound.
+This upper bound is tight since there exists a set of vectors that requires it. 
+For data that lends itself to density estimation, however, one should expect input vectors to be clustered together.
+In such cases, the algorithm algorithm above performs much better than the worst-case bound predicts.
 We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
-
 \bibliography{density}
@@
 Specifically, we start with a single compactor and open a second once it produced any output, then open a third compactor once the second produced output, etc.
-Number the compactors $0,\ldots,H$. The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
+Number the compactors $0,\ldots,H$. The weight of items given to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
+Each compactor contributes at most $w_h n_h K_m \le n K_m$ error.
+Moreover since $n_h \le n/2^h$ \el{and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
+TODO: Not sure this is going in the right direction...}
 The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 

### 2019-01-22 komlos.tex
minor stuff
typo fixes

@@
 We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$.
+For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ \zk{It seems confusing that we are moving from $f\in \F$ to a universal single function $f$, $f(q,x)$.
+I'm thinking of calling it $g \in \F$ above and saying the for $\Q \equiv \F$, meaning there is a bijective mapping between them, we have $g(x)=f(q,x)$ for all $x$, for any matching pair $f,q$}.
 One should think about $q$ as either the model parameters or a query for the sketch.
@@
 \end{definition}
-The discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
-Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$. 
+The discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any subset of $\X$ of size $m$.
+Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
+Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
@@
 
-To understand our motivation, consider the following informal explanation of the Radamacher Complexity applied to ML problems. 
-In PAC learning there exists a set of examples (with labels).
+To understand our motivation, consider the following informal explanation of the Rademacher Complexity applied to ML problems. 
+In PAC learning there exists a set of examples (often with labels).
 We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
-Having a low Radamacher complexity means that we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
+Having a low Rademacher complexity means that we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
 Low Rademacher complexity guaranties that, in expectation, twice the loss on the sample is roughly the same as the loss on the entire set.
 This translates to a generalization bound. 
-In other words, the Radamacher complexity gives a guarantee for the loss of coresets chosen uniformly at random.
+In other words, the Rademacher complexity gives a guarantee for the loss of coresets chosen uniformly at random.
 
@@
 We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is, in fact, a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
+This set is, in fact, a coreset. The discrepancy of a problem helps us determine the obtainable coreset size. 
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
@@
 \begin{theorem} \label{thm:streaming22}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ \el{$O\left(c^2\log^3\log(n?/\delta) /\eps^2\right)$}whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ \el{$O\left(c^2\log^3\log(n?/\delta) /\eps^2\right)$} \zk{its not a typo - we only need the dependence on $n$ in the case of $K_m=c/m$} whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \end{theorem}
@@
 
-\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+\item Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of any analog to Radamacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+We are not aware of any analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
 There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
@@
 %
-%\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
+%\item Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
 For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
@@
 We are now ready to apply Banaszczyk's theorem. 
-There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
+There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$, meaning $\|\psi\|_T \leq C$.
 Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that 
@@
 &\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)\\
-&\le& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2 \\
+&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2\left| \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \right| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2 \\
 \end{eqnarray*}
@@
 For data that lends itself to density estimation, however, one should expect input vectors to be clustered together.
-In such cases, the algorithm algorithm above performs much better than the worst-case bound predicts.
-We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
+In such cases, the algorithm above performs much better than the worst-case bound predicts. We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
 \bibliography{density}
@@
 %As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Radamacher r.v. scaled by a magnitude of at most $K_k$ as required.
+%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Rademacher r.v. scaled by a magnitude of at most $K_k$ as required.
 %\end{proof}
@@
 Number the compactors $0,\ldots,H$. The weight of items given to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error.
-Moreover since $n_h \le n/2^h$ \el{and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
-TODO: Not sure this is going in the right direction...}
+Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since the $H-1$ layer had outputs, we must have $m \leq n_{H-1}$ and
+$$  \log_2(m) \leq \log_2(n_{H-1}) \leq \log_2(n) - (H-1)$$
+leading to a bound $H \le \floor{log_2(n/m)}+1$.
 The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 

### 2019-01-27 komlos.tex
some related works

@@
 
-\begin{fact}
+\begin{fact} \label{fct:eps1}
 Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/m)$. Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$. There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
 \end{fact}
-\begin{fact}
+\begin{fact}  \label{fct:eps2}
 Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
@@
 \begin{itemize}
-\item coresets - motivation, some papers, streaming algorithms for coresets
+\item coresets - motivation, some papers, streaming algorithms for coresets.
+
+\item Streaming coresets - MRL, etc.
+It is in fact known that for certain family types, a random sample of size $\log(1/\delta)/\eps^2$ is an $\eps$-coreset with probability $1-\delta$.
+For example, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
 
@@
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of any analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
-There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
+We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+The connection between coresets and discrepancy have been known in the non-streaming setting.
+For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
 %
@@
 The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
+The authors provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
+It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
+$1-\delta$ for some kernel types.
 

### 2019-01-28 komlos.tex
changing definitions

--- 2019-01-20 komlos.tex
@@
 \newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
 
@@
 \begin{abstract}
-This paper defines the discrepancy for families of functions.  It shows that low discrepancy classes admit small offline and streaming coresets.
+This paper defines the notion of class discrepancy for families of functions.
+It shows that low discrepancy classes admit small offline and streaming coresets.
 We provide general techniques for bounding the discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
-Our result resolves a long standing open question regarding minimal cardinality coresets for Gaussian kernel density estimation.  
+Our result resolves a long standing open question regarding the coreset complexity of Gaussian kernel density estimation.  
 We provide two more related but independent results. 
@@
 
-\section{Discrepancy of a Function Class}
+\section{Class Discrepancy and Coreset Discrepancy}
+
+\todo{Write short intro for this section}
+\subsection{Class Discrepancy}
 We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
 
-\begin{definition}
-Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the discrepancy of $A$ is 
+\begin{definition}[\bf Class Discrepancy] \label{cd1}
+Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the class discrepancy of $A$ is 
 \[
-K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_i  \sigma_i  a_i\right| 
+K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_{i=1}^{m}  \sigma_i  a_i\right| 
 \]
@@
 %
-\begin{definition}
+\begin{definition}[\bf Class Discrepancy]\label{cd2}
 Let $f:\X,\Q\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+The class discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
 \[
@@
 %
-\begin{definition}
+\begin{definition}[\bf Class Discrepancy]\label{cd3}
 Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+The class discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
 \[
@@
 \end{definition}
-The discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
+The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
 Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
@@
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
-The set $A$ is the set of possible induces losses. Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
-The equivalence between the definitions is therefore straight forward.
+Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
+For the equivalence of Definition~\ref{cd1}, the set $A$ should be thought of as the set of possible induces losses. 
+Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
+The three equivalent definitions between the definitions is therefore straight forward.
 
@@
 We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is, in fact, a coreset. The discrepancy of a problem helps us determine what coreset sized are possible. 
+This set is, in fact, a coreset. The class discrepancy of a problem helps us determine what coreset sized are possible. 
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
@@
 
-\subsection{General Framework for Coresets}
-In what follows it will be convenient to use the notation $f(x,q)$ and consider $K_m(f)$.
-%
-%to represent the function family as a family of vectors representing the functions.
-The vector family will be denoted as $Q$, where we use $q$ to denote a single vector corresponding to a function.
-We a universal function $f$ such that $f(x,q)$ corresponds to the value of the function matching $q$ when applied to $x$.
-We will assume from hereon that for any $x,q$ $|f(x,q)| \leq 1$; this allows to simplify the presentation.
-Our results can extend to $|f(x,q)| \leq R$ and will have dependencies on the bound $R$.
-Achieving these bounds is a purely technical task that we defer for the sake of readability.
-Consider the function $F(q) = \sum_{i=1}^{m} f(x_i,q)$ and the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+\subsection{Coreset Complexity}
+Here, we point out a direct connection between Coreset Complexity and Class Discrepancy.
+The connection is a direct application of the folklore argument know as the ``the halving trick".
+
+\begin{definition} [\bf Coreset Complexity] For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
+For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
+The Coreset Complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
+\end{definition}
+
+\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
+\begin{fact}
+Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Coreset Complexity of $f$ $O(c/\eps)$.
+The constant $c$ does not depend on $m$.
+\end{fact}
+\begin{fact}
+Any function $f$ with Class Discrepancy $K_m(f) = O(c/\sqrt{m})$ has Coreset Complexity $O(c^2/\eps^2)$.
+The constant $c$ does not depend on $m$.
+\end{fact}
+\begin{proof}
+\noindent
+
+Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
 Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
 We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$.
-
-%
 The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-Note that we can select signs such that $|E(q)| \le m K_m(f)$.
-The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-The constant $c$ does not depend on $m$ but could depend on other parameters of the problem.
-
-\begin{fact}
-Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/m)$. Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$. There exists a coreset for $F$ of size $O(c/\eps)$ whose error is at most $\eps n$.
-\end{fact}
-\begin{fact}
-Let $f$ be a function with a corresponding discrepancy $K_m(f) = O(c/\sqrt{m})$.
-Let $F(q) = \sum_{i=1}^{n}f(x_i, q)$.
-There exists a coreset for $F$ of size $O(c^2/\eps^2)$ whose error is at most $\eps n$.
-\end{fact}
-
-\noindent Proving both facts is trivial and known in the folklore as ``the halving trick". 
+By Definition we can select signs such that $|E(q)| \le m K_m(f)$.
+
+Naturally, one could iterate this process.
 At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, we repeat the process and create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
+Then, create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
 Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
 Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
-
-\subsection{General Framework for Sketching}\label{sec:sketch}
-We claim that low discrepancy implies concise streaming mergeable coresets as well. 
-Surprisingly, the space complexity of the streaming algorithms is only poly-logarithmically larger than the best offline coreset.
-This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
+\end{proof}
+
+\subsection{Streaming Coreset Complexity}\label{sec:sketch}
+We claim that low Class Discrepancy implies concise streaming mergeable coresets as well. 
+%
+\begin{definition} [\bf Streaming Coreset Algorithm] 
+A streaming coreset algorithm for $f:\X,\Q \rightarrow \R$ receives and arbitrary set $\{x_1,\ldots,x_m\} \subset \X$ one item after the other.
+At time $t \le m$, the algorithm maintains a subset $S_t \subset \{x_1,\ldots,x_t\}$ and uses at most $O(|S_t|)$ auxiliary memory. 
+At the end of the stream, the algorithm must output $S$ and $w$ such that  $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$ where 
+$F(q) = \sum_{i=1}^{m} f(x_i,q)$ and $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$.
+The size of the streaming coreset is $\max_t |S_t|$.
+\end{definition}
+
+\begin{definition} [\bf Streaming Coreset Complexity] 
+The Streaming Coreset Complexity for $f:\X,\Q \rightarrow \R$ is the minimal streaming coreset size among all possible 
+streaming coreset algorithms for $f$.
+\end{definition}
+
+\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
+%This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
 
 \begin{theorem} \label{thm:streaming11}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Streaming Coreset Complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
+The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 \begin{theorem} \label{thm:streaming21}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+Any function $f$ with Class Discrepancy $K_m = O(c/\sqrt{m})$ has Streaming Coreset Complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
+The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 \begin{theorem} \label{thm:streaming12}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset randomized algorithm of size $O\left(c\log^2\log(n/\delta)/\eps\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Streaming Coreset Complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
 \end{theorem}
@@
 \begin{theorem} \label{thm:streaming22}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(1/\delta) /\eps^2\right)$ \el{$O\left(c^2\log^3\log(n?/\delta) /\eps^2\right)$}whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+Any function $f$ with Class Discrepancy $K_m(f) = O(c/\sqrt{m})$ has Streaming Coreset Complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
+The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
 \end{theorem}
 
-Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
+%Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
 Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
@@
 
-The algorithms must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
+The algorithms above must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
 The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
@@
 
-\section{The Complexity of Analytic Functions of Dot Products} \label{sec:analytic}
-
-Now that we proved the usefulness of discrepancy we move to upper bound it for common family functions.
+\section{Class Discrepancy of Analytic Functions of Dot Products} \label{sec:analytic}
+
+Now that we proved the usefulness of low discrepancy, we move to upper bound it for common family functions.
 We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or squared Euclidean distance $\|q-x\|^2$.
@@
 It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
+\todo{Can we say the same for $1/(1 + \exp(\ip{q,x}))$.
+It might be more interesting than the logistic loss cos it's not convex...}
 
@@
 %%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
-%%\el{this is clunky way to say this...}
+%%\todo{this is clunky way to say this...}
 %The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
@@
 %Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-%Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \el{TODO: double check the math.}
+%Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \todo: double check the math.}
 %\end{proof}
@@
 %We get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-%Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \el{TODO: double check the math.}
+%Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \todo: double check the math.}
 %\end{proof}
@@
 %Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
-%\el{Add the description of the randomized algorithms.}
+%\todo{Add the description of the randomized algorithms.}
 %
@@
 Each compactor contributes at most $w_h n_h K_m \le n K_m$ error.
-Moreover since $n_h \le n/2^h$ \el{and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
+Moreover since $n_h \le n/2^h$ \todo{and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
 TODO: Not sure this is going in the right direction...}
@@
 Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $K_m = c/\sqrt{m}$. 
-We get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $_0$, as required. 
+We get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the big-$O$ term of $m_0$, as required. 
 Since we have $H = O(log(\eps^2 n/c^2))$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c^2) /\eps^2\right)$. 
@@
 Once a compactor observed more than $\tilde{n} = O(\log(1/\delta)/\eps^2)$ items, it will no longer use a buffer of size $m$ but rather a buffer of size 2.
-For every two items observed it will output a single one uniformly at random.
+For every two items observed it will output one of them uniformly at random.
 It is easy to see that a sequence of such compactors can in fact be implemented with $O(1)$ memory via reservoir sampling.
-The memory of this process is therefor identical, at least asymptotically, to
+The memory of this process is therefor identical, at least asymptotically, to the above.
 
@@
 %
-%\el{changed notation until here...}
+%\todo{changed notation until here...}
 %\begin{proof}

### 2019-01-28 komlos.tex

@@
 \end{definition}
-The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any such set.
-Throughout the manuscript we assume a one to one mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$.
+The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any subset of $\X$ of size $m$.
+Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
+Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
@@
 We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is, in fact, a coreset. The class discrepancy of a problem helps us determine what coreset sized are possible. 
+This set is, in fact, a coreset. The class discrepancy of a problem helps us determine the obtainable coreset size. 
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
@@
 \begin{proof}
-\noindent
-
-Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
 Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
@@
 \begin{itemize}
-\item coresets - motivation, some papers, streaming algorithms for coresets
-
-\item Radamacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+\item coresets - motivation, some papers, streaming algorithms for coresets.
+
+\item Streaming coresets - MRL, etc.
+It is in fact known that for certain family types, a random sample of size $\log(1/\delta)/\eps^2$ is an $\eps$-coreset with probability $1-\delta$.
+For example, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
+
+\item Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of any analog to Radamacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
-There are papers such as \cite{tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
+We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+The connection between coresets and discrepancy have been known in the non-streaming setting.
+For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
 %
@@
 Number the compactors $0,\ldots,H$. The weight of items given to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error.
-Moreover since $n_h \le n/2^h$ \todo{and compactor number $H-1$ observed at least $m$ items we know that $H \le \floor{log_2(n/m)}+1$.
-TODO: Not sure this is going in the right direction...}
+
+Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since the $H-1$ layer had outputs, we must have $m \leq n_{H-1}$ and
+$$  \log_2(m) \leq \log_2(n_{H-1}) \leq \log_2(n) - (H-1)$$
+leading to a bound $H \le \floor{log_2(n/m)}+1$.
 The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 

### 2019-01-29 komlos.tex
eps net def

@@
 \noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-\begin{fact}
+\begin{fact} \label{fct:eps1}
 Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Coreset Complexity of $f$ $O(c/\eps)$.
@@
 \end{fact}
-\begin{fact}
+\begin{fact} \label{fct:eps2}.
 Any function $f$ with Class Discrepancy $K_m(f) = O(c/\sqrt{m})$ has Coreset Complexity $O(c^2/\eps^2)$.
@@
 \end{proof}
+
+Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
+Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
 
@@
 
-\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
+%\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
 %This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
+\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bound are only poly-logarithmically larger than their offline counterparts.
 
@@
 \end{theorem}
+
+\noindent In the stream setting we can achieve smaller coresets via a randomized approach.
+Our argument go through a union bound over a $\eps$-net for $\Q$ we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
+We note that although the size $|Q_\eps|$ is often exponential in the input size, our dependence over the failure probability is \emph{doubly} logarithmic, hence the extra log terms are still logarithmic in the input size.
 
@@
 The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
-Most of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}.
-Generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
+Although many of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}, generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
 The main ideas are as follows.
@@
 The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ no longer has exactly half the size $F$.
-In the general setting, this only true in expectation.
+In the general setting, this only holds in expectation.
 

### 2019-01-29 komlos.tex
some small edits

--- 2019-01-28 komlos.tex
@@
 In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
-Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \mathcal X$ are either sampled training examples or an arbitrary set of stream items.
-Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn i.i.d.\ from underlying distribution.
+Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \X$ are either sampled training examples or an arbitrary set of stream items.
+Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn i.i.d.\ from an underlying distribution.
 We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \mathcal Q$ to index into $\F$ explicitly $F(q) = \sum_{i=1}^{n} f(x_i, q)$ \zk{It seems confusing that we are moving from $f\in \F$ to a universal single function $f$, $f(q,x)$.
-I'm thinking of calling it $g \in \F$ above and saying the for $\Q \equiv \F$, meaning there is a bijective mapping between them, we have $g(x)=f(q,x)$ for all $x$, for any matching pair $f,q$}.
+For notational convenience we use a parameter $q \in \Q$ to index into $\F$ explicitly.
+In other words, there is a bijective mapping between $\Q \equiv \F$ such that $f(x) \in \F$ iff there exists $q\in\Q$ such that $f(x,q)=f(x)$.
+We keep using the two different functions $f:\X\rightarrow\R$ and $f:\X,\Q\rightarrow\R$ interchangeably. 
 One should think about $q$ as either the model parameters or a query for the sketch.
 
-The goal is to produce a coreset. This is a set of weights $w$ with at small number of non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
+The goal is to produce a coreset. This is a small set $S\subset [n]$ and weights $w \in\R_+^{n}$ such that $\tilde F(q) = \sum_{i \in S} w_i f(x_i,q)$ approximates $F(q)$.
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
 There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
@@
 \subsection{Coreset Complexity}
-Here, we point out a direct connection between Coreset Complexity and Class Discrepancy.
-The connection is a direct application of the folklore argument know as the ``the halving trick".
-
-\begin{definition} [\bf Coreset Complexity] For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
+In this section we point out a direct connection between coreset complexity and class discrepancy.
+The connection is a simple application of the folklore argument know as the ``the halving trick".
+For simplicity, in what follows we focus on functions $f$ whose range is $[0,1]$.
+
+\begin{definition} [\bf Coreset Complexity] 
+For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
 For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
-The Coreset Complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
+The coreset complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
 \end{definition}
@@
 \begin{fact}
-Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Coreset Complexity of $f$ $O(c/\eps)$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
 The constant $c$ does not depend on $m$.
@@
 \begin{fact}
-Any function $f$ with Class Discrepancy $K_m(f) = O(c/\sqrt{m})$ has Coreset Complexity $O(c^2/\eps^2)$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
 The constant $c$ does not depend on $m$.
@@
 \subsection{Streaming Coreset Complexity}\label{sec:sketch}
-We claim that low Class Discrepancy implies concise streaming mergeable coresets as well. 
+We claim that low class discrepancy implies concise streaming mergeable coresets as well. 
 %
@@
 \begin{definition} [\bf Streaming Coreset Complexity] 
-The Streaming Coreset Complexity for $f:\X,\Q \rightarrow \R$ is the minimal streaming coreset size among all possible 
+The streaming coreset complexity for $f:\X,\Q \rightarrow \R$ is the minimal streaming coreset size among all possible 
 streaming coreset algorithms for $f$.
@@
 \begin{theorem} \label{thm:streaming11}
-Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Streaming Coreset Complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
 The constant $c$ does not depend on $m$.
@@
 \begin{theorem} \label{thm:streaming21}
-Any function $f$ with Class Discrepancy $K_m = O(c/\sqrt{m})$ has Streaming Coreset Complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
+Any function $f$ with class discrepancy $K_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
 The constant $c$ does not depend on $m$.
@@
 \begin{theorem} \label{thm:streaming12}
-Any function $f$ with Class Discrepancy $K_m(f) = O(c/m)$ has Streaming Coreset Complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
 The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
@@
 \begin{theorem} \label{thm:streaming22}
-Any function $f$ with Class Discrepancy $K_m(f) = O(c/\sqrt{m})$ has Streaming Coreset Complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
 The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
@@
 Let $f$ be a function of the inner product $f(x,q) = f(\langle x,q\rangle)$ and let $f = \sum_k \alpha_k \langle x,q\rangle^k$ be its Taylor expansion. 
-The discrepancy of $f$ indexed by $\|q\| \leq 1$ is bounded by
+The class discrepancy of $f$ indexed by $\|q\| \leq 1$ is bounded by
 \[
@@
 \begin{theorem}\label{analitic1}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has discrepancy $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 \begin{corollary}
-The discrepancy of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+The class discrepancy of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
 \end{corollary}
@@
 \begin{corollary}
-The discrepancy of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+The class discrepancy of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
 This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescaled columns of the matrix $X$.
@@
 \begin{theorem} \label{thm:analytic2}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has discrepancy $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 \begin{corollary}
-The discrepancy of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
+The class discrepancy of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
 \end{corollary} 
@@
 \section{A Simple Algorithm for Kernel Density Estimation}
-From section \ref{sec:analytic} we know that the discrepancy of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. 
+From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. 
 %The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently. 
@@
 $\max_q |\sum_i \sigma_i f(x_i,q)| \leq m K_m$. 
-Note that such a sequence is guarantied to exist by the definition of the discrepancy.
+Note that such a sequence is guarantied to exist by the definition of the class discrepancy.
 For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
@@
 A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
-The above gives a discrepancy of $1/m$ for quantile approximation.
+The above gives class discrepancy of $1/m$ for quantile approximation.
 Below we generalize this algorithm to any low discrepancy class.
 
+\todo{Replace with the above?}
 \paragraph{Theorem~\ref{thm:streaming11}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
 \begin{proof}
@@
 \paragraph{Theorem~\ref{thm:streaming21}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}
@@
 \paragraph{Theorem~\ref{thm:streaming22}}
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \begin{proof}
@@
 \paragraph{Theorem~\ref{thm:streaming12}} 
-For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}

### 2019-01-29 komlos.tex

@@
 For bounded functions $f$, uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
-While $|\mathcal Q|$ is often infinite it reduces to a finite (albeit usually exponentially large) set through standard epsilon net arguments. 
+While $|\mathcal Q|$ is often infinite it can be replaced by a finite (albeit usually exponentially large) epsilon net $Q_\eps$. 
 %
 We present a mechanism for producing coresets which are much smaller than those achieved by sampling for a large class of problems in a unified manner.  
-Moreover, our solution creates streaming algorithms with fully mergeable sketches. 
-The size of the coreset above appears to be intimately tied to the discrepancy properties of the associated functions.
-
-\section{Class Discrepancy and Coreset Discrepancy}
+Moreover, our solutions create streaming algorithms with fully mergeable sketches. 
+The size of the coreset above appears to be intimately tied to the class discrepancy properties of the associated functions.
+
+\section{Class Discrepancy and Coreset Complexity}
 
@@
 \noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-\begin{fact}
+\begin{fact}\label{fct:eps1}
 Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
@@
 \end{fact}
-\begin{fact}
+\begin{fact}\label{fct:eps2}
 Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
@@
 
+Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
+Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
+
 \subsection{Streaming Coreset Complexity}\label{sec:sketch}

### 2019-01-29 komlos.tex
switch section order

@@
 We provide general techniques for bounding the discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
-Our result resolves a long standing open question regarding the coreset complexity of Gaussian kernel density estimation.  
+Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
 We provide two more related but independent results. 
@@
 Second, an extremely simple algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
-This paper makes an explicit connection between low discrepancy, coresets, learnability, and streaming algorithms. 
+This paper establishes some explicit connections between low class discrepancy, coreset complexity, learnability, and streaming algorithms. 
 \end{abstract}
@@
 \section{Introduction}
-In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
-Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \X$ are either sampled training examples or an arbitrary set of stream items.
-Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn i.i.d.\ from an underlying distribution.
-We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \Q$ to index into $\F$ explicitly.
-In other words, there is a bijective mapping between $\Q \equiv \F$ such that $f(x) \in \F$ iff there exists $q\in\Q$ such that $f(x,q)=f(x)$.
-We keep using the two different functions $f:\X\rightarrow\R$ and $f:\X,\Q\rightarrow\R$ interchangeably. 
-One should think about $q$ as either the model parameters or a query for the sketch.
-
-The goal is to produce a coreset. This is a small set $S\subset [n]$ and weights $w \in\R_+^{n}$ such that $\tilde F(q) = \sum_{i \in S} w_i f(x_i,q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
-There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
-Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
-Moreover, if the resulting coresets are mergeable, this could be done on separate streams without the need for communication or assuming randomness in the partitioning.
-
-For bounded functions $f$, uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
-While $|\mathcal Q|$ is often infinite it can be replaced by a finite (albeit usually exponentially large) epsilon net $Q_\eps$. 
-%
-We present a mechanism for producing coresets which are much smaller than those achieved by sampling for a large class of problems in a unified manner.  
-Moreover, our solutions create streaming algorithms with fully mergeable sketches. 
-The size of the coreset above appears to be intimately tied to the class discrepancy properties of the associated functions.
-
-\section{Class Discrepancy and Coreset Complexity}
-
-\todo{Write short intro for this section}
-\subsection{Class Discrepancy}
-We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
-
-\begin{definition}[\bf Class Discrepancy] \label{cd1}
-Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the class discrepancy of $A$ is 
-\[
-K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_{i=1}^{m}  \sigma_i  a_i\right| 
-\]
-\end{definition}
-%
-\begin{definition}[\bf Class Discrepancy]\label{cd2}
-Let $f:\X,\Q\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The class discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
-\[
-K_m(f) =  \min_{\sigma} \max_{q \in \Q}  \left|\frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
-\]
-\end{definition}
-%
-\begin{definition}[\bf Class Discrepancy]\label{cd3}
-Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
-The class discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
-\[
-K_m(\F) =  \min_{\sigma} \max_{f \in \F}  \left| \frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i)\right|
-\]
-\end{definition}
-The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any subset of $\X$ of size $m$.
-Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
-In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
-Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
-For the equivalence of Definition~\ref{cd1}, the set $A$ should be thought of as the set of possible induces losses. 
-Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
-The three equivalent definitions between the definitions is therefore straight forward.
-
-These definition are very similar to the Rademacher complexity $R_m(\F)$.
-The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
-Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the name ``discrepancy'' to define a different quantity than the one above.}
- We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
-Trivially,  $K_m \le R_m$. We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
-
-To understand our motivation, consider the following informal explanation of the Rademacher Complexity applied to ML problems. 
-In PAC learning there exists a set of examples (often with labels).
-We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
-Having a low Rademacher complexity means that we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
-Low Rademacher complexity guaranties that, in expectation, twice the loss on the sample is roughly the same as the loss on the entire set.
-This translates to a generalization bound. 
-In other words, the Rademacher complexity gives a guarantee for the loss of coresets chosen uniformly at random.
-
-Coming back to discrepancy. Having the ability to choose the signs arbitrarily lets us choose an advantageous subset of examples.
-We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
-This set is, in fact, a coreset. The class discrepancy of a problem helps us determine the obtainable coreset size. 
-We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
-This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
-This intuition is restated more explicitly in the next section.
-
-\subsection{Coreset Complexity}
-In this section we point out a direct connection between coreset complexity and class discrepancy.
-The connection is a simple application of the folklore argument know as the ``the halving trick".
-For simplicity, in what follows we focus on functions $f$ whose range is $[0,1]$.
-
-\begin{definition} [\bf Coreset Complexity] 
-For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
-For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
-The coreset complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
-\end{definition}
-
-\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-\begin{fact}\label{fct:eps1}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
-The constant $c$ does not depend on $m$.
-\end{fact}
-\begin{fact}\label{fct:eps2}
-Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
-The constant $c$ does not depend on $m$.
-\end{fact}
-\begin{proof}
-\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
-We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$.
-The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-By Definition we can select signs such that $|E(q)| \le m K_m(f)$.
-
-Naturally, one could iterate this process.
-At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
-Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
-Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
-\end{proof}
-
-Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
-Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
-
-\subsection{Streaming Coreset Complexity}\label{sec:sketch}
-We claim that low class discrepancy implies concise streaming mergeable coresets as well. 
-%
-\begin{definition} [\bf Streaming Coreset Algorithm] 
-A streaming coreset algorithm for $f:\X,\Q \rightarrow \R$ receives and arbitrary set $\{x_1,\ldots,x_m\} \subset \X$ one item after the other.
-At time $t \le m$, the algorithm maintains a subset $S_t \subset \{x_1,\ldots,x_t\}$ and uses at most $O(|S_t|)$ auxiliary memory. 
-At the end of the stream, the algorithm must output $S$ and $w$ such that  $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$ where 
-$F(q) = \sum_{i=1}^{m} f(x_i,q)$ and $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$.
-The size of the streaming coreset is $\max_t |S_t|$.
-\end{definition}
-
-\begin{definition} [\bf Streaming Coreset Complexity] 
-The streaming coreset complexity for $f:\X,\Q \rightarrow \R$ is the minimal streaming coreset size among all possible 
-streaming coreset algorithms for $f$.
-\end{definition}
-
-%\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
-%This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
-\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bound are only poly-logarithmically larger than their offline counterparts.
-
-\begin{theorem} \label{thm:streaming11}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
-The constant $c$ does not depend on $m$.
-\end{theorem}
-
-\begin{theorem} \label{thm:streaming21}
-Any function $f$ with class discrepancy $K_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
-The constant $c$ does not depend on $m$.
-\end{theorem}
-
-\noindent In the stream setting we can achieve smaller coresets via a randomized approach.
-Our argument go through a union bound over a $\eps$-net for $\Q$ we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
-We note that although the size $|Q_\eps|$ is often exponential in the input size, our dependence over the failure probability is \emph{doubly} logarithmic, hence the extra log terms are still logarithmic in the input size.
-
-\begin{theorem} \label{thm:streaming12}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
-The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
-The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
-\end{theorem}
-
-\begin{theorem} \label{thm:streaming22}
-Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
-The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
-The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
-\end{theorem}
-
-%Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
-Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
-Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provides a coreset for an entire family that matches the non-streaming version up to poly-logarithmic terms.
-
-The algorithms above must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
-The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
-Although many of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}, generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
-The main ideas are as follows.
-In the last section we argued that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
-We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
-Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
-In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
-This allows us to use concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ no longer has exactly half the size $F$.
-In the general setting, this only holds in expectation.
-
-\section{Related Work}
+
 \begin{itemize}
@@
 \end{itemize}
+
+\section{Class Discrepancy and Coreset Complexity}
+
+In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
+Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \X$ are either sampled training examples or an arbitrary set of stream items.
+Standard generalization results show that for a large enough value of $n$ the average approximates the mean if the complexity of $\F$ is bounded and the samples $x_i$ are drawn i.i.d.\ from an underlying distribution.
+We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
+For notational convenience we use a parameter $q \in \Q$ to index into $\F$ explicitly.
+In other words, there is a bijective mapping between $\Q \equiv \F$ such that $f(x) \in \F$ iff there exists $q\in\Q$ such that $f(x,q)=f(x)$.
+We keep using the two different functions $f:\X\rightarrow\R$ and $f:\X,\Q\rightarrow\R$ interchangeably. 
+One should think about $q$ as either the model parameters or a query for the sketch.
+
+The goal is to produce a coreset. This is a small set $S\subset [n]$ and weights $w \in\R_+^{n}$ such that $\tilde F(q) = \sum_{i \in S} w_i f(x_i,q)$ approximates $F(q)$.
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
+There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
+Generating a concise representation $\tilde F$ for $F$ allows one to optimize over $\tilde F$ instead of $F$ which is more efficient. 
+Moreover, if the resulting coresets are mergeable, this could be done on separate streams without the need for communication or assuming randomness in the partitioning.
+
+For bounded functions $f$, uniform sampling of $O(\log(1/\delta)/\eps^2)$ combined with a union bound over $|\mathcal Q|$ always provides a valid solution using $O(\log(|\mathcal Q|)/\eps^2)$ items. 
+While $|\mathcal Q|$ is often infinite it can be replaced by a finite (albeit usually exponentially large) epsilon net $Q_\eps$. 
+%
+We present a mechanism for producing coresets which are much smaller than those achieved by sampling for a large class of problems in a unified manner.  
+Moreover, our solutions create streaming algorithms with fully mergeable sketches. 
+The size of the coreset above appears to be intimately tied to the class discrepancy properties of the associated functions.
+
+\subsection{Class Discrepancy}
+We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript.
+
+\begin{definition}[\bf Class Discrepancy] \label{cd1}
+Let $A \subset \R^m$ and $\sigma \in \{-1,1\}^m$ the class discrepancy of $A$ is 
+$
+K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_{i=1}^{m}  \sigma_i  a_i\right| 
+$.
+\end{definition}
+%
+\begin{definition}[\bf Class Discrepancy]\label{cd2}
+Let $f:\X,\Q\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The class discrepancy of $f$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+$
+K_m(f) =  \min_{\sigma} \max_{q \in \Q}  \left|\frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
+$.
+\end{definition}
+%
+\begin{definition}[\bf Class Discrepancy]\label{cd3}
+Let $\F$ be a family of functions $f:\X\rightarrow\R$ and $\sigma \in \{-1,1\}^m$. 
+The class discrepancy of $\F$ w.r.t.\ $\{x_1,\ldots,x_m\} \subset \X$ is 
+$
+K_m(\F) =  \min_{\sigma} \max_{f \in \F}  \left| \frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i)\right|
+$.
+\end{definition}
+The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any subset of $\X$ of size $m$.
+Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
+Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
+In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
+Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
+For the equivalence of Definition~\ref{cd1}, the set $A$ should be thought of as the set of possible induces losses. 
+Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
+The three equivalent definitions between the definitions is therefore straight forward.
+
+These definition are very similar to the Rademacher complexity $R_m(\F)$.
+The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
+Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the name ``discrepancy'' to define a different quantity than the one above.}
+ We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
+Trivially,  $K_m \le R_m$. We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+
+To understand our motivation, consider the following informal explanation of the Rademacher Complexity applied to ML problems. 
+In PAC learning there exists a set of examples (often with labels).
+We aim to find a regressor/classifier from a given family that suffers the least loss on the set. 
+Having a low Rademacher complexity means that we can optimize over a sample of roughly half the examples at random (each w.p.\ $1/2$).
+Low Rademacher complexity guaranties that, in expectation, twice the loss on the sample is roughly the same as the loss on the entire set.
+This translates to a generalization bound. 
+In other words, the Rademacher complexity gives a guarantee for the loss of coresets chosen uniformly at random.
+
+Coming back to discrepancy. Having the ability to choose the signs arbitrarily lets us choose an advantageous subset of examples.
+We can algorithmically choose to minimize the induced error and guaranty to have (roughly) the same performance on the entire set. 
+This set is, in fact, a coreset. The class discrepancy of a problem helps us determine the obtainable coreset size. 
+We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
+This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
+This intuition is restated more explicitly in the next section.
+
+\subsection{Coreset Complexity}
+In this section we point out a direct connection between coreset complexity and class discrepancy.
+The connection is a simple application of the folklore argument know as the ``the halving trick".
+For simplicity, in what follows we focus on functions $f$ whose range is $[0,1]$.
+
+\begin{definition} [\bf Coreset Complexity] 
+For a function $f:\X,\Q\rightarrow \R$ let $F(q) = \sum_{i=1}^{m} f(x_i,q)$ for a any set $\{x_1,\ldots,x_m\} \subset \X$.
+For a set $S \subset [m]$ let $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$ for some $w\in\R_+^m$ which is independent of $q$.
+The coreset complexity of $f$ is the size of the smallest set $S$ such that $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$.
+\end{definition}
+
+\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
+\begin{fact}\label{fct:eps1}
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
+The constant $c$ does not depend on $m$.
+\end{fact}
+\begin{fact}\label{fct:eps2}
+Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
+The constant $c$ does not depend on $m$.
+\end{fact}
+\begin{proof}
+\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$.
+We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$.
+The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
+By Definition we can select signs such that $|E(q)| \le m K_m(f)$.
+
+Naturally, one could iterate this process.
+At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
+Then, create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
+Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
+Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
+\end{proof}
+
+Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
+Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
+
+\subsection{Streaming Coreset Complexity}\label{sec:sketch}
+We claim that low class discrepancy implies concise streaming mergeable coresets as well. 
+%
+\begin{definition} [\bf Streaming Coreset Algorithm] 
+A streaming coreset algorithm for $f:\X,\Q \rightarrow \R$ receives and arbitrary set $\{x_1,\ldots,x_m\} \subset \X$ one item after the other.
+At time $t \le m$, the algorithm maintains a subset $S_t \subset \{x_1,\ldots,x_t\}$ and uses at most $O(|S_t|)$ auxiliary memory. 
+At the end of the stream, the algorithm must output $S$ and $w$ such that  $\forall q \in \Q \; |F(q)  - \tilde F(q)| \le \eps m$ where 
+$F(q) = \sum_{i=1}^{m} f(x_i,q)$ and $\tilde F(q) = \sum_{i \in S}w_i f(x_i,q)$.
+The size of the streaming coreset is $\max_t |S_t|$.
+\end{definition}
+
+\begin{definition} [\bf Streaming Coreset Complexity] 
+The streaming coreset complexity for $f:\X,\Q \rightarrow \R$ is the minimal streaming coreset size among all possible 
+streaming coreset algorithms for $f$.
+\end{definition}
+
+%\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
+%This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
+\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bound are only poly-logarithmically larger than their offline counterparts.
+
+\begin{theorem} \label{thm:streaming11}
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
+The constant $c$ does not depend on $m$.
+\end{theorem}
+
+\begin{theorem} \label{thm:streaming21}
+Any function $f$ with class discrepancy $K_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
+The constant $c$ does not depend on $m$.
+\end{theorem}
+
+\noindent In the stream setting we can achieve smaller coresets via a randomized approach.
+Our argument go through a union bound over a $\eps$-net for $\Q$ we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
+We note that although the size $|Q_\eps|$ is often exponential in the input size, our dependence over the failure probability is \emph{doubly} logarithmic, hence the extra log terms are still logarithmic in the input size.
+
+\begin{theorem} \label{thm:streaming12}
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
+\end{theorem}
+
+\begin{theorem} \label{thm:streaming22}
+Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
+The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
+\end{theorem}
+
+%Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
+Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
+Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provides a coreset for an entire family that matches the non-streaming version up to poly-logarithmic terms.
+
+The algorithms above must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
+The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
+Although many of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}, generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
+The main ideas are as follows.
+In the last section we argued that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
+We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
+Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
+In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
+This allows us to use concentration results to bound the overall error.
+The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ no longer has exactly half the size $F$.
+In the general setting, this only holds in expectation.
 

### 2019-01-29 komlos.tex
edits

@@
 \end{definition}
-
 \noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
+\todo{add citation to jeff's thesis}.
 \begin{fact}\label{fct:eps1}
@@
 Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
-The constant $c$ does not depend on $m$.
+%The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 Any function $f$ with class discrepancy $K_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
-The constant $c$ does not depend on $m$.
+%The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 \noindent In the stream setting we can achieve smaller coresets via a randomized approach. 
-Our argument go through a union bound over a $\eps$-net for $\Q$ we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
-We note that although the size $|Q_\eps|$ is often exponential in the input size, our dependence over the failure probability is \emph{doubly} logarithmic, hence the extra log terms are still logarithmic in the input size.
+Our argument goes through a union bound over an $\eps$-net for $\Q$ which we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
+We note that the size $|Q_\eps|$ is often exponential in the problem parameters. 
+Nevertheless, our dependence on the failure probability is \emph{doubly} logarithmic. 
+This means the dependence on the problem parameters is still only polylogarithmic.
 

### 2019-01-30 komlos.tex
const does not depent on m
bad intro

@@
 It shows that low discrepancy classes admit small offline and streaming coresets.
-We provide general techniques for bounding the discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
+We provide general techniques for bounding the class discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
 Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
@@
 \section{Introduction}
-
-\begin{itemize}
-\item coresets - motivation, some papers, streaming algorithms for coresets.
-
-\item Streaming coresets - MRL, etc.
-It is in fact known that for certain family types, a random sample of size $\log(1/\delta)/\eps^2$ is an $\eps$-coreset with probability $1-\delta$.
-For example, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
-
-\item Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+The study of coresets in optimization as a whole and in machine learning specifically has a long history. 
+The basic setup is as follows.
+Suppose you are trying to optimize an expression over a set of items, data points, or examples.
+The optimization problem is difficult and often exponential in the input set size.
+Therefore, there is a strong incentive to reduce the cardinality of that set. 
+The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
+This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
+clustering \cite{DBLP:conf/compgeom/Har-PeledK05} \cite{DBLP:conf/stoc/FeldmanL11}, classification \cite{DBLP:conf/ijcai/Har-PeledRZ07}, regression \cite{DBLP:conf/nips/MunteanuSSW18} 
+machine learning \cite{bachem2017practical}, density estimation \cite{DBLP:journals/corr/abs-1802-01751}, and many other problems.
+
+Obtaining small coresets and understanding the coreset complexity of different problems is of significant theoretical and practical importance.
+While some problems obviously do not admit small coresets, other do. 
+There are several results that connect the simplicity of the measure and its coreset complexity (the size of the minimal coreset).
+In this manuscript, we focus solely on sums of functions applied to the input items.
+That is, for $\{x_i,\ldots,x_n\} \subset \X$ we measure $F(q) = \sum_i f(x_i,q)$ for $q \in \Q$ which is either some model parameters or a query.
+For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x,q}))$ and $x,q\in \R^d$.
+Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
+In general, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
+For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
+For Gaussian kernel density, it is know that a sample size of $O(1/\eps^2)$ suffices independently of $d$.
+
+Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
@@
 For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
-%
-% There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
-For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
-However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
-
-%
-%\item Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944}, There is literature about the complexity of active learning for the supervised setting but that is out of scope as we deal with the setting where all labels are available, or the problem is unsupervised.
-For the complexity of coresets, the total sensitivity of the dataset and the VC dimension of the function class is often used as tools for construction \zk{cite something?}.
-However, to the best of our knowledge there is no clear characterization of the size of coresets based on some complexity measure of the dataset and function class.
-
-\item Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
+
+Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
 Among other applications, this tool is used for outlier detection \cite{schubert2014generalized}, regression \cite{fan2018local}, and clustering \cite{rinaldo2010generalized}.
@@
 For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
-Their result holds for Lipchitz bounded positive semi-definite kernels.
+Their result holds for any Lipchitz bounded positive semi-definite kernels.
 The result is constructive though it is polynomial rather than (quasi-)linear in the data size.
@@
 The authors provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
-It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
+It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
 $1-\delta$ for some kernel types.
-
-\item Logistic Regression is an extremely popular technique for classification.
+In this paper we resolve this question and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$ which matches the lower bound provided by \cite{DBLP:journals/corr/abs-1802-01751}.
+In fact, we should that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
+Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
+
+Logistic Regression is an extremely popular technique for classification.
 We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
@@
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
-
-\item Linear Regression \cite{DBLP:journals/jmlr/DerezinskiW18}
-%\item coreset of logistic regression  \cite{DBLP:journals/corr/abs-1805-08571}, \cite{DBLP:conf/nips/HugginsCB16}.
-Give multiplicative approximation.
-This is impossible in general so they depend on a different restriction on the regressor or dataset.
-Based on sensitivity scores.
-\cite{DBLP:conf/nips/HugginsCB16} use a heuristic of using $k$-means to approximate sensitivity scores and prove that given good sensitivity scores they get a good coreset.
-\cite{tolochinsky2018coresets} gives a generic coreset construction for any monotonic function as long as it comes with an $\ell_2^2$ regularization.
-The dependence they get is, ignoring polynomial factors, $d/\eps^2$.
-\cite{DBLP:journals/corr/abs-1805-08571} have a different method, relying on a measure of complexity of the dataset and obtain roughly $\sqrt{n}d^{3/2}/\eps^2$ sized dataset.
-\end{itemize}
 
@@
 Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
-The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+$Q_\eps$ is an epsilon net for $f$ on $\Q$. 
 The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
@@
 Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
-The constant $c$ does not depend on $m$, $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+$Q_\eps$ is an epsilon net for $f$ on $\Q$. 
 The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
@@
 
-Now that we proved the usefulness of low discrepancy, we move to upper bound it for common family functions.
+Now that we proved the usefulness of low class discrepancy, we move to upper bound it for common family functions.
 We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or squared Euclidean distance $\|q-x\|^2$.

### 2019-01-30 komlos.tex
minor stuff

--- 2019-01-29 komlos.tex
@@
 By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
-It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$ or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
-\todo{Can we say the same for $1/(1 + \exp(\ip{q,x}))$.
-It might be more interesting than the logistic loss cos it's not convex...}
+It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$, sigmoid activation $\sigma(q,x)=1/(1 + \exp(\ip{q,x}))$, or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
 

### 2019-01-30 komlos.tex
section 2.2

@@
 That is, for $\{x_i,\ldots,x_n\} \subset \X$ we measure $F(q) = \sum_i f(x_i,q)$ for $q \in \Q$ which is either some model parameters or a query.
-For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x,q}))$ and $x,q\in \R^d$.
+For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x_i,q}))$ and $x,q\in \R^d$.
 Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
@@
 
-\noindent In the stream setting we can achieve smaller coresets via a randomized approach. 
-Our argument goes through a union bound over an $\eps$-net for $\Q$ which we denote by $Q_\eps$, meaning a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$.
-We note that the size $|Q_\eps|$ is often exponential in the problem parameters. 
-Nevertheless, our dependence on the failure probability is \emph{doubly} logarithmic. 
-This means the dependence on the problem parameters is still only polylogarithmic.
+Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21} are achieved by deterministic algorithms. 
+They could be thought of extensions of the MRL algorithm \cite{MRL} for streaming quantile sketching. 
+Quantile sketching falls into this framework since it corresponds to $f(x,q) = 1$ if $x>q$ and $0$ else. 
+More details and the proof of correctness are given in Appendix ~\ref{app:sketch proof}.
+
+Recently, {\cite{DBLP:conf/focs/KarninLL16} provided an improved (optimal) streaming quantile coreset algorithm. 
+Generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} requires more work. 
+The main ideas are as follows. 
+We argued above that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
+We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
+Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
+In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
+This allows us to use concentration results to bound the overall error.
+The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ has half the support of $F$ only in expectation.
 
@@
 
-%Notice that the randomized versions above hold w.h.p.\ for any fixed $f \in \F$.
-Although $\F$ is typically inifinite, it is almost always the case that there exists an $\eps$-net over $\F$ whose size is exponential in the input parameters.
-Since the dependence over the error probability is doubly logarithmic, the randomized versions coupled with a union bound provides a coreset for an entire family that matches the non-streaming version up to poly-logarithmic terms.
-
-The algorithms above must be given $\eps, \delta$ as input but do not need to know the length of the stream, $n$, in advance. 
-The proofs of the above two theorems are quite technical and delegated to Appendix~\ref{app:sketch proof}.
-Although many of the ideas are already present in the recent breakthrough work on streaming quantiles \cite{DBLP:conf/focs/KarninLL16}, generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} required resolving some added complications.
-The main ideas are as follows.
-In the last section we argued that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
-We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
-Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
-In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
-This allows us to use concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ no longer has exactly half the size $F$.
-In the general setting, this only holds in expectation.
+The set $Q_\eps$ is an $\eps$-net for $\Q$. 
+It is a finite subset of $\Q$ such that for every $q \in \Q$ there exist some $\tilde{q} \in Q_\eps$ for which $\sup_{x \in \X} |f(q,x) - f(\tilde{q},x)| < \eps$. 
+We note that the size $|Q_\eps|$ is often exponential in the problem parameters. 
+Nevertheless, our dependence on the failure probability is \emph{doubly} logarithmic. 
+This means the dependence on the problem parameters is still only polylogarithmic.
 
@@
 We provide a coreset suitable for analytical functions of the inner product $\ip{q,x}$ or squared Euclidean distance $\|q-x\|^2$.
-
+%
 The idea is to find a set of signs that simultaneously balance $\ip{q,x}^k$ for all powers $k$ and unit vectors\footnote{We Assume that $\|x\|,\|q\| \leq 1$ for ease of presentation.
@@
 By controlling all powers of $\ip{q,x}$ we control any sum of these powers.
-It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$, sigmoid activation $\sigma(q,x)=1/(1 + \exp(\ip{q,x}))$, or the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$.
+It follows that this coreset can be used to control, for example, the logistic loss function $L(q,x) = \log(1+\exp(\ip{q,x}))$, the gaussian Kernel $K(q,x) = \exp(-\lambda \|q-x\|^2)$, or the sigmoid activation loss $1/(1 + \exp(\ip{q,x}))$.
 

### 2019-01-31 komlos.tex
minor change

--- 2019-01-30 komlos.tex
@@
 Suppose you are trying to optimize an expression over a set of items, data points, or examples.
-The optimization problem is difficult and often exponential in the input set size.
+%The optimization problem is difficult and often exponential in the input set size.
+The optimization problem is difficult and often square, cubic or even exponential in the input set size.
 Therefore, there is a strong incentive to reduce the cardinality of that set. 
@@
 For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
-For Gaussian kernel density, it is know that a sample size of $O(1/\eps^2)$ suffices independently of $d$.
+For Gaussian kernel density, it is known that a sample size of $O(1/\eps^2)$ suffices independently of $d$  \cite{lopez2015towards}.
 
@@
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-The connection between coresets and discrepancy have been known in the non-streaming setting.
+%The connection between coresets and discrepancy have been known in the non-streaming setting.
 For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
+The connection between coresets and discrepancy have been known in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 
@@
 The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
-The authors provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
+Additionally, they provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
 It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
 $1-\delta$ for some kernel types.
-In this paper we resolve this question and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$ which matches the lower bound provided by \cite{DBLP:journals/corr/abs-1802-01751}.
-In fact, we should that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
+In this paper we resolve the open question by \cite{DBLP:journals/corr/abs-1802-01751} and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$, matching the lower bound.
+In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
 Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
@@
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
+Our results mentioned above prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.
 
@@
 \noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-\todo{add citation to jeff's thesis}.
+Although they were previously known (see e.g., \cite{phillips2009small}, Theorem 1.1) we give their proof here for completeness.
 \begin{fact}\label{fct:eps1}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
-The constant $c$ does not depend on $m$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
+%The constant $c$ does not depend on $m$.
 \end{fact}
@@
 Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
-The constant $c$ does not depend on $m$.
+%The constant $c$ does not depend on $m$.
 \end{fact}
@@
 The above gives class discrepancy of $1/m$ for quantile approximation.
-Below we generalize this algorithm to any low discrepancy class.
-
-\todo{Replace with the above?}
+%Below we generalize this algorithm to any low discrepancy class.
+Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21} below generalize this algorithm to any low discrepancy class.
+
+\el{Replace with the above?} \zk{changed `Below we generalize this algorithm to any low discrepancy class.' to the line above. Does that resolve the issue?}
 \paragraph{Theorem~\ref{thm:streaming11}}
@@
 \paragraph{Theorem~\ref{thm:streaming12}} 
-For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+$Q_\eps$ is an epsilon net for $f$ on $\Q$. 
+The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
+%For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}

### 2019-01-31 komlos.tex
typo

@@
 Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
-Taking for example the bound of Fact~\ref{fct:eps1}, we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
+Taking for example the bound of Fact~\ref{fct:eps1}, if we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
 

### 2019-01-31 komlos.tex
small edits

--- 2019-01-31 komlos.tex
@@
 It shows that low discrepancy classes admit small offline and streaming coresets.
-We provide general techniques for bounding the class discrepancy of machine learning problems and specifically do so for matrix covariance approximation, logistic regression, kernel density and any analytic function of the dot product or the squared distance.
+We provide general techniques for bounding the class discrepancy of machine learning problems.
+As corollaries of the general technique we bound the discrepancy of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
 Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
@@
 First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
-Second, an extremely simple algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
-This paper establishes some explicit connections between low class discrepancy, coreset complexity, learnability, and streaming algorithms. 
+Second, an extremely simple deterministic algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
+This paper establishes some explicit connections between class discrepancy, coreset complexity, learnability, and streaming algorithms. 
 \end{abstract}
@@
 Suppose you are trying to optimize an expression over a set of items, data points, or examples.
-%The optimization problem is difficult and often exponential in the input set size.
-The optimization problem is difficult and often square, cubic or even exponential in the input set size.
+The optimization problem is difficult and often exponential in the input set size.
 Therefore, there is a strong incentive to reduce the cardinality of that set. 
@@
 Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
-In general, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
+In general, for families of VC dimension $v$, a sample of $(v+\log(1/\delta))/\eps^2$ suffices \cite{talagrand1994sharper}.
 For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
-For Gaussian kernel density, it is known that a sample size of $O(1/\eps^2)$ suffices independently of $d$  \cite{lopez2015towards}.
-
-Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+For Gaussian kernel density, it is know that a sample size of $O(1/\eps^2)$ suffices independently of $d$.
+
+Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
@@
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-%The connection between coresets and discrepancy have been known in the non-streaming setting.
+The connection between coresets and discrepancy have been known in the non-streaming setting.
 For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
-The connection between coresets and discrepancy have been known in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 
@@
 A thorough survey could be found in \cite{silverman2018density}.
-Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
+Given a set of $n$ data points $\{x_1,\ldots,x_n\}$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
 The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that
@@
 The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds.
-Additionally, they provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
+The authors provide a simple algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
 It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
 $1-\delta$ for some kernel types.
-In this paper we resolve the open question by \cite{DBLP:journals/corr/abs-1802-01751} and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$, matching the lower bound.
-In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
+In this paper we resolve this question and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$ which matches the lower bound provided by \cite{DBLP:journals/corr/abs-1802-01751}.
+In fact, we should that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
 Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
@@
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
-Our results mentioned above prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.
 
@@
 We begin by giving three equivalent definitions of complexity based on discrepancy for sets, functions, and function families. We will use all three interchangeably throughout the manuscript. 
+Our notation is intentionally similar to the definition of the Rademacher complexity for reasons that will become clear later.
 
@@
 \noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
-Although they were previously known (see e.g., \cite{phillips2009small}, Theorem 1.1) we give their proof here for completeness.
+\todo{add citation to jeff's thesis}.
 \begin{fact}\label{fct:eps1}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
-%The constant $c$ does not depend on $m$.
+Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $f$ $O(c/\eps)$.
+The constant $c$ does not depend on $m$.
 \end{fact}
@@
 Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
-%The constant $c$ does not depend on $m$.
+The constant $c$ does not depend on $m$.
 \end{fact}
@@
 Let $x_1,\ldots,x_n$ be vectors with $\|x_i\| \leq 1$. 
-Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
+Then, there exist signs $\sigma$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some constant $C$.
 
@@
 \begin{theorem}\label{analitic1}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that functions $f = f(\ip{q,x})$, indexed by $\|q\| \leq R$, have class discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 The above gives class discrepancy of $1/m$ for quantile approximation.
-%Below we generalize this algorithm to any low discrepancy class.
-Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21} below generalize this algorithm to any low discrepancy class.
-
-\el{Replace with the above?} \zk{changed `Below we generalize this algorithm to any low discrepancy class.' to the line above. Does that resolve the issue?}
+Below we generalize this algorithm to any low discrepancy class.
+
+\todo{Replace with the above?}
 \paragraph{Theorem~\ref{thm:streaming11}}
@@
 \paragraph{Theorem~\ref{thm:streaming12}} 
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
-$Q_\eps$ is an epsilon net for $f$ on $\Q$. 
-The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
-%For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}

### 2019-01-31 komlos.tex

--- 2019-01-31 komlos.tex
@@
 Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
-In general, for families of VC dimension $v$, a sample of $(1/\eps^2)(v+\log(1/\delta))$ suffices \cite{talagrand1994sharper}.
+In general, for families of VC dimension $v$, a sample of $(v+\log(1/\delta))/\eps^2$ suffices \cite{talagrand1994sharper}.
 For logistic regression and many other problems $O(d/\eps)$ samples are enough due to fast rate generalization results \cite{van2015fast}.
@@
 
-Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d sampled points.
+Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
@@
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-%The connection between coresets and discrepancy have been known in the non-streaming setting.
-For example, \cite{phillips2009small} (Theorem 1.1) provide an analog to our Facts~\ref{fct:eps1},~\ref{fct:eps2}.
-The connection between coresets and discrepancy have been known in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
+Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 

### 2019-01-31 komlos.tex
post manual merge

@@
 They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$.
-The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is complexity measure of the dataset.
+The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
 \cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
-Our results mentioned above prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.
+Our results prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.
 
@@
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
-Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
-For the equivalence of Definition~\ref{cd1}, the set $A$ should be thought of as the set of possible induces losses. 
+%Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
+The set $A$ should be thought of as the set of all possible induces losses vectors. 
 Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
-The three equivalent definitions between the definitions is therefore straight forward.
-
-These definition are very similar to the Rademacher complexity $R_m(\F)$.
+
+\todo{This paragraph seems to be repeated/duplicated bellow.}
+
+These definition are intentionally very similar to those of the Rademacher complexity $R_m(\F)$.
 The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
 Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the name ``discrepancy'' to define a different quantity than the one above.}
- We claim that $K_m$ is the measure more suitable for creating coresets and for creating mergeable sketches.
-Trivially,  $K_m \le R_m$. We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the term ``discrepancy'' to define a different quantity than the one above.}
+We claim that $K_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
+Trivially,  $K_m \le R_m$. 
+We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+This immediately proves the existence of small coresets for these problems.
 

### 2019-02-01 komlos.tex
minor touches intro

@@
 Therefore, there is a strong incentive to reduce the cardinality of that set. 
-The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
+The goal is therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
 This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
@@
 
-Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
+%Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
 A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
@@
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
-
+%Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
+
+Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
+We aim here to find an analog for actively selected, rather than i.i.d.\ sampled, points.
+\cite{langberg2010universal, tolochinsky2018coresets} and references within tie the coreset complexity to the VC dimension of the family function, and the average sensitivity of the dataset.
+However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+We point out the connection between the discrepancy of a function family, informally defined as the result of a two player game, one choosing a set of signs and the other a function from the family, and coreset complexity.
+Is is known that small discrepancy implies an offline coreset construction algorithm  (see e.g.\ \cite{phillips2009small}, Theorem 1.1).
+In this paper we point out this connection and provide an algorithm taking use of a small discrepancy bound to construct a coreset in the streaming setting, as well as the offline setting.
+
+An important application of our generic coreset results is in the area of Kernel density estimation.
 Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
@@
 Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
-
+Although the worst case lower bound is $1/\eps^2$, we conjecture that in realistic scenarios, the deterministic algorithm should outperform random sampling as it explicitly takes advantage of negative correlations.
+
+Another application of our coreset results applies to logistic regression.
 Logistic Regression is an extremely popular technique for classification.

### 2019-02-01 komlos.tex
edits

--- 2019-01-31 komlos.tex
@@
 %\usepackage{amsthm}
+\usepackage{algorithm}
 \usepackage[noend]{algorithmic}
-\usepackage{algorithm}
+%\usepackage{algorithmic}
+%\usepackage{algorithm}
+%\usepackage[noend]{algorithmic}
 %\usepackage[margin=1in]{geometry}
@@
 
-\usepackage[]{algorithm2e}
+\usepackage{algorithm2e}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cdlogistic}
 The class discrepancy of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
 \end{corollary}
+\begin{corollary}\label{cdsigmoid}
+The class discrepancy of the sigmoid activation loss function $f(\ip{q,x}) = 1/(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
+\end{corollary}
 
@@
 The class discrepancy of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
-This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescaled columns of the matrix $X$.
+This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains only $O(\sqrt{d}/\eps)$ rescaled columns of the matrix $X$.
 \end{corollary}
@@
 \begin{theorem} \label{thm:analytic2}
-Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
+Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function $f(\|x-q\|^2)$, indexed by $\|q\| \leq R$, has class discrepancy $O(\sqrt{d}/m)$. 
 \end{theorem}
@@
 This also resolves the open problem raised by \cite{DBLP:journals/corr/abs-1802-01751} and matches their lower bound.   
-
-\begin{proof}
-W.l.o.g. the maximum distance $\|q-x\|$ is 1. The Taylor series of the Gaussian kernel $K$ becomes
-$ \sum_{k=0}^\infty \frac{(-\gamma)^k}{k!} $.
+For non-constant $\gamma$ assume w.l.o.g. $\|q-x\| \le 1$. The Taylor series of the Gaussian kernel $K$ exhibits $|\alpha_k| \le \gamma^k/k!$.
 Plugging into the equation in the proof of Theorem~\ref{thm:analytic2} we get that the sum determining the constant is upper bounded by
-$ \sum_{k=0}^\infty \frac{\gamma^{k}\sqrt{ k\log^3(k)}}{k!} = O\left((1+\gamma) \exp(\gamma)\right)$.
-\end{proof}
+$\sum_{k=1}^\infty \gamma^{k}(k\log^3(k))^{1/2}/k! = O\left((1+\gamma) \exp(\gamma)\right)$.
+
 %\end{proof}
@@
 More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
-Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
-$$ F(q) = \sum_{i=1}^{n} K(x_i,q) $$
-Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
-$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
+Given a collection of data points $X = \{x_1,\ldots, x_n\}$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as $ F(q) = \sum_{i=1}^{n} K(x_i,q) $.
+Here, $K$ is any \emph{positive semi-definite kernel} function. The most frequent examples include
+$$ K(x,q) = \exp(- \|x-q\|_2^2/\lambda^2),\;\; K(x,q) = \exp(- \|x-q\|/\lambda) ,\;\;  K(x,q) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
 where $\lambda$ is a scaling parameter.
 For simplicity, we assume that $K(x,x) \leq 1$ for all data points.
-Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.
-
-\begin{algorithm}[H]
- \KwData{Kernel function $K:(\R^d,\R^d)\rightarrow[0,1]$, points  $x_1,\ldots,x_m$}
- \KwResult{$\sigma \in \{-1,1\}^m$ such that $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$}
- $\sigma_1 = 1$;\\
- \For{$i = 2,\ldots,m$}
- {$\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$}
-% \EndFor
-\caption{Low Discrepancy Algorithm for Positive Kernels}
+Notice that for any kernel based on the distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.
+
+\begin{algorithm}
+\begin{algorithmic}
+\STATE {\bf input:} Kernel function $K:(\R^d,\R^d)\rightarrow[0,1]$, points  $\{x_1,\ldots,x_m\}$
+\STATE {\bf output:} $\sigma \in \{-1,1\}^m$ such that $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$
+\STATE$\sigma_1 = 1$
+\FOR {$i = 2,\ldots,m$} 
+        \STATE $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$
+\ENDFOR 
+\end{algorithmic}
+\caption{Low Discrepancy Algorithm for Positive Kernels}\label{kernelAlg}
 \end{algorithm}
 
-%The algorithm works as follows: Set $\sigma_1 = 1$. For $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
 \begin{theorem} \label{thm:disc simple kernel}
-The algorithm above achieves $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$.
+Algorithm \ref{kernelAlg} achieves $\max_q |\sum_i \sigma_i K(x_i,q) | \le \sqrt{m}$.
 \end{theorem}
@@
 \begin{proof}
-For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
+For any positive semi-definite kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
 $ K(x,q) = \ip{\phi(x), \phi(q)} $.
@@
 We show by induction on $i$ that 
-$$\left\| \sum_{j=1}^i \sigma_j \phi(x_j) \right\|^2 \le \sum_{j=1}^i \left\|\phi(x_j)\right\|^2 \leq i$$
+$\left\| \sum_{j=1}^i \sigma_j \phi(x_j) \right\|^2 \le \sum_{j=1}^i \left\|\phi(x_j)\right\|^2 \leq i$.
 This is trivially true for $i=1$ since $\|\phi(x)\| \leq 1$. 
@@
 
-Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
+Using the framework above provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde F(q) - F(q)| \le \eps n$.
 This matches and simplifies the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
 Theorem~\ref{thm:streaming21} leads to a deterministic streaming algorithm with a memory complexity of $O(\log^3(\eps^2 n)/\eps^2)$.
-For $L$-Lipchitz kernels, meaning $K$ such that $|K(x,q+h) - K(x,q)|/\|h\| \leq L$ for all $h \neq 0$, Theorem~\ref{thm:streaming22} leads to a randomized streaming algorithm with a memory complexity of $O\left(\log^3 \left( d \log\left(RLn/\delta\eps\right) \right) / \eps^2 \right)$ that succeeds finding a coreset with probability $1-\delta$.
+For $L$-Lipchitz kernels, meaning $K$ such that $|K(x,q+h) - K(x,q)|/\|h\| \leq L$ for all $h \neq 0$, Theorem~\ref{thm:streaming22} leads to a randomized streaming algorithm with a memory complexity of $O\left(\log^3 \left( d \log\left(RLn/\delta\eps\right) \right) / \eps^2 \right)$ that succeeds in finding a coreset with probability $1-\delta$.
 The parameter $R$ is the maximum norm of a query.

### 2019-02-01 komlos.tex
K to D

@@
 $
-K_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_{i=1}^{m}  \sigma_i  a_i\right| 
+D_m(A)  = \min_\sigma \max_{a\in A} \left| \frac{1}{m} \sum_{i=1}^{m}  \sigma_i  a_i\right| 
 $.
@@
 $
-K_m(f) =  \min_{\sigma} \max_{q \in \Q}  \left|\frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
+D_m(f) =  \min_{\sigma} \max_{q \in \Q}  \left|\frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i,q)\right|
 $.
@@
 $
-K_m(\F) =  \min_{\sigma} \max_{f \in \F}  \left| \frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i)\right|
+D_m(\F) =  \min_{\sigma} \max_{f \in \F}  \left| \frac{1}{m} \sum_{i=1}^{m}\sigma_i f(x_i)\right|
 $.
@@
 See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the term ``discrepancy'' to define a different quantity than the one above.}
-We claim that $K_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
-Trivially,  $K_m \le R_m$. 
-We show, however, that $K_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+We claim that $D_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
+Trivially,  $D_m \le R_m$. 
+We show, however, that $D_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
 This immediately proves the existence of small coresets for these problems.
@@
 We will show in the following sections several examples for which a coreset can be significantly smaller than the random sample while maintaining the same guarantees.
-This will be done by showing that for a wide range of interesting problems in machine learning $K_m(\F) = o(R_m(\F))$.
+This will be done by showing that for a wide range of interesting problems in machine learning $D_m(\F) = o(R_m(\F))$.
 This intuition is restated more explicitly in the next section.
@@
 \end{definition}
-\noindent The following facts are true for the common cases where $K_m = O(c/m)$ or $K_m = O(c/\sqrt{m})$.
+\noindent The following facts are true for the common cases where $D_m = O(c/m)$ or $D_m = O(c/\sqrt{m})$.
 Although they were previously known (see e.g., \cite{phillips2009small}, Theorem 1.1) we give their proof here for completeness.
 \begin{fact}\label{fct:eps1}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
 %The constant $c$ does not depend on $m$.
@@
 \begin{fact}\label{fct:eps2}
-Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
 %The constant $c$ does not depend on $m$.
@@
 The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-By Definition we can select signs such that $|E(q)| \le m K_m(f)$.
+By Definition we can select signs such that $|E(q)| \le m D_m(f)$.
 
@@
 \begin{theorem} \label{thm:streaming11}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
 %The constant $c$ does not depend on $m$.
@@
 \begin{theorem} \label{thm:streaming21}
-Any function $f$ with class discrepancy $K_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
+Any function $f$ with class discrepancy $D_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
 %The constant $c$ does not depend on $m$.
@@
 \begin{theorem} \label{thm:streaming12}
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
 $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
@@
 \begin{theorem} \label{thm:streaming22}
-Any function $f$ with class discrepancy $K_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3\log(|Q_\eps|/\delta) /\eps^2\right)$.
 $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
@@
 \[
-K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
+D_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
 \]
@@
 \[
-K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
+D_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
 \]
@@
 \section{A Simple Algorithm for Kernel Density Estimation}
-From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. 
+From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $D_m = O(\sqrt{d}/m)$. 
 %The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently. 
@@
 Together with the results of Section~\ref{sec:sketch} this provides an efficient sketching algorithm for Kernel Density Estimation.
-In fact, we show that for any positive kernel $K_m = O(1/\sqrt{m})$.
+In fact, we show that for any positive kernel $D_m = O(1/\sqrt{m})$.
 This bound is superior to that of the previous section for high dimensions $d > \sqrt{m}$.
@@
 \end{eqnarray*}
-The first equality simply unpacks the squared vector norm, the second transition is due to the induction assumption and the last substitutes our choice of %$\sigma$.
-This completes the proof that $|\sum_{i=1}^m \sigma_i K(x_i,q)| \le \sqrt{m}$ for all $q$.
+The first equality simply unpacks the squared vector norm, the second transition is due to the induction assumption and the last substitutes our choice of 
+$\sigma$. This completes the proof that $|\sum_{i=1}^m \sigma_i K(x_i,q)| \le \sqrt{m}$ for all $q$.
 \end{proof}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
-
-%\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} 
-%
-%\begin{lemma} \label{lem:compactor}
-%Let $k$ be an integer and assume we have black box access to a solver that for any $k$ inputs $x_1,\ldots,x_k$ obtains $k$ signs $\sigma_1,\ldots,\sigma_k$ such that
-%$$\max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$$
-%Then there exist a streaming algorithm requiring a memory buffer of $k$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_m$ with the following properties
-%\begin{itemize}
-%\item $\{z_i\}_i$ is a subset of $\{x_i\}$
-%\item $\E[m] = n/2$
-%\item For $\rho >0$, $\Pr[m \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{k}\right)\right)$
-%\item For any fixed query $q$, the error associated with $q$, defined as
-%$$\text{Err}(q) = 2\sum_{i=1}^m f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
-%Can be decomposed as a sum
-%$$\text{Err}(q) = \sum_{j=1}^{n/k} \text{Err}_j(q)$$
-%where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
-%\end{itemize}
-%\end{lemma}
-%
-%Note that signs achieving $max_q \left| \sum_{i=1}^{k} \sigma_i f(x_i, q)\right| \leq K_k$ are guarantied to exist by the definition of the discrepancy.
-In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
-%
-%\begin{proof}
-%The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
-%$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
-%Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
-%$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
-%$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
-%
-%%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
-%%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
-%%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
-%%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
-%%\todo{this is clunky way to say this...}
-%The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
-Moreover, the output length is a sum of $n/k$ independent random variables with mean $k/2$ and a maximum value of $k$.
-Chernoff-Hoeffding's bound can guarantee the stated concentration around $\E[m]$.
-%As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Rademacher r.v. scaled by a magnitude of at most $K_k$ as required.
-%\end{proof}
-%
-%Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
-%$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} = \sqrt{\frac{K_k^2 n}{k}}$$
-%This high probability bound will be used below for our streaming algorithm.
-In high level the idea is to have a sequence of streaming boxes that we call compactors, each receiving an input stream and outputting a stream that is of half the size of the input (in expectation).
-Eventually we will get to a stream that is small enough to store in memory.
-The randomized bound above shows that for the compactors that handle a large stream, we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$ even if all they do is uniformly sample half of the stream.
-However, for the compactors that observe the shorter streams that high probability bound is no longer as strong and we will have to make use of the fact that $K_k \ll k$.
-%
-%
-%\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
-%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
-The streaming algorithm operates as follows.
-At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
-The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
-In the beginning we have a single compactor at level $h=0$.
-Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
-After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
-%
-%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
-For a query $q$ and hierarchy level $h$ we analyze the error
-%$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
-%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
-The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
-The sum over $j$ is over the number of compactions at level $h$.
-$K_h$ is used to denote the discrepancy of each compaction using a buffer of $k_h$ points.
-Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
-The overall error for the query $q$ is the sum over all levels of its errors
-%$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
-%
-%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
-%$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
-%
-%We are however interested in a high probability bound.
-Specifically we would like to guarantee for $\delta > 0$ that for any query $q$ the error is bounded by $\eps n$ w.p.\ at least $1-\delta$.
-To this end we consider a different analysis for the top and bottom layers.
-For the top layers, the stream can be arbitrarily short so we will use the deterministic analysis as above.
-For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
-%
-%The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
-%\begin{equation} \label{eq:Htag_nh}
-% \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
-%\end{equation}
-%for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
-%
-%According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
-%$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
-%We can now union bound over all 
-%$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
-%and conclude that w.p.\ at least $1-\delta/2$
-%\begin{equation} \label{eq:Htag}
-%H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
-%\end{equation}
-%and
-%\begin{equation} \label{eq:nh small}
-%\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
-%\end{equation}
-%
-%
-%Let's proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
-%$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
-%$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
-%$$
-%We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
-Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
-We get that since $n_h \leq 3n/2^h$
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
-%\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
-%$$
-%In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
-%and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
-%$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
-%and 
-%$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
-%
-%Let's proceed to bound the error on the top layers $H'+1$ to $H$.
-In these top layers we use a deterministic algorithm guaranteeing the stream is cut at least times 2 from layer to layer.
-We assign all top layers a budget of $k_h=k$ for the compactors.
-Since $2^{H+1} < n/k$ this gives a bound of
-%$$
-%H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
-%$$
-%$$
-%O\left( \log \log(n/\delta) \right)
-%$$
-%leading to a bound of 
-%$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
-%and an overall bound of
-%\begin{equation} \label{eq:err total}
-%|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
-%\end{equation}
-%
-%We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
-Recall that we aim to deal with two settings.
-In the first $K_k=\min\{\komconstant,k\}$ and in the second $K_k=\min\{\komconstant \sqrt{k}, k\}$.
-In both cases  $\komconstant$ is independent of $k$.
-We start by dealing with the first scenario.
-%
-%We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
-%\begin{align*}
-%\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
-%  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
-%    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
-%\end{align*}
-%We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
-%$$
-%\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
-%(3/4)^{H'-h}
-%$$
-%For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
-%\begin{align*}
-% \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
-%    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
-%	   &  O\left( (1/2)^{H''-h}   \right) 
-%\end{align*}
-%
-%If follows that 
-%$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
-%translating to an overall bound for the error of
-%$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
-%The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
-The top layers require $O(\log\log(n/\delta)k)$ memory.
-If follows that by setting $k= O\left(\komconstant \log\log(n/\delta) / \eps\right)$ the error is bounded by $\eps n$ w.p.
-$1-\delta$ and the overall memory requirement is
-%$$ O\left( \log \log(n/\delta)^2 (\komconstant/\eps)  \right) $$
-%
-%
-%We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
-%\begin{align*}
-%\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
-%  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
-%\end{align*}
-%and 
-%$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
-%Plugging this to the overall error in Equation~\eqref{eq:err total} we get
-%$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
-%
-%Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
-%$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
-%we get a bound of $\eps n$ for the error and a memory usage of 
-%$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
-%\end{proof}
-%
-
-%\section{Appendix Appendix Appendix...}
-%
-%
-%The proofs of Theorems \ref{thm:streaming11}, \ref{thm:streaming12}, \ref{thm:streaming21}, and \ref{thm:streaming22} all use the basic concept of a compactor.
-A compactor consumes a stream of items and outputs another stream.
-%The output stream contains at most half (in expectation) the items from the input stream with double the weight. 
-%It does so by keeping a buffer of a certain capacity $m$. When a new item is inserted into the compactor it is added to its buffer. 
-%If the buffer is full, a compaction operation takes place. 
-%The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
-%$\max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
-%Note that such a sequence is guarantied to exist by the definition of the discrepancy. 
-%However, an algorithm for finding such a sequence might not exist. 
-%From this point onwards, we assume the existence of such an algorithm.
-%%In other words, our theorems hold for problems which admit such a solution.
-%The compactor then outputs either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ with double the weight.
-%
-%We begin with showing some basic properties of deterministic compactors which always output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
-Consider a single compaction and let $\tilde F_{+}$ denote the function evaluated on $\{ x_i | \sigma_i = 1\}$ (similarly $\tilde F_{-}$).
-%Let $E(q) = \sum_i \sigma_i f(x_i,q)$ for the signs $\sigma$ computed by the algorithm above. 
-%$$\tilde F_{+}(q) = \sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q) = F(q) + E(q)$$
-%$$\tilde F_{-}(q) = \sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q) = F(q) - E(q)$$
-%Note that $|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = O(mK_m)$. 
-%Now, aggregating over the $n/m$ compactions we get that $|\tilde F(q) - F(q)| \le n K_m$. Moreover, the stream length is clearly cut (at least) in half.
-%
-%These facts alone already allow us to prove Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21}. 
-%The algorithms are a direct extension the well know MRL algorithm \cite{MRL} for quantile sketching. 
-%Note that for quantiles, $f(x,q) = 1$ if $q > x$ and $0$ else. 
-%A low discrepancy sequence is achieved simply by sorting the values and assigning $\sigma_i = 1$ for all evenly positioned values in the sorted order and $\sigma_i=-1$ to the odd positions.
-The above gives a discrepancy of $1/m$ for quantile approximation.
-%Below we generalize this algorithm to any low discrepancy class.
-%
-%\paragraph{Theorem~\ref{thm:streaming11}}
-%For any function family $\F$ with a corresponding discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
-%\begin{proof}
-%Consider feeding the output of the first compactor into a second one etc. Number the compactors $0,\ldots,H$.
-%The weight of item to compactors $h$ have weight $w_h = 2^h$. The length of the input stream seen by compactor is $n_h \le n/2^h$.
-%Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since $n_h \le n/2^h$ we know that $H \le log(n/m)$.
-%The total error is therefore $H n K_m \le log(n/m) n K_m$. 
-%Setting $m \ge c\log(\eps n/c)/\eps$ and replacing $K_m = c/m$ we get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-%Since we have $H \le log(\eps n)$ such compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. \todo: double check the math.}
-%\end{proof}
-%
-%\paragraph{Theorem~\ref{thm:streaming21}}
-%For any function family $\F$ with a corresponding discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
-%\begin{proof}
-%The proof is identical to the one above except for the variable setting of
-%Setting $m \ge c^2\log^2(\eps^2 n/c^2)/\eps^2$ and replacing $K_m = c/\sqrt{m}$. 
-%We get that the error is at most $log(n/m) n K_m \le \eps n$ as required. 
-%Since we have $H \le log(\eps^2 n)$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$. \todo: double check the math.}
-%\end{proof}
-%
-%Proving Theorem~\ref{thm:streaming12} and Theorem~\ref{thm:streaming22} is more involved. 
-%\todo{Add the description of the randomized algorithms.}
-%
-%\zk{define compactor in an algorithm for thm about $\sqrt{m}$}
-
-%%%%%%%%%%%%%%
-%%%
-%%%
-%%%
-%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The compaction takes the elements in the buffer $x_1,\ldots,x_m$ and finds a low discrepancy assignment $\sigma$ such that 
-$\max_q |\sum_i \sigma_i f(x_i,q)| \leq m K_m$. 
+$\max_q |\sum_i \sigma_i f(x_i,q)| \leq m D_m$. 
 Note that such a sequence is guarantied to exist by the definition of the class discrepancy.
 For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
-That is, if it is possible to obtain a bound of $K_m$ yet we can only find signs obtaining a bound of $\tilde{K}_m$, our results for the obtainable signs apply for $\tilde{K}_m$.
+That is, if it is possible to obtain a bound of $D_m$ yet we can only find signs obtaining a bound of $\tilde{K}_m$, our results for the obtainable signs apply for $\tilde{K}_m$.
 Given the sign vector $\sigma$, the compactor appends either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ to the output stream.
@@
 A deterministic compactor output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
-Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $K_m n$
+Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $D_m n$
 \end{lemma}
@@
 meaning that the error for the items of the single compaction is bounded by
-$$|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = mK_m$$
-Summing over all $n/m$ compactions we get that the overall error is bounded, in absolute value, by $nK_m$.
+$$|\tilde F_{\pm}(q) - F(q)| = |E(q)| \le \max_q |\sum_i \sigma_i f(x_i,q)| = mD_m$$
+Summing over all $n/m$ compactions we get that the overall error is bounded, in absolute value, by $nD_m$.
 \end{proof}
@@
 The above gives class discrepancy of $1/m$ for quantile approximation.
-%Below we generalize this algorithm to any low discrepancy class.
 Theorems~\ref{thm:streaming11} and~\ref{thm:streaming21} below generalize this algorithm to any low discrepancy class.
 
-\el{Replace with the above?} \zk{changed `Below we generalize this algorithm to any low discrepancy class.' to the line above. Does that resolve the issue?}
 \paragraph{Theorem~\ref{thm:streaming11}}
-For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $D_m = O(c/m)$ there exists an fully-mergeable streaming coreset deterministic algorithm of size $O\left(c\log^2(\eps n/c)/\eps\right)$ whose error is at most $\eps n$.
 \begin{proof}
@@
 
-Each compactor contributes at most $w_h n_h K_m \le n K_m$ error. Moreover since the $H-1$ layer had outputs, we must have $m \leq n_{H-1}$ and
+Each compactor contributes at most $w_h n_h D_m \le n D_m$ error. Moreover since the $H-1$ layer had outputs, we must have $m \leq n_{H-1}$ and
 $$  \log_2(m) \leq \log_2(n_{H-1}) \leq \log_2(n) - (H-1)$$
 leading to a bound $H \le \floor{log_2(n/m)}+1$.
-The total error is therefore $H n K_m \le O(log(n/m) n K_m)$. 
-Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $K_m = c/m$ we get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the $O()$ term of $m_0$, as required.
+The total error is therefore $H n D_m \le O(log(n/m) n D_m)$. 
+Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $D_m = c/m$ we get that the error is at most $O(log(n/m) n D_m) \le \eps n$ for appropriate constants in the $O()$ term of $m_0$, as required.
 Since we have $H = O(log(\eps n/c))$ compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. 
@@
 \paragraph{Theorem~\ref{thm:streaming21}}
-For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+For any function family $\F$ with a corresponding class discrepancy $D_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}
 The proof is identical to the one above except for the variable setting of
-Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $K_m = c/\sqrt{m}$. 
-We get that the error is at most $O(log(n/m) n K_m) \le \eps n$ for appropriate constants in the big-$O$ term of $m_0$, as required. 
+Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $D_m = c/\sqrt{m}$. 
+We get that the error is at most $O(log(n/m) n D_m) \le \eps n$ for appropriate constants in the big-$O$ term of $m_0$, as required. 
 Since we have $H = O(log(\eps^2 n/c^2))$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c^2) /\eps^2\right)$. 
@@
 \paragraph{Theorem~\ref{thm:streaming22}}
-For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
+For any function family $\F$ with a corresponding class discrepancy $D_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset randomized algorithm of size $O\left(c^2\log^3\log(n/\delta) /\eps^2\right)$ whose error for any fixed function $f \in \F$ is at most $\eps n$ with probability at least $1-\delta$.
 \begin{proof}
@@
 We continue to bound the error.
-For the top compactors of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n K_m$.
-Since we will use $m \geq 1/\eps^2$ we get that the error for all top compactors is $O(nK_m\log\log(1/\delta))$.
+For the top compactors of level $h=H'+1,\ldots,H$ we get as in the deterministic case that the error for each is $n D_m$.
+Since we will use $m \geq 1/\eps^2$ we get that the error for all top compactors is $O(nD_m\log\log(1/\delta))$.
 Consider now a compactor of level $h \leq H'$.
-For the first $\tilde{n}$ items it observed, the error is bounded by $2^h\tilde{n}K_m \leq 2^{h-H'}nK_m$.
+For the first $\tilde{n}$ items it observed, the error is bounded by $2^h\tilde{n}D_m \leq 2^{h-H'}nD_m$.
 Fix a query $q$; for the items following the first $\tilde{n}$ items the compactor is operating in the sampling mode.
@@
 To explain the high level idea consider again the easier setting where we know $n$, the length of the stream in advance.
-As in the $K_m=c/\sqrt{m}$ case, we will split the compactors into the top $\log\log(1/\delta)$ ones acting deterministically and bottom compactors yielding random outputs.
+As in the $D_m=c/\sqrt{m}$ case, we will split the compactors into the top $\log\log(1/\delta)$ ones acting deterministically and bottom compactors yielding random outputs.
 The issue comes from the choice of $m$.
@@
 \paragraph{Theorem~\ref{thm:streaming12}} 
-Any function $f$ with class discrepancy $K_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
+Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2\log(|Q_\eps|/\delta)/\eps\right)$.
 $Q_\eps$ is an epsilon net for $f$ on $\Q$. 
 The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
-%For any function family $\F$ with a corresponding class discrepancy $K_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
+%For any function family $\F$ with a corresponding class discrepancy $D_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}
@@
 Compactors of level $h >H'$ act in a deterministic manner.
-Namely, once the buffer is full with items $x_1,\ldots,x_m$ we find the sign assignment $\sigma$ giving $\left|\max_q \sum \sigma_i f(x_i, q)\right| < m_hK_{m_h}=mK_m$ and output the smallest of the sets $X_+=\{x_i | \sigma_i > 0 \}$, $X_- = \{x_i | \sigma_i < 0 \}$.
+Namely, once the buffer is full with items $x_1,\ldots,x_m$ we find the sign assignment $\sigma$ giving $\left|\max_q \sum \sigma_i f(x_i, q)\right| < m_hD_{m_h}=mD_m$ and output the smallest of the sets $X_+=\{x_i | \sigma_i > 0 \}$, $X_- = \{x_i | \sigma_i < 0 \}$.
 Compactors of level $h \leq H'$ act in a random manner; they output either the items of $X_-$ or $X_+$ with equal probability.
@@
 
-With the assumption of all compactions being done with a buffer of size $m_h$, the number of compactions is $n_h/m_h$ and the error associated with each compaction is a zero mean random variable, with an absolute value of $2^h m_h K_{m_h}$.
+With the assumption of all compactions being done with a buffer of size $m_h$, the number of compactions is $n_h/m_h$ and the error associated with each compaction is a zero mean random variable, with an absolute value of $2^h m_h D_{m_h}$.
 The overall error $E_h(q)$ is the sum of these independent random variables.
@@
 \begin{equation} \label{eq:err low1}
-\Pr\left[ E_h(q) > 2^h m_h K_{m_h} \eps_h n_h \right] = \exp \left( -\Omega\left( \eps_h^2 n_h m_h \right) \right)
+\Pr\left[ E_h(q) > 2^h m_h D_{m_h} \eps_h n_h \right] = \exp \left( -\Omega\left( \eps_h^2 n_h m_h \right) \right)
 \end{equation}
@@
 \begin{equation} \label{eq:err low2}
-\Pr\left[ E_h(q) > m_h K_{m_h} \eps_h n \right] = \exp \left( -\Omega\left( \frac{\eps_h^2 m_h n}{2^h} \right) \right)
+\Pr\left[ E_h(q) > m_h D_{m_h} \eps_h n \right] = \exp \left( -\Omega\left( \frac{\eps_h^2 m_h n}{2^h} \right) \right)
 \end{equation}
@@
 $$
-Plugging this into Equation~\eqref{eq:err low2}, with $\eps_h = (3/4)^{h-H'}/m$ and using $m_h K_{m_h} \leq c$ we get
+Plugging this into Equation~\eqref{eq:err low2}, with $\eps_h = (3/4)^{h-H'}/m$ and using $m_h D_{m_h} \leq c$ we get
 \begin{equation} \label{eq:err low3}
@@
 With the length of the output stream we use the fact that the top layers are deterministic and can apply Lemma~\ref{lem:det compactor} to bound their error of each of these layers by
-$$ 3K_m n \leq (3c/m) n $$
+$$ 3D_m n \leq (3c/m) n $$
 Since there are $O(\log\log(n/\delta))$ such layers, we conclude that for $m=\Omega(\log\log(n/\delta) c/\eps)$ with appropriate constant it holds for a fixed $q$, w.p.\ at least $1-\delta$ that the overall error of the sketch is bounded by $\eps n$.
@@
 
-%According to Lemma~\ref{lem:det compactor} we know that for a compactor observing $n_h$ items of weight $w_h=2^h$, the error associated with the compactor will be deterministically bounded by $n_hw_hK_{m_h}$, and the number of items it outputs is in expectation $n_h/2$.
 \end{proof}
 
-%%%%%%%%%%%%%%
-%%%
-%%%
-%%%
-%%%%%%%%%%%%%%
-
-%
-%\section{Proofs for Section~\ref{sec:sketch}, Sketching Coresets} \label{app:sketch proof}
-%
-%\begin{lemma} \label{lem:compactor}
-%Assume we have black box access to a solver that for any integer $m$ and inputs $x_1,\ldots,x_m$ obtains signs $\sigma_1,\ldots,\sigma_m$ such that $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ for some function $f$ whose discrepancy is $K_m$.\footnote{An constant factor approximation algorithm achieving $\max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| = O(K_m)$ would also clearly suffice.}
-%Then there exist a streaming algorithm requiring a memory buffer of $m$ input items that given a stream of length $n$ outputs a stream $z_1,\ldots,z_{n'}$ with the following properties
-%\begin{itemize}
-%\item $\{z_i\}_i$ is a subset of $\{x_i\}$
-%\item $\E[n'] = n/2$
-%\item For $\rho >0$, $\Pr[n' \geq (1+\rho)n/2] \leq \exp \left( -O\left(\frac{n\rho^2}{m}\right)\right)$
-%\item For any fixed query $q$, the error associated with $q$, defined as
-%$$\text{Err}(q) = 2\sum_{i=1}^{n'} f(z_i,q) - \sum_{i=1}^n f(x_i,q)  $$
-%Can be decomposed as a sum
-%$$\text{Err}(q) = \sum_{j=1}^{n/m} \text{Err}_j(q)$$
-%where the different $\text{Err}_j(q)$ are independent, have mean 0 and $|\text{Err}_j(q)| \leq K_k$
-%\end{itemize}
-%\end{lemma}
-%
-%Note that signs achieving $max_q \left| \sum_{i=1}^{m} \sigma_i f(x_i, q)\right| \leq K_m$ are guarantied to exist by the definition of the discrepancy.
-In fact, the quantity above is potentially much smaller than its upper bound because it is computed for a specific set of points $x_i$ as opposed to the worst such possible set.
-%
-%
-%\todo{changed notation until here...}
-%\begin{proof}
-%The algorithm operates as follows. It keeps a buffer of $k$ items. Once the buffer fills with $x_1,\ldots,x_k$ it obtains the signs guaranteeing
-%$$\max_q \left| \sum_i \sigma_i f(x_i, q)\right| \leq K_k$$
-%Then, the algorithm output to the stream the with probability $1/2$ each data points $\{x_i \; | \; \sigma_i = 1\}$ or $\{x_i \; | \; \sigma_i = -1\}$ with twice the weight.
-%$$\sum_{i ,\; \sigma_i=1} 2f(x_i, q) = \sum_{i} f(x_i, q) +  \sum_{i} \sigma_i f(x_i, q)$$
-%$$\sum_{i ,\; \sigma_i=-1} 2f(x_i, q) = \sum_{i} f(x_i, q) - \sum_{i} \sigma_i f(x_i, q)$$
-%
-%%Now, consider the set $P=\{i:\sigma_i=1\}$ and $N=\{i:\sigma_i=-1\}$.
-%%$$ \sum_i \sigma_i f(x_i, q) = \sum_i \sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in P} f(x_i,q) - \sum_i f(x_i, q)   $$
-%%$$ -\sum_i \sigma_i f(x_i, q) = \sum_i -\sigma_i f(x_i, q) + \sum_i f(x_i,q) - \sum_i f(x_i,q) = 2\sum_{i \in N} f(x_i,q) - \sum_i f(x_i, q)   $$
-%%Thus, we draw a random coin and either output to the stream the data points of $P$ or $N$. We call this operation a single compaction. 
-%%\todo{this is clunky way to say this...}
-%The expected output length is $k/2$ for every $k$ inputs, insuring $\E[m]=n/2$.
-Moreover, the output length is a sum of $n/k$ independent random variables with mean $k/2$ and a maximum value of $k$.
-Chernoff-Hoeffding's bound can guarantee the stated concentration around $\E[m]$.
-%As for the error term w.r.t.\ a fixed query $q$, it is clearly the sum of errors accumulated in each compaction. The error incurred in a compaction is either 
-%$\sum_i \sigma_i f(x_i, q)$ or $-\sum_i \sigma_i f(x_i, q)$ with equal probability. It follows that it is a Rademacher r.v. scaled by a magnitude of at most $K_k$ as required.
-%\end{proof}
-%
-%Notice in the above lemma the last property of the streaming algorithm; it ensures that deterministically $|\text{Err}(q)| \leq (K_k/k) n$, and that w.h.p.\ (via Chernoff's inequality) for a fixed $q$
-%$$|\text{Err}(q)| \lesssim K_k \sqrt{n/k} $$
-%This high probability bound will be used below for our streaming algorithm. 
-%The high level idea is to have a sequence of streaming objects that we call compactors. 
-%Each compactor receives an input stream and outputs a stream that is of half the size of the input (in expectation). 
-%Eventually we get to a stream that is small enough to store in memory. 
-%The randomized bound above shows that for the compactors that handle a large stream, 
-%we can afford to have a very crude sketch because the error that they incur is roughly $\sqrt{n}$. 
-%That is true even if all they do is uniformly sample half of the stream. 
-%However, for the compactors that observe the shorter streams, a high probability bound is no longer strong enough. 
-%For those we will make use of the fact that $K_k \ll k$.
-%
-%
-%\begin{proof} [Proof of Theorems~\ref{thm:streaming} and~\ref{thm:streaming2}]
-%Denote the streaming algorithm of Lemma~\ref{lem:compactor} as a compactor.
-The streaming algorithm operates as follows.
-At any given time it maintains a hierarchy of compactors where the hierarchy is measured in levels, starting from 0.
-The Compactor of level $h$ receives inputs of weight $2^h$ and outputs items of weight $2^{h+1}$.
-In the beginning we have a single compactor at level $h=0$.
-Once it outputs items to its output stream we open a compactor at level $h=1$ and so on.
-After observing $n$ items let $H$ be the level of the final compactor, meaning the compactor that never began an output stream.
-%
-%The sketch at that point contains all the data points contained in the buffers of the different compactors, weighted according to the level of the compactor.
-For a query $q$ and hierarchy level $h$ we analyze the error
-%$$\text{Err}_h(q) = 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \ .$$
-%Here, $k_h$ is the capacity of the buffers at level $h$, $n_h$ is the length of the stream observed at level $h$.
-The multiplier of $2^h$ is there since level $h$ observes items of weight $2^h$.
-The sum over $j$ is over the number of compactions at level $h$.
-$K_h$ is used to denote the discrepancy of each compaction using a buffer of $k_h$ points.
-Finally, the $Y_{ij}$ are independent random variables with mean zero and absolute value of at most $1$.
-The overall error for the query $q$ is the sum over all levels of its errors
-%$$ \text{Err}(q) = \sum_{h=0}^H \text{Err}_h(q)$$
-%
-%To achieve a deterministic bound we set all $k_h=k$, and set the compactors to choose the signed set with the least cardinality, ensuring $n_h \leq n_{h-1}/2$ and $H \leq \log_2(n/k)$, thus
-%$$ \text{Err}(q) \leq (K_k/k) \log_2(n/k) n $$
-%
-%We are however interested in a high probability bound.
-Specifically we would like to guarantee for $\delta > 0$ that for any query $q$ the error is bounded by $\eps n$ w.p.\ at least $1-\delta$.
-To this end we consider a different analysis for the top and bottom layers.
-For the top layers, the stream can be arbitrarily short so we will use the deterministic analysis as above.
-For the bottom layers, we can guarantee a minimal length to the stream and obtain tighter bounds.
-%
-%The bottom layers will be those of height $h=0$ up to $h=H'$ where $H'$ is set adaptively in a way that $H'$ is the maximum integer such that for all $h \leq H'$, 
-%\begin{equation} \label{eq:Htag_nh}
-% \forall h \leq H' , \ \ n_h \geq c_1 k \log^2(n) \log(\log(n)/(c_2 \delta ))
-%\end{equation}
-%for some sufficiently large constant $c_1$ and small constant $c_2$ to be determined later.
-%
-%According to Lemma~\ref{lem:compactor} we have for $ h\leq H'$ that for some appropriate constant $c_1$ in  \eqref{eq:Htag_nh},
-%$$ \Pr[n_{h+1} \geq (1+1/\log(n))n_{h}/2] \leq \exp\left( -\frac{n_{h}}{k_h \log^2(n)}  \right) \leq c_2\delta/  \log(n) $$
-%We can now union bound over all 
-%$$h \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta\log(n))) \right)\right) + 2 \leq \log_2(n)$$
-%and conclude that w.p.\ at least $1-\delta/2$
-%\begin{equation} \label{eq:Htag}
-%H' \leq \log_2\left( n / \left( c_1 k \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) + 2 \leq \log_2(n)
-%\end{equation}
-%and
-%\begin{equation} \label{eq:nh small}
-%\forall h \leq H', \ \ n_{h} \leq 3 \cdot n/2^{h}
-%\end{equation}
-%
-%
-%We proceed to bound the error of layer $h$. Since this error is a sum of i.i.d.\ bounded variables of mean zero we can use Chernoff- Hoeffding's inequality and obtain that
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] =$$
-%$$ \Pr\left[   \left| 2^h \sum_{j=1}^{\floor{n_h/k_h} } K_h Y_{ij} \right| \geq \eps n \right] \leq \exp \left( O\left( -\frac{ \eps^2 n^2}{ 2^{2h} \sum_{j=1}^{\floor{n_h/k_h} } K_h^2}   \right)\right) =$$
-%$$\exp \left( -O\left(\frac{\eps^2 n^2}{n_h 2^{2h} K_h^2/k_h  } \right) \right) 
-%$$
-%We now make use of the the bound on $n_h$ in Equation~\eqref{eq:nh small}.
-Notice that the random events determining the length $n_h$ do not affect the realization of the random variables used in layer $h$, so we can indeed use the bound on $n_h$ for controlling the error at level $h$.
-We get that since $n_h \leq 3n/2^h$
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq 
-%\exp \left( -O\left(\frac{\eps^2 n}{ 2^h K_h^2/k_h  } \right) \right) 
-%$$
-%In particular, for $\eps_h = O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right)$  it holds that
-%$$ \Pr\left[   \left| \text{Err}_h(q) \right| \geq \eps n \right] \leq \delta/4(H'-h+1)^2$$
-%and a union bound ensures that with probability at least $1-\delta$, in addition to Equations~\eqref{eq:Htag} and~\eqref{eq:nh small} we have for all $h \leq H'$ that
-%$$\left| \text{Err}_h(q) \right| \leq \eps_h n$$
-%and 
-%$$\left| \sum_{h=0}^{H'} \text{Err}_h(q) \right| \leq \left(\sum_{h=0}^{H'} \eps_h\right)n $$
-%
-%We proceed to bound the error on the top layers $H'+1$ to $H$.
-In these top layers we use a deterministic algorithm guaranteeing the stream is cut in half from layer to layer.
-We assign all top layers a budget of $k_h=k$ for the compactors.
-Since $2^{H+1} < n/k$ this gives a bound of
-%$$
-%H-H' \leq \log_2(n/k2^{H'}) = O\left( \log\left( c_1 \log^2(n) \log(1/(c_2 \delta \log(n))) \right)\right) = 
-%$$
-%$$
-%O\left( \log \log(n/\delta) \right)
-%$$
-%leading to a bound of 
-%$$ \left| \sum_{h=H'+1}^H \text{Err}_h(q) \right| \leq O\left( \log \log(n/\delta) (K_k/k) n \right) $$
-%and an overall bound of
-%\begin{equation} \label{eq:err total}
-%|\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(K_k/k) + \sum_{h=0}^{H'} \eps_h \right)
-%\end{equation}
-%
-%We are now left with the task of defining $k_h$ for the lower layers; we do so differently depending on the value of $K_k$ as a function of $k$.
-Recall that we aim to deal with two settings.
-In the first $K_k=\min\{\komconstant,k\}$ and in the second $K_k=\min\{\komconstant \sqrt{k}, k\}$.
-In both cases  $\komconstant$ is independent of $k$.
-We start by dealing with the first scenario.
-%
-%We set $k_h = \max\{2, \ceil{(2/3)^{H'-h}k}\}$. By using the definition of $H'$ in Equation~\eqref{eq:Htag} we see that
-%\begin{align*}
-%\eps_h = & O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k^2 \log((H'-h+1)^2/\delta)}{k_h K_k^2 n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)) \\
-%  	   &  O\left( \frac{K_k}{k} \sqrt{\frac{2^h K_h^2 k }{k_h K_k^2 2^{H'}}} \right) = \\
-%    	   &  O\left( \frac{K_k}{k} \sqrt{\frac{K_h^2 k }{k_h K_k^2 2^{H'-h}}} \right)
-%\end{align*}
-%We move to control the sum over $\eps_h$ by bounding the multiple of $K_k/k$. For $k_h \geq \komconstant$
-%$$
-%\frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} \leq \frac{\komconstant^2 k}{2^{H'-h} \komconstant^2 (2/3)^{H'-h}k} =
-%(3/4)^{H'-h}
-%$$
-%For $k_h \leq \komconstant$ we must have $h \leq H''$ with $(2/3)^{H'-H''} \leq \komconstant/k$, meaning that $2^{H'-H''} \geq k/\komconstant$. For such $h$ we get
-%\begin{align*}
-% \frac{K_h^2 k}{2^{H'-h} K_k^2 k_{h}} = &  O\left( \frac{ k_h k}{2^{H'-h} \komconstant^2 } \right) =  \\
-%    	   &  O\left( \frac{ k_h k}{2^{H''-h} k\komconstant } \right) = & k_h \leq \komconstant\\
-%	   &  O\left( (1/2)^{H''-h}   \right) 
-%\end{align*}
-%
-%If follows that 
-%$$ \sum_{h=0}^{H'} \eps_h = O(K_k/k) = O(\komconstant/k) $$
-%translating to an overall bound for the error of
-%$$ |\text{Err}(q)| \leq n \cdot O\left( \log \log(n/\delta)(\komconstant/k)  \right)$$
-%The overall memory consumption for the bottom layers is $O(k)$ since all layers of size 2 can be implemented jointly by sampling.
-The top layers require $O(\log\log(n/\delta)k)$ memory.
-If follows that by setting $k= O\left(\komconstant \log\log(n/\delta) / \eps\right)$ the error is bounded by $\eps n$ w.p.
-$1-\delta$ and the overall memory requirement is
-%$$ O\left( \log^2 \log(n/\delta) (\komconstant/\eps)  \right) $$
-%
-%
-%We are now ready for the case where $K_k = \min\{k, \komconstant\sqrt{k}\}$. We set $k_h=2$, resulting in $K_h=2$, for all $h \leq H'$ and obtain
-%\begin{align*}
-%\eps_h = & O\left( \sqrt{\frac{2^h K_h^2 \log((H'-h+1)^2/\delta)}{k_h n}} \right) = & n=\Omega(2^{H'}k\log(H'/\delta)), \ K_h^2/k_h=O(1) \\
-%  	   &  O\left( \sqrt{2^{h-H'}/k} \right) 
-%\end{align*}
-%and 
-%$$ \sum_h \eps_h = O\left(1/\sqrt{k}\right) $$
-%Plugging this to the overall error in Equation~\eqref{eq:err total} we get
-%$$ \text{Err}(q) = n \cdot O\left( \frac{\log \log(n/\delta)\komconstant + 1}{\sqrt{k}}  \right) =  n \cdot O\left( \frac{\log \log(n/\delta)\komconstant }{\sqrt{k}}  \right) $$
-%
-%Since layers of $k_h=2$ can all be implemented in constant memory the memory requirement is dominated by the top layers and is in the order of $k \cdot \log\log(n/\delta)$, hence by setting 
-%$$k \approx \frac{\komconstant^2 \log^2\log(n/\delta)}{\eps^2}$$ 
-%we get a bound of $\eps n$ for the error and a memory usage of 
-%$$ O\left( \frac{\komconstant^2 \log^3\log(n/\delta)}{\eps^2}\right) $$
-%\end{proof}
-
 \end{document}

### 2019-02-01 komlos.tex

@@
 However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
+%Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 
+Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
+We aim here to find an analog for actively selected, rather than i.i.d.\ sampled, points.
+\cite{langberg2010universal, tolochinsky2018coresets} and references within tie the coreset complexity to the VC dimension of the family function, and the average sensitivity of the dataset.
+However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+We point out the connection between the discrepancy of a function family, informally defined as the result of a two player game, one choosing a set of signs and the other a function from the family, and coreset complexity.
+Is is known that small discrepancy implies an offline coreset construction algorithm  (see e.g.\ \cite{phillips2009small}, Theorem 1.1).
+In this paper we point out this connection and provide an algorithm taking use of a small discrepancy bound to construct a coreset in the streaming setting, as well as the offline setting.
+
+An important application of our generic coreset results is in the area of Kernel density estimation.
 Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
@@
 Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
+Although the worst case lower bound is $1/\eps^2$, we conjecture that in realistic scenarios, the deterministic algorithm should outperform random sampling as it explicitly takes advantage of negative correlations.
 
+Another application of our coreset results applies to logistic regression.
 Logistic Regression is an extremely popular technique for classification.

### 2019-02-01 komlos.tex
cleanups

--- 2019-02-01 komlos.tex
@@
 \end{algorithmic}
-\caption{Low Discrepancy Algorithm for Positive Kernels}\label{kernelAlg}
+\caption{Low discrepancy algorithm for positive semi-definite kernels}\label{kernelAlg}
 \end{algorithm}
@@
 \paragraph{Note} Theorem~\ref{thm:disc simple kernel} provides an upper bound of $\sqrt{m}$ for the sign discrepancy. 
-This upper bound is tight since there exists a set of vectors that requires it. 
+This upper bound is tight since there exist sets of vectors in high dimensions that requires it. 
 For data that lends itself to density estimation, however, one should expect input vectors to be clustered together.
-In such cases, the algorithm above performs much better than the worst-case bound predicts. We leave it to future work to define properties of the data that ensure better guarantees by our algorithm.
+In such cases, the algorithm above performs much better than the worst-case bound predicts. 
+We leave it to future work to define properties of the data that ensure algorithm better guarantees by Algorithm~\ref{kernelAlg}.
 \bibliography{density}

### 2019-02-01 komlos.tex
gamma proof

--- 2019-02-01 komlos.tex
@@
 Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
-We aim here to find an analog for actively selected, rather than i.i.d.\ sampled, points.
+We aim here to find an analog for actively selected, rather than i.i.d.\ sampled points.
 \cite{langberg2010universal, tolochinsky2018coresets} and references within tie the coreset complexity to the VC dimension of the family function, and the average sensitivity of the dataset.
@@
 
-These definition are intentionally very similar to those of the Rademacher complexity $R_m(\F)$.
-The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
-Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
+%These definition are intentionally very similar to those of the Rademacher complexity $R_m(\F)$.
+%The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
+%Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
 See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the term ``discrepancy'' to define a different quantity than the one above.}
-We claim that $D_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
-Trivially,  $D_m \le R_m$. 
-We show, however, that $D_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
-This immediately proves the existence of small coresets for these problems.
+%We claim that $D_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
+%Trivially,  $D_m \le R_m$. 
+%We show, however, that $D_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
+%This immediately proves the existence of small coresets for these problems.
 
@@
 \begin{corollary}
-The class discrepancy of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O((1+\gamma)\exp(\gamma)\sqrt{d}/m)$.
+For cases where $\|q-x\| \leq 1$ for all $q,x$, the class discrepancy of the Gaussian kernel $K(q,x) = \exp(-\gamma \|x-q\|^2)$ in dimension $d$ is $O(\gamma\exp(\gamma)\sqrt{d}/m)$.
 \end{corollary} 
@@
 Plugging into the equation in the proof of Theorem~\ref{thm:analytic2} we get that the sum determining the constant is upper bounded by
-$\sum_{k=1}^\infty \gamma^{k}(k\log^3(k))^{1/2}/k! = O\left((1+\gamma) \exp(\gamma)\right)$.
+$$\sum_{k=1}^\infty \gamma^{k}(k\log^3(k))^{1/2}/k! = O\left(\sum_{k=1}^\infty \gamma^{k}/(k-1)!\right) = O\left(\gamma \exp(\gamma)\right)$$
 

### 2019-02-01 komlos.tex
forgotten line deleted
before merge

--- 2019-02-01 komlos.tex
@@
 
-Obtaining small coresets and understanding the coreset complexity of different problems is of significant theoretical and practical importance.
+Obtaining small coresets and understanding the coreset complexity (the size of the minimal coreset) of different problems is of significant theoretical and practical importance.
 While some problems obviously do not admit small coresets, other do. 
-There are several results that connect the simplicity of the measure and its coreset complexity (the size of the minimal coreset).
+There are several results that connect the simplicity of the measure and its coreset complexity.
 In this manuscript, we focus solely on sums of functions applied to the input items.
@@
 For example, one could consider the sum of sigmoid activation losses $F(q) = \sum_{i=1}^{n} 1/(1+ \exp(\ip{x_i,q}))$ and $x,q\in \R^d$.
-Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items give an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
+Using Chernoff's inequality and a union bound already shows that sampling $\tilde O(d/\eps^2)$ items gives an $\eps n$ approximation to this sum.\footnote{Using $\tilde O(\cdot)$ to suppress poly-logarithmic terms.}
 In general, for families of VC dimension $v$, a sample of $(v+\log(1/\delta))/\eps^2$ suffices \cite{talagrand1994sharper}.
@@
 For Gaussian kernel density, it is known that a sample size of $O(1/\eps^2)$ suffices independently of $d$  \cite{lopez2015towards}.
+These results require different analyses and seem to stem from different mathematical underpinnings. 
+This paper provides a general framework for obtaining, and improving on, these results.
 
 Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
-A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+In that sense, Rademacher complexity is a good measure of sample complexity. 
+That is, the generalization of coresets which are chosen i.i.d.\ from the data (or the underlying distribution).
+A carefully selected coreset can be better than a uniformly sampled one. 
+It can be smaller and still give the same generalization power. 
+Alternatively, it can give better generalization with the same number of data points. 
+That is the usefulness of coresets in the context of machine learning. 
+This paper defines the analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
+
 There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.

### 2019-02-01 komlos.tex

--- 2019-02-01 komlos.tex
@@
 For Gaussian kernel density, it is known that a sample size of $O(1/\eps^2)$ suffices independently of $d$  \cite{lopez2015towards}.
+These results require different analyses and seem to stem from different mathematical underpinnings. 
+This paper provides a general framework for obtaining, and improving on, these results.
 
-%Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
-A carefully selected set of points can potentially obtain a better generalization bound, and that is the usefulness of coresets in the context of machine learning.
-We are not aware of a complete analog to Rademacher complexity that aims to measure the generalization ability of a coreset of a fixed finite size.
-There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references within that tie the coreset to the VC dimension of the family function, and the average sensitivity of the dataset.
-However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
+Rademacher complexity (see for example \cite{Bartlett:2003:RGC:944919.944944}) is a standard measure of generalization.
+In other words, bounding the Rademacher complexity is a good way to upper bound the sample complexity. 
+A sample is an instance of a coreset which is chosen i.i.d.\ from the data (or the underlying distribution).
+A carefully selected coreset can, at least potentially, be better than a uniformly sampled one. 
+It can be smaller and still give the same generalization power. 
+Alternatively, it can give better generalization with the same number of data points. 
+%That is the usefulness of coresets in the context of machine learning. 
+There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references therein that tie the coreset size to the VC dimension of the  function family, and the average sensitivity of the dataset.
+These relationships come up as tools for constructing coresets rather than complexity measures aimed to characterize generalization ability. 
+This paper defines the analog to Rademacher complexity that aims to characterize the coreset complexity, i.e., the generalization ability of the best possible coreset of a fixed size.
+
 %Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 
-Rademacher complexity \cite{Bartlett:2003:RGC:944919.944944} is a known method to estimate the generalization ability of an empirical risk minimizer (ERM) of a family of function over a finite set of i.i.d.\ sampled points.
-We aim here to find an analog for actively selected, rather than i.i.d.\ sampled points.
-\cite{langberg2010universal, tolochinsky2018coresets} and references within tie the coreset complexity to the VC dimension of the family function, and the average sensitivity of the dataset.
-However, these relationships come up more as tools for constructing a coreset rather than a single complexity measure aimed to characterize some generalization ability.
-We point out the connection between the discrepancy of a function family, informally defined as the result of a two player game, one choosing a set of signs and the other a function from the family, and coreset complexity.
-Is is known that small discrepancy implies an offline coreset construction algorithm  (see e.g.\ \cite{phillips2009small}, Theorem 1.1).
-In this paper we point out this connection and provide an algorithm taking use of a small discrepancy bound to construct a coreset in the streaming setting, as well as the offline setting.
-
-An important application of our generic coreset results is in the area of Kernel density estimation.
+An important application of our generic coreset result is Kernel density estimation.
 Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points.
@@
 
-\todo{This paragraph seems to be repeated/duplicated bellow.}
+%\todo{This paragraph seems to be repeated/duplicated bellow.}
 

### 2019-02-02 komlos.tex
edits to intro

@@
 
-An important application of our generic coreset result is Kernel density estimation.
+We show that our result applies to any analytic function of the dot product. 
+These include Logistic Regression $F(q) =  \sum_i \log(1+\exp(\ip{y_ix_i,q}))$, Covariance or matrix approximation  $F(q) =  \sum_i \ip{x_i,q}^2$, sigmoid activation loss $F(q) =  \sum_i 1/(1+\exp(\ip{y_ix_i,q}))$, linear regression $F(q) =  \sum_i (\ip{y_ix_i,q} -y_i)^2$ and many others.
+For all the aforementioned  $x,q \in R^d$ and $y_i \in \{-1,-1\}$.
+By bounding the class discrepancy of all such functions we obtain coresets of size $O(\sqrt{d}/\eps)$ for all of them.
+
+We note that while we obtain universal {\it additive guarantee} it is often much harder to get a  {\it multiplicative guarantee}
+For Logistic regression, for example, a recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a  {\it multiplicative guarantee} that is based on an average sensitivity property of the dataset.
+They provide a lower bound for the size of a multiplicative error coreset.
+They show that in general it is not possible to achieve $m \ll n$. 
+The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
+\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
+The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
+
+We show that our result also applies to any analytic function of the squared distance.
+A prime example of that is Gaussian kernel density estimation.
 Kernel density estimation is a popular tool in data analysis aimed to estimate a continuous distribution with a finite set of points. 
@@
 A thorough survey could be found in \cite{silverman2018density}. 
-Given a set of $n$ data points $x_1,\ldots,x_n$ and a query $q$, the density estimate of $q$ is the average $\frac{1}{n} \sum_i K(x_i,q)$ of the kernel evaluations with the data points.
-The task of finding a coreset for kernel density estimates consists of obtaining a set of points $z_1,\ldots,z_m$ with weights $w_1,\ldots,w_m$ for some $m \ll n$ such that for any query $q$ it holds that
-$\frac{1}{n} \sum_i K(x_i,q) = \frac{1}{m} \sum_i w_i K(z_i,q) \pm \eps$.
-For this task, the state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751}, achieving $m=\sqrt{d\log(1/\eps)}/\eps$ where $d$ is the dimension of the original data points.
+Given a set of $n$ data points $\{x_1,\ldots,x_n\}$ and a query $q$, the Gaussian density estimate at point $q$ is given by $\sum_i K(x_i,q) = \sum_i e^{-\|x-q\|^2}$. 
+Obtaining the smallest possible coreset for this problem has been open for several years.
+The state-of-the-art is given by \cite{DBLP:journals/corr/abs-1802-01751} (see references within). 
+They achieve coresets of size $O(\sqrt{d\log(1/\eps)}/\eps)$ where $d$ is the dimension of the original data points. 
 Their result holds for any Lipchitz bounded positive semi-definite kernels. 
@@
 The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds. 
-Additionally, they provide a simpler algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset.
-It is in fact known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p.
-$1-\delta$ for some kernel types.
+Additionally, they provide an algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset. 
+It is, in fact, known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p. $1-\delta$ for some kernel types. 
 In this paper we resolve the open question by \cite{DBLP:journals/corr/abs-1802-01751} and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$, matching the lower bound.
-In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = g(\|x-q\|^2)$.
-Moreover, we provide a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive kernel.
-Although the worst case lower bound is $1/\eps^2$, we conjecture that in realistic scenarios, the deterministic algorithm should outperform random sampling as it explicitly takes advantage of negative correlations.
+In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = f(\|x-q\|^2)$.
 
-Another application of our coreset results applies to logistic regression.
-Logistic Regression is an extremely popular technique for classification.
-We are given a set of $n$ pairs $x_i,y_i$ with $x_i \in \R^d$ and $y_i \in \{-1,1\}$.
-The objective is to find a regressor $q \in \R^d$ minimizing the logistic loss defined as $\E_i \log(1+\exp(x_i^\top q y_i))$.
-A coreset for logistic regression is a set of $m \ll n$ pairs $z_i, v_i$ in $\R^d, \{-1,1\}$ correspondingly along with weights $w_i$, with the property that for any regressor $q$, either $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) \pm \eps$ or $\E_i \log(1+\exp(x_i^\top q y_i)) = \E_i \log(1+\exp(z_i^\top q v_i)) (1 \pm \eps)$.
-A recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a multiplicative guarantee that is based on an average sensitivity property of the dataset.
-They provide a lower bound for the size of a multiplicative coreset showing that in general it is not possible to achieve $m \ll n$.
-The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
-\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
-The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
-Our results prove that for an additive guarantee, it is possible to obtain a coreset of size $O(\sqrt{d}/\eps)$.
+We also provide another independent result; 
+a very simple and deterministic algorithm for constructing coresets of size $O(1/\eps^2)$ for any positive semi-definite kernel. 
+Although the worst case lower bound is $O(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
 

### 2019-02-02 komlos.tex
typos

@@
 A carefully selected coreset can, at least potentially, be better than a uniformly sampled one. 
-It can be smaller and still give the same generalization power. 
-Alternatively, it can give better generalization with the same number of data points. 
+It can be smaller and still give the same generalization power or give better generalization with the same number of data points. 
 %That is the usefulness of coresets in the context of machine learning. 
@@
 These include Logistic Regression $F(q) =  \sum_i \log(1+\exp(\ip{y_ix_i,q}))$, Covariance or matrix approximation  $F(q) =  \sum_i \ip{x_i,q}^2$, sigmoid activation loss $F(q) =  \sum_i 1/(1+\exp(\ip{y_ix_i,q}))$, linear regression $F(q) =  \sum_i (\ip{y_ix_i,q} -y_i)^2$ and many others.
-For all the aforementioned  $x,q \in R^d$ and $y_i \in \{-1,-1\}$.
+For all the aforementioned  $x,q \in R^d$ and $y_i \in \{-1,1\}$.
 By bounding the class discrepancy of all such functions we obtain coresets of size $O(\sqrt{d}/\eps)$ for all of them.
@@
 For Logistic regression, for example, a recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a  {\it multiplicative guarantee} that is based on an average sensitivity property of the dataset.
-They provide a lower bound for the size of a multiplicative error coreset.
-They show that in general it is not possible to achieve $m \ll n$. 
+They provide a lower bound for the size of a multiplicative error coreset
+proving in particular that in general it is not possible to achieve $m \ll n$. 
+%They show that in general it is not possible to achieve $m \ll n$. 
 The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
@@
 a very simple and deterministic algorithm for constructing coresets of size $O(1/\eps^2)$ for any positive semi-definite kernel. 
-Although the worst case lower bound is $O(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
+Although the worst case lower bound is $\Omega(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
 

### 2019-02-13 komlos.tex
changing the title...
typos

@@
-\documentclass[anon,12pt]{colt2019} % Anonymized submission
-% \documentclass[12pt]{colt2019} % Include author names
+%\documentclass[anon,12pt]{colt2019} % Anonymized submission
+\documentclass[12pt]{colt2019} % Include author names
 
@@
 This paper establishes some explicit connections between class discrepancy, coreset complexity, learnability, and streaming algorithms.
+
+%In this talk we ask the question, how much data do you really need?
+To answer that, we explore the notion of coresets in machine learning.
+Those are small sets of data points (or examples) with the following unique property.
+For all models, the loss suffered on the coreset is roughly the same as the loss on the entire data.
+As a result, optimizing (training) over the coreset is simultaneously more efficient and provably close to optimal.
+Much research was devoted to finding small coresets for logistic regression, linear regression, clustering, density estimation, covariance approximation and many other problems.
+This talk will present a new measure of function class complexity, namely, class discrepancy.
+Class discrepancy captures the coreset complexity (minimal coreset size) for all the above problems and many others.
+These coresets are asymptotically smaller than those currently known and are often provably optimal.
+In fact, there exist mergeable streaming coreset constructions for all machine learning problems with bounded class discrepancy.
+This, information theoretically, allows for communication free, distributed, order agnostic, streaming machine learning.
 \end{abstract}
@@
 The goal is to produce a coreset. This is a small set $S\subset [n]$ and weights $w \in\R_+^{n}$ such that $\tilde F(q) = \sum_{i \in S} w_i f(x_i,q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
 There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
@@
 Moreover, our solutions create streaming algorithms with fully mergeable sketches. 
-The size of the coreset above appears to be intimately tied to the class discrepancy properties of the associated functions.
+The size of the coresets appear to be intimately tied to the class discrepancy properties of the associated functions.
 

### 2019-02-13 src/signedRankOneProjections.py

@@ -1,24 +1,46 @@
-from numpy import outer, dot
-from numpy.random import randn
+from numpy import outer, dot, zeros, sum
+from numpy.random import randn, random, randint
 from numpy.linalg import norm
 
-for d in range(221,301):
-    for t in range(10):
-        n = 1000
-        X = randn(n,d)
-        S = randn(n)
+
+for d in range(1,101):
+    for t in range(1):
+        n = 10000
+        #X = random((n,d))
+        #X = randn(n,d)
+        X = zeros((n,d))
+        S = zeros(n)
+        C = zeros((d,d))
         for i in range(n):
-            X[i,:] = X[i,:]/norm(X[i,:])
-            S[i] = 1.0 if S[i] > 0.0 else -1.0 
-        
-        C = sum(S[i]*outer(X[i,:],X[i,:]))
+            #x = random(d)
+            #x = randn(d)
+            x = zeros(d)
+            x[randint(0,d)] =  1.0
+            x[randint(0,d)] = -1.0
+            x = x/norm(x)
+            X[i,:] = x
+            S[i] = 1.0 if random() > 0.5 else -1.0 
+            C += S[i]*outer(X[i],X[i])
+
         curr_norm = norm(C,2)
-        for _ in range(10):
+        sign_changes_list = [0]
+        norm_list = [curr_norm]
+        sign_changes = 1
+        while sign_changes > 0:
+            sign_changes = 0
             for i in range(1,n):
                 change_C = C - 2*S[i]*outer(X[i,:],X[i,:])
-                if norm(change_C) < curr_norm:
+                change_norm = norm(change_C,2)
+                if change_norm < curr_norm:
                     C = change_C
-                    S[i] = -1.0 if S[i] > 0.0 else -1.0
-
-        C = sum(S[i]*outer(X[i,:],X[i,:]))
-        print('%s,%f'%(d,norm(C,2)))
+                    curr_norm = change_norm
+                    S[i] = -1.0 if S[i] > 0.0 else 1.0
+                    sign_changes+=1
+                    
+            sign_changes_list.append(sign_changes)
+            norm_list.append(curr_norm)
+            
+        final_C = sum(S[i]*outer(X[i,:],X[i,:]) for i in range(n))
+        final_norm = norm(final_C,2)
+        s = ' ,'.join('%d, %f'%(sc, cn) for (sc, cn) in zip(sign_changes_list ,norm_list))
+        print('%s, %f, '%(d,final_norm) + s)

### 2019-03-25 response.md
initial respose in markdown

### Interesting paper with new but simple techniques. References and comparisons are missing

The paper does _not_ offer new bound on the Rademacher complexity. It suggests a new measure of complexity. Namely, the class discrepancy. The two quantities are contrasted and compared for discussion and intuition building. In fact, the new bound don’t hold for sampling but rather for algorithmic selection of coresets.

Regarding additive coresets, indeed, coresets are more often discussed in the context of multiplicative approximation. The authors will make sure to emphasize that this is not the case here. It is important to note that additive bounds for coresets and sketches are quite common. One could argue that additive error bounds are more important because they give smaller coresets while still allowing generalization results.

Regarding running time, the algorithm is actually not exponential but rather relies on constructive version of Banaszczyk’s theorem [1]. The authors will add that discussion into the paper.

It is not clear to the authors how one would obtain these results by extending results for 1-mean and low rank.  Regarding the suggested references. The authors will include those and explain the connections to the current work.

[1] Nikhil Bansal, Daniel Dadush, Shashwat Garg, Shachar Lovett:
The gram-schmidt walk: a cure for the Banaszczyk blues. STOC 2018: 587-597

Algorithm 1 is not an optimal discrepancy solution but rather a “neat trick” which works well in practice (experiments omitted because it’s not the focus of the paper). While 1/eps^2 coresets are indeed achievable for Frank Wolfe Algorithms (see Philips et al.) this algorithm is different, straight forward, and elegant. See actual python code for it below

```python
def split(vectors, kernel):
    set1 = []; set2 = []
    for v in vectors:
        sum1 = sum([kernel(v,o) for o in set1])
        sum2 = sum([kernel(v,o) for o in set2])
        if sum1 < sum2:
            set1.append(v)
        else:
            set2.append(v)                
    return (set1,set2) 
```

### nice, elegant contribution

The review is very thoughtful and thorough, thank you. We would only like to point out that the presented result actually do give generalization bounds. In fact, class discrepancy of sqrt(d)/m immediately translates to generalization of the form 
R < R* + O(sqrt(d)/m)
Where R is the Risk of the model obtained by ERM on an optimal coreset of size m.
The authors thought it was not worth including in paper but would be happy to include in the final version.

### reasonable paper but a bit incremental

* The given result does not depend on the Gaussian kernel parameter.
* Theorem 16 indeed “plays with notation” mainly in order to make the vector balancing lemma (14) standalone. 
* It is not clear what the reviewer is saying wrt to R. For clarity, the radius of convergence does not depend on the input set of points. The bounds hold universality for any set of points. 
* The improved merge-and-reduce hold for _all_ queries exactly like previous constructions. The analysis goes through a single query high probability bound and union bound which might be the source of confusion.
* Regarding the novelty, the author never claim to be the first to identify any connection between coresets, machine learning, and discrepancy. Some of these connections are literally text book material. For example, Machine Learning and coresets received a whole chapter in Bernard Chazelle’s classic text book “the discrepancy method”. Nevertheless, the presented connection is new, especially elegant, and very useful as a framework. This is made clear by achieving a large set of new results in one fell swoop. These include Gaussian KDE which received intensive research.

##### Answers to questions
*In Corollary 21, there is the assumption that the norm of x-q is bounded. Is this assumption also made in the prior work?*

TODO

*Does prior work assume gamma to be constant?*

TODO

*Why do Corollaries 17 and 18 follow from the previous Theorem for ||q|| <=1?*

TODO

*How does the paper compare to earlier work? What are the novel ideas?*

The core of the paper is based on three contribution all of which are new

1. A new measure of complexity for function classes, the class discrepancy.
2. New generalization results, coresets, and streaming algorithms based on the class discrepancy. Offline coresets constructions are indeed trivial and provided for completeness (which is clearly stated and not “over sold”). The streaming algorithms are new and improve on prior results.
3. Tight bound on the class discrepancy of several well studied problems (which require some mathematically involved lemmas)

### Interesting general framework, but comparison and presentation are not compelling

*sec 4 focuses on the special case of Kernel density estimation, which is the only case presented where the proposed framework leads to a new algorithm*

Section 4 does _not_ include an algorithm based on this framework but rather a standalone result. The framework produces algorithms for all of the stated problems including all analytic functions of the dot product or the squared distance. The algorithm is based on new constructive version of Banaszczyk’s Lemma.

[1] Nikhil Bansal, Daniel Dadush, Shashwat Garg, Shachar Lovett:
The gram-schmidt walk: a cure for the Banaszczyk blues. STOC 2018: 587-597

*The technical tools used to obtain the results are well known*

We highly contest this statement. The result is not only new and mathematically involved, it also improves on several recent papers one of which appeared in STOC as recently as last year.

The authors will take under advisement the add more survey material on frameworks for coresets and streaming algorithms (such the Braverman et al). These, however, do not compare directly for two main reasons. First, they consider multiplicative approximation and we consider additive approximation. Second, they are mostly sensitivity and sampling based and the bounds they achieve are not stated using similar quantities.

*How related are CD and RC in reality? Can we really convert RC bounds into CD bounds?*

RC and CD are connected conceptually connected but require completely different tools for analyzing them. The only formal connection is that CD<RC which is both trivial and uninteresting. It is analogous to saying that random sampling is a valid algorithm for choosing coreset. The paper shows that careful selection of a coreset is asymptotically better (CD = o(RC)).

No. To the best of knowledge, RC bounds cannot be converted to CD bounds.

*How much of the machinery from RC analysis can be converted for CD analysis? How much has this been done in the current proofs?*

See above answer, while we reviewed the literature and techniques for bounding RC, these did not carry through to CD (except for standard transitions using Cauchy-Swartz etc.)

*3.A) The reported complexity d/eps in regression problems is for multiplicative error bounds, which are harder. What are existing additive bounds for this problem?*

We are not aware of additive bounds for regression coresets.

*3.B) Similarly, bounds for multiplicative error in matrix column subset selection are of the order of d/eps. Here we achieve d^(1/2)/eps, but for additive bound. How does this result compares to existing work e.g. in spectral graph sparsification.*

We have corresponded about this topic with experts in these areas including Chris Musco, Nikhil Srivastava, and Nikhil Bansal. These appear to be new results that don’t quite stack against existing work due to the different kind of bounds (additive) they produce.  They do, however, greatly overperform matrix concentration-based sampling results (which is unsurprising and therefore not boasted in the paper)

*If there are computationally efficient (i.e. at least poly(n)) algorithms that could be extracted from this framework, it should be discussed in the paper, at least at the level of conjectures.*

The authors can add such statements to the paper. General algorithms require running the result of Bansal, Dadush, Garg, and Lovett which is, indeed, polynomial. The authors, however, acknowledge that above approach is not attractive enough for practitioners and leave it to future research to find more efficient algorithms that achieve the presented bounds.

*Quadratic complexity becomes quickly unfeasible as n grows.*

We agree with the reviewer. An o(n^2) algorithm would indeed be more desirable. This is subject to further research.

*What is the actual computational comparison between the proposed approach and existing poly(n) methods?*

These provide asymptotically different results. If the question is about experimental results, we can report that that O(n^2) algorithm produces much better coresets than sampling. We did not, however, code the solver for the general problem. This is left for future work.

*The appendix contains an interesting discussion*

The reviewer is correct, the authors will add more information regarding compactors in the body of the paper.

Regarding the “duality” of ‘n’ and ‘m’. The authors agree and will do their best to unify those.

### 2019-03-25 response.md
action items

@@
+### Suggested modifcations edits
+* unify n and m if possible
+* Add a generalization like result for ERM on the coreset
+* Add many citation (all from the reviews) plus Bernard Chazelle's book.
+* Add more discussion on the compactors (is the page limit really 12 pages?)
+* Answer TODO questions below
+* Discuss the algorithm explicitly
+* Are there other results on additive coresets that we are missing? 
+* How does the matrix column subsets selection compare to BSS?
+
 ### Interesting paper with new but simple techniques. References and comparisons are missing
@@
 It suggests a new measure of complexity.
-Namely, the class discrepancy.
+Namely, the Class Discrepancy.
 The two quantities are contrasted and compared for discussion and intuition building.
-In fact, the new bound don’t hold for sampling but rather for algorithmic selection of coresets.
+In fact, the new bound don’t hold for sampling but rather for algorithmic selection of coresets only.
 
@@
 
-We have corresponded about this topic with experts in these areas including Chris Musco, Nikhil Srivastava, and Nikhil Bansal.
+We have corresponded about this topic with experts in these areas including Christopher Musco, Nikhil Srivastava, and Nikhil Bansal.
 These appear to be new results that don’t quite stack against existing work due to the different kind of bounds (additive) they produce.

### 2019-03-26 response.md
response v2

@@
 
-### Interesting paper with new but simple techniques. References and comparisons are missing
+### General notes
 
-The paper does _not_ offer new bound on the Rademacher complexity.
-It suggests a new measure of complexity.
-Namely, the Class Discrepancy.
-The two quantities are contrasted and compared for discussion and intuition building.
-In fact, the new bound don’t hold for sampling but rather for algorithmic selection of coresets only.
+We'd like to thank the reviewers for their thoughtful feedbacks. A few general comments
 
-Regarding additive coresets, indeed, coresets are more often discussed in the context of multiplicative approximation.
-The authors will make sure to emphasize that this is not the case here.
-It is important to note that additive bounds for coresets and sketches are quite common.
-One could argue that additive error bounds are more important because they give smaller coresets while still allowing generalization results.
-
-Regarding running time, the algorithm is actually not exponential but rather relies on constructive version of Banaszczyk’s theorem [1]. The authors will add that discussion into the paper.
-
-It is not clear to the authors how one would obtain these results by extending results for 1-mean and low rank.
-Regarding the suggested references.
-The authors will include those and explain the connections to the current work.
+* missing citations: Thank you for pointing out missing citations. Below we address the connections to these papers and we will add this discussion to the paper.
+* run time: The results of section 3 prove the existence of an algorithm achieving a coreset for analytical functions.
+While a naive implementation is exponential, we in fact do conjecture there is a polynomial time algorithm given the constructive version of Banaszczyk's theorem [1].
+We will add a discussion about this.
+* Algorithm 1 is indeed similar to the Frank-Wolfe algorithm given in Philips et al., yet is conceptually simpler, easier to implement, and has smaller constants in its run-time.
+The novelty here is the simplification.
+* Regarding the novelty, the author never claim to be the first to identify any connection between coresets, machine learning, and discrepancy.
+Some of these connections are literally text book material.
+For example, Machine Learning and coresets received a whole chapter in Bernard Chazelle's classic text book the discrepancy method.
+Nevertheless, the presented connection is new, especially elegant, and very useful as a framework.
+This is made clear by achieving a large set of new results in one fell swoop.
+These include optimally resolving Gaussian KDE which received intensive research.
 
@@
 
-Algorithm 1 is not an optimal discrepancy solution but rather a “neat trick” which works well in practice (experiments omitted because it’s not the focus of the paper).
-While 1/eps^2 coresets are indeed achievable for Frank Wolfe Algorithms (see Philips et al.) this algorithm is different, straight forward, and elegant.
-See actual python code for it below
+### AnonReviewer2
 
-```python
-def split(vectors, kernel):
-    set1 = []; set2 = []
-    for v in vectors:
-        sum1 = sum([kernel(v,o) for o in set1])
-        sum2 = sum([kernel(v,o) for o in set2])
-        if sum1 < sum2:
-            set1.append(v)
-        else:
-            set2.append(v)                
-    return (set1,set2) 
-```
+We wanted to point out that the paper does not provide new bounds for Radamacher complexity nor does it hold for randomly sampled points.
+The result brings a new complexity measure, namely Class Discrepancy, that measures the generalization bound for an actively chosen, rather than randomly chosen, set.
 
-### nice, elegant contribution
+Regarding the merge-reduce algorithms: The main novelty of the paper is in setting up the problem so that existing merge-reduce techniques can be applied in order to achieve a streaming coreset.
+In particular we combine the general merge-reduce trick with the concept of compactors using variable length coresets.
+Since the tools are standard we feel that the proofs and algorithm should be in the appendix
+
+We are not sure about the connection to 1-mean queries and low-rank approximations. We'll try to see if one can be drawn and if so, add a small discussion about it
+
+[10] indeed provide coresets for the Gaussian Kernel but it is weak, multiplicative and larger in size compared to ours. Since we provide an additive bound the results are not comparable
+
+### Program Committee Member1
 
 The review is very thoughtful and thorough, thank you.
-We would only like to point out that the presented result actually do give generalization bounds.
+We would only like to point out that the presented result actually does give generalization bounds.
 In fact, class discrepancy of sqrt(d)/m immediately translates to generalization of the form
@@
 
-### reasonable paper but a bit incremental
+### Program Committee Member3
 
-* The given result does not depend on the Gaussian kernel parameter.
-* Theorem 16 indeed “plays with notation” mainly in order to make the vector balancing lemma (14) standalone. 
-* It is not clear what the reviewer is saying wrt to R. For clarity, the radius of convergence does not depend on the input set of points. The bounds hold universality for any set of points. 
-* The improved merge-and-reduce hold for _all_ queries exactly like previous constructions.
+* We indeed depend on a scaling parameter unlike the result of Philips et al. Still, the contribution is a new view and the application of kernel density estimation is one of many
+* Corollaries 17,18 follow from observing the Taylor expansion of the functions they apply to. We will note this in the paper
+* Theorem 16 indeed "plays with notations" mainly in order to make the vector balancing lemma (14) standalone. It applies for compact sets, in particular of radius R. We will make this clearer
+* The improved merge-and-reduce hold for *all* queries exactly like previous constructions.
 The analysis goes through a single query high probability bound and union bound which might be the source of confusion.
-* Regarding the novelty, the author never claim to be the first to identify any connection between coresets, machine learning, and discrepancy.
-Some of these connections are literally text book material.
-For example, Machine Learning and coresets received a whole chapter in Bernard Chazelle’s classic text book “the discrepancy method”.
-Nevertheless, the presented connection is new, especially elegant, and very useful as a framework.
-This is made clear by achieving a large set of new results in one fell swoop.
-These include Gaussian KDE which received intensive research.
 
-##### Answers to questions
+"the main ideas have been already used": We respectfully disagree.
+Indeed the connection between discrepancy and coresets has been drawn in the past.
+Alas, defining the Class Discrepancy in this way lands itself using strong tools like Banaszczyk's theorem which is completely new.
+We never claimed to have invented the halving trick or merge-reduce, that said we do improve on those construction with a variable compactor size.
+
 *In Corollary 21, there is the assumption that the norm of x-q is bounded. Is this assumption also made in the prior work?*
 
-TODO
+Some works do not need that assumption. The bounded norm is indeed an issue to be addressed. We will emphasize this in our paper.
 
@@
 
-TODO
-
-*Why do Corollaries 17 and 18 follow from the previous Theorem for ||q|| <=1?*
-
-TODO
+Some do not. This is a side effect of using a Taylor series based argument which is arguably too weak. We hope to eliminate that limitation in future research.
 
@@
 The core of the paper is based on three contribution all of which are new
-
 1. A new measure of complexity for function classes, the class discrepancy.
 2.
-New generalization results, coresets, and streaming algorithms based on the class discrepancy.
-Offline coresets constructions are indeed trivial and provided for completeness (which is clearly stated and not “over sold”).
+New generalization results, coresets, and streaming algorithms based only on class discrepancy.
+Offline coresets constructions are indeed trivial and provided for completeness (which is clearly stated and not ‚"over sold").
 The streaming algorithms are new and improve on prior results.
-3. Tight bound on the class discrepancy of several well studied problems (which require some mathematically involved lemmas)
+3. Tight bound on the class discrepancy of several well studied problems. This requires some mathematically involved lemmas will be useful independently in generalizing our results.
 
-### Interesting general framework, but comparison and presentation are not compelling
+### AnonReviewer1
 
@@
 
-Section 4 does _not_ include an algorithm based on this framework but rather a standalone result.
-The framework produces algorithms for all of the stated problems including all analytic functions of the dot product or the squared distance.
-The algorithm is based on new constructive version of Banaszczyk’s Lemma.
+Section 4 does _not_ include an algorithm based on this framework but rather a standalone result which generates a coreset of size 1/eps^2 (instead of sqrt(d)/eps).
+The framework produces algorithms for all of the stated problems including all analytic functions of the dot product or the squared distance, albeit of exponential complexity.
+We claim that the mere existence of these algorithms is an interesting result.
+Finding an efficient version is a problem we believe is feasible due to [1] yet leave for future work.
 
@@
 
-RC and CD are connected conceptually connected but require completely different tools for analyzing them.
+RC and CD are connected conceptually but require completely different tools for analyzing them.
 The only formal connection is that CD<RC which is both trivial and uninteresting.
-It is analogous to saying that random sampling is a valid algorithm for choosing coreset.
-The paper shows that careful selection of a coreset is asymptotically better (CD = o(RC)).
-
-No. To the best of knowledge, RC bounds cannot be converted to CD bounds.
+It is analogous to saying that the best active set achieves at least as good a generalization bound as a random set.
+The interesting question is how much better can an actively selected set (coreset) do compared to a random one.
+The fact that CD=o(RC) translates to the answer "asymptotically better".
+Quite strikingly, RC based generalizations tend to decay at 1/sqrt(n) while DC based tend to decay like 1/n.
 
@@
 
-See above answer, while we reviewed the literature and techniques for bounding RC, these did not carry through to CD (except for standard transitions using Cauchy-Swartz etc.)
+There is little to no connection, as far as we can tell. The machinery for proving RC and CD are quite different. We'll mention this in the paper.
 
@@
 
-We are not aware of additive bounds for regression coresets.
+We are not aware of published results for additive bounds for regression coresets.
 
@@
 We have corresponded about this topic with experts in these areas including Christopher Musco, Nikhil Srivastava, and Nikhil Bansal.
-These appear to be new results that don’t quite stack against existing work due to the different kind of bounds (additive) they produce.
-They do, however, greatly overperform matrix concentration-based sampling results (which is unsurprising and therefore not boasted in the paper)
+These appear to be new results that don't quite stack against existing work due to the different kind of bounds (additive) they produce.
+They do, however, greatly out-perform matrix-concentration based sampling results (which is unsurprising and therefore not called out in the paper)
 
@@
 
-The authors can add such statements to the paper.
-General algorithms require running the result of Bansal, Dadush, Garg, and Lovett which is, indeed, polynomial.
-The authors, however, acknowledge that above approach is not attractive enough for practitioners and leave it to future research to find more efficient algorithms that achieve the presented bounds.
+We conjecture the existence of polynomial algorithms but leave that to future work.
 
@@
 These provide asymptotically different results.
-If the question is about experimental results, we can report that that O(n^2) algorithm produces much better coresets than sampling.
-We did not, however, code the solver for the general problem.
-This is left for future work.
+If the question is about experimental results, we can report that that the O(n^2) algorithm produces much better coresets than sampling.
+We did not, however, code the solver for the general problem because that would probably be infeasible.
+We hope future work will yield efficient algorithms that provably match the optimal coreset size.
 
@@
 
-Regarding the “duality” of ‘n’ and ‘m’. The authors agree and will do their best to unify those.
+Regarding the duality of n and m, the authors agree and will do their best to unify those.

### 2019-03-29 komlos.tex
typo fix
minor fixes
cleanup

--- 2019-02-02 komlos.tex
@@
 \usepackage{amsmath}
-%\usepackage{amsthm}
 \usepackage{algorithm}
 \usepackage[noend]{algorithmic}
-%\usepackage{algorithmic}
-%\usepackage{algorithm}
-%\usepackage[noend]{algorithmic}
-%\usepackage[margin=1in]{geometry}
 \usepackage{xcolor}
@@
 \usepackage{ amssymb }
+\usepackage{algorithm2e}
+\newtheorem{fact}[theorem]{Fact}
 
-\usepackage{algorithm2e}
-
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{conjecture}{Conjecture}[section]
-%\newtheorem{claim}[theorem]{Claim}
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{remark}[theorem]{Remark}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{observation}[theorem]{Observation}
-%\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{fact}[theorem]{Fact}
-%\newtheorem*{definition*}{Definition}
-%\newtheorem{definition}{Definition}
-%\newtheorem{claim}{Claim}
-%\newtheorem{theorem}{Theorem}
-
-\newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
-\newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
-
-%\newcommand{\zk}[1]{}
-%\newcommand{\el}[1]{}
+%\newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
+%\newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
+%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
 
@@
 \newcommand{\E}{\mathbb{E}}
-\newcommand{\D}{\rho}
 \newcommand{\eps}{\epsilon}
@@
 \newcommand{\Q}{\mathcal{Q}}
-%\usepackage{ntheorem}
 \newcommand{\floor}[1]{\left \lfloor #1 \right \rfloor}
 \newcommand{\ceil}[1]{\left \lceil #1 \right \rceil}
-\newcommand{\disc}{\text{disc}}
-\renewcommand{\Pr}{\operatorname{Pr}}
-
-\newcommand{\komconstant}{c}
 
@@
 Suppose you are trying to optimize an expression over a set of items, data points, or examples.
-%The optimization problem is difficult and often exponential in the input set size.
 The optimization problem is difficult and often square, cubic or even exponential in the input set size.
@@
 It can be smaller and still give the same generalization power or give better generalization with the same number of data points. 
-%That is the usefulness of coresets in the context of machine learning. 
 There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references therein that tie the coreset size to the VC dimension of the  function family, and the average sensitivity of the dataset.
@@
 This paper defines the analog to Rademacher complexity that aims to characterize the coreset complexity, i.e., the generalization ability of the best possible coreset of a fixed size.
-
-%Connection between coresets and discrepancy have been made in the non-streaming setting \cite{phillips2009small}, Theorem 1.1.
 
@@
 proving in particular that in general it is not possible to achieve $m \ll n$. 
-%They show that in general it is not possible to achieve $m \ll n$. 
 The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
@@
 The goal is to produce a coreset. This is a small set $S\subset [n]$ and weights $w \in\R_+^{n}$ such that $\tilde F(q) = \sum_{i \in S} w_i f(x_i,q)$ approximates $F(q)$.
-Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all $q \in \mathcal Q$ simultaneously. % or for every fixed $q$ with probability at least $1-\delta$. 
+Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ for all $q \in \mathcal Q$ simultaneously. 
 There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript. 
@@
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
-%Definitions~\ref{cd2} and \ref{cd3} are therefore equivalent. 
 The set $A$ should be thought of as the set of all possible induces losses vectors. 
 Namely, $a\in A$ if there is a model $q$ such $a_i = f(x_i,q)$.
-
-%\todo{This paragraph seems to be repeated/duplicated bellow.}
-
-%These definition are intentionally very similar to those of the Rademacher complexity $R_m(\F)$.
-%The only difference is that we consider the minimal value over $\sigma$ rather than its expectation for a uniform random $\sigma$.
-%Rademacher complexity uses random signs because it measures the effect of data being chosen uniformly at random (or drawn from an unknown distribution).
-See \cite{Bartlett:2003:RGC:944919.944944} for other notions of complexity and relationships between them.\footnote{\cite{Bartlett:2003:RGC:944919.944944} use the term ``discrepancy'' to define a different quantity than the one above.}
-%We claim that $D_m$ is the right measure of complexity for bounding the size of coresets (coreset complexity) and for creating mergeable sketches (streaming coreset complexity).
-%Trivially,  $D_m \le R_m$. 
-%We show, however, that $D_m(\F) = o(R_m(\F))$ for a wide range of interesting problems in machine learning.
-%This immediately proves the existence of small coresets for these problems.
 
@@
 Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
-%The constant $c$ does not depend on $m$.
 \end{fact}
@@
 Any function $f$ with class discrepancy $D_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
-%The constant $c$ does not depend on $m$.
 \end{fact}
@@
 
-%\noindent Surprisingly, we give upper bounds on streaming coreset complexities for functions which are only poly-logarithmically larger than their offline coreset complexities.
-%This section assumes access to an algorithm for finding low discrepancy signs $\sigma$.
 \noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bound are only poly-logarithmically larger than their offline counterparts.
@@
 Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has streaming coreset complexity of $O\left(c\log^2(\eps n/c)/\eps\right)$.
-%The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 Any function $f$ with class discrepancy $D_m = O(c/\sqrt{m})$ has streaming coreset complexity of $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$.
-%The constant $c$ does not depend on $m$.
 \end{theorem}
@@
 We now define a mapping $\psi(x)$ of $x\in \R^d$ to a high dimensional space. 
-%The function $\operatorname{flat}(X)$ simply strings the entry values of the tensor $X$ into a vector.
 $$\psi(x) = \left[x, \frac{\operatorname{flat}(x^{\otimes 2})}{\sqrt{2\log^2(2)}}, \frac{\operatorname{flat}(x^{\otimes 3})}{\sqrt{3\log^2(3)}}, \ldots,\frac{\operatorname{flat}(x^{\otimes k})}{\sqrt{k\log^2(k)}},\ldots \right]$$
@@
 
-%\end{proof}
-
 \section{A Simple Algorithm for Kernel Density Estimation}
 From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $D_m = O(\sqrt{d}/m)$. 
-%The result however is non-constructive in the sense that we are not aware of an algorithm that can obtain the $\sigma$ signs efficiently. 
 Here, we provide a computationally efficient bound that can be achieved with a straightforward algorithm of complexity $O(m^2)$.
@@
 In fact, we show that for any positive kernel $D_m = O(1/\sqrt{m})$.
-This bound is superior to that of the previous section for high dimensions $d > \sqrt{m}$.
+This bound is superior to that of the previous section for high dimensions $d > m$.
 More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
@@
 The streaming coreset algorithm is randomized and fails with probability at most $\delta$.
-%For any function family $\F$ with a corresponding class discrepancy $D_m = O(c/\sqrt{m})$ there exists a fully-mergeable streaming coreset deterministic algorithm of size $O\left(c^2\log^3(\eps^2 n/c) /\eps^2\right)$ whose error is at most $\eps n$.
 \begin{proof}

### 2019-03-29 komlos.tex
more cleanup

@@
 As corollaries of the general technique we bound the discrepancy of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
-Our result resolves a long standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
+Our result resolves a long-standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
 We provide two more related but independent results. 
@@
 Therefore, there is a strong incentive to reduce the cardinality of that set. 
-The goal is therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
+The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
 This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
@@
 Obtaining small coresets and understanding the coreset complexity (the size of the minimal coreset) of different problems is of significant theoretical and practical importance.
-While some problems obviously do not admit small coresets, other do. 
+While some problems obviously do not admit small coresets, others do. 
 There are several results that connect the simplicity of the measure and its coreset complexity.
@@
 These results require different analyses and seem to stem from different mathematical underpinnings. 
-This paper provides a general framework for obtaining, and improving on, these results.
+This paper provides a general framework for obtaining and improving on these results.
 
@@
 We show that our result applies to any analytic function of the dot product. 
-These include Logistic Regression $F(q) =  \sum_i \log(1+\exp(\ip{y_ix_i,q}))$, Covariance or matrix approximation  $F(q) =  \sum_i \ip{x_i,q}^2$, sigmoid activation loss $F(q) =  \sum_i 1/(1+\exp(\ip{y_ix_i,q}))$, linear regression $F(q) =  \sum_i (\ip{y_ix_i,q} -y_i)^2$ and many others.
+These include Logistic Regression $F(q) =  \sum_i \log(1+\exp(\ip{y_ix_i,q}))$, Covariance or matrix approximation 
+$F(q) =  \sum_i \ip{x_i,q}^2$, sigmoid activation loss $F(q) =  \sum_i 1/(1+\exp(\ip{y_ix_i,q}))$, linear regression $F(q) =  \sum_i (\ip{y_ix_i,q} -y_i)^2$ and many others. 
 For all the aforementioned  $x,q \in R^d$ and $y_i \in \{-1,1\}$.
@@
 
-We note that while we obtain universal {\it additive guarantee} it is often much harder to get a  {\it multiplicative guarantee}
+We note that while we obtain a universal {\it additive guarantee} it is often much harder to get a  {\it multiplicative guarantee}.
 For Logistic regression, for example, a recent paper \cite{DBLP:journals/corr/abs-1805-08571} provides a coreset with a  {\it multiplicative guarantee} that is based on an average sensitivity property of the dataset.
-They provide a lower bound for the size of a multiplicative error coreset
-proving in particular that in general it is not possible to achieve $m \ll n$. 
+They provide a lower bound for the size of a multiplicative error coreset proving in particular that in general, it is not possible to achieve $m \ll n$. 
 The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.
@@
 a very simple and deterministic algorithm for constructing coresets of size $O(1/\eps^2)$ for any positive semi-definite kernel. 
-Although the worst case lower bound is $\Omega(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
+Although the worst-case lower bound is $\Omega(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
 
@@
 
-In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well behaved functions.
+In both machine learning and in streaming and sketching problems our goal is (often) to approximate sums or expectations of well-behaved functions.
 Specifically, we need to approximate $\E_x f(x)$ or $\frac{1}{n}\sum_{i=1}^{n} f(x_i)$ for every $f\in \F$ where $\F$ is a family of functions and $x_i \in \X$ are either sampled training examples or an arbitrary set of stream items.
@@
 We therefore focus on approximating the average, or rather, the sum $\sum_{i=1}^{n} f(x_i)$.
-For notational convenience we use a parameter $q \in \Q$ to index into $\F$ explicitly.
+For notational convenience, we use a parameter $q \in \Q$ to index into $\F$ explicitly. 
 In other words, there is a bijective mapping between $\Q \equiv \F$ such that $f(x) \in \F$ iff there exists $q\in\Q$ such that $f(x,q)=f(x)$.
@@
 Moreover, our solutions create streaming algorithms with fully mergeable sketches. 
-The size of the coresets appear to be intimately tied to the class discrepancy properties of the associated functions.
+The size of the optimal coreset appears to be intimately tied to the class discrepancy properties of the associated functions.
 
@@
 The class discrepancy of $f$ or $\F$ without a reference a set $\{x_1,\ldots,x_m\}$ is the upper bound on any subset of $\X$ of size $m$.
-Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
+Throughout the manuscript, we assume a bijective mapping between $\F$ and $\Q$. 
 Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
@@
 \subsection{Coreset Complexity}
-In this section we point out a direct connection between coreset complexity and class discrepancy.
+In this section, we point out a direct connection between coreset complexity and class discrepancy.
 The connection is a simple application of the folklore argument know as the ``the halving trick".
@@
 Together with the results of Section~\ref{sec:sketch} this provides an efficient sketching algorithm for Kernel Density Estimation.
-In fact, we show that for any positive kernel $D_m = O(1/\sqrt{m})$.
-This bound is superior to that of the previous section for high dimensions $d > m$.
-More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$.
+In fact, we show that for any positive kernel $D_m = O(1/\sqrt{m})$. This bound is superior to that of the previous section for high dimensions $d > m$. 
+More importantly, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$. 
 Given a collection of data points $X = \{x_1,\ldots, x_n\}$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as $ F(q) = \sum_{i=1}^{n} K(x_i,q) $.
@@
 $\max_q |\sum_i \sigma_i f(x_i,q)| \leq m D_m$. 
-Note that such a sequence is guarantied to exist by the definition of the class discrepancy.
+Note that such a sequence is guaranteed to exist by the definition of the class discrepancy.
 For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
@@
 For every two items observed it will output one of them uniformly at random.
-It is easy to see that a sequence of such compactors can in fact be implemented with $O(1)$ memory via reservoir sampling.
-The memory of this process is therefor identical, at least asymptotically, to the above.
+It is easy to see that a sequence of such compactors can, in fact, be implemented with $O(1)$ memory via reservoir sampling.
+The memory of this process is therefore identical, at least asymptotically, to the above.
 
@@
 Here we extend the idea of \cite{DBLP:conf/focs/KarninLL16} applied for quantiles to general coresets.
-To explain the high level idea consider again the easier setting where we know $n$, the length of the stream in advance.
+To explain the high-level idea consider again the easier setting where we know $n$, the length of the stream in advance.
 As in the $D_m=c/\sqrt{m}$ case, we will split the compactors into the top $\log\log(1/\delta)$ ones acting deterministically and bottom compactors yielding random outputs.

### 2019-03-29 komlos.tex
adds generalization result

@@
 \newtheorem{fact}[theorem]{Fact}
+\usepackage{soul}
 
 %\newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
-%\newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
+\newcommand{\el}[1]{\textcolor{blue}{EL: #1}}
+\newcommand{\add}[1]{\textcolor{blue}{ADD: #1}}
 %\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
@@
 \begin{fact}\label{fct:eps1}
-Any function $f$ with class discrepancy $D_m(f) = O(c/m)$ has coreset complexity of $O(c/\eps)$.
+Any function $f$ with class discrepancy $D_m = O(c/m)$ has coreset complexity of $O(c/\eps)$.
 \end{fact}
 \begin{fact}\label{fct:eps2}
-Any function $f$ with class discrepancy $D_m(f) = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
+Any function $f$ with class discrepancy $D_m = O(c/\sqrt{m})$ has coreset complexity $O(c^2/\eps^2)$.
 \end{fact}
 \begin{proof}
-\noindent  Consider the signed sum of error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+\noindent  Consider the signed-sum error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
 Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. 
-We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item weights of $2$ and an error at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$.
+We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item-weight $2$. 
+The error is at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$. 
 The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-By Definition we can select signs such that $|E(q)| \le m D_m(f)$.
+By Definition we can select signs such that $|E(q)| \le m D_m$.
 
+\add{
+Naturally, one could iterate this process. Starting with $n$ items and ending with $m$.
+Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset. 
+\[
+F = F_0 = 2F_1 \pm n_0D_{n_0} = 4F_{2} \pm 2n_1D_{n_1} \pm n_0D_{n_0} = \ldots = 2^T F_T \pm \sum_{t=0}^{T-1} 2^t n_t D_{n_t}
+\]
+Here $T$ stand for the total number of iterations needed for reaching a coreset of size $m$. 
+Given $n_t \le n/2^{t}$ and the polynomial dependence of $D_m$ on $m$ we have 
+$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{n_T})$ for all $T$.
+Specifically, for $T$ such that $n_T \approx m$, setting the weights $w = 2^T$ we have $F(q) = \tilde F(q) \pm O(nD_m)$.
+Substituting the above expressions for $D_m$ completes the proof.
+}
+\st{
 Naturally, one could iterate this process.
-At step one, create a coreset of size at most $n/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{n}$.
-Then, create a coreset of size $n/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{n/2}  = c\sqrt{2n}$.
+Noting that the last term in above is a geometric sum we can conclude that 
+At step one, create a coreset of size at most $m/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{m}$.
+Then, create a coreset of size $m/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{m/2}  = c\sqrt{2m}$.
 Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
 Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
+}
 \end{proof}
 
-Notice that these bounds are (asymptotically) tight in the context of unweighted coresets.
-Taking for example the bound of Fact~\ref{fct:eps1}, if we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
+\begin{fact}
+Class discrepancy bounds are tight asymptoticly for {\it unweighted} coreset complexity.
+\end{fact}
+\begin{proof}Taking for example the bound of Fact~\ref{fct:eps1}, if we can guarantee the existence of an unweighted coreset of size $c/\eps$, then for $m$ items a coreset of size $m/2$ provides a sign assignment with an error of $\eps=2c/m$, leading to an upper bound of $O(c/m)$ on the class discrepancy.
+\end{proof}
+
+\add{
+The following it a straight forward fact which is provided mainly for convenience. 
+It loosely says that optimizing models on coresets generalizes. In other words, ERM works as expected.
+\begin{fact}
+Let $f(x,q)$ be the loss suffered by model $q$ on example $x$. 
+Let $R(q) = \frac{1}{n}F(q) = \frac{1}{n} \sum_{i=1}^n f(x_i,q)$ be the {\it empirical} risk associated with it.
+Let $q^*$ denote the best empirical risk minimizer on the data ($q^* = \arg\min_q F(q)$).
+Let $\tilde q$ be the minimizer of $q$ over an optimal weighted coreset of size $m$ ($\tilde q = \arg\min_q \tilde F(q)$).
+Then $R(\tilde q) \le R(q^*) + O(D_m)$.
+\end{fact}
+\begin{proof}
+This fact follows from the standard argument about empirical risk minimization.
+\[
+R(\tilde q) = \frac1n F(\tilde q)  \le  \frac{1}{n} \tilde F(\tilde q) + O(D_m) \le \frac{1}{n} \tilde F(q^*) + O(D_m) \le  \frac{1}{n}  F(q^*) + O(D_m)  = R(q^*)+ O(D_m)
+\]
+The first and last transitions are by definition. The second and fourth are by the approximation bounds above.
+The third transition is due to the optimality of $\tilde q$ for $\tilde F$
+\end{proof}
+}
 

### 2019-04-27 komlos.tex
add acknoledgement

@@
 \end{abstract}
+
+\paragraph{Acknowledgments:} The authors sincerely thank Nikhil Bansal, Nikhil Srivastava, Jeff Phillips, Wai Ming Tai, and Camron Musco 
+for generously sharing their time and ideas.
+They helped us uncover the usefulness of Banaszczyk's theorem for proving Lemma~\ref{uc}, compare to other results on coresets and discrepancy
+(specifically on Gaussian Kernel Density estimation), and understand the connection to graph sparsification and matrix column subset selection results.
 
@@
 
-\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bound are only poly-logarithmically larger than their offline counterparts.
+\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bounds are only poly-logarithmically larger than their offline counterparts.
 
@@
 We argued above that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
-We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ equally likely. 
+We can also take $\tilde F_{\pm}$ which is $\tilde F_{+}$ or $\tilde F_{-}$ with equally probability. 
 Clearly $|\tilde F_{\pm} - F| \le |E|$ as before. But now, $\E[\tilde F_{\pm}] = F$ as well. 
-In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times over small subsets of items from the stream.
+In the streaming algorithm, we apply this compaction (converting $F$ to $\tilde F_{\pm}$) many times to small subsets of items from the stream.
 This allows us to use concentration results to bound the overall error.
@@
 We prove the claim directly from the definition of a norm.
-Notice that for any $X \neq 0$, $\ip{X, q^{\otimes}}$ is a non-zero polynomial in $q$.
+Notice that for any $X \neq 0$, $\ip{X, q^{\otimes k}}$ is a non-zero polynomial in $q$.
 It follows that there must be $q$ for which its value is non-zero, meaning that $\|X\|_{T_k}=0$ iff $X=0$.

### 2019-04-27 komlos.tex
small changes

@@
 $$\max_k \frac{\|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k}}{\sqrt{k \log^{3}(k)}} \le O\left( \sqrt{d} \right)$$
+This concludes the proof of the statement.
 \end{proof}
@@
 The first equality simply unpacks the squared vector norm, the second transition is due to the induction assumption and the last substitutes our choice of 
-$\sigma$. This completes the proof that $|\sum_{i=1}^m \sigma_i K(x_i,q)| \le \sqrt{m}$ for all $q$.
+$\sigma$ (and $\operatorname{sign}(z)\cdot z =  |z|$). This completes the proof that $|\sum_{i=1}^m \sigma_i K(x_i,q)| \le \sqrt{m}$ for all $q$.
 \end{proof}
@@
 In such cases, the algorithm above performs much better than the worst-case bound predicts. 
-We leave it to future work to define properties of the data that ensure algorithm better guarantees by Algorithm~\ref{kernelAlg}.
+We leave it to future work to define properties of the data that ensure better guarantees for Algorithm~\ref{kernelAlg}.
 \bibliography{density}

### 2019-04-30 komlos.tex

--- 2019-03-29 komlos.tex
@@
 \begin{proof}
-\noindent  Consider the signed-sum error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
-Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. 
+\noindent For a set of $n$ points $x_1,\ldots,x_n$ and arbitrary query $q$, consider the signed-sum error function $E(q) = \sum_{i=1}^{n} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+Recalling $F(q) = \sum f(x_i,q)$, we consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. 
 We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item-weight $2$. 
-The error is at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$. 
+The error is at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$, and one of the coresets are of cardinality of at most $n/2$. 
 The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
-By Definition we can select signs such that $|E(q)| \le m D_m$.
+By definition we can select signs such that $|E(q)| \le m D_n$.
 
-\add{
-Naturally, one could iterate this process. Starting with $n$ items and ending with $m$.
-Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset. 
+Naturally, one could iterate this process. Starting with $n$ items and ending with $k$.
+Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset\footnote{We use the term $a=b \pm c$ to mention $|a-b| \leq c$ }. 
 \[
@@
 \]
-Here $T$ stand for the total number of iterations needed for reaching a coreset of size $m$. 
+Here $T$ stand for the total number of iterations. Let us analyze the error term.
 Given $n_t \le n/2^{t}$ and the polynomial dependence of $D_m$ on $m$ we have 
-$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{n_T})$ for all $T$.
-Specifically, for $T$ such that $n_T \approx m$, setting the weights $w = 2^T$ we have $F(q) = \tilde F(q) \pm O(nD_m)$.
-Substituting the above expressions for $D_m$ completes the proof.
-}
-\st{
-Naturally, one could iterate this process.
-Noting that the last term in above is a geometric sum we can conclude that 
-At step one, create a coreset of size at most $m/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{m}$.
-Then, create a coreset of size $m/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{m/2}  = c\sqrt{2m}$.
-Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
-Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
-}
+$$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{n_T}) . $$ 
+Setting $n_T$ in a way that $D_{n_T} = O(\eps)$ leads to a coreset with item weights of $w^T$ of the appropriate cardinality and completes the proof.
+
+%
+%\noindent  Consider the signed-sum error function $E(q) = \sum_{i=1}^{m} \sigma_i f(x_i,q)$ where $\sigma_i \in \{-1,1\}$.
+%Now consider $\tilde F_{+}(q) = F(q) + E(q)   = \sum_{i | \sigma_i=1} 2 f(x_i,q)$ and similarly $\tilde F_{-}(q) = F(q) - E(q)  =  \sum_{i | \sigma_i=-1} 2 f(x_i,q)$. 
+%We have that both $\tilde F_{+}(q)$ and $\tilde F_{-}(q)$ are approximations for $F(q)$ obtained by coresets of item-weight $2$. 
+%The error is at most $|\tilde F_{\pm}(q)- F(q)| =  |E(q)|$. 
+%The above is true for any choice of signs $\sigma$, specifically, for those minimizing $\max_q | E(q)|$.
+%By definition we can select signs such that $|E(q)| \le m D_m$. 
+%
+%\add{
+%Naturally, one could iterate this process. Starting with $n$ items and ending with $m$.
+%Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset. 
+%\[
+%F = F_0 = 2F_1 \pm n_0D_{n_0} = 4F_{2} \pm 2n_1D_{n_1} \pm n_0D_{n_0} = \ldots = 2^T F_T \pm \sum_{t=0}^{T-1} 2^t n_t D_{n_t}
+%\]
+%Here $T$ stand for the total number of iterations needed for reaching a coreset of size $m$. 
+%Given $n_t \le n/2^{t}$ and the polynomial dependence of $D_m$ on $m$ we have 
+%$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{n_T})$ for all $T$.
+%Specifically, for $T$ such that $n_T \approx m$, setting the weights $w = 2^T$ we have $F(q) = \tilde F(q) \pm O(nD_m)$.
+%Substituting the above expressions for $D_m$ completes the proof.
+%}
+%\st{
+%Naturally, one could iterate this process.
+%Noting that the last term in above is a geometric sum we can conclude that 
+%At step one, create a coreset of size at most $m/2$ of items of weight $2$ and incur an error of at most $c$ or $c \sqrt{m}$.
+%Then, create a coreset of size $m/4$ of items of weight $4$. Here, you incur error of $2c$ or $2c\sqrt{m/2}  = c\sqrt{2m}$.
+%Note that the sum of errors is a geometric sequence that is asymptotically dominated by its last element. 
+%Halting the compression at $\Theta(c/\eps)$ or $\Theta(c^2/\eps^2)$ items respectively achieves the goal.
+%}
 \end{proof}
@@
 
-\add{
 The following it a straight forward fact which is provided mainly for convenience. 
@@
 \end{proof}
-}
 
@@
 
-\section{A Simple Algorithm for Kernel Density Estimation}
+\subsection{Towards an Efficient Algorithm}
+
+%\section{A Simple Algorithm for Kernel Density Estimation}
 From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $D_m = O(\sqrt{d}/m)$. 

### 2019-05-09 karninliberty19.tex
camera ready v1

--- 2019-04-27 komlos.tex
@@
 Suppose you are trying to optimize an expression over a set of items, data points, or examples.
-The optimization problem is difficult and often square, cubic or even exponential in the input set size.
-Therefore, there is a strong incentive to reduce the cardinality of that set. 
-The goal is, therefore, to pinpoint a small subset of the data items which approximates the entire input set with respect to some function or geometric measure. Such small sets are called coresets. 
+The optimization problem is difficult. 
+Its running time dependence on the input set size is square, cubic, or even exponential.
+As a result, there is a strong incentive to reduce the cardinality of that set. 
+The goal is, therefore, to pinpoint a small subset of data items which approximates the entire input set with respect to the optimization at hand. 
+Such small sets are called coresets. 
 This idea is very general and applies to geometric properties of the data \cite{agarwal2005geometric}, 
@@
 It can be smaller and still give the same generalization power or give better generalization with the same number of data points. 
-There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references therein that tie the coreset size to the VC dimension of the function family, and the average sensitivity of the dataset.
+There are papers such as \cite{langberg2010universal, tolochinsky2018coresets} and references therein that tie the coreset size to the VC dimension of the function family and the average sensitivity of the dataset.
 These relationships come up as tools for constructing coresets rather than complexity measures aimed to characterize generalization ability. 
@@
 For all the aforementioned  $x,q \in R^d$ and $y_i \in \{-1,1\}$.
-By bounding the class discrepancy of all such functions we obtain coresets of size $O(\sqrt{d}/\eps)$ for all of them.
+By bounding the class discrepancy of all such functions we prove the existence of coresets of size $O(\sqrt{d}/\eps)$ for all of them.
 
@@
 The coreset they build is of cardinality $m \approx \mu\sqrt{nd^3}/\eps^2$ where $\mu \geq 1$ is a complexity measure of the dataset.  
-\cite{tolochinsky2018coresets} gives a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization.
+\cite{tolochinsky2018coresets} give a generic multiplicative coreset construction for any monotonic function with $\ell_2^2$ regularization. 
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors.
@@
 The authors give an almost matching lower bound of $\sqrt{d}/\eps$ and pose an open question for closing the gap between the bounds. 
-Additionally, they provide an algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset. 
-It is, in fact, known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p. $1-\delta$ for some kernel types. 
 In this paper we resolve the open question by \cite{DBLP:journals/corr/abs-1802-01751} and prove that the coreset complexity of Gaussian kernel density is indeed $O(\sqrt{d}/\eps)$, matching the lower bound.
-In fact, we show that this is the coreset complexity for any analytic function of the squared distance $f(x,q) = f(\|x-q\|^2)$.
+In fact, we show that this is the coreset complexity for any bounded analytic function of the squared distance $f(x,q) = f(\|x-q\|^2)$.
 
-We also provide another independent result; 
-a very simple and deterministic algorithm for constructing coresets of size $O(1/\eps^2)$ for any positive semi-definite kernel. 
-Although the worst-case lower bound is $\Omega(1/\eps^2)$ which matches the coreset achieved by sampling, we conjecture that in realistic scenarios, the deterministic algorithm will outperform random sampling as it explicitly takes advantage of negative correlations.
+In high dimensions $\sqrt{d}/\eps$ could be large. 
+It is known (see \cite{lopez2015towards}, Theorem 1) that a uniform random sample of $\log(1/\delta)/\eps^2$ points gives a coreset w.p. $1-\delta$ for some kernel types. 
+\cite{DBLP:journals/corr/abs-1802-01751} provide an algorithm based on the Frank-Wolf method that achieves a $1/\eps^2$ sized coreset. 
+In section \ref{kde2} we provide (as a stand alone result) a very simple and deterministic algorithm for constructing coresets of size $1/\eps^2$ for any positive semi-definite kernel.
+The worst-case coreset lower bound is $\Omega(1/\eps^2)$ which matches the coreset achieved by sampling.
+Yet, for real data the deterministic algorithm outperforms random sampling significantly (experiments not included in this manuscript).
 
@@
 
-\section{A Simple Algorithm for Kernel Density Estimation}
+\section{A Simple Algorithm for Kernel Density Estimation}\label{kde2}
 From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $D_m = O(\sqrt{d}/m)$. 
@@
 We leave it to future work to define properties of the data that ensure better guarantees for Algorithm~\ref{kernelAlg}.
-\bibliography{density}
+\bibliography{karninliberty19}
 

### 2019-05-09 response.md

@@
 * We indeed depend on a scaling parameter unlike the result of Philips et al. Still, the contribution is a new view and the application of kernel density estimation is one of many
-* Corollaries 17,18 follow from observing the Taylor expansion of the functions they apply to. We will note this in the paper
+* Corollaries 17,18 follow from a trivial bound to the coefficient in the Taylor expansion of the functions they apply to. We will note this in the paper
 * Theorem 16 indeed "plays with notations" mainly in order to make the vector balancing lemma (14) standalone. It applies for compact sets, in particular of radius R. We will make this clearer
@@
 New generalization results, coresets, and streaming algorithms based only on class discrepancy.
-Offline coresets constructions are indeed trivial and provided for completeness (which is clearly stated and not ‚"over sold").
+Offline coresets constructions are indeed trivial and provided for completeness (which is clearly stated and not "over sold").
 The streaming algorithms are new and improve on prior results.
-3. Tight bound on the class discrepancy of several well studied problems. This requires some mathematically involved lemmas will be useful independently in generalizing our results.
+3. Tight bound on the class discrepancy of several well studied problems. This requires some mathematically involved lemmas independently useful in generalizing our results.
 

### 2019-05-09 komlos.tex

@@
 
+\paragraph{Acknowledgments:} The authors sincerely thank Nikhil Bansal, Nikhil Srivastava, Jeff Phillips, Wai Ming Tai, and Camron Musco 
+for generously sharing their time and ideas.
+They helped us uncover the usefulness of Banaszczyk's theorem for proving Lemma~\ref{uc}, compare to other results on coresets and discrepancy
+(specifically on Gaussian Kernel Density estimation), and understand the connection to graph sparsification and matrix column subset selection results.
+
 \section{Introduction}
@@
 
-Naturally, one could iterate this process. Starting with $n$ items and ending with $k$.
-Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset\footnote{We use the term $a=b \pm c$ to mention $|a-b| \leq c$ }. 
+Naturally, one could iterate this process. Starting with $n$ items and ending with $m$.
+Let $F_t$ denote the (unweighted) sum of functions $f$ after $t$ iterations and $n_t$ denote the cardinality of the coreset\footnote{The expression $a=b \pm c$ means $|a-b| \leq c$}. 
 \[
@@
 Here $T$ stand for the total number of iterations. Let us analyze the error term.
-Given $n_t \le n/2^{t}$ and the polynomial dependence of $D_m$ on $m$ we have 
-$$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{n_T}) . $$ 
-Setting $n_T$ in a way that $D_{n_T} = O(\eps)$ leads to a coreset with item weights of $w^T$ of the appropriate cardinality and completes the proof.
+Given $n_t \le n/2^{t} \approx m$ and the polynomial dependence of $D_m$ on $m$ we have 
+$$\sum_{t=0}^{T-1} 2^t n_t D_{n_t} \le n \sum_{t=0}^{T-1} D_{n/2^t} = n\cdot O(D_{m}) . $$ 
+Setting $m$ for which $D_{m} = \eps$ gets coresets with appropriate cardinalities and completes the proof.
 
@@
 
-\subsection{Towards an Efficient Algorithm}
+\subsection{Towards an Efficient Algorithm}\label{kde2}
+%\section{A Simple Algorithm for Kernel Density Estimation}
 
-%\section{A Simple Algorithm for Kernel Density Estimation}
 From section \ref{sec:analytic} we know that the class discrepancy of the Gaussian kernel is $D_m = O(\sqrt{d}/m)$. 

### 2019-05-30 komlos20190225_COLT2019_orig.tex
typo fixes

--- 2019-02-13 komlos.tex
@@
-%\documentclass[anon,12pt]{colt2019} % Anonymized submission
-\documentclass[12pt]{colt2019} % Include author names
+\documentclass[anon,12pt]{colt2019} % Anonymized submission
+%\documentclass[12pt]{colt2019} % Include author names
 
@@
 Throughout the manuscript we assume a bijective mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
+Specifically, every element of $\F$ can be written as $f_q$ and has a unique $q \in \Q$ such that $f_q(x) = f(x,q)$. 
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
@@
 In this section we point out a direct connection between coreset complexity and class discrepancy.
-The connection is a simple application of the folklore argument know as the ``the halving trick".
+The connection is a simple application of the folklore argument known as the ``the halving trick".
 For simplicity, in what follows we focus on functions $f$ whose range is $[0,1]$.

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
adds citation to merge reduce

--- 2019-05-09 komlos.tex
@@
 
+\newtheorem*{theorem*}{Theorem}
+
 %\newcommand{\zk}[1]{\textcolor{red}{ZK: #1}}
@@
 We provide general techniques for bounding the class discrepancy of machine learning problems. 
-As corollaries of the general technique we bound the discrepancy of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
+As corollaries of the general technique we bound the discrepancy (and therefore coreset complexity) of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
 Our result resolves a long-standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
 We provide two more related but independent results. 
-First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
+First, an exponential improvement of the widely used merge-and-reduce trick \cite{BENTLEY1980301} which gives improved streaming sketches for any low discrepancy problem.
 Second, an extremely simple deterministic algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
@@
 For cases where an algorithm for finding this sequence $\sigma$ is not known, our result applies for the guarantee of the $\sigma$ sequence obtained by the algorithm.
-That is, if it is possible to obtain a bound of $D_m$ yet we can only find signs obtaining a bound of $\tilde{K}_m$, our results for the obtainable signs apply for $\tilde{K}_m$.
+That is, if it is possible to obtain a bound of $D_m$ yet we can only find signs obtaining a bound of $\tilde{D}_m > D_m$, our results for the obtainable signs apply for $\tilde{D}_m$.
 Given the sign vector $\sigma$, the compactor appends either $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$ to the output stream.
@@
 A deterministic compactor output the smaller of the two sets  $\{ x_i | \sigma_i = 1\}$ or  $\{ x_i | \sigma_i = -1\}$.
-Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $D_m n$
+Given an input of length $n$, the output has at most $n/2$ items, and the error of the output stream is bounded in absolute value by $nD_m$
 \end{lemma}
@@
 The total error is therefore $H n D_m \le O(log(n/m) n D_m)$. 
-Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $D_m = c/m$ we get that the error is at most $O(log(n/m) n D_m) \le \eps n$ for appropriate constants in the $O()$ term of $m_0$, as required.
+Setting $m \ge m_0 = O(c\log(\eps n/c)/\eps)$ and replacing $D_m = c/m$ we get that the error is at most $O(log(n/m) n D_m) \le \eps n$.
 Since we have $H = O(log(\eps n/c))$ compactors the overall space complexity is $O(c\log^2(\eps n/c)/\eps)$. 
@@
 Setting $m \ge m_0 = O(c^2\log^2(\eps^2 n/c^2)/\eps^2)$ and replacing $D_m = c/\sqrt{m}$. 
-We get that the error is at most $O(log(n/m) n D_m) \le \eps n$ for appropriate constants in the big-$O$ term of $m_0$, as required. 
+We get that the error is at most $O(log(n/m) n D_m) \le \eps n$. 
 Since we have $H = O(log(\eps^2 n/c^2))$ such compactors the overall space complexity is $O\left(c^2\log^3(\eps^2 n/c^2) /\eps^2\right)$. 
@@
 The resulting memory requirement $O(\log^2\log(n/\delta) c/\eps)$, as claimed.
-
 \end{proof}
 
+%\section{Signed sum of matrices}
+%%\begin{theorem}[Nikhil Bansal]\label{BansalInDaHouz}
+%\begin{theorem*}
+%For any set of matrices $X_1,...,X_n \in \R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $\sigma_i \in \{-1,1\}$ such that $||\sum_i \sigma_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
+%\end{theorem*}
+%\begin{proof}
+%First, recount Banaszczyk's theorem. 
+%Let $\mathcal K$ be a convex body in $\R^d$ such that $\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is Gaussian i.i.d.
+%Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
+%Then, there exist signs $s_i$ such that $\sum s_i x_i \in C \mathcal K$ for some universal constant $C$.
+%
+%To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
+%Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $10\sqrt{d_1 + d_2}$.
+%More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le 10\sqrt{d_1+d_2}\}$. 
+%Due to $\operatorname{stack}$ being linear $\mathcal K$ is convex. 
+%Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices.
+%Banaszczyk's theorem says that there exist signs $s_i$ such that $\sum s_i \operatorname{flatten}(X_i) \in C \mathcal K$.
+%In other words $\| \sum s_i X_i\| = \| \operatorname{stack}( \sum s_i \operatorname{flatten}(x_i x_i^T)) \| \le 10 C \sqrt{d}$. 
+%\end{proof}
+
 \end{document}

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
Corrects citation location

@@
 We provide two more related but independent results. 
-First, an exponential improvement of the widely used merge-and-reduce trick \cite{BENTLEY1980301} which gives improved streaming sketches for any low discrepancy problem.
+First, an exponential improvement of the widely used merge-and-reduce trick which gives improved streaming sketches for any low discrepancy problem.
 Second, an extremely simple deterministic algorithm for finding low discrepancy sequences (and therefore coresets) for any positive semi-definite kernel. 
@@
 This means the dependence on the problem parameters is still only polylogarithmic.
+The above improves on the well know merge-and-reduce tree construction by \cite{BENTLEY1980301}.
 

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
typos
Additive approx and eps-approx link to dicrepancy paper from 2017

@@
 \newcommand{\add}[1]{\textcolor{blue}{ADD: #1}}
-%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
 
@@
 The dependence they get is $\tilde O(d/\eps^2)$ ignoring logarithmic factors. 
+Additive approximation coresets are also studies in the $\eps$-approximation literature which is also related to the discrepancy of the problem \cite{DBLP:journals/corr/MustafaV17}.
 
@@
 This means the dependence on the problem parameters is still only polylogarithmic.
-The above improves on the well know merge-and-reduce tree construction by \cite{BENTLEY1980301}.
+The above improves on the well-known merge-and-reduce tree construction by \cite{BENTLEY1980301}.
+Moreover, it is quite likely that a uniform $\eps$-net for $\Q$ for the sake of minimization (ERM on the final sketch).
+See literature on weak coresets and concentration results based on doubling dimensions for Lipchitz functions. \todo{add citation}
 

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
Adding weak coresets and doubling dimension
Added future work comment

@@
 The above improves on the well-known merge-and-reduce tree construction by \cite{BENTLEY1980301}.
-Moreover, it is quite likely that a uniform $\eps$-net for $\Q$ for the sake of minimization (ERM on the final sketch).
-See literature on weak coresets and concentration results based on doubling dimensions for Lipchitz functions. \todo{add citation}
+Moreover, it is likely that a uniform $\eps$-net for $\Q$ is not required for the sake of minimization (ERM on the final sketch).
+See literature on weak coresets and (e.g.
+\cite{Feldman:2007:PKC:1247069.1247072}) concentration results based on doubling dimensions in classification/query space \cite{BSHOUTY2009323}.
+The refinement of the above results is left for future work.
 

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
ada

--- 2019-05-30 COLT_camera_ready/karninliberty19.tex
@@
 Throughout the manuscript, we assume a bijective mapping between $\F$ and $\Q$. 
-Specifically, $f \in \F$ if there exists $q \in \Q$ such that $f(x) = f(x,q)$ and vice versa. 
+Specifically, any function in $\F$ can be written as $f_q$ and has a unique $q \in \Q$ such that $f_q(x)=f(x,q)$. 
 In the context of machine learning, one should think about $f(x,q)$ as the loss associated with example $x$ and model parameters $q$.
@@
 
-\noindent The following statements upper bound streaming coreset complexities for functions. Surprisingly, these bounds are only poly-logarithmically larger than their offline counterparts.
+\noindent The following statements upper bound streaming coreset complexities for functions. We note that these bounds are only poly-logarithmically larger than their offline counterparts.
 

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
sqrt(d)/eps in abstract

--- 2019-05-30 COLT_camera_ready/karninliberty19.tex
@@
 As corollaries of the general technique we bound the discrepancy (and therefore coreset complexity) of logistic regression, sigmoid activation loss, matrix covariance, kernel density and any analytic function of the dot product or the squared distance.
-Our result resolves a long-standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
+Our results prove the existence of $\eps$-approximation $O(\sqrt{d}/\eps)$ sized coresets for the above problems. 
+This resolves the long-standing open problem regarding the coreset complexity of Gaussian kernel density estimation.  
 We provide two more related but independent results. 
@@
 Moreover, it is likely that a uniform $\eps$-net for $\Q$ is not required for the sake of minimization (ERM on the final sketch).
-See literature on weak coresets and (e.g.
-\cite{Feldman:2007:PKC:1247069.1247072}) concentration results based on doubling dimensions in classification/query space \cite{BSHOUTY2009323}.
+See literature on weak coresets (e.g.
+\cite{Feldman:2007:PKC:1247069.1247072}) and concentration results based on doubling dimensions in classification/query space \cite{BSHOUTY2009323}.
 The refinement of the above results is left for future work.

### 2019-05-30 COLT_camera_ready/karninliberty19.tex
asd

@@
 \end{proof}
+
+The following two corollaries apply to the Logistic function and sigmoid activation loss function. They are easy to obtain by noticing the coefficients of the functions' Taylor expansion.
 

### 2019-05-31 COLT_camera_ready/karninliberty19.tex
adding some references

@@
 Additive approximation coresets are also studies in the $\eps$-approximation literature which is also related to the discrepancy of the problem \cite{DBLP:journals/corr/MustafaV17}.
+In~\cite{braverman2016new}, some connections are drawn between additive and multiplicative guarantees by providing a method to use an additive guarantee along with sensitivity scores in order to provide a multiplicative guarantee\footnote{These methods might be combined with our results to obtain improved multiplicative guarantees, but this would not be a trivial result and we defer it to future research.}.
 
@@
 Quantile sketching falls into this framework since it corresponds to $f(x,q) = 1$ if $x>q$ and $0$ else.
+The techniques of the above Theorems could also be associated with~\cite{matousek1995approximations}, providing a merge-reduce framework for additive coresets.
 More details and the proof of correctness are given in Appendix ~\ref{app:sketch proof}.
 
-Recently, {\cite{DBLP:conf/focs/KarninLL16} provided an improved (optimal) streaming quantile coreset algorithm. 
-Generalizing the construction at  \cite{DBLP:conf/focs/KarninLL16} requires more work. 
-The main ideas are as follows. 
+Recently, \cite{DBLP:conf/focs/KarninLL16} provided an improved (optimal) streaming quantile coreset algorithm by improving the merge-reduce technique in a way tailored to the quantile problem.
+In the typical merge-reduce framework, the algorithm is based on finding an $\eps$-coreset on subsets of size dependent on $\eps$ rather than on $n$.
+The novelty of \cite{DBLP:conf/focs/KarninLL16} is in suggesting a way to use different values of $\eps$ for these local coreset constructions.
+This ends up providing a randomized algorithm with no dependence on $n$ and doubly logarithmic dependence on the failure probability.
+%
+%In high level, their novelty is using 
+Generalizing their construction requires more work and the main ideas are as follows. 
 We argued above that $\tilde F_{+}$ and $\tilde F_{-}$ are both good approximations for $F$. 
@@
 This allows us to use concentration results to bound the overall error.
-The main departure from \cite{DBLP:conf/focs/KarninLL16} is that $\tilde F_{\pm}$ has half the support of $F$ only in expectation.
+So far, analogous ideas where used in \cite{DBLP:conf/focs/KarninLL16};
+the main departure is that $\tilde F_{\pm}$ has half the support of $F$ only in expectation.
 
